### 2018-04-23 manuscript/case.tex
manuscript added

\section{Case Study}

\subsection{OVERVIEW Case 1: City Folding}

compare the distorted maps from various groups

\subsection{DETAIL Case 2: Look into Detail}

check the detail information of a group

### 2018-04-23 manuscript/data.tex
manuscript added

\section{Data}

Some pre-analysis result of the data

### 2018-04-23 manuscript/relatedwork.tex
manuscript added

\section{Related Work}

The related work is discussed around the related methods in map distortion, and the work analyzing facility accessbility....

\paragraph{Map Distrotion}

\paragraph{Facility Accessibility Analysis}

### 2018-04-23 manuscript/visualdesign.tex
manuscript added

\section{Demographics Driven Map Distortion Method}

### 2018-05-03 code/server/application.py
code init

@@ -1,0 +1,24 @@
+#!/usr/bin/env python
+#coding:utf-8
+
+from url import url 
+
+import tornado.web
+import os
+
+# import pymongo
+# from pymongo import MongoClient
+
+setting = dict(
+  # template_path=os.path.join(os.path.dirname(__file__),"template"),
+  static_path=os.path.join(os.path.dirname(__file__),"../"), #.. 上级目录，.当前目录
+  template_path=os.path.join(os.path.dirname(__file__), "./")
+)
+
+application = tornado.web.Application(
+  handlers=url,
+  debug=True,
+  **setting
+)
+
+

### 2018-05-03 code/server/handler/kdehandler.py

@@ -1,0 +1,123 @@
+
+import tornado.web
+from tornado.options import options
+
+import pymongo
+from pymongo import MongoClient
+
+import setting
+
+from PIL import Image
+import io
+import os.path
+
+import json
+
+import subprocess
+
+from scipy import stats
+import numpy as np
+from skimage import measure
+
+class KDEHandler(tornado.web.RequestHandler):
+	def post(self):
+		self.set_header('Access-Control-Allow-Origin', "*")
+		clusterNum = json.loads(self.get_argument('cluster'));
+		
+		print('clusterNum', clusterNum)
+
+		xmin=-6
+		xmax=6
+		ymin=-6
+		ymax=6
+		
+		m1,m2 = self.measure1(2000)
+		m3,m4 = self.measure(2000)
+
+		liDot1 = self.listZip(m1, m2)
+		liDot2 = self.listZip(m3, m4)
+
+		Z1 = self.kde(m1, m2)
+		Z2 = self.kde(m3, m4)
+
+		liDensity1 = list(Z1.ravel()) #self.kde(m1, m2)
+		liDensity2 = list(Z2.ravel()) #self.kde(m3, m4)
+		# list(np.rot90(Z).ravel());
+
+		mapContour1 = self.getContours(Z1)
+		mapContour2 = self.getContours(Z2)
+
+		liCluster = []
+		liCluster.append({
+			'dots': liDot1,
+			'densitys': liDensity1,
+			'mindensity': Z1.ravel().min(),
+			'maxdensity': Z1.ravel().max(),
+			'contours': mapContour1
+			})
+
+		liCluster.append({
+			'dots': liDot2,
+			'densitys': liDensity2,
+			'mindensity': Z2.ravel().min(),
+			'maxdensity': Z2.ravel().max(),
+			'contours': mapContour2
+			})
+
+		self.write({'clusters': liCluster, 'mm': [xmin, xmax, ymin, ymax]})
+
+	def listZip(self, m1, m2):
+		list1 = list(m1)
+		list2 = list(m2)
+		return list(zip(list1, list2))
+
+	def measure1(self, n):
+		m1 = np.random.normal(size=n)
+		m2 = np.random.normal(scale=0.5, size=n)
+		return 2 + m1-m2, -1 + (m1+m2)
+
+	def measure(self, n):
+	    m1 = np.random.normal(size=n)
+	    m2 = np.random.normal(scale=0.5, size=n)
[…]

### 2018-05-03 code/server/handler/pointhandler.py

@@ -1,0 +1,26 @@
+
+import tornado.web
+from tornado.options import options
+
+import pymongo
+from pymongo import MongoClient
+
+import setting
+
+from PIL import Image
+import io
+import os.path
+
+import json
+
+import subprocess
+
+class TestHandler(tornado.web.RequestHandler):
+    def get(self, word):
+        print('getsurvey handler', word);       
+        self.write('ok');
+
+
+class IndexHandler(tornado.web.RequestHandler):
+	def get(self):
+		self.render('index.html')

### 2018-05-03 code/server/setting.py

@@ -1,0 +1,5 @@
+from tornado.options import define,options
+
+define("port",default=30030,help="run on th given port",type=int)
+#define("db", default="trajlit", help="database", type=str)
+#define("title", default="Survey of trajectory visual analytics", help="the topic of literature, e.g. trajlit", type=str)

### 2018-05-03 code/server/url.py

@@ -1,0 +1,19 @@
+#!/usr/bin/env python
+#coding:utf-8
+
+import sys
+# from imp import reload
+# reload(sys)
+# sys.setdefaultencoding('utf-8')
+
+from handler.pointhandler import IndexHandler
+from handler.pointhandler import TestHandler
+
+from handler.kdehandler import KDEHandler
+
+url=[
+	(r'/', IndexHandler),
+    (r'/test/(\w+)', TestHandler),
+
+    # (r'/clusterKDE', KDEHandler),
+]

### 2018-05-04 manuscript/relatedwork.tex
manuscript updated

@@
 
-\paragraph{Map Distrotion}
+\textbf{Anonymous Movement Analysis} Introduce the classifical movement analysis focus.
+Data mining (Zheng Yu's work), Specially in the field of visual analytics, also most of work focus on the efficiency of the travel infrustions, (Wang, Lu, Zeng, Qu, Wu Yingcai).
 
-\paragraph{Facility Accessibility Analysis}
+\textbf{Social Related Analysis} In the GIS field, (Liu Yu), Soical Media (Chen, CaoNan)

### 2018-05-07 manuscript/data.tex

@@
 Some pre-analysis result of the data
+
+In the report (looking for some report), the penetration of mobile device is XXX, almost every XX people got a Mobile Phone in the urban.
+XX.
+As Figure~\ref{fig:data_over} shows, multiple social characteristics of a people is sampled, including income, education, etc.
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/data_over1}
+ \caption{Overview of Social Characteristics}
+ \label{fig:data_over}
+\end{figure}
+
+The coverage of the data in spatial and social aspects. The distribution of age is consistent to the traditional survey (Shenzhen Census?).... Figure~\ref{fig:data_stat} shows...
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/data_detail}
+ \caption{Statistics}
+ \label{fig:data_stat}
+\end{figure}

### 2018-05-07 manuscript/discussion.tex

\section{Discussion}

\textbf{Compatibility}

Compared to other static visual cuing, animation effect has better compatibility by not importing other markers.

\textbf{Mapping}

Kinetic effects is driven by data with what kind of mapping, linear, non-linear? relationship to perceptual driven, tuned by perception.

\textbf{Visual Tired/ Distracting the reading of other visual channel}

 Does it disturb the reading of original static charts?

 What we show in this work is to add kinetic effect all in, the extreme case of visual information enhancement. If applying to certain part of visual objects, it would for sure significantly reduce the visual distraction and facilitate the attention attraction.

\textbf{Interactive Enhancement / Adaptive Dynamic Control}

For sure the kinetic effects can be used in the interactive visual analytics system, as the cuing techniques after interactions, e.g., annotation, filtering, query, etc. For most of visual analytics, existing visual cuing is static and because of buried in rich visual encoding, it is usually hard to stand out. Kinetic effects can be considered as efficient attention attraction encoding.

Also, it also allows the users' manual control on playing/stopping kinetic effect, to call the enhancement of information on demand

Adaptive dynamic enhancement, e.g., sleep the kinetic effects ?

### 2018-05-07 manuscript/visualdesign.tex

@@
 \section{Demographics Driven Map Distortion Method}
+
+\subsection{Data-driven Profile Design}
+
+Figure~\ref{fig:design_profile} shows the legend for the user profile. Those design dimensions are driven by data. an intuitive perception of the social characteristics.
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/design_profile}
+ \caption{Design Profile}
+ \label{fig:design_profile}
+\end{figure}
+
+Various profiles are generated. Figure~\ref{fig:div_profile} shows some results.
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/design_div}
+ \caption{Diverse Profile}
+ \label{fig:div_profile}
+\end{figure}
+
+\subsection{Interactive Group Classification}
+
+Figure~\ref{fig:mds} is the MDS project of diversse users. Contour detected. Classification Updated. Automatic ensembling of diverse profiles.
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/mds}
+ \caption{Interactive Labelling and Classification}
+ \label{fig:mds}
+\end{figure}

### 2018-05-08 manuscript/data.tex
data part updated

--- 2018-04-23 manuscript/data.tex
@@
 
-Some pre-analysis result of the data
+The advent of mobile sensing techniques makes it possible to develop urban geography from social media source. Complement the infrequenly collect census. 
+The wide use of social media brings the benefit of high disaggregate in terms of space and time, which supports to reach a wide range of individuals as well as sampling the rare movement, such as the night-time activity.
+
+Via Wechat, a wide used social media in China, 25481 individual volunteers were reached and returned feedbacks during the releasing time period (June - October, 2016).
+As Figure~\ref{fig:data_over} illustrates, each individual hands in his or her personal characteristics from social, economic and deomgraphic aspects.
+For privacy issue, all detailed personal information are desensitized to categorical levels.
+Finally, XX variables are created, falling into eight domains.
+Those domains give a generalized depiction of the individual characteristics and serve as the ingredients for the analysis of urban dynamics over diverse people.
+At the same time, individual is asked to tag the moving tracks according to his or her willingness.
+Individuals are motivated by a credit system which retains the track contribution and rewards who in the top contribution list.
+Over the time period of collection, XXX trips are collected and XX trips per individual.
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/data_over}
+ \caption{Overview}
+ \label{fig:data_over}
+\end{figure}
+
+Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, a series of statistical analysis is performed to check whether it is rich enough to represent a wide range of human individuals in the city.
+
+\textit{Overview} As Figure~\ref{fig:data_stat} shows, age... As reported in evenly sampled, geolocation is ...
+\textit{Compared to Census} In the report (looking for some report), the penetration of mobile device is XXX, almost every XX people got a Mobile Phone in the urban.
+XX.
+multiple social characteristics of a people is sampled, including income, education, etc.
+age and income distribution follows the social architecture.
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/data_detail}
+ \caption{Statistical Overview of Social Characteristics}
+ \label{fig:data_stat}
+\end{figure}

### 2018-05-09 manuscript/data.tex
data writing updated

@@
 
-The advent of mobile sensing techniques makes it possible to develop urban geography from social media source. Complement the infrequenly collect census. 
-The wide use of social media brings the benefit of high disaggregate in terms of space and time, which supports to reach a wide range of individuals as well as sampling the rare movement, such as the night-time activity.
+The advent of mobile sensing techniques makes it possible to develop urban geography from social media source.
+Complement the conventional census, social media brings the benefit of larger sampling frequency and higher disaggregate in terms of space and time, which reaches a wide range of individuals as well as collects the movement in human inactive time, such as the mid-night.
 
-Via Wechat, a wide used social media in China, 25481 individual volunteers were reached and returned feedbacks during the releasing time period (June - October, 2016).
-As Figure~\ref{fig:data_over} illustrates, each individual hands in his or her personal characteristics from social, economic and deomgraphic aspects.
-For privacy issue, all detailed personal information are desensitized to categorical levels.
-Finally, XX variables are created, falling into eight domains.
+By Wechat, a widely used social media app we deployed the data collecting experiment in Shenzhen, one of the modernest metropolis in China.
+Figure~\ref{fig:app} shows the interfaces of the collecting app.
+Each individual hands in his or her personal characteristics from social, economic and deomgraphic aspects.
+For privacy issue, all detailed personal information are desensitized to categorical levels (Figure~\ref{fig:app}(b)).
+Also, individual is encouraged to upload trips (Figure~\ref{fig:app}(c)), including the information of start/end location and time, the traveling purpose and modes.
+A credit system is built up to retain the trip contribution of individuals and rewards those in the top contribution list (Figure~\ref{fig:app}(d)).
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/survey_app}
+ \caption{Collecting Interface: (a) welcome page; (b) personal characteristics collecting page; (c) trips collecting page; (d) credit system page}
+ \label{fig:app}
+\end{figure}
+
+Over the releasing time period from June to October in 2015, 25481 individules were reached and XXX trips are collected, XX trips per individual.
+Figure~\ref{fig:data_over} lists the XX variables, falling into 8 domains.
 Those domains give a generalized depiction of the individual characteristics and serve as the ingredients for the analysis of urban dynamics over diverse people.
-At the same time, individual is asked to tag the moving tracks according to his or her willingness.
-Individuals are motivated by a credit system which retains the track contribution and rewards who in the top contribution list.
-Over the time period of collection, XXX trips are collected and XX trips per individual.
+
+Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, a series of statistical analysis is performed to check whether it is rich enough to represent a wide range of human individuals in the city.
 
@@
  \includegraphics[width=\columnwidth]{pictures/data_over}
- \caption{Overview}
+ \caption{Profile of Individual: XX variables falling into 8 domains enriches the analysis of urban dynamics}
  \label{fig:data_over}
@@
 
-Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, a series of statistical analysis is performed to check whether it is rich enough to represent a wide range of human individuals in the city.
+According to the 2015 Annual Census Statistics report~\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5.
+Shenzhen is majority of young people.
 
-\textit{Overview} As Figure~\ref{fig:data_stat} shows, age... As reported in evenly sampled, geolocation is ...
+\textit{Overview} Figure~\ref{fig:data_stat} shows samples covering almost all ages and age between 18 to 45. The
+
 \textit{Compared to Census} In the report (looking for some report), the penetration of mobile device is XXX, almost every XX people got a Mobile Phone in the urban.

### 2018-05-10 manuscript/data.tex
data updated

@@
 
-By Wechat, a widely used social media app we deployed the data collecting experiment in Shenzhen, one of the modernest metropolis in China.
-Figure~\ref{fig:app} shows the interfaces of the collecting app.
+In this work, we performed the demographical survey in Shenzhen, which is one of the most modern metropolis in China.
+The experiment is deployed on Wechat, a widely used social media application.
+Figure~\ref{fig:app} shows the data collecting interfaces.
 Each individual hands in his or her personal characteristics from social, economic and deomgraphic aspects.
 For privacy issue, all detailed personal information are desensitized to categorical levels (Figure~\ref{fig:app}(b)).
-Also, individual is encouraged to upload trips (Figure~\ref{fig:app}(c)), including the information of start/end location and time, the traveling purpose and modes.
-A credit system is built up to retain the trip contribution of individuals and rewards those in the top contribution list (Figure~\ref{fig:app}(d)).
+Besides to those static features, each individual can upload dynamic traveling trips (Figure~\ref{fig:app}(c)).
+Each trip requires the information of start/end location and time, the traveling purpose and modes.
+To encourage the trip uploading, a credit system retains the contribution of individuals on trips and rewards those with the top credits (Figure~\ref{fig:app}(d)).
 
@@
 
-Over the releasing time period from June to October in 2015, 25481 individules were reached and XXX trips are collected, XX trips per individual.
+Over the releasing time period from June to October in 2015, 25481 individules (XX\% females and XX\% males)were reached and XXX trips are collected, XX trips per individual.
 Figure~\ref{fig:data_over} lists the XX variables, falling into 8 domains.
@@
 
-Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, a series of statistical analysis is performed to check whether it is rich enough to represent a wide range of human individuals in the city.
+Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, a series of preliminary statistics is performed to check whether it is rich enough to represent a wide range of human individuals in the city.
 
@@
 
+In the report (looking for some report), the penetration of mobile device is XXX, almost every XX people got a Mobile Phone in the urban.
+Figure~\ref{fig:data_age_edu} shows samples covering a wide range of all ages, dominately between 18 to 45.
 According to the 2015 Annual Census Statistics report~\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5.
-Shenzhen is majority of young people.
-
-\textit{Overview} Figure~\ref{fig:data_stat} shows samples covering almost all ages and age between 18 to 45. The
-
-\textit{Compared to Census} In the report (looking for some report), the penetration of mobile device is XXX, almost every XX people got a Mobile Phone in the urban.
-XX.
-multiple social characteristics of a people is sampled, including income, education, etc.
-age and income distribution follows the social architecture.
+The distribution aligns to the fact that Shenzhen is a city where the majority is young people.
+The education levels is diverse from low to high.
 
@@
  \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/data_detail}
+ \includegraphics[width=\columnwidth]{pictures/data1}
+ \caption{Evenly Distributed Age and Education: (a) age distribution; (b) education distribution}
+ \label{fig:data_age_edu}
+\end{figure}
+
+As Figure~\ref{fig:data_job_inc} shows, the job types of sampling individuals includes the workers, officers, bussinessmen, which is very diverse.
+The yearly income various from the range from low to high.
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/data2}
+ \caption{Diverse Job and Income Distribution: (a) job types; (b) income portion}
+ \label{fig:data_job_inc}
+\end{figure}
+
+Figure~\ref{fig:data_geometry} shows the statistics of spatial activity.
+The activity time distribution in traveling obeys the commen sense.
+Morning and late afternoon peaks are detected in the data.
+The house distribution reports that our data has higher dense sampling in Futian, Nanshan districts, because those two are the most developed districts in Shenzhen.
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/data3}
  \caption{Statistical Overview of Social Characteristics}
- \label{fig:data_stat}
+ \label{fig:data_geometry}
 \end{figure}

### 2018-05-11 manuscript/data.tex
data updated

@@
 
-Over the releasing time period from June to October in 2015, 25481 individules (XX\% females and XX\% males)were reached and XXX trips are collected, XX trips per individual.
+Over the releasing time period from June to October in 2015, 25481 individules (48\% females and 52\% males) were reached and XXX trips are collected.
+The majority of our 25481 volunteers contribute XXX trips.
 Figure~\ref{fig:data_over} lists the XX variables, falling into 8 domains.
@@
 
-Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, a series of preliminary statistics is performed to check whether it is rich enough to represent a wide range of human individuals in the city.
+Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of individuals in the city.
 
@@
 Figure~\ref{fig:data_age_edu} shows samples covering a wide range of all ages, dominately between 18 to 45.
+There is also a few records pertaining to individuals below the age of 18 or above 70.
+The distribution aligns to the fact that Shenzhen is a city where the majority is young people.
 According to the 2015 Annual Census Statistics report~\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5.
-The distribution aligns to the fact that Shenzhen is a city where the majority is young people.
-The education levels is diverse from low to high.
+Figure~\ref{fig:data_age_edu} gives the distribution of education levels, diverse from low to high.
 
@@
 
-Figure~\ref{fig:data_geometry} shows the statistics of spatial activity.
-The activity time distribution in traveling obeys the commen sense.
+Figure~\ref{fig:data_geometry} shows the statistics of spatial related activity.
+In Figure~\ref{fig:data_geometry}(a), ...The activity time distribution in traveling obeys the commen sense.
 Morning and late afternoon peaks are detected in the data.
-The house distribution reports that our data has higher dense sampling in Futian, Nanshan districts, because those two are the most developed districts in Shenzhen.
+Figure~\ref{fig:data_geometry}(b) shows the map of the origins and destinations spot by volunteers in Shenzhen.
+It shows that more trips uploaded by volunteers located in Futian and Nanshan districts, the city's heart part of than the surrounding outer areas.
+This is consistent to Batty's exposition of the focus of city networks and interaction patterns~\cite{batty2013new}.
+
+Trips are uploaded in a wide range of purpose in addition to home, work, but also includes XX entertainment, visiting, etc.
+The diverse purposes make it possible to characterize the flows across the city between different functional places.
 
@@
 \end{figure}
+
+While the subset can not fully represent the ground true of society awide, the distribution shows positive sign in even indication.
+We takes it as a step into the social-spatial dynamics exploration in the context of big social media data.
+% As a note, although it is a subset of all people with

### 2018-05-14 manuscript/data.tex
intro, data, related updated

@@
 
+Our case-study data is confined to a small proportion of Wechat users who opt to contribute their information and trips.
 Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of individuals in the city.
@@
 
-While the subset can not fully represent the ground true of society awide, the distribution shows positive sign in even indication.
-We takes it as a step into the social-spatial dynamics exploration in the context of big social media data.
+While there is unevitable bias inherent in fully representing the ground true of society awide, the distribution shows positive sign in even indication.
+
+We takes it as a step into the social-spatial dynamics exploration in the context of big social media data and align it with the avaliable of individual characteristics.
+We believe this work to be one of the nature steps into research of social understanding of the city.
 % As a note, although it is a subset of all people with

### 2018-05-14 manuscript/relatedwork.tex
intro, data, related updated

@@
 
-\textbf{Anonymous Movement Analysis} Introduce the classifical movement analysis focus.
+\textbf{Anonymous/Conventional Movement Analysis} Introduce the classifical movement analysis focus.
 Data mining (Zheng Yu's work), Specially in the field of visual analytics, also most of work focus on the efficiency of the travel infrustions, (Wang, Lu, Zeng, Qu, Wu Yingcai).
 
-\textbf{Social Related Analysis} In the GIS field, (Liu Yu), Soical Media (Chen, CaoNan)
+\textbf{Social Related Analysis} As the mass adaption of social medial serivces, such as Twitter, Facebook, ti has become an hot research area of ...
+The new and rich data as Twitter flowerish the research.
+...
+As social media data continues attracting the attention from research fields, such social science, there are lot of research performed around this topics.
+Most of work infer key characteristics from individuals using social media.
+
+In the GIS field, (Liu Yu), Soical Media (Chen, CaoNan)
+
+\cite{Longley2015}\cite{Paul2016_twitter} identifies and assess the biases inherent in social media usage in social research and evaluate the deployment of social media data in research applications.

### 2018-05-14 manuscript/visualdesign.tex
intro, data, related updated

@@
-\section{Demographics Driven Map Distortion Method}
+\section{Idea}
 
-\subsection{Data-driven Profile Design}
+Classification method, flow clustering method, Semantic representation.
+
+The key of our work is to align the analysis of urban dynamics with the available of individual characteristics.
+
+Problem to solve: 
+\begin{itemize}
+\item \textit{Groups of people}: multiple attributes, semantic understanding, loose attribute boundary
+\item \textit{Urban Dynamics of People Group}: where those people go and how they access the ... in a city. the patterns of behaviour classified by different social characteristics.  
+\end{itemize}
+
+\section{City-folding Visual Analytics}
+
+Semantic understanding of social characteristics.
+
+\subsection{Data-driven Visual Profile}
+
+to abstract to concrete and semantic understanding, to help users clues to do the classification.
+
+Face... Data-driven inforgraphics~\cite{}.
 
 Figure~\ref{fig:design_profile} shows the legend for the user profile. Those design dimensions are driven by data. an intuitive perception of the social characteristics.
+
+Considering the driven machinsm in two attributes: 
+\begin{itemize}
+\item \textit{Numerical}
+\item \textit{Categorical}
+\end{itemize}
 
@@
 
+Groups from demographics
+
 \begin{figure}[htb!]
@@
 \end{figure}
+
+\subsection{Spatial Visualization}
+
+The space visualization is embedded in 2.5D space.
+TAZ is used as the ....
+The height of space is put as the occurrence of visiting.
+For each group of people, we adjust the DB-Scan Algorithm in the context of TAZ.

### 2018-05-15 manuscript/relatedwork.tex
rw updated

@@
 
-\textbf{Anonymous/Conventional Movement Analysis} Introduce the classifical movement analysis focus.
-Data mining (Zheng Yu's work), Specially in the field of visual analytics, also most of work focus on the efficiency of the travel infrustions, (Wang, Lu, Zeng, Qu, Wu Yingcai).
+As the involvement of various data collected in urban context, the unpercedent opportunities give rise to the emerge of urban computing(zhengyu).
+It also triggers a broad use of visual analytics, to do data exploration and pattern interpretation, and visual learning~\cite{zheng2016visual}.
 
-\textbf{Social Related Analysis} As the mass adaption of social medial serivces, such as Twitter, Facebook, ti has become an hot research area of ...
+\textbf{Anonymous/Conventional Movement Analysis} (Introduce the conventional traffic analysis) Introduce the classifical movement analysis focus.
+Data mining (Zheng Yu's work), Specially in the field of visual analytics, also most of work focus on the efficiency of the travel infrustions, Such as traffic jam propagation~\cite{wang2013visual}, route travel behaviour~\cite{lu2015trajrank} (Wang, Lu, Zeng, Qu, Wu Yingcai.
+zeng wei).
+~\cite{andrienko2010discovering}.
+
+\textbf{Demographical Analysis} As the mass adaption of social medial serivces, such as Twitter, Facebook, ti has become an hot research area of ...
 The new and rich data as Twitter flowerish the research.
@@
 Most of work infer key characteristics from individuals using social media.
+Liu et al.~\cite{liu2015social} emphasize the geospatial big data as social sensing as an analogue of remote sensing data in social science research.
 
-In the GIS field, (Liu Yu), Soical Media (Chen, CaoNan)
+Social media...
+In the GIS field, (Liu Yu), Chen et al.~\cite{chen2016interactive} presents a visual analytics system to support the exploraiton of sparcely sampled trajectory from social media.
+Wu et al.
+also explore the ~\cite{wu2016telcovis}
 
+(Chen, CaoNan)
+
+Although real information is not enforced, a significant fractions of users tend to provide real names~\cite{peddinti2014internet}, which make it possible to breakdown the demographic characteristics of social media users.
+Luo et al.~\cite{luo2016explore} derive race, gender and age as three demographics dimensions to analyze its impact on the urban human mobility patterns.
 \cite{Longley2015}\cite{Paul2016_twitter} identifies and assess the biases inherent in social media usage in social research and evaluate the deployment of social media data in research applications.

### 2018-05-16 code/js/window1.js
new code

@@ -1,0 +1,242 @@
+function resetOptions(){
+		g_CurrentAttribteOptions = {}
+		g_CurrentShowFigureIndex = -1
+		for(var i = 0; i < g_liAttrName.length; i ++){
+			g_CurrentAttribteOptions[g_liAttrName[i]] = [];
+		}
+	}
+
+
+function updateOptions(dressBag, attrClicked){
+
+		var attr = dressBag['attr']
+		var option = dressBag['option']
+
+		var index = g_CurrentAttribteOptions[attr].indexOf(option)
+		if(attrClicked == true && index == -1){
+			g_CurrentAttribteOptions[attr].push(option)
+		}else if(attrClicked == false && index != -1){
+			g_CurrentAttribteOptions[attr].splice(index, 1);
+		}
+
+		console.log(" g_CurrentAttribteOptions ", g_CurrentAttribteOptions);
+
+		//update render
+		var multiple = false
+		// var liMultipleOptionAttribute = []
+		var mapMAttriOptions = {}
+		var liSingleOptionAttribute = []
+		for(var i = 0; i < g_liAttrName.length; i ++){
+			var attr = g_liAttrName[i]
+			if(g_CurrentAttribteOptions[attr].length > 1){
+				multiple = true
+				mapMAttriOptions[attr] = g_CurrentAttribteOptions[attr]
+			}else if(g_CurrentAttribteOptions[attr].length == 1){
+				liSingleOptionAttribute.push(attr);
+			}
+		}
+		g_Root.getItem({'name': 'button_checkmore'}).visible = multiple;
+
+		//create the Figure
+		for(var i = 0; i < g_liFigure.length; i ++){
+			for(var j = 0; j < g_liFigure[i].length; j ++){
+				g_liFigure[i][j].visible = false;
+				g_liFigure[i][j].remove();
+			}
+		}
+		g_liFigure = []
+
+		console.log(" SINGLE = ", liSingleOptionAttribute, ' MULTIPE = ', liMultipleOptionAttribute)
+
+		var liFigureOptions = []
+		var commonOption = [];
+
+		// console.log(" liCommoptonp before ", commonOption_t, commonOption_t.length, commonOption_t[0], liFigureOptions_t);
+
+		for(var i = 0; i < liSingleOptionAttribute.length; i ++){
+			var singleAttr = liSingleOptionAttribute[i]
+			var option = g_CurrentAttribteOptions[singleAttr];
[…]

### 2018-05-16 code/js/window3.js

@@ -1,0 +1,366 @@
+
+ function d3threeD( exports ) {
+        var DEGS_TO_RADS = Math.PI / 180, UNIT_SIZE = 100;
+        var DIGIT_0 = 48, DIGIT_9 = 57, COMMA = 44, SPACE = 32, PERIOD = 46, MINUS = 45;
+        exports.transformSVGPath = function transformSVGPath( pathStr ) {
+            var path = new THREE.ShapePath();
+            var idx = 1, len = pathStr.length, activeCmd,
+                    x = 0, y = 0, nx = 0, ny = 0, firstX = null, firstY = null,
+                    x1 = 0, x2 = 0, y1 = 0, y2 = 0,
+                    rx = 0, ry = 0, xar = 0, laf = 0, sf = 0, cx, cy;
+            function eatNum() {
+                var sidx, c, isFloat = false, s;
+                // eat delims
+                while ( idx < len ) {
+                    c = pathStr.charCodeAt( idx );
+                    if ( c !== COMMA && c !== SPACE ) break;
+                    idx ++;
+                }
+                if ( c === MINUS ) {
+                    sidx = idx ++;
+                } else {
+                    sidx = idx;
+                }
+                // eat number
+                while ( idx < len ) {
+                    c = pathStr.charCodeAt( idx );
+                    if ( DIGIT_0 <= c && c <= DIGIT_9 ) {
+                        idx ++;
+                        continue;
+                    } else if ( c === PERIOD ) {
+                        idx ++;
+                        isFloat = true;
+                        continue;
+                    }
+                    s = pathStr.substring( sidx, idx );
+                    return isFloat ? parseFloat( s ) : parseInt( s );
+                }
+                s = pathStr.substring( sidx );
+                return isFloat ? parseFloat( s ) : parseInt( s );
+            }
+            function nextIsNum() {
+                var c;
+                // do permanently eat any delims...
+                while ( idx < len ) {
+                    c = pathStr.charCodeAt( idx );
+                    if ( c !== COMMA && c !== SPACE ) break;
+                    idx ++;
+                }
+                c = pathStr.charCodeAt( idx );
+                return ( c === MINUS || ( DIGIT_0 <= c && c <= DIGIT_9 ) );
+            }
+            var canRepeat;
+            activeCmd = pathStr[ 0 ];
+            while ( idx <= len ) {
+                canRepeat = true;
+                switch ( activeCmd ) {
+                    // moveto commands, become lineto's if repeated
+                    case 'M':
+                        x = eatNum();
[…]

### 2018-05-16 code/server/handler/odhandler.py

@@ -1,0 +1,166 @@
+import tornado.web
+from tornado.options import options
+
+import pymongo
+from pymongo import MongoClient
+
+import setting
+
+from PIL import Image
+import io
+import os.path
+
+import json
+
+import subprocess
+
+
+class DataHandler(tornado.web.RequestHandler):
+    def post(self):
+        va = self.get_argument('value');
+        st = int(self.get_argument('st'));
+        et = int(self.get_argument('et'));
+        m = int(self.get_argument('m'));
+        userId = va.split(',')
+
+        ods = {}
+        sumtrips = 0
+        ods, sumtrips = self.get_trips(userId, st, et, m)
+        ods2 = dict(sorted(ods.items(), key=lambda e: e[1], reverse=True))
+        avg = sumtrips // len(ods)
+        print("avg", avg)
+
+        clustered = self.clusterDBSCAN(ods2, avg)
+        print('clusters', len(clustered))
+
+        stringnumber = '['
+        flag = 1
+        for key in ods2.keys():
+            if flag==1:
+                stringnumber += "{\"id\":"+str(key)+", \"n\":"+str(ods2.get(key))+"}"
+                flag = 2
+            else:
+                stringnumber += ",{\"id\":" + str(key) + ", \"n\":" + str(ods2.get(key)) + "}"
+        stringnumber += "]"
+
+        stringcluster = '['
+        flag = 1
+        for i in range(len(clustered)):
+            for j in range(len(clustered[i])):
+                if flag==1:
+                    stringcluster += '{\"id\":'+str(clustered[i][j])+", \"c\":"+str(i)+'}'
+                    flag = 2
+                else:
+                    stringcluster += ',{\"id\":'+str(clustered[i][j])+", \"c\":"+str(i)+'}'
+        stringcluster += ']'
+
+        result = {'sum': sumtrips, 'number': stringnumber, 'cluster': stringcluster}
+        #print(result);
+        self.set_header('Access-Control-Allow-Origin', '*');
+        self.write(result);
+
+    def get_trips(self, uidsinput, time1, time2, mode):
+
+        mongo_url = "192.168.153.129:27017"
+        client = pymongo.MongoClient(mongo_url);
+        db = client['wechat']
+
+        if mode == 1:
+            timeString = 'startminute'
+            bidString = 'sbid'
+        else:
+            timeString = 'endminute'
+            bidString = 'ebid'
+
+        collection = db["od"]
+        ods = {}
[…]

### 2018-05-16 code/server/url.py

@@ -8,12 +8,14 @@ import sys
 
 from handler.pointhandler import IndexHandler
 from handler.pointhandler import TestHandler
+from handler.odhandler import DataHandler
 
 from handler.kdehandler import KDEHandler
 
 url=[
 	(r'/', IndexHandler),
     (r'/test/(\w+)', TestHandler),
+    (r'/window3', DataHandler)
 
     # (r'/clusterKDE', KDEHandler),
 ]

### 2018-05-17 code/js/window1.js
connect window1,2,3, with error

@@ -1,169 +1,30 @@
-function resetOptions(){
-		g_CurrentAttribteOptions = {}
-		g_CurrentShowFigureIndex = -1
-		for(var i = 0; i < g_liAttrName.length; i ++){
-			g_CurrentAttribteOptions[g_liAttrName[i]] = [];
-		}
-	}
-
-
-function updateOptions(dressBag, attrClicked){
-
-		var attr = dressBag['attr']
-		var option = dressBag['option']
-
-		var index = g_CurrentAttribteOptions[attr].indexOf(option)
-		if(attrClicked == true && index == -1){
-			g_CurrentAttribteOptions[attr].push(option)
-		}else if(attrClicked == false && index != -1){
-			g_CurrentAttribteOptions[attr].splice(index, 1);
-		}
-
-		console.log(" g_CurrentAttribteOptions ", g_CurrentAttribteOptions);
-
-		//update render
-		var multiple = false
-		// var liMultipleOptionAttribute = []
-		var mapMAttriOptions = {}
-		var liSingleOptionAttribute = []
-		for(var i = 0; i < g_liAttrName.length; i ++){
-			var attr = g_liAttrName[i]
-			if(g_CurrentAttribteOptions[attr].length > 1){
-				multiple = true
-				mapMAttriOptions[attr] = g_CurrentAttribteOptions[attr]
-			}else if(g_CurrentAttribteOptions[attr].length == 1){
-				liSingleOptionAttribute.push(attr);
-			}
-		}
-		g_Root.getItem({'name': 'button_checkmore'}).visible = multiple;
-
-		//create the Figure
-		for(var i = 0; i < g_liFigure.length; i ++){
-			for(var j = 0; j < g_liFigure[i].length; j ++){
-				g_liFigure[i][j].visible = false;
-				g_liFigure[i][j].remove();
-			}
-		}
-		g_liFigure = []
-
-		console.log(" SINGLE = ", liSingleOptionAttribute, ' MULTIPE = ', liMultipleOptionAttribute)
-
-		var liFigureOptions = []
-		var commonOption = [];
-
-		// console.log(" liCommoptonp before ", commonOption_t, commonOption_t.length, commonOption_t[0], liFigureOptions_t);
-
-		for(var i = 0; i < liSingleOptionAttribute.length; i ++){
-			var singleAttr = liSingleOptionAttribute[i]
-			var option = g_CurrentAttribteOptions[singleAttr];
[…]

### 2018-05-17 code/js/window2.js

@@ -1,0 +1,80 @@
+function squareSelect(dataPortrait){
+         var clickTime = "";
+         var startLoc = [];
+         var endLoc = [];
+         var flag = "";
+	     var rect = svg.append("rect")
+	                   .attr("width", 0)
+	                   .attr("height", 0)
+	                   .style("fill", "rgba(22,22,22,0.3)")
+	                   .style("stroke", "#ccc")
+	                   .style("stroke-width", "2px")
+	                   .attr("id", "squareSelect");
+
+	          svg.on("mousedown", function(){
+	                 clickTime = (new Date()).getTime();
+	                 flag = true;
+	                 rect.attr("transform", "translate("+d3.event.layerX+","+d3.event.layerY+")");
+	                 startLoc = [d3.event.layerX, d3.event.layerY];
+	          });
+
+	          svg.on("mouseover", function(){
+                    if(d3.event.target.localName == 'svg' && flag==true ||d3.event.target.localName == "rect" && flag == true) {
+                             var width = d3.event.layerX - startLoc[0];
+                             var height = d3.event.layerY - startLoc[1];
+                             if (width < 0) {
+                                   rect.attr("transform", "translate(" + d3.event.layerX + "," + startLoc[1] + ")");
+                             }
+                             if (height < 0) {
+                                   rect.attr("transform", "translate(" + startLoc[0] + "," + d3.event.layerY + ")");
+                             }
+                             if (height < 0 && width < 0) {
+                                   rect.attr("transform", "translate(" + d3.event.layerX + "," + d3.event.layerY + ")");
+                             }
+                                   rect.attr("width", Math.abs(width)).attr("height", Math.abs(height));
+                    }
+	          });
+
+	          svg.on("mouseup", function(){
+                     if(flag == true){
+                             flag = false;
+                             endLoc = [d3.event.layerX, d3.event.layerY];
+                             console.log("end", endLoc);
+                             var leftTop = [];
+                             var rightBottom = []
+                             if(endLoc[0]>=startLoc[0]){
+                                     leftTop[0] = startLoc[0];
+                                     rightBottom[0] = endLoc[0];
+                             }else{
+                                     leftTop[0] = endLoc[0];
+                                     rightBottom[0] = startLoc[0];
+                             }
+
+                             if(endLoc[1]>=startLoc[1]){
+                                     leftTop[1] = startLoc[1];
+                                     rightBottom[1] = endLoc[1];
+                             }else{
[…]

### 2018-05-17 code/js/window3.js

@@ -1,366 +1,220 @@
-
- function d3threeD( exports ) {
-        var DEGS_TO_RADS = Math.PI / 180, UNIT_SIZE = 100;
-        var DIGIT_0 = 48, DIGIT_9 = 57, COMMA = 44, SPACE = 32, PERIOD = 46, MINUS = 45;
-        exports.transformSVGPath = function transformSVGPath( pathStr ) {
-            var path = new THREE.ShapePath();
-            var idx = 1, len = pathStr.length, activeCmd,
-                    x = 0, y = 0, nx = 0, ny = 0, firstX = null, firstY = null,
-                    x1 = 0, x2 = 0, y1 = 0, y2 = 0,
-                    rx = 0, ry = 0, xar = 0, laf = 0, sf = 0, cx, cy;
-            function eatNum() {
-                var sidx, c, isFloat = false, s;
-                // eat delims
-                while ( idx < len ) {
-                    c = pathStr.charCodeAt( idx );
-                    if ( c !== COMMA && c !== SPACE ) break;
-                    idx ++;
-                }
-                if ( c === MINUS ) {
-                    sidx = idx ++;
-                } else {
-                    sidx = idx;
-                }
-                // eat number
-                while ( idx < len ) {
-                    c = pathStr.charCodeAt( idx );
-                    if ( DIGIT_0 <= c && c <= DIGIT_9 ) {
-                        idx ++;
-                        continue;
-                    } else if ( c === PERIOD ) {
-                        idx ++;
-                        isFloat = true;
-                        continue;
-                    }
-                    s = pathStr.substring( sidx, idx );
-                    return isFloat ? parseFloat( s ) : parseInt( s );
-                }
-                s = pathStr.substring( sidx );
-                return isFloat ? parseFloat( s ) : parseInt( s );
-            }
-            function nextIsNum() {
-                var c;
-                // do permanently eat any delims...
-                while ( idx < len ) {
-                    c = pathStr.charCodeAt( idx );
-                    if ( c !== COMMA && c !== SPACE ) break;
-                    idx ++;
-                }
-                c = pathStr.charCodeAt( idx );
-                return ( c === MINUS || ( DIGIT_0 <= c && c <= DIGIT_9 ) );
-            }
-            var canRepeat;
-            activeCmd = pathStr[ 0 ];
-            while ( idx <= len ) {
-                canRepeat = true;
-                switch ( activeCmd ) {
-                    // moveto commands, become lineto's if repeated
-                    case 'M':
[…]

### 2018-05-17 code/js/window4.js

@@ -1,0 +1,367 @@
+
+ function d3threeD( exports ) {
+        var DEGS_TO_RADS = Math.PI / 180, UNIT_SIZE = 100;
+        var DIGIT_0 = 48, DIGIT_9 = 57, COMMA = 44, SPACE = 32, PERIOD = 46, MINUS = 45;
+        exports.transformSVGPath = function transformSVGPath( pathStr ) {
+            var path = new THREE.ShapePath();
+            var idx = 1, len = pathStr.length, activeCmd,
+                    x = 0, y = 0, nx = 0, ny = 0, firstX = null, firstY = null,
+                    x1 = 0, x2 = 0, y1 = 0, y2 = 0,
+                    rx = 0, ry = 0, xar = 0, laf = 0, sf = 0, cx, cy;
+            function eatNum() {
+                var sidx, c, isFloat = false, s;
+                // eat delims
+                while ( idx < len ) {
+                    c = pathStr.charCodeAt( idx );
+                    if ( c !== COMMA && c !== SPACE ) break;
+                    idx ++;
+                }
+                if ( c === MINUS ) {
+                    sidx = idx ++;
+                } else {
+                    sidx = idx;
+                }
+                // eat number
+                while ( idx < len ) {
+                    c = pathStr.charCodeAt( idx );
+                    if ( DIGIT_0 <= c && c <= DIGIT_9 ) {
+                        idx ++;
+                        continue;
+                    } else if ( c === PERIOD ) {
+                        idx ++;
+                        isFloat = true;
+                        continue;
+                    }
+                    s = pathStr.substring( sidx, idx );
+                    return isFloat ? parseFloat( s ) : parseInt( s );
+                }
+                s = pathStr.substring( sidx );
+                return isFloat ? parseFloat( s ) : parseInt( s );
+            }
+            function nextIsNum() {
+                var c;
+                // do permanently eat any delims...
+                while ( idx < len ) {
+                    c = pathStr.charCodeAt( idx );
+                    if ( c !== COMMA && c !== SPACE ) break;
+                    idx ++;
+                }
+                c = pathStr.charCodeAt( idx );
+                return ( c === MINUS || ( DIGIT_0 <= c && c <= DIGIT_9 ) );
+            }
+            var canRepeat;
+            activeCmd = pathStr[ 0 ];
+            while ( idx <= len ) {
+                canRepeat = true;
+                switch ( activeCmd ) {
+                    // moveto commands, become lineto's if repeated
+                    case 'M':
+                        x = eatNum();
[…]

### 2018-05-18 code/js/window3.js
bug fixed

@@ -1,6 +1,6 @@
 function clearCurrentFigures(){
 			setBasicPathsVisible(false);
-			var libasePaths = g_Root.getItems({'name': 'temp'});
+			var libasePaths = g_16Root.getItems({'name': 'temp'});
 			console.log(' pre page click! ', libasePaths.length);
 			for(var i = 0; i < libasePaths.length; i ++){
 				var path_temp = libasePaths[i];
@@ -16,15 +16,18 @@ function clearCurrentFigures(){
 
   function drawFigure(index, mapFeature, count){
 
-	   	var libasePaths = g_Root.getItems({'name': /^suser_base/});
+  		console.log(" [1] ")
+	   	var libasePaths = g_16Root.getItems({'name': /^suser_base/});
+		console.log(" [2] ", libasePaths.length)
 	   	libasePaths[index].visible = true
 	   	var pos = getBasePos(libasePaths[index]);
 	   	var boundaryBox = libasePaths[index].bounds;
 
 	   	console.log(" Boundary Box ", boundaryBox);
 
-	   	//gender
-	   	addGender(mapFeature[1], pos);
+	   	console.log(' mapFeature ', mapFeature, mapFeature[1]);
+	   //gender
+	   addGender(mapFeature[1], pos);
 
 	   //education
 	   addEdu(mapFeature[2], pos);
@@ -50,7 +53,7 @@ function clearCurrentFigures(){
 	   //count text
 	   addText(count, pos, boundaryBox);
 
-	   // var glassitem = g_Root.children[mapFeature['edu'] + '_glass']
+	   // var glassitem = g_16Root.children[mapFeature['edu'] + '_glass']
 	   // var glass_copy = glassitem.clone();
 	   // glass_copy.visible = true;
 	   // glass_copy.position = pos + new Point(SHIFTBAG['glass'][0], SHIFTBAG['glass'][1]);
@@ -58,7 +61,7 @@ function clearCurrentFigures(){
 
 
 	function setBasicPathsVisible(visible){
-		var libasePaths = g_Root.getItems({'name': /^suser_base/});
+		var libasePaths = g_16Root.getItems({'name': /^suser_base/});
 		for(var i = 0; i < libasePaths.length; i ++){
 			var basePath = libasePaths[i];
 			basePath.visible = visible;
@@ -67,11 +70,13 @@ function clearCurrentFigures(){
 
 
 	function addGender(gender, pos){
[…]

### 2018-05-19 code/js/window2.js
a copy. left done.

@@ -1,4 +1,4 @@
-function squareSelect(dataPortrait){
+function squareSelect(uids){
          var clickTime = "";
          var startLoc = [];
          var endLoc = [];
@@ -9,7 +9,7 @@ function squareSelect(dataPortrait){
 	                   .style("fill", "rgba(22,22,22,0.3)")
 	                   .style("stroke", "#ccc")
 	                   .style("stroke-width", "2px")
-	                   .attr("id", "squareSelect");
+	                   .attr("id", "idSquareSelect");
 
 	          svg.on("mousedown", function(){
 	                 clickTime = (new Date()).getTime();
@@ -39,7 +39,6 @@ function squareSelect(dataPortrait){
                      if(flag == true){
                              flag = false;
                              endLoc = [d3.event.layerX, d3.event.layerY];
-                             console.log("end", endLoc);
                              var leftTop = [];
                              var rightBottom = []
                              if(endLoc[0]>=startLoc[0]){
@@ -61,20 +60,19 @@ function squareSelect(dataPortrait){
                          d3.selectAll("#idPoint")
                             .attr("temp", function(d){
                                   if(xScale(d.x)<rightBottom[0] && xScale(d.x)>leftTop[0] && yScale(d.y)>leftTop[1] && yScale(d.y)<rightBottom[1]){
-                                              for(var i=0;i<uids.length;i++){
-                                                   if(uids[i]==d.uid){
-                                                         console.log("selected");
-                                                         if(d.attr.toString() in dataPortrait){
-                                                              dataPortraitFromW2[d.attr.toString()] = dataPortraitFromW2[d.attr.toString()]+1;
-                                                         }else{
-                                                              dataPortraitFromW2[d.attr.toString()] = 1;
-                                                         }
-                                                   }
-                                              }
+                                          if(d.attr.toString() in dataPortrait){
+                                                if(d.attr.toString() in dataPortraitFromW2){
+                                                      dataPortraitFromW2[d.attr.toString()] = dataPortraitFromW2[d.attr.toString()]+1;
+                                                }else{
+                                                      dataPortraitFromW2[d.attr.toString()] = 1;
+                                                }
+                                                d3.select(this).style("fill", "purple");
+                                          }
                                   }
                          });
-              rect.attr("width",0).attr("height",0);
+              //rect.attr("width",0).attr("height",0);
             }
-            drawWindow3(dataPortraitFromW2);
+            current = 2;
+            drawWindow3(dataPortraitFromW2, page);
         });
 }

### 2018-05-19 code/js/window3.js

@@ -1,7 +1,6 @@
 function clearCurrentFigures(){
 			setBasicPathsVisible(false);
 			var libasePaths = g_16Root.getItems({'name': 'temp'});
-			console.log(' pre page click! ', libasePaths.length);
 			for(var i = 0; i < libasePaths.length; i ++){
 				var path_temp = libasePaths[i];
 				path_temp.remove()
@@ -16,16 +15,17 @@ function clearCurrentFigures(){
 
   function drawFigure(index, mapFeature, count){
 
-  		console.log(" [1] ")
-	   	var libasePaths = g_16Root.getItems({'name': /^suser_base/});
-		console.log(" [2] ", libasePaths.length)
+  	    var libasePaths = g_16Root.getItems({'name': /^suser_base/});
+
 	   	libasePaths[index].visible = true
 	   	var pos = getBasePos(libasePaths[index]);
 	   	var boundaryBox = libasePaths[index].bounds;
 
-	   	console.log(" Boundary Box ", boundaryBox);
+	   	//console.log(' mapFeature ', mapFeature, mapFeature[1]);
 
-	   	console.log(' mapFeature ', mapFeature, mapFeature[1]);
+	   //job
+	   addJob(mapFeature[4], pos);
+
 	   //gender
 	   addGender(mapFeature[1], pos);
 
@@ -34,9 +34,6 @@ function clearCurrentFigures(){
 
 	   //age
 	   addAge(mapFeature[1], mapFeature[0], pos);
-
-	   //job
-	   addJob(mapFeature[4], pos);
 
 	   //income
 	   addIncome(mapFeature[3], pos);
@@ -53,10 +50,6 @@ function clearCurrentFigures(){
 	   //count text
 	   addText(count, pos, boundaryBox);
 
-	   // var glassitem = g_16Root.children[mapFeature['edu'] + '_glass']
-	   // var glass_copy = glassitem.clone();
-	   // glass_copy.visible = true;
-	   // glass_copy.position = pos + new Point(SHIFTBAG['glass'][0], SHIFTBAG['glass'][1]);
   }
 
 
@@ -70,146 +63,128 @@ function clearCurrentFigures(){
 
 
 	function addGender(gender, pos){
-		console.log(' error [1] ', 'gender_' + gender)
-	   	var hairitem = g_16Root.children['gender_' + gender]
+	   	var hairitem = g_16Root.children['gender_' + gender.toString()]
[…]

### 2018-05-20 manuscript/visualdesign.tex
abstract, title updated

@@
-\section{Idea}
-
-Classification method, flow clustering method, Semantic representation.
-
-The key of our work is to align the analysis of urban dynamics with the available of individual characteristics.
-
-Problem to solve: 
-\begin{itemize}
-\item \textit{Groups of people}: multiple attributes, semantic understanding, loose attribute boundary
-\item \textit{Urban Dynamics of People Group}: where those people go and how they access the ... in a city. the patterns of behaviour classified by different social characteristics.  
-\end{itemize}
-
 \section{City-folding Visual Analytics}
@@
 
+Glyph design is
+
 to abstract to concrete and semantic understanding, to help users clues to do the classification.
 
-Face... Data-driven inforgraphics~\cite{}.
+Face...
+Data-driven inforgraphics~\cite{}.
+Following the idea of Chernoff Face~\cite{1973}, we utilize that we better know the perceptual figures well before we use them.
+By designing different visual dimensions, knowned as a type of glyph, a graphical representation of people with specific social characteristics.
+Those visual profiles are intended for intutive visual understanding and clustering.
 

### 2018-05-21 manuscript/visualdesign.tex
method updated

--- 2018-05-07 manuscript/visualdesign.tex
@@
-\section{Demographics Driven Map Distortion Method}
+\section{City-folding Visual Analytics}
 
-\subsection{Data-driven Profile Design}
+Semantic understanding of social characteristics.
 
-Figure~\ref{fig:design_profile} shows the legend for the user profile. Those design dimensions are driven by data. an intuitive perception of the social characteristics.
+\subsection{Data-driven Profile Visualization}
+
+Glyph-based visualization~\cite{borgo2013glyph} is the form of visual design to compose multivaribles into a collection of unified visual symbols, known as glyph.
+Glyph is intended for quick understanding and aligned comparison.
+Among glyph design, Chernoff Face~\cite{chernoff1973use} represents data variabules by the different features of a cartoon face.
+Following the idea of Chernoff Face~\cite{chernoff1973use}, we design a type of glyph, a graphical representation of people with specific demographic characteristics.
+The idea behind using faces is that humans easily recognize faces and notice small changes without difficulty.
+Those visual profiles are intended for intutive visual understanding and clustering, to abstract to concrete and semantic understanding, to help users clues to target the interested individual groups effectively.
+
+Figure~\ref{fig:design_profile} shows the legend for the user profile.
+Those design dimensions are driven by data.The eight demographic dimensions are systematically designed into different visual symbols.
+Considering there are two types of variables, i.e., the numeric attributes and categorical attributes.
+By different composition, stimulus pattern which has the abstract deomgraphic measurement of individuals.
+
+\begin{itemize}
+\item \textbf{Gender} the gender is visually mapped to the hair style of the avatar. 
+\item \textbf{Age} age is implied by the decoration on the hair.
+For the elder above 70, the hair is dyed to gray.
+For the youth beneath 18, hair decoration for girls and boys are adapted to the hair style.
+\item \textbf{Education} The thickness of eye glasses is used to indicate the different levels in education.
+\item \textbf{Job} The clothes is designed to imply the job of the individual. There are 9 types of clothes.
+\item \textbf{Belongings} for house, car, residential license are considered as the belongings to the individual, so we design each of them as an add-on decoration to imply whether the individual has it or not.
+\item \textbf{Income} a money symbol is used to show the different income levels.
+\end{itemize}
 
@@
 
-Various profiles are generated. Figure~\ref{fig:div_profile} shows some results.
+With the visual mapping, the profiles varies from individual to individual.
+Figure~\ref{fig:div_profile} shows some examples.
+By concretizing the attributes which otherwise is too abstract to percept, users can scan and search for interesting target organically in figures.
 
@@
 
-\subsection{Interactive Group Classification}
+\subsection{T-SNE Projection}
 
-Figure~\ref{fig:mds} is the MDS project of diversse users. Contour detected. Classification Updated. Automatic ensembling of diverse profiles.
+Each individual is denoted as a vector with eight factors and projected as a dot into the 2D view by the T-SNE project~\cite{}. As 
+Figure~\ref{fig:mds} shows, the whole space of volunteers are plotted evenly in the 2D view, which idnicates the uniformly sampled. Cross-filter~\cite{} from
+
+Classification Updated. Automatic ensembling of diverse profiles.
+
+Groups from demographics
 
@@
 \end{figure}
+
+\subsection{2.5D Spatial Visualization}
+
+The space visualization is embedded in 2.5D space.
+TAZ is used as the ....
+The height of space is put as the occurrence of visiting.
+For each group of people, we adjust the DB-Scan Algorithm in the context of TAZ.
+
+Travel Purpose, Clustering, Small Multiple Comparison

### 2018-05-22 manuscript/visualdesign.tex
system design updated

@@
-\section{City-folding Visual Analytics}
+\section{System Design}
+
+This work we try to answer following questions:
+
+Problem to solve: 
+\begin{itemize}
+\item \textit{What flows of people with certain demographic characteristics}: multiple attributes, semantic understanding, loose attribute boundary
+\item \textit{What the Urban Dynamics of the Group}: where those people go and how they access the ...
+in a city.
+the patterns of behaviour classified by different social characteristics.
+Including travel purpose,
+\item \textit{Compare of moving patterns between different groups}: what the similar and difference between groups in their traveling behaviour
+\end{itemize}
+
+We derive the design considerations:
+
+\begin{itemize}
+\item \textbf{C1: semantic understanding of demographic cahracteristics}: since the concept of groups is vague to define directly quantitativily.
+The visual design needs to consider how to help end-users to pick desirable ones from the mass.
+\item \textbf{C2: }
+\end{itemize}
+
+Classification method, flow clustering method, Semantic representation.
+
+The key of our work is to align the analysis of urban dynamics with the available of individual characteristics.
 
@@
 
-\subsection{T-SNE Projection}
+\subsection{t-SNE Projection}
 
-Each individual is denoted as a vector with eight factors and projected as a dot into the 2D view by the T-SNE project~\cite{}. As 
-Figure~\ref{fig:mds} shows, the whole space of volunteers are plotted evenly in the 2D view, which idnicates the uniformly sampled. Cross-filter~\cite{} from
+Each individual is denoted as a vector with eight factors and projected as a dot into the 2D view via t-SNE project~\cite{maaten2008visualizing}, which well suits high-dimensional data for visualization in a low-dimensional space of two dimensions.
+As Figure~\ref{fig:tsne}(a)shows, all volunteers are embedded evenly in the 2D view, indicating the uniformly sampling over demographical space.
 
-Classification Updated. Automatic ensembling of diverse profiles.
-
-Groups from demographics
+Multiple views of abstract view, t-SNE proection and semantic data driven profile visualization are coordinated in a Cross-filter machinesm~\cite{Weaver2010}.
+It allows end-users to interactive drill-dowm into individuals with interested characteristics from multiple perspectives.
+Starting from the abstract criterion constraints, the scope of interest is narrowed down to individuals with(out) certian properties.
+And then further cross-filtering with semantically visual profiles, to check the combination of 8 characteristical variables.
+Figure~\ref{fig:tsne}(b) examplifies four groups of interest.
 
@@
  \includegraphics[width=\columnwidth]{pictures/mds}
- \caption{Interactive Labelling and Classification}
- \label{fig:mds}
+ \caption{t-SNE project with four groups of the interest}
+ \label{fig:tsne}
 \end{figure}
@@
 
-The space visualization is embedded in 2.5D space.
-TAZ is used as the ....
-The height of space is put as the occurrence of visiting.
-For each group of people, we adjust the DB-Scan Algorithm in the context of TAZ.
+Embedding multiple variables in the spatial map is a challenging problem.
+Distortion technique 2D spatial, such as the partial route embedding~\cite{sun2016embedding}.
+However, when it comes to the global visualization, the trade-off between occlusion-free and the spatial perception.
+Follow the idea of 2.5D space design~\cite{Tominski2012_stacking}, the space visualization is embedded in 2.5D space, which also can smoothly transited back to the conventional 2D view.
 
-Travel Purpose, Clustering, Small Multiple Comparison
+ Each TAZ is grown as a prism whose height encodes the occurrence of visiting.
+Brunch of TAZ with similar visiting pattern and purpose are grouped by an heuristic DB-Scan Algorithm in the context of TAZ.
+From a center TAZ, walk to neighbour TAZ to check whether aggregation or not.
+The aggregated TAZ brunch indicates the region visiting by the group of people in same purpose, which is often the popular traveling places.
+The TAZ brunch is visualized...
+
+ To compare the mobility patterns across different groups of people, a Small Multiple dock is used to reserve the ever explored interesting result.
+To simply the comparion over spatial distribution, the snapshot is rendered in the 2D space, which can be magnified to check for the details in the 2.5D space.
+
+ In this view, it supports end-users to direct manipulate the space, e.g., zooming, panning, etc. Also, detail information about the visiting can be checked by direct clicking on the TAZ.

### 2018-05-23 code/js/window1.js
left done, right doING.

@@ -6,7 +6,6 @@
 			var liOptionBar = childItem.getItems(
 				{'name': /^attr/});
 
-
 			for(var j = 0; j < liOptionBar.length; j ++){
 				var optionBar = liOptionBar[j]
 			    optionBar._AttrClick = true
@@ -75,7 +74,6 @@
                   inp[zu].splice(n,1);
               }
          }
-         console.log("inp set", inp);
          drawWindow2(inp, 1);
 	}
 

### 2018-05-23 code/js/window3.js

@@ -1,125 +1,257 @@
-function clearCurrentFigures(){
-			setBasicPathsVisible(false);
-			var libasePaths = g_16Root.getItems({'name': 'temp'});
+function clearCurrentFigures(m){
+			setSuserbaseVisible(false, m);
+			var temp = "temp"+m;
+			var libasePaths = g_16Root.getItems({'name': temp});
+			console.log(libasePaths.length);
 			for(var i = 0; i < libasePaths.length; i ++){
 				var path_temp = libasePaths[i];
 				path_temp.remove()
 			}
-			for(var i = 0; i < g_liText.length; i ++){
-				var path_temp = g_liText[i];
+			for(var i = 0; i < g_liText[m].length; i ++){
+				var path_temp = g_liText[m][i];
 				path_temp.remove()
 			}
-			g_liText = []
+			g_liText[m] = []
 		}
 
 
-  function drawFigure(index, mapFeature, count){
-
-  	    var libasePaths = g_16Root.getItems({'name': /^suser_base/});
-
-	   	libasePaths[index].visible = true
-	   	var pos = getBasePos(libasePaths[index]);
-	   	var boundaryBox = libasePaths[index].bounds;
-
-	   	//console.log(' mapFeature ', mapFeature, mapFeature[1]);
-
-	   //job
-	   addJob(mapFeature[4], pos);
-
-	   //gender
-	   addGender(mapFeature[1], pos);
-
-	   //education
-	   addEdu(mapFeature[2], pos);
-
-	   //age
-	   addAge(mapFeature[1], mapFeature[0], pos);
-
-	   //income
-	   addIncome(mapFeature[3], pos);
-
-	   //resident
-	   addResident(mapFeature[5], pos);
-
-	   //house
-	   addHouse(mapFeature[7], pos);
-
-	   //car
-	   addCar(mapFeature[6], pos);
-
-	   //count text
-	   addText(count, pos, boundaryBox);
-
-  }
-
-
-	function setBasicPathsVisible(visible){
-		var libasePaths = g_16Root.getItems({'name': /^suser_base/});
+	function setSuserbaseVisible(visible, mode){
+	    var libasePaths;
+	    if(mode==5){
+	         libasePaths = g_16Root.getItems({'name': /^suser_base/});
+	    }else if(mode==0){
+	         libasePaths = g_16Root.getItems({'name': /^suser_base_0/});
+	    }else if(mode==1){
[…]

### 2018-05-23 code/js/window4v2.js

@@ -1,3 +1,33 @@
+function initPurpose(item){
+
+  for(var j=1;j<11;j++){
+            var a = "p"+String(j);
+            var pBar = item.children[a];
+
+
+            pBar._AttrClick = true
+			pBar.strokeWidth = 4;
+			pBar.strokeColor = 'black';
+		    pBar.onClick = function(){
+					this._AttrClick = !this._AttrClick;
+					if(this._AttrClick){
+						this.strokeColor = 'black';
+						this.strokeWidth = 4;
+					}else{
+						this.strokeColor = null;
+						this.strokeWidth = 1;
+					}
+			}
+			pBar.onMouseEnter = function(){
+					this.strokeColor = 'black';
+		    }
+			pBar.onMouseLeave = function(){
+					if(this._AttrClick == false)
+						this.strokeColor = null;
+			}
+        }
+}
+
 
  function d3threeD( exports ) {
         var DEGS_TO_RADS = Math.PI / 180, UNIT_SIZE = 100;
@@ -203,20 +233,21 @@
         }
     }
 
-  function init() {
-
-        var container = document.getElementById( 'window3' );
+  function init41() {
+        container = document.getElementById( 'window41' );
+        if(container.childNodes.length!=0){
+            container.removeChild(container.childNodes[0]);
+        }
 
         raycaster = new THREE.Raycaster();
         //
         scene = new THREE.Scene();
         scene.background = new THREE.Color( 0x8b8b8b );
 
-        //
-        camera = new THREE.PerspectiveCamera( 50, window.innerWidth*0.65 / window.innerHeight, 0.1, 100 );
-        camera.position.set( 0, 18, 0 );
-        //camera.position.set(8.278324114488553, 23.715105536749885, 5.334970045945842);
-        camera.up.set(0, 0.3, -0.3);
+        console.log(window.innerWidth, window.innerHeight);
+        camera = new THREE.OrthographicCamera( window.innerWidth*0.19/-260, window.innerWidth*0.19/260, window.innerHeight*0.3/260, window.innerHeight*0.3/-260, 1, 100 );
+        camera.lookAt(new THREE.Vector3(0,0,0));
+        camera.position.set(0,10,0);
 
         //
         var group = new THREE.Group();
@@ -226,32 +257,22 @@
         var directionalLight = new THREE.DirectionalLight( 0xffffff, 0.6 );
         directionalLight.position.set( 0.75, 0.75, 1.0 ).normalize();
[…]

### 2018-05-23 code/server/handler/hwhandler.py

@@ -1,0 +1,142 @@
+import tornado.web
+from tornado.options import options
+
+import pymongo
+from pymongo import MongoClient
+
+import setting
+
+from PIL import Image
+import io
+import os.path
+
+import json
+
+import subprocess
+
+
+class HWHandler(tornado.web.RequestHandler):
+    def post(self):
+        va = self.get_argument('value')
+        userId = va.split(',')
+
+        ods41 = {}
+        ods42 = {}
+        ods41, ods42 = self.getCount(userId)
+
+        max = 0;
+        for key in ods41.keys():
+            temp = ods41.get(key)
+            if(temp>max):
+                max = temp
+        for key2 in ods42.keys():
+            temp2 = ods42.get(key2)
+            if(temp2>max):
+                max = temp2
+
+        stringnumber41 = '['
+        flag = 1
+        for key3 in ods41.keys():
+            if flag==1:
+                stringnumber41 += "{\"id\":"+str(key3)+", \"n\":"+str(ods41.get(key3))+"}"
+                flag = 2
+            else:
+                stringnumber41 += ",{\"id\":" + str(key3) + ", \"n\":" + str(ods41.get(key3)) + "}"
+        stringnumber41 += "]"
+
+        stringnumber42 = '['
+        flag = 1
+        for key4 in ods42.keys():
+            if flag == 1:
+                stringnumber42 += "{\"id\":" + str(key4) + ", \"n\":" + str(ods42.get(key4)) + "}"
+                flag = 2
+            else:
+                stringnumber42 += ",{\"id\":" + str(key4) + ", \"n\":" + str(ods42.get(key4)) + "}"
+        stringnumber42 += "]"
+
+        result = {'r1': stringnumber41, 'r2': stringnumber42, 'max': max}
+        #print(result);
+        self.set_header('Access-Control-Allow-Origin', '*')
+        self.write(result)
+
+    def getCount(self, uidsinput):
+
+        mongo_url = "192.168.153.139:27017"
+        client = pymongo.MongoClient(mongo_url);
+        db = client['wechat']
+        collection = db["userbid"]
+
+        ods1 = {}
+        ods2 = {}
+        for j in range(len(uidsinput)):
+            cursor = collection.find({"uid": uidsinput[j]})
+
+            for item in cursor:
+                h = item['homebid']
+                if (h in ods1):
+                    temp = ods1.get(h)
+                    ods1[h] = temp + 1
+                else:
+                    ods1[h] = 1
+
+                w = item['companybid']
[…]

### 2018-05-23 code/server/handler/odhandler.py

@@ -15,62 +15,38 @@ import json
 import subprocess
 
 
-class DataHandler(tornado.web.RequestHandler):
+class ChartHandler(tornado.web.RequestHandler):
     def post(self):
         va = self.get_argument('value');
         st = int(self.get_argument('st'));
         et = int(self.get_argument('et'));
-        m = int(self.get_argument('m'));
+        ebid = int(self.get_argument('ebid'));
         userId = va.split(',')
 
         ods = {}
         sumtrips = 0
-        ods, sumtrips = self.get_trips(userId, st, et, m)
-        ods2 = dict(sorted(ods.items(), key=lambda e: e[1], reverse=True))
-        avg = sumtrips // len(ods)
-        print("avg", avg)
-
-        clustered = self.clusterDBSCAN(ods2, avg)
-        print('clusters', len(clustered))
+        ods, sumtrips = self.getpurpose(userId, st, et, ebid)
 
         stringnumber = '['
         flag = 1
-        for key in ods2.keys():
+        for key in ods.keys():
             if flag==1:
-                stringnumber += "{\"id\":"+str(key)+", \"n\":"+str(ods2.get(key))+"}"
+                stringnumber += "{\"x\":"+str(key)+", \"y\":"+str(ods.get(key)*100//sumtrips)+"}"
                 flag = 2
             else:
-                stringnumber += ",{\"id\":" + str(key) + ", \"n\":" + str(ods2.get(key)) + "}"
+                stringnumber += ",{\"x\":" + str(key) + ", \"y\":" + str(ods.get(key)*100//sumtrips) + "}"
         stringnumber += "]"
 
-        stringcluster = '['
-        flag = 1
-        for i in range(len(clustered)):
-            for j in range(len(clustered[i])):
-                if flag==1:
-                    stringcluster += '{\"id\":'+str(clustered[i][j])+", \"c\":"+str(i)+'}'
-                    flag = 2
-                else:
-                    stringcluster += ',{\"id\":'+str(clustered[i][j])+", \"c\":"+str(i)+'}'
-        stringcluster += ']'
-
-        result = {'sum': sumtrips, 'number': stringnumber, 'cluster': stringcluster}
+        result = {'number': stringnumber}
         #print(result);
         self.set_header('Access-Control-Allow-Origin', '*');
         self.write(result);
 
-    def get_trips(self, uidsinput, time1, time2, mode):
[…]

### 2018-05-23 code/server/url.py

@@ -9,13 +9,24 @@ import sys
 from handler.pointhandler import IndexHandler
 from handler.pointhandler import TestHandler
 from handler.odhandler import DataHandler
+from handler.odhandler import ChartHandler
+from handler.odhandler import PurposeHandler
+from handler.odhandler import PClusterHandler
+from handler.hwhandler import HWHandler
+from handler.hwhandler import ActHandler
 
 from handler.kdehandler import KDEHandler
 
 url=[
 	(r'/', IndexHandler),
     (r'/test/(\w+)', TestHandler),
-    (r'/window3', DataHandler)
+    (r'/window5', DataHandler),
+    (r'/window4', HWHandler),
+    (r'/window43', ActHandler),
+    (r'/chart', ChartHandler),
+    (r'/purpose', PurposeHandler),
+    (r'/pCluster', PClusterHandler),
+
 
     # (r'/clusterKDE', KDEHandler),
 ]

### 2018-05-25 manuscript/visualdesign.tex
abs, intro, updated

@@
 
-This work we try to answer following questions:
+This work we try to answer a couple of questions:
 
@@
 The visual design needs to consider how to help end-users to pick desirable ones from the mass.
-\item \textbf{C2: }
+\item \textbf{C2: multivariate comparison in the constraint of spatial space}: 
 \end{itemize}
@@
 
-The key of our work is to align the analysis of urban dynamics with the available of individual characteristics.
+The key of our work is to align the analysis of urban dynamics with the available of demographic characteristics.
 

### 2018-05-25 code/js/window1.js

@@ -9,25 +9,33 @@
 			for(var j = 0; j < liOptionBar.length; j ++){
 				var optionBar = liOptionBar[j]
 			    optionBar._AttrClick = true
-				optionBar.strokeWidth = 4;
-				optionBar.strokeColor = 'blue';
+				optionBar.strokeWidth = 1;
+				optionBar.opacity = 1.
+				// optionBar.strokeColor = 'blue';
 				optionBar.onClick = function(){
 					this._AttrClick = !this._AttrClick;
 					if(this._AttrClick){
-						this.strokeColor = 'blue';
-						this.strokeWidth = 4;
+						this.opacity = 1.;
+						// this.strokeColor = 'blue';
+						this.strokeWidth = 1;
 					}else{
+						this.opacity = 0.1;
 						this.strokeColor = null;
-						this.strokeWidth = 2;
+						// this.strokeWidth = 2;
 					}
                     get8dDataset(this._name, this._AttrClick);
 				}
 				optionBar.onMouseEnter = function(){
-					this.strokeColor = 'blue';
+					this.opacity = 1.;
+					this.strokeColor = 'gray';
+					this.strokeWidth = 0.5
 				}
 				optionBar.onMouseLeave = function(){
-					if(this._AttrClick == false)
-						this.strokeColor = null;
+
+					this.strokeColor = null;
+					// this.strokeWidth = 0.5
+					// if(this._AttrClick == false)
+						// this.strokeColor = null;
 				}
 			}
 		}

### 2018-05-27 manuscript/visualdesign.tex
abstract done

@@
 
-This work we try to answer a couple of questions:
+The system design is task-driven. Before diving into the design of system, we introduce  the couple of tasks the system works for.
 
-Problem to solve: 
 \begin{itemize}
-\item \textit{What flows of people with certain demographic characteristics}: multiple attributes, semantic understanding, loose attribute boundary
-\item \textit{What the Urban Dynamics of the Group}: where those people go and how they access the ...
+\item \textit{Identify the group of people with specific individual characteristics (T1)}: multiple attributes, semantic understanding, loose attribute boundary
+\item \textit{Explore the mobility patterns of a group (T2)}: where those people go and how they access the ...
 in a city.
-the patterns of behaviour classified by different social characteristics.
-Including travel purpose,
-\item \textit{Compare of moving patterns between different groups}: what the similar and difference between groups in their traveling behaviour
+the patterns of behaviour classified by different social characteristics, including travel demands.
+\item \textit{Compare mobility patterns among multiple groups (T3)}: what the similar and difference between groups in their traveling behaviour
 \end{itemize}
 
-We derive the design considerations:
+Based on tasks, we derive the design considerations:
 
 \begin{itemize}
-\item \textbf{C1: semantic understanding of demographic cahracteristics}: since the concept of groups is vague to define directly quantitativily.
+\item \textit{C1: multivarible filter of individual characteristics}: Cross filter...
+\textbf{C3: referrable transpotation}: TAZ
+\item \textit{C2: intuitive understanding/combination understanding of individual characteristics}: since the concept of groups is vague to define directly quantitativily.
 The visual design needs to consider how to help end-users to pick desirable ones from the mass.
-\item \textbf{C2: multivariate comparison in the constraint of spatial space}: 
+\item \textit{C3: conventional travel analysis}: TAZ based
+\item \textit{C4: multivariate analysis of mobility patterns in the constraint of spatial space}: the analysis of mobility patterns include multivariables, including the conventional spatial and temporal dimensions, as well as travel demands, frequency, etc.
+\item \textit{C5: knowledgable, not too fractional findings}
+\item \textit{C6: easy comparison}: 
 \end{itemize}

### 2018-05-28 manuscript/relatedwork.tex
related work 1st draft

--- 2018-05-04 manuscript/relatedwork.tex
@@
 
-The related work is discussed around the related methods in map distortion, and the work analyzing facility accessbility....
+The related work is expanded around the visual analytics of spatial patterns in the context of urban.
+In the past decades, the power of visual analytics in exploring spatial-temporal data has been regcognized and well developped.
+Andrienko et al.~\cite{andrienko2013visual} summarise the spatio-temporal data to spatial, temporal and thematic components.
+Most of them focus on the analysis of anonymous movement patterns.
+The presense of social media makes it possible to embed the spatial analysis with semnatic explanation, but most of them emphasizing thematic information of moving.
+In this work, we aim to continue to narrow the gap between mobility patterns and individuals' charecteristic features.
 
-\textbf{Anonymous Movement Analysis} Introduce the classifical movement analysis focus.
-Data mining (Zheng Yu's work), Specially in the field of visual analytics, also most of work focus on the efficiency of the travel infrustions, (Wang, Lu, Zeng, Qu, Wu Yingcai).
+\textbf{Anonymous Movement Analysis}
 
-\textbf{Social Related Analysis} In the GIS field, (Liu Yu), Soical Media (Chen, CaoNan)
+ With the development of location-acquistion techniques, massive spatial trajectories are generated, which represent the mobility of various moving objects.
+Many techniques have been proposed to process, mining trajectory~\cite{Zheng2015_trajectory}.
+In the field of visualization and visual analytic, spatial visualizations are specifically designed for the time, locations spatial-temporal information and other properties in the traffic data~\cite{chen2015survey}.
+A large number of visual analytics tools and applications cover situation-aware exploration, pattern discovery and traffic situation monitoring.
+Wang et al~\cite{wang2013visual} extract the traffic jam propagation graph extraction to reveal underlying data patterns.
+Guo et al.~\cite{guo2011tripvista} and Zeng et al.~\cite{zeng2013visualizing} et al.
+construct geographical regions and visually aggregate the in-between movements as flows.
+To discover the route travel patterns, Lu et al.~\cite{lu2015trajrank} propose TrajRank to explore the route travel behaviour based on ranking.
+For multiple routes, Liu et al.~\cite{liu2011_routediversity} study the route diversity between locations and Lu et al.~\cite{Lu2017_multipleroute} explore the route choice behaviour among multiple routes.
+
+\textbf{Geo-tagged Social Media Data Analysis}
+
+As the prevence of social medial serivces, social media data with geo-tags are collected to track people's movements in daily lifes.
+As an analogue of remote sensing data in social science research, the geospatial big data has been proposed as social sensing ~\cite{liu2015social}.
+Hence, analyzing movement information along with rich text has become a hot research area in recent years.
+Those works infer thematic information from the semantic texts.
+Cao et al.~\cite{cao2012whisper} propose \textit{Whisper} for tracing the pathways of tweets on a spatial hierarchical layouts, to investigate how information flow among multiple places.
+Krueger et al.~\cite{krueger2014visual} used GPS and location-based service data to support the analysis of movement behaviors.
+Chen et al.~\cite{chen2016interactive} present a visual analytics system to support the exploraiton of sparcely sampled trajectory from social media.
+Some other researches tend to infer real information, such as names, gender, etc~\cite{peddinti2014internet}, to break down the demographic characteristics of social media users.
+Luo et al.~\cite{luo2016explore} derive race, gender and age as three demographics dimensions to analyze its impact on the urban human mobility patterns.
+Since real information is not enforced in social media, wrong infering is inevitable.
+Longley et al.~\cite{Longley2015}~\cite{Paul2016_twitter} identifies and assess the biases inherent in social media usage in social research and evaluate the deployment of social media data in research applications.
+
+Different from anonymous movement analysis, in this work, we focus on investigating the how the mobility patterns varies to individual characteristics.
+We perform a census experiment via Social Media to collect the real information from volunteers, to get rid of indirect data inferring.

### 2018-05-29 manuscript/data.tex
data

@@
-\section{Data}
+\section{Online Census}
 
 The advent of mobile sensing techniques makes it possible to develop urban geography from social media source.
-Complement the conventional census, social media brings the benefit of larger sampling frequency and higher disaggregate in terms of space and time, which reaches a wide range of individuals as well as collects the movement in human inactive time, such as the mid-night.
+Complementary to the conventional census, social media brings the benefit of larger sampling frequency and higher disaggregate in terms of space and time.
+It is possible to reach a wide range of individuals and collect the movement in human inactive time, such as the mid-night.
 
-In this work, we performed the demographical survey in Shenzhen, which is one of the most modern metropolis in China.
+In this work, we perform the census survey in Shenzhen, which is one of the most modern metropolis in China.
 The experiment is deployed on Wechat, a widely used social media application.
@@
 Each individual hands in his or her personal characteristics from social, economic and deomgraphic aspects.
-For privacy issue, all detailed personal information are desensitized to categorical levels (Figure~\ref{fig:app}(b)).
-Besides to those static features, each individual can upload dynamic traveling trips (Figure~\ref{fig:app}(c)).
+For privacy issue, all detailed personal information are desensitized to categorical levels (Figure~\ref{fig:app}(a)).
+Besides to those static features, each individual can upload dynamic traveling trips (Figure~\ref{fig:app}(b)).
 Each trip requires the information of start/end location and time, the traveling purpose and modes.
-To encourage the trip uploading, a credit system retains the contribution of individuals on trips and rewards those with the top credits (Figure~\ref{fig:app}(d)).
+To encourage the trip uploading, a credit system retains the contribution of individuals on trips and rewards those with the top credits (Figure~\ref{fig:app}(c)).
 
@@
  \includegraphics[width=\columnwidth]{pictures/survey_app}
- \caption{Collecting Interface: (a) welcome page; (b) personal characteristics collecting page; (c) trips collecting page; (d) credit system page}
+ \caption{Census Interface: (a) personal characteristics collecting page; (b) trips collecting page; (c) credit system page}
  \label{fig:app}
@@
 
-Over the releasing time period from June to October in 2015, 25481 individules (48\% females and 52\% males) were reached and XXX trips are collected.
-The majority of our 25481 volunteers contribute XXX trips.
-Figure~\ref{fig:data_over} lists the XX variables, falling into 8 domains.
-Those domains give a generalized depiction of the individual characteristics and serve as the ingredients for the analysis of urban dynamics over diverse people.
+Figure~\ref{fig:data_over} lists the 8 domains, which give a generalized description of the individual characteristics.
+The profile will serve as the ingredients for the analysis of mobility patterns over diverse individuals.
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/data_over}
+ \caption{Profile of Individual: 8 domains about individual characteristics enrich the analysis of mobility patterns}
+ \label{fig:data_over}
+\end{figure}
+
+\subsection{Basic Statistics of Data}
+
+Over the releasing time period from \m{June to October} in 2015, 25481 individules (48\% females and 52\% males) were reached and \m{XXX} trips are collected.
+The majority of our 25481 volunteers contribute \m{XXX} trips.
 
@@
 
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/data_over}
- \caption{Profile of Individual: XX variables falling into 8 domains enriches the analysis of urban dynamics}
- \label{fig:data_over}
-\end{figure}
-
-In the report (looking for some report), the penetration of mobile device is XXX, almost every XX people got a Mobile Phone in the urban.
+In the report (looking for some report), the penetration of mobile device is \m{XXX}, almost every XX people got a Mobile Phone in the urban.
 Figure~\ref{fig:data_age_edu} shows samples covering a wide range of all ages, dominately between 18 to 45.

### 2018-05-29 manuscript/relatedwork.tex
intro...
data

@@
 
-The related work is expanded around the visual analytics of spatial patterns in the context of urban.
-In the past decades, the power of visual analytics in exploring spatial-temporal data has been regcognized and well developped.
-Andrienko et al.~\cite{andrienko2013visual} summarise the spatio-temporal data to spatial, temporal and thematic components.
-Most of them focus on the analysis of anonymous movement patterns.
-The presense of social media makes it possible to embed the spatial analysis with semnatic explanation, but most of them emphasizing thematic information of moving.
-In this work, we aim to continue to narrow the gap between mobility patterns and individuals' charecteristic features.
+This work concerns to the research topic of spatial data visual analytics.
+Spatio-temporal data has three components, i.e., spatial, temporal and thematic~\cite{andrienko2013visual}.
+Lots of related work focus on the spatio-temporal analysis in movement data, in the absence of thematic information.
+The presense of geo-tagged social media data flourishes the exploration of thematic information along with movement.
+By analyzing the texts, those work explain what drive the moving activities or what is resulted from.
+This work continues the thematic research in movement data, but focus more on individual charecteristics.
+Landed by a census experiment, this work is able to analyze the profile information directly, to get rid of indirect data inferred from social media data as other related work do.
 
-\textbf{Anonymous Movement Analysis}
+\textbf{Movement Data Analysis}
 
- With the development of location-acquistion techniques, massive spatial trajectories are generated, which represent the mobility of various moving objects.
+ With the development of location-acquistion techniques, massive spatial trajectories are collected, to keep track of the trajectories of various moving objects.
 Many techniques have been proposed to process, mining trajectory~\cite{Zheng2015_trajectory}.
-In the field of visualization and visual analytic, spatial visualizations are specifically designed for the time, locations spatial-temporal information and other properties in the traffic data~\cite{chen2015survey}.
+In the field of visualization and visual analytic, spatial visualizations are specifically designed for the time, locations, spatial-temporal information and other properties in the traffic data~\cite{chen2015survey}.
 A large number of visual analytics tools and applications cover situation-aware exploration, pattern discovery and traffic situation monitoring.
@@
 Longley et al.~\cite{Longley2015}~\cite{Paul2016_twitter} identifies and assess the biases inherent in social media usage in social research and evaluate the deployment of social media data in research applications.
-
-Different from anonymous movement analysis, in this work, we focus on investigating the how the mobility patterns varies to individual characteristics.
-We perform a census experiment via Social Media to collect the real information from volunteers, to get rid of indirect data inferring.

### 2018-05-30 manuscript/data.tex
data new fig!

@@
 
-Over the releasing time period from \m{June to October} in 2015, 25481 individules (48\% females and 52\% males) were reached and \m{XXX} trips are collected.
-The majority of our 25481 volunteers contribute \m{XXX} trips.
+Over the releasing time period from \m{2016-11 to 2018-01}, 25481 individules (48\% females and 52\% males) were reached and \m{229155} trips are collected.
+The majority of our 25481 volunteers contribute \m{9} trips averagly.
 
@@
 
-In the report (looking for some report), the penetration of mobile device is \m{XXX}, almost every XX people got a Mobile Phone in the urban.
-Figure~\ref{fig:data_age_edu} shows samples covering a wide range of all ages, dominately between 18 to 45.
+Figure~\ref{fig:data_age_edu} gives the distribution of age and education over the population.
+It shows that samples cover a wide range of all ages, dominately between 18 to 45.
 There is also a few records pertaining to individuals below the age of 18 or above 70.
-The distribution aligns to the fact that Shenzhen is a city where the majority is young people.
-According to the 2015 Annual Census Statistics report~\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5.
-Figure~\ref{fig:data_age_edu} gives the distribution of education levels, diverse from low to high.
+The distribution follows the fact that Shenzhen is a city where the majority is young people.
+According to the 2015 Annual Census Statistics report\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5.
+Figure~\ref{fig:data_age_edu} gives the distribution of education levels, ranging from low to high.
+The technical college and university dominates the education at the 61\% occupancy rate.
+
+% In the report (looking for some report), the penetration of mobile device is \m{XXX}, almost every XX people got a Mobile Phone in the urban.
 

### 2018-05-30 manuscript/data.tex
data done

@@
 It is possible to reach a wide range of individuals and collect the movement in human inactive time, such as the mid-night.
-
-In this work, we perform the census survey in Shenzhen, which is one of the most modern metropolis in China.
-The experiment is deployed on Wechat, a widely used social media application.
-Figure~\ref{fig:app} shows the data collecting interfaces.
-Each individual hands in his or her personal characteristics from social, economic and deomgraphic aspects.
-For privacy issue, all detailed personal information are desensitized to categorical levels (Figure~\ref{fig:app}(a)).
-Besides to those static features, each individual can upload dynamic traveling trips (Figure~\ref{fig:app}(b)).
-Each trip requires the information of start/end location and time, the traveling purpose and modes.
-To encourage the trip uploading, a credit system retains the contribution of individuals on trips and rewards those with the top credits (Figure~\ref{fig:app}(c)).
 
@@
 
-Figure~\ref{fig:data_over} lists the 8 domains, which give a generalized description of the individual characteristics.
+In this work, we perform the census survey in Shenzhen, which is one of the most modern metropolis in China.
+The experiment is deployed on Wechat, a widely used social media application.
+Figure~\ref{fig:app} shows the data collecting interfaces.
+Each individual hands in his or her personal characteristics.
+For privacy issue, all detailed personal information are desensitized to categorical levels (Figure~\ref{fig:app}(a)).
+
+\textbf{Individual Characteristics} Figure~\ref{fig:data_over} lists the \textit{eight domains}, including social, economic and deomgraphic aspects, to give a generalized description of the individual characteristics.
 The profile will serve as the ingredients for the analysis of mobility patterns over diverse individuals.
@@
  \includegraphics[width=\columnwidth]{pictures/data_over}
- \caption{Profile of Individual: 8 domains about individual characteristics enrich the analysis of mobility patterns}
+ \caption{Profile of Individual: eight individual characteristics enrich the analysis of mobility patterns}
  \label{fig:data_over}
@@
 
+\textbf{Traveling Trips} Besides to those individual characteristics, each individual can upload dynamic traveling trips (Figure~\ref{fig:app}(b)).
+Each trip requires the information of \textit{start/end location}, \textit{start/end time}, \textit{traveling purpose}.
+
+To encourage the trip uploading, a credit system retains the contribution of individuals on trips and rewards the volunteers with the top credits (Figure~\ref{fig:app}(c)).
+
 \subsection{Basic Statistics of Data}
 
-Over the releasing time period from \m{2016-11 to 2018-01}, 25481 individules (48\% females and 52\% males) were reached and \m{229155} trips are collected.
-The majority of our 25481 volunteers contribute \m{9} trips averagly.
+Over the releasing time period from \m{2016-11 to 2018-01}, 21435 individules (48\% females and 52\% males) were reached and \m{229155} trips are collected.
+The majority of our 25481 volunteers contribute \m{11} trips averagly.
 
@@
  \includegraphics[width=\columnwidth]{pictures/data1}
- \caption{Evenly Distributed Age and Education: (a) age distribution; (b) education distribution}
+ \caption{Age and Education Distribution: (a) age; (b) education}
  \label{fig:data_age_edu}
@@
 
-As Figure~\ref{fig:data_job_inc} shows, the job types of sampling individuals includes the workers, officers, bussinessmen, which is very diverse.
-The yearly income various from the range from low to high.
+Figure~\ref{fig:data_job_inc}(a) shows the job types of sampled individuals, who are servants, workers, officers, bussinessmen.
+The covering of jobs is pretty wide.
+Figure~\ref{fig:data_job_inc}(b) gives the radar diagram of the annual pay.
+The majority get paid below 200 000.
+Some individuals with higher salary are also reached in our census.
 
@@
  \includegraphics[width=\columnwidth]{pictures/data2}
- \caption{Diverse Job and Income Distribution: (a) job types; (b) income portion}
+ \caption{Job and Income Distribution: (a) job; (b) income}
  \label{fig:data_job_inc}
@@
 
-Figure~\ref{fig:data_geometry} shows the statistics of spatial related activity.
-In Figure~\ref{fig:data_geometry}(a), ...The activity time distribution in traveling obeys the commen sense.
-Morning and late afternoon peaks are detected in the data.
-Figure~\ref{fig:data_geometry}(b) shows the map of the origins and destinations spot by volunteers in Shenzhen.
-It shows that more trips uploaded by volunteers located in Futian and Nanshan districts, the city's heart part of than the surrounding outer areas.
+Figure~\ref{fig:data_geometry} shows the basic statistics related to trips.
+In Figure~\ref{fig:data_geometry}(a), the active traveling time (here, we take the start time as the representative of active time) follows the common sense of urban life.
+There are obvious morning and late afternoon peaks.
+Figure~\ref{fig:data_geometry}(b) gives the counting of different traveling purposes.
+95\% trips are tagged with traveling purpose in the data.
+33\% are going home and 37\% are going to work.
+Besides this kind of routine traveling, there are also substantial trips such as going shopping, going hospital, etc.
+Figure~\ref{fig:data_geometry}(c) shows the spatial distribution of the origins and destinations spot.
+It is found that more trips uploaded by volunteers located in Futian and Nanshan districts, the city's heart part of than the surrounding outer areas.
 This is consistent to Batty's exposition of the focus of city networks and interaction patterns~\cite{batty2013new}.
 
-Trips are uploaded in a wide range of purpose in addition to home, work, but also includes XX entertainment, visiting, etc.
+% Trips are uploaded in a wide range of purpose in addition to home, work, but also includes XX entertainment, visiting, etc.
 The diverse purposes make it possible to characterize the flows across the city between different functional places.
@@
  \includegraphics[width=\columnwidth]{pictures/data3}
- \caption{Statistical Overview of Social Characteristics}
+ \caption{Statistics of Trips: (a) start time of trips; (b) purpose of trips; (c) distribution of origins/destinations }
  \label{fig:data_geometry}
@@
 
-While there is unevitable bias inherent in fully representing the ground true of society awide, the distribution shows positive sign in even indication.
-
-We takes it as a step into the social-spatial dynamics exploration in the context of big social media data and align it with the avaliable of individual characteristics.
-We believe this work to be one of the nature steps into research of social understanding of the city.
+Because there is always unevitable bias inherent in fully representing the ground true of society awide, the prelimeary statistical analysis shows positive sign of a relatively even sampling of the population.
 % As a note, although it is a subset of all people with

### 2018-05-30 manuscript/visualdesign.tex
teaser

--- 2018-05-22 manuscript/visualdesign.tex
@@
-\section{System Design}
+\section{Visual Design}
 
-This work we try to answer following questions:
+The design of system is driven by tasks, to align the analysis of mobility patterns with individual characteristics characteristics.
+Before diving into the design of system, we introduce the couple of specifical tasks the system intended for.
 
-Problem to solve: 
 \begin{itemize}
-\item \textit{What flows of people with certain demographic characteristics}: multiple attributes, semantic understanding, loose attribute boundary
-\item \textit{What the Urban Dynamics of the Group}: where those people go and how they access the ...
-in a city.
-the patterns of behaviour classified by different social characteristics.
-Including travel purpose,
-\item \textit{Compare of moving patterns between different groups}: what the similar and difference between groups in their traveling behaviour
+\item \textit{Task 1: Identify the group with specific individual characteristics}: to get groups of people with common or close attributes, to explore the correlation among individual characteristics.
+\item \textit{Task 2: Explore the mobility patterns of a group}: to explore where, how and why an interested group go in city. 
+\item \textit{Task 3: Compare mobility patterns among multiple groups}: to know the similarities and differences between different groups in their mobility patterns, to investigate the relationship between movement and individual characteristics.
 \end{itemize}
 
-We derive the design considerations:
+\subsection{Design Considerations}
+
+With these three tasks, we derive following design considerations:
 
 \begin{itemize}
-\item \textbf{C1: semantic understanding of demographic cahracteristics}: since the concept of groups is vague to define directly quantitativily.
-The visual design needs to consider how to help end-users to pick desirable ones from the mass.
-\item \textbf{C2: }
+\item \textit{Effective multivarible cross-filter for individual characteristics (C1)}: there are eight domains to describe an individual.
+The system is supposed to provide a straright-forward way for easy filtering by the eight criteria.
+\item \textit{Good overview of the multivarible individuals (C2)}: following the visual analytics manta by Shneiderman~\cite{RN459}, it is very important to provide a good overview of all the individuals then the users know where to explore.
+\item \textit{Intuitive perception of an individual as an organic complex (C3)}: the system should make use of users' daily life experience in knowing people to provide intuitive visualization, instead of the lifeless representation by number.
+The visual design needs to help end-users to pick desirable ones from the mass.
+\item \textit{Compact visualization of mobility patterns in the constraint of spatial space (C4)}: the analysis of mobility patterns include multivariables, including the conventional spatial and temporal dimensions, as well as other dimensions, e.g., travel demands, frequency, etc.
+The system should handle a compact layout to make the correlation between spatial and abstract information easily.
+\item \textit{Flexible interactions to explore the mobility patterns within one group or between groups (C5)}: since the system needs to support the comparison among groups, \textit{Task 3} \m{TO BE WRITTEN...}
 \end{itemize}
 
-Classification method, flow clustering method, Semantic representation.
+% Classification method, flow clustering method, Semantic representation.
 
-The key of our work is to align the analysis of urban dynamics with the available of individual characteristics.
-
-Semantic understanding of social characteristics.
+With those design considerations, we develop a visual analytics system as Figure~\ref{fig:teaser} shows.
+It composes of individual panel to explore and identify groups (\textit{Task 1}) and spatial panel to explore and compare the mobility pattern (\textit{Task 2 and 3}).
+% Semantic understanding of social characteristics.
 

### 2018-05-30 manuscript/visualdesign.tex
profile added

@@
 Following the idea of Chernoff Face~\cite{chernoff1973use}, we design a type of glyph, a graphical representation of people with specific demographic characteristics.
-The idea behind using faces is that humans easily recognize faces and notice small changes without difficulty.
+The idea behind using faces is that humans easily recognize faces and notice small changes without difficulty (\textit{C3}).
 Those visual profiles are intended for intutive visual understanding and clustering, to abstract to concrete and semantic understanding, to help users clues to target the interested individual groups effectively.
@@
 With the visual mapping, the profiles varies from individual to individual.
-Figure~\ref{fig:div_profile} shows some examples.
 By concretizing the attributes which otherwise is too abstract to percept, users can scan and search for interesting target organically in figures.
+For example, Figure~\ref{fig:div_example} lists the top profiles filtered by jobs, in descending order.
+Textual number beneath the profile is the number of individual with same characteristics.
+It is found that the majority of workmen earn low and have no residential license.
+For the officers, all of them have residential licensemost and most of them has house.
+Some of retired people are in old age.
+Most of managers are at undergraduates, even graduates.
+
+% \begin{figure}[htb!]
+%  \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+%  \includegraphics[width=\columnwidth]{pictures/design_div}
+%  \caption{Diverse Profile}
+%  \label{fig:div_profile}
+% \end{figure}
 
@@
  \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/design_div}
- \caption{Diverse Profile}
- \label{fig:div_profile}
+ \includegraphics[width=\columnwidth]{pictures/design_example}
+ \caption{Top filtered profiles categoriesd job}
+ \label{fig:div_example}
 \end{figure}

### 2018-05-31 manuscript/visualdesign.tex
figure done

@@
 The visual design needs to help end-users to pick desirable ones from the mass.
-\item \textit{Compact visualization of mobility patterns in the constraint of spatial space (C4)}: the analysis of mobility patterns include multivariables, including the conventional spatial and temporal dimensions, as well as other dimensions, e.g., travel demands, frequency, etc.
-The system should handle a compact layout to make the correlation between spatial and abstract information easily.
-\item \textit{Flexible interactions to explore the mobility patterns within one group or between groups (C5)}: since the system needs to support the comparison among groups, \textit{Task 3} \m{TO BE WRITTEN...}
+\item \textit{Compact visualization of mobility patterns in the constraint of spatial space (C4)}: the analysis of mobility patterns not only includes the conventional spatial and temporal dimensions, but also other abstract dimensions, e.g., travel purpose, visiting frequency, etc.
+The system should handle a compact layout to support the easy correlation between spatial and abstract information.
+\item \textit{Flexible interactions to explore the mobility patterns either within one group or between groups (C5)}: to support the comparison among groups, \textit{Task 3}, the system should maintains flexbile interactions which allows the end-users to explore freely.
 \end{itemize}
@@
 It composes of individual panel to explore and identify groups (\textit{Task 1}) and spatial panel to explore and compare the mobility pattern (\textit{Task 2 and 3}).
+\m{EXPAND...}
 % Semantic understanding of social characteristics.
@@
 Among glyph design, Chernoff Face~\cite{chernoff1973use} represents data variabules by the different features of a cartoon face.
-Following the idea of Chernoff Face~\cite{chernoff1973use}, we design a type of glyph, a graphical representation of people with specific demographic characteristics.
+Following the idea of Chernoff Face, we design a type of glyph, a graphical representation of people with specific individual characteristics.
 The idea behind using faces is that humans easily recognize faces and notice small changes without difficulty (\textit{C3}).
-Those visual profiles are intended for intutive visual understanding and clustering, to abstract to concrete and semantic understanding, to help users clues to target the interested individual groups effectively.
+Those visual profiles are intended for intutive visual understanding, from abstract to concrete and semantic understanding, to support users to target the interested individual groups effectively.
 
 Figure~\ref{fig:design_profile} shows the legend for the user profile.
-Those design dimensions are driven by data.The eight demographic dimensions are systematically designed into different visual symbols.
-Considering there are two types of variables, i.e., the numeric attributes and categorical attributes.
-By different composition, stimulus pattern which has the abstract deomgraphic measurement of individuals.
+The eight domains are encoded by visual symbols and organically organized in a human figure.
+There are bascially three types of variables to drive the figure, i.e., the numeric, categorical and boolean ones.
+For numeric attributes such as income and education levels, visual symbol keeps consistent design but with changing visual variation, such as size, thickness.
+For the categorical attributes such as job, visual symbols are designed seperately for better semantic meaning.
+For the boolean attribute like car, house, a symbol is designed to indicate its existence.
+With this consideration, the eight domains are designed as following:
+
+% For numeric attributes.
+
+% By different composition, stimulus pattern which has the abstract deomgraphic measurement of individuals.
 
@@
 For the elder above 70, the hair is dyed to gray.
-For the youth beneath 18, hair decoration for girls and boys are adapted to the hair style.
+For the youth beneath 18, a hair decoration is adapted for the different hair styles of girls and boys.
 \item \textbf{Education} The thickness of eye glasses is used to indicate the different levels in education.
 \item \textbf{Job} The clothes is designed to imply the job of the individual. There are 9 types of clothes.
-\item \textbf{Belongings} for house, car, residential license are considered as the belongings to the individual, so we design each of them as an add-on decoration to imply whether the individual has it or not.
-\item \textbf{Income} a money symbol is used to show the different income levels.
+\item \textbf{Belongings} for real estate, car, residential license are considered as the belongings to the individual, so we design each of them as an add-on decoration to imply whether the individual has it or not.
+\item \textbf{Income} a money symbol is used to represent the income, whose size encodes the income level. The more money an individual earns, the larger the symbol is.
 \end{itemize}
@@
  \includegraphics[width=\columnwidth]{pictures/design_profile}
- \caption{Design Profile}
+ \caption{Design Profile: the eight characteritical domains are encoded and organized in an organic human figure.}
  \label{fig:design_profile}
@@
 
-With the visual mapping, the profiles varies from individual to individual.
-By concretizing the attributes which otherwise is too abstract to percept, users can scan and search for interesting target organically in figures.
-For example, Figure~\ref{fig:div_example} lists the top profiles filtered by jobs, in descending order.
-Textual number beneath the profile is the number of individual with same characteristics.
-It is found that the majority of workmen earn low and have no residential license.
-For the officers, all of them have residential licensemost and most of them has house.
-Some of retired people are in old age.
+With the visual mapping, the profile varies from individual to individual.
+By concretizing the attributes which otherwise is too abstract to percept, users can scan and search for interesting target effectively.
+Figure~\ref{fig:div_example} lists the figures with the top 10 largest population in some job.
+The textual number beneath indicates the population.
+It is found that the majority of workmen earn low salary and most of them have no residential license.
+On the contrary, for the officers, all of them have residential license and most of them has house.
+Some of the retired people are in old age.
 Most of managers are at undergraduates, even graduates.
@@
  \includegraphics[width=\columnwidth]{pictures/design_example}
- \caption{Top filtered profiles categoriesd job}
+ \caption{Representative figures with the top 10 largest population in four jobs}
  \label{fig:div_example}

### 2018-05-31 manuscript/visualdesign.tex
teaser updated

@@
 It composes of individual panel to explore and identify groups (\textit{Task 1}) and spatial panel to explore and compare the mobility pattern (\textit{Task 2 and 3}).
-\m{EXPAND...}
+\m{EXPAND..., it gives an infographical overview of the data.
+Encode information but also allow users to set multiple criteria (\textit{C1}).
+Support users to slice the data by different domains.}
 % Semantic understanding of social characteristics.
@@
 For the boolean attribute like car, house, a symbol is designed to indicate its existence.
-With this consideration, the eight domains are designed as following:
+With this consideration, the domains are designed as following:
 
@@
 
-\subsection{t-SNE Projection}
+\subsection{t-SNE Projection of Individuals}
 
-Each individual is denoted as a vector with eight factors and projected as a dot into the 2D view via t-SNE project~\cite{maaten2008visualizing}, which well suits high-dimensional data for visualization in a low-dimensional space of two dimensions.
+% \begin{figure}[htb!]
+%  \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+%  \includegraphics[width=0.7\columnwidth]{pictures/data_overview}
+%  \caption{Overview of Multiple Variables}
+%  \label{fig:figoverview}
+% \end{figure}
+
+In our case, each individual can be denoted as a vector $x_i$ with eight factors, and we get high dimensional data set $X={x_1, x_2, ..., x_n}$.
+The dimensionality reduction techniques are to preserve the local structure of high dimensional data in low dimensional space, which are efficient approaches to provide a good overview of the multivarible individuals.
+We adapt t-SNE project~\cite{maaten2008visualizing} to project $X$ as two-dimensional dots $Y={y_1, y_2, ..., y_n}$.
+
+t-SNE computes the conditional probabilities to represent the similarity based on the distance between high dimenional datapoints.
+The conditional probability $p_{j\mid i}$ between $x_j$ and $x_i$ is given by:
+
+\begin{equation}
+p_{j\mid i} = \frac{exp({\left \| x_i - x_j \right \|}^2/2\alpha_i ^{2})}{\sum _{k\neq i}exp({\left \| x_i - x_k \right \|}^2/2\alpha_i ^{2})}
+\end{equation}
+
+ which well suits high-dimensional data for visualization in a low-dimensional space of two dimensions (\textit{C2}).
+
 As Figure~\ref{fig:tsne}(a)shows, all volunteers are embedded evenly in the 2D view, indicating the uniformly sampling over demographical space.
@@
 Multiple views of abstract view, t-SNE proection and semantic data driven profile visualization are coordinated in a Cross-filter machinesm~\cite{Weaver2010}.
-It allows end-users to interactive drill-dowm into individuals with interested characteristics from multiple perspectives.
+It allows end-users to interactive drill-down into individuals with interested characteristics from multiple perspectives.
 Starting from the abstract criterion constraints, the scope of interest is narrowed down to individuals with(out) certian properties.

### 2018-05-31 manuscript/case12.tex
case, 2.5D...

\section{Case Study}
We apply our method with our data. Two cases are derived to demonstrate the powerness of our method. We believe this work to be one of the nature steps into research of social understanding of the city.

\subsection{Case 1: City Folding}

\begin{figure}
\centering
\subfigure[Top aristocracy.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case111.eps}}}\hspace{5pt}
\subfigure[The underclass.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case112.eps}}}\hspace{5pt}
\subfigure[New rich.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case113.eps}}}\hspace{5pt}
\subfigure[Antizen.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case114.eps}}}\hspace{5pt}
\caption{XXX of different groups.}
\label{case11}
\end{figure}

\begin{figure}
\centering
\subfigure[Top aristocracy.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case121.eps}}}\hspace{5pt}
\subfigure[The underclass.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case122.eps}}}\hspace{5pt}
\subfigure[New rich.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case123.eps}}}\hspace{5pt}
\subfigure[Antizen.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case124.eps}}}\hspace{5pt}
\caption{Distributions of home and working space of different groups.}
\label{case12}
\end{figure}

\begin{figure}
\centering
\subfigure[Top aristocracy.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case131.eps}}}\hspace{5pt}
\subfigure[The underclass.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case132.eps}}}\hspace{5pt}
\subfigure[New rich.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case133.eps}}}\hspace{5pt}
\subfigure[Antizen.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case134.eps}}}\hspace{5pt}
\caption{Distribution of ``not essential" activity of different groups.}
\label{case13}
\end{figure}
The most important factors in \textit{Folding Beijing} are wealth and social status. In this case, we select ``income" and ``education" to express the two factors to explore citizens' mobility and city usage.

We deem persons earning more than 300,000 yuan a year are in rich group, while less than 100,000 yuan are in poor group. Persons with undergraduate diploma belong to high education group. So, there are four groups formed. The first one is ``top aristocracy" with high income and education level. Opposite of them, ``the underclass" have lowest income and little education. Group ``new rich" collects people who are rich but have less education. ``Antizen" is a new word to describe people have good education but earn little, which is the fourth group.

Fig. \ref{case11} shows the top 13 persons' images in each group. Except for income and education, other social features describe every group in different ways. As shown, nearly all of ``top aristocracy" are locals owing house and car. On the contrary, ``the underclass" do not owe local residence, neither the house and car. ``New rich" can afford house. Most of them are in service industry.

To understand how citizens live in the city, there are two crucial aspects to be known: during the night where they sleep, and where do they go during the daytime.
We divide daytime mobility activities into ``essential activity" and ``no essential activity" two categories to capture movement patterns. ``Essential activity" is made up with ``go to work", ``go to school" and ``go back home". Movements with other purposes are ``not essential". People do these movement activities due to their personal willingness and living patterns. Therefore, ``home location", ``working location" and ``not essential" activity space outline one's living space. Our system meets this requirement.

Fig. \ref{case12} shows examples of living space of the four groups. Fig. \ref{case12}(a) and Fig. \ref{case12}(b) show the distributions of home and working space. These two distributions are similar in four groups. ``Top aristocracy" and ``new rich" live concentrated in downtown area of Shenzhen, where the living cost is higher, especially the housing cost. ``The underclass" distribute dispersively all over the whole city. Compared to the rich, the outer space are prefered because of the lower living cost. Lots of ``antizen" live in Nanshan District. There are many universities and high-tech industrial parks are located in Nanshan which attracts good educated persons. The distribution of ``not essential activity" is shown in Fig. \ref{case13}. From the dimension of space, ``new rich" prefer to live in the west of the city. They do not go south east in most times. Other three groups reach the whole city. The height of the bar stands for the percentage of ``not essential activity" in the whole activities. Higher height means that the group has more willingness and cost more time in ``not essential activity", while lower height means more time on work. Comparing four groups, it can be seen that the poor spend more time on work, especially ``the underclass". Working percentage is really small in group ``new rich". They have diverse lives because they do many other things except for working.

\subsection{Case 2: Home-work Distance}
\begin{figure}
\centering
\subfigure[Group of people whose income more than 500,000yuan per year.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case21.eps}}}\hspace{5pt}
\subfigure[Group of people whose income between 200,000 yuan to 300,000 yuan per year.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case22.eps}}}\hspace{5pt}
\subfigure[Group of people whose income less than 100,000yuan per year.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case23.eps}}}\hspace{5pt}
\subfigure[Group of people who owe house.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case24.eps}}}\hspace{5pt}
\subfigure[Group of people who rent house.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case25.eps}}}\hspace{5pt}
\caption{Home-work distances of different groups.}
\label{case2}
\end{figure}
Home-work space and commuting behavior is an important concept in economics, geography and sociology. It is influenced by many factors like transportation, housing, land using, etc. Understanding it helps know how city functions for a better planning. In this case, we use a graph of ``working space and commuting distance" to demonstrate our system's help in movement behavior understanding.

We use ``income" and ``have house" to distinguish citizens and learn their home-work distance. Fig. \ref{case2} shows examples of five groups. Fig. \ref{case2}(a), Fig. \ref{case2}(b) and Fig. \ref{case2}(c) are formed according to ``income". They are ``more than 500,000 yuan", ``200,000 to 300,000 yuan" and ``less than 100,000 yuan" levels separately. Fig. \ref{case2}(d) and Fig. \ref{case2}(e) are for group of people ``owing house" and ``rent house".

The height of the bar stands for working frequency of the TAZ. From the figure, it is seen that the working locations are mainly in three areas which are circled in white in Fig. \ref{case2}(c). Space in green circle is another hot working area which only are preferred by the poor.

The color of the bar stands for home-work distance of people working in the TAZ. On the whole, home-work distance is short in Shenzhen for most of the TAZs with different groups have darker color, especially in downtown. When focusing on downtown area, it is seen that there are differences between Futian District with the other two. By comparing three groups distinguished by income, it takes more time to work in Futian District with the decrease of the income. Meanwhile, the opposite is true in others. In combination with Fig. \ref{case2}(d) and Fig. \ref{case2}(e), we find that Nanshan District and Luohu District belongs to all but Futian District belongs to the rich. The poor could rent house living in Nanshan and Luohu to enjoy short home-work distance. In Futian, only the rich working there have short home-work distance. There may be no much housing for rent.

### 2018-05-31 manuscript/visualdesign.tex
case, 2.5D...

@@
 \begin{itemize}
-\item \textit{Effective multivarible cross-filter for individual characteristics (C1)}: there are eight domains to describe an individual.
+\item \textit{Intuitive perception of an individual as an organic complex (C1)}: the system should make use of users' daily life experience in knowing people to provide intuitive visualization, instead of the lifeless representation by number.
+The visual design needs to help end-users to pick desirable ones from the mass.
+\item \textit{Good overview of the multivarible individuals (C2)}: following the visual analytics manta by Shneiderman~\cite{RN459}, it is very important to provide a good overview of all the individuals then the users know where to explore.
+\item \textit{Effective multivarible cross-filter for individual characteristics (C3)}: there are eight domains to describe an individual.
 The system is supposed to provide a straright-forward way for easy filtering by the eight criteria.
-\item \textit{Good overview of the multivarible individuals (C2)}: following the visual analytics manta by Shneiderman~\cite{RN459}, it is very important to provide a good overview of all the individuals then the users know where to explore.
-\item \textit{Intuitive perception of an individual as an organic complex (C3)}: the system should make use of users' daily life experience in knowing people to provide intuitive visualization, instead of the lifeless representation by number.
-The visual design needs to help end-users to pick desirable ones from the mass.
 \item \textit{Compact visualization of mobility patterns in the constraint of spatial space (C4)}: the analysis of mobility patterns not only includes the conventional spatial and temporal dimensions, but also other abstract dimensions, e.g., travel purpose, visiting frequency, etc.
@@
 Following the idea of Chernoff Face, we design a type of glyph, a graphical representation of people with specific individual characteristics.
-The idea behind using faces is that humans easily recognize faces and notice small changes without difficulty (\textit{C3}).
+The idea behind using faces is that humans easily recognize faces and notice small changes without difficulty (\textit{C1}).
 Those visual profiles are intended for intutive visual understanding, from abstract to concrete and semantic understanding, to support users to target the interested individual groups effectively.
@@
 In our case, each individual can be denoted as a vector $x_i$ with eight factors, and we get high dimensional data set $X={x_1, x_2, ..., x_n}$.
-The dimensionality reduction techniques are to preserve the local structure of high dimensional data in low dimensional space, which are efficient approaches to provide a good overview of the multivarible individuals.
+The dimensionality reduction techniques are to preserve the local structure of high dimensional data in low dimensional space, which are efficient approaches to provide a good overview of the multivarible individuals (\textit{C2}).
 We adapt t-SNE project~\cite{maaten2008visualizing} to project $X$ as two-dimensional dots $Y={y_1, y_2, ..., y_n}$.
-
-t-SNE computes the conditional probabilities to represent the similarity based on the distance between high dimenional datapoints.
+One of steps in t-SNE is to compute the conditional probabilities to represent the similarity based on the distance between high dimenional datapoints.
 The conditional probability $p_{j\mid i}$ between $x_j$ and $x_i$ is given by:
@@
 
- which well suits high-dimensional data for visualization in a low-dimensional space of two dimensions (\textit{C2}).
+where $\alpha_i$ is the variance of the Gaussian that is centered on $x_i$.
+Specifically in our context, the high-dimensional Euclidean distances $\left \| x_i - x_j \right \|$ between $x_i$ and $x_j$ needs to be apdated the numerical and categorical characteristics.
+Characteristics such as age, income, are numerical and comparable, so the difference exactly explains when they are different.
+But the other characteritics, i.e.
+job, real estate, car, residention, are ordinal.
+There is not the numeric order.
+For example, the job distance from a manager to a businessman and a workman is not comparable, which is considered the same distance, i.e., set to 1.
 
-As Figure~\ref{fig:tsne}(a)shows, all volunteers are embedded evenly in the 2D view, indicating the uniformly sampling over demographical space.
+% So $\left \| x_i - x_j \right \|$ is adapted as following:
+
+% \begin{equation}
+% \left \| x_i - x_j \right \| = 
+% \left\{\begin{matrix}
+% 0, f_{pi} \equiv f_{pj} \Lambda f_{p} \epsilon \{Gender, Residence, Estate, Car, Job\} \\ 
+% 1, f_{pi} \not\equiv f_{pj}  \Lambda f_{p} \epsilon \{Gender, Residence, Estate, Car, Job\} \\ 
+% \left \| f_{pi} - f_{pj} \right \|, f_p \epsilon\{Age, Education, Income, \}
+% \end{matrix}\right
+% \end{equation}
+
+As Figure~\ref{fig:tsne}(a)shows, all 21435 volunteers are embedded in the 2D view, where the closer two dots are, the more similar they are in the eight characteristics.
+Figure~\ref{fig:tsne}(b-e) examplifies four groups of dots in neighbour.
+In the visual profiles, it is found that they are the group of \m{XX} ((b)), \m{XX} ((c)).
 
 Multiple views of abstract view, t-SNE proection and semantic data driven profile visualization are coordinated in a Cross-filter machinesm~\cite{Weaver2010}.
-It allows end-users to interactive drill-down into individuals with interested characteristics from multiple perspectives.
-Starting from the abstract criterion constraints, the scope of interest is narrowed down to individuals with(out) certian properties.
-And then further cross-filtering with semantically visual profiles, to check the combination of 8 characteristical variables.
-Figure~\ref{fig:tsne}(b) examplifies four groups of interest.
+It allows end-users to interactive drill-down into individuals with interested characteristics from multiple perspectives(\textit{C3}).
+Starting from the abstract criterion constraints, the scope of interest is narrowed down to individuals with(out) certian characteristics.
+And then further cross-filtering with semantically visual profiles can be performed, to check the combination of 8 characteristical variables.
 
@@
  \includegraphics[width=\columnwidth]{pictures/mds}
- \caption{t-SNE project with four groups of the interest}
+ \caption{t-SNE project with four groups of the interest: (a) t-SNE project }
  \label{fig:tsne}
@@
 Embedding multiple variables in the spatial map is a challenging problem.
-Distortion technique 2D spatial, such as the partial route embedding~\cite{sun2016embedding}.
-However, when it comes to the global visualization, the trade-off between occlusion-free and the spatial perception.
-Follow the idea of 2.5D space design~\cite{Tominski2012_stacking}, the space visualization is embedded in 2.5D space, which also can smoothly transited back to the conventional 2D view.
+Distorting 2D spatial for better space usage, such as the partial route embedding~\cite{sun2016embedding} is an effective where there are a few local focis.
+When it comes to the global visualization, there is always a trade-off between occlusion-free and the compact spatial perception.
+Following the idea of stacking 2.5D space design~\cite{Tominski2012_stacking}, the space in this work is embedded in 2.5D space, to relax the z-axis for addtional abstract information encoding.
 
- Each TAZ is grown as a prism whose height encodes the occurrence of visiting.
+Figure~\ref{fig:2.5D}(a) shows the 2.5D visualization.
+The spatial map is consisted of Traffic Analysis Zone (TAZ), which is the unit of geography holding a certain number of people.
+For the 2.5D, each TAZ is grown as a prism whose height and color are developed to encode abstract information, e.g., the occurrence of visiting.
+With difference encoding choices, it is capable to visualize the colleration between spatial and different attributes (\textit{C4}).
+For example, in Figure~\ref{fig:2.5D}(a), prisms' height and color both encode the ratio of none-routine trips (such as go entertainment, go hosptial, etc.) in the whole.
+For better 3D visual perception, lighting is turned on.
+Also, a lid is laid over for each prism to clear bound its extent at the z-axis.
+
 Brunch of TAZ with similar visiting pattern and purpose are grouped by an heuristic DB-Scan Algorithm in the context of TAZ.
@@
  In this view, it supports end-users to direct manipulate the space, e.g., zooming, panning, etc. Also, detail information about the visiting can be checked by direct clicking on the TAZ.
+
+\begin{figure}
+\centering
+\subfigure[]{
+\resizebox*{9cm}{!}{\includegraphics{pictures/space1.eps}}}\hspace{5pt}
+\subfigure[]{
+\resizebox*{9cm}{!}{\includegraphics{pictures/space2.eps}}}\hspace{5pt}
+\caption{2.5D Spatial Visualization for Mobility Patterns}
+\label{fig:2.5D}
+\end{figure}

### 2018-05-31 manuscript/visualdesign.tex
...

@@
 With those design considerations, we develop a visual analytics system as Figure~\ref{fig:teaser} shows.
-It composes of individual panel to explore and identify groups (\textit{Task 1}) and spatial panel to explore and compare the mobility pattern (\textit{Task 2 and 3}).
-\m{EXPAND..., it gives an infographical overview of the data.
-Encode information but also allow users to set multiple criteria (\textit{C1}).
-Support users to slice the data by different domains.}
+It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}).
+In the individual panel, an interactive inforgraphics, t-SNE visualization and data-driven profiles support users to narrow the scope down to groups of individuals with interested characteristics.
+With the chosen group of individuals, its moving related information is visualized and explored in an 2.5D spatio-temporal view.
+
+% overview of the data. Encode information but also allow users to set multiple criteria (\textit{C1}). Support users to slice the data by different domains.}
 % Semantic understanding of social characteristics.
@@
 
-As Figure~\ref{fig:tsne}(a)shows, all 21435 volunteers are embedded in the 2D view, where the closer two dots are, the more similar they are in the eight characteristics.
-Figure~\ref{fig:tsne}(b-e) examplifies four groups of dots in neighbour.
-In the visual profiles, it is found that they are the group of \m{XX} ((b)), \m{XX} ((c)).
+As Figure~\ref{fig:tsne}shows, all 21435 volunteers are embedded in the 2D view, where the closer two dots are, the more similar they are in the eight characteristics.
+Figure~\ref{fig:tsne} examplifies four features groups of dots in neighbour.
 
@@
  \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/mds}
+ \includegraphics[width=\columnwidth]{pictures/tsne}
  \caption{t-SNE project with four groups of the interest: (a) t-SNE project }
@@
 For better 3D visual perception, lighting is turned on.
-Also, a lid is laid over for each prism to clear bound its extent at the z-axis.
+Also, a lid is laid on the top of each prism to clearly bound its extent at the z-axis.
 
-Brunch of TAZ with similar visiting pattern and purpose are grouped by an heuristic DB-Scan Algorithm in the context of TAZ.
-From a center TAZ, walk to neighbour TAZ to check whether aggregation or not.
-The aggregated TAZ brunch indicates the region visiting by the group of people in same purpose, which is often the popular traveling places.
-The TAZ brunch is visualized...
-
- To compare the mobility patterns across different groups of people, a Small Multiple dock is used to reserve the ever explored interesting result.
-To simply the comparion over spatial distribution, the snapshot is rendered in the 2D space, which can be magnified to check for the details in the 2.5D space.
-
- In this view, it supports end-users to direct manipulate the space, e.g., zooming, panning, etc. Also, detail information about the visiting can be checked by direct clicking on the TAZ.
-
-\begin{figure}
+\begin{figure}[htb!]
 \centering
@@
 \resizebox*{9cm}{!}{\includegraphics{pictures/space2.eps}}}\hspace{5pt}
-\caption{2.5D Spatial Visualization for Mobility Patterns}
+\caption{2.5D Spatial Visualization: (a) 2.5D spatial visualization with z-axis to encode addition information; (b) detail slicing in 2.5D space.}
 \label{fig:2.5D}
 \end{figure}
+
+Several interaction are integrated in the spatial view to alleviate the occlusion problem (\textit{C5}).
+The manipuation of 2.5D view supports users with rotate, zoom, pan operations, which are so continously flexible that users probably find a suitable observing point.
+In the cases where occlusion is inevitable, an interaction named as \textit{Detail Slicing} is developed, as Figure~\ref{fig:2.5D}(b) shows.
+Detail Slicing is the operation to put a cross-section in the 2.5D space to expose the TAZ inside.
+To contextualize the cross-section, TAZs are visually adapted according to the intersection by ray casting.
+The TAZ in foreground will be hidden, the intersected TAZs will be fully visualized and the ones in the background will be in semi-transparency.
+% Brunch of TAZ with similar visiting pattern and purpose are grouped by an heuristic DB-Scan Algorithm in the context of TAZ.
+From a center TAZ, walk to neighbour TAZ to check whether aggregation or not.
+The aggregated TAZ brunch indicates the region visiting by the group of people in same purpose, which is often the popular traveling places.
+The TAZ brunch is visualized...
+
+ To compare the mobility patterns across different groups of people, a Small Multiple dock is used to reserve the ever explored interesting result (Figure~\ref{fig:teaser}(f)).
+To simply the comparion over spatial distribution, the snapshot is also rendered in the 2.5D space, which maintains the same interactions as the main 2.5D space does.
+
+ % In this view, it supports end-users to direct manipulate the space, e.g., zooming, panning, etc. Also, detail information about the visiting can be checked by direct clicking on the TAZ.

### 2018-06-04 manuscript/case12.tex
1st submit to ChinaVis 2018

@@
 \section{Case Study}
-We apply our method with our data.
-Two cases are derived to demonstrate the powerness of our method.
-We believe this work to be one of the nature steps into research of social understanding of the city.
 
-\subsection{Case 1: City Folding}
+In this section, we apply the method described above to study the case of Shenzhen. We introduce the several cases to demonstrate the usage and effectiveness of the system.
 
-\begin{figure}
-\centering
-\subfigure[Top aristocracy.]{
-\resizebox*{4.4cm}{!}{\includegraphics{pictures/case111.eps}}}\hspace{5pt}
-\subfigure[The underclass.]{
-\resizebox*{4.4cm}{!}{\includegraphics{pictures/case112.eps}}}\hspace{5pt}
-\subfigure[New rich.]{
-\resizebox*{4.4cm}{!}{\includegraphics{pictures/case113.eps}}}\hspace{5pt}
-\subfigure[Antizen.]{
-\resizebox*{4.4cm}{!}{\includegraphics{pictures/case114.eps}}}\hspace{5pt}
-\caption{XXX of different groups.}
+%The cases of analysis how individuals use the city are derived to demonstrate the powers. We believe this work would be one of the natural steps into research of social understanding of the city.
+
+\subsection{Case 1: Work-life Balance VS Income/Education}
+
+% \begin{figure}
+% \centering
+% \subfigure[Top aristocracy.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case111.eps}}}\hspace{5pt}
+% \subfigure[The underclass.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case112.eps}}}\hspace{5pt}
+% \subfigure[New rich.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case113.eps}}}\hspace{5pt}
+% \subfigure[Antizen.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case114.eps}}}\hspace{5pt}
+% \caption{XXXXXX of different groups.}
+% \label{case11}
+% \end{figure}
+
+% \begin{figure}
+% \centering
+% \subfigure[Top aristocracy.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case121.eps}}}\hspace{5pt}
+% \subfigure[The underclass.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case122.eps}}}\hspace{5pt}
+% \subfigure[New rich.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case123.eps}}}\hspace{5pt}
+% \subfigure[Antizen.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case124.eps}}}\hspace{5pt}
+% \caption{}
+% \label{case12}
+% \end{figure}
+
+This work is inspired and motivated by the implication in science fiction~\textit{Folding Beijing}, which is that people are categorized into three classes and behave in the parallel spatial-temporal patterns.
+The first cast explores whether the folding city exists in reality or not.
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/case1_1}
+ \caption{Four Groups Divided by Income and Education Characteristics}
  \label{case11}
@@
 
-\begin{figure}
-\centering
-\subfigure[Top aristocracy.]{
-\resizebox*{4.4cm}{!}{\includegraphics{pictures/case121.eps}}}\hspace{5pt}
-\subfigure[The underclass.]{
-\resizebox*{4.4cm}{!}{\includegraphics{pictures/case122.eps}}}\hspace{5pt}
-\subfigure[New rich.]{
-\resizebox*{4.4cm}{!}{\includegraphics{pictures/case123.eps}}}\hspace{5pt}
-\subfigure[Antizen.]{
-\resizebox*{4.4cm}{!}{\includegraphics{pictures/case124.eps}}}\hspace{5pt}
-\caption{Distributions of home and working space of different groups.}
+Although it is incomplete, income and education are two of the most essential characteristics to tag an individual with a good resource or not. 
+As Figure~\ref{case11} shows, taking income and education as the two dimensions, taking 300K yuan as the border between high and low income and an undergraduate bachelor degree as the border between high and low education level, four different groups are generated in the four quadrants.
+In the first quadrant, individuals are rich and well educated, who are in a group of so-called \textit{top aristocracy}.
+The second quadrant holds the group of \textit{new rich}, i.e., individuals with high income but low education income.
+In the third quadrant, they are the \textit{underclass} who has both low income and education level.
+The fourth quadrant is \textit{Antizen}, which is a new word to describe people have a good education but earn little.
+
+Figure~\ref{case11} shows the top 12 profiles with the maximum population in each group.
+In each group, other characteristics surprisingly demonstrate the high correlation to income and education.
+For example, almost all of the \textit{top aristocracy} is with the residential license,  house, and car.
+On the contrary, \textit{underclass} do not have the residential license residence, neither the house nor the car.
+Most of \textit{New rich} has a house and work in the service industry.
+
+Before diving into the complex mobility pattern analysis, we explore the home distribution of the four groups.
+As Figure~\ref{case12} shows, \textit{top aristocracy} and most of \textit{new rich} live concentrated in the downtown area of Shenzhen, where the living cost is higher, especially the housing cost.
+A small part of \textit{new rich} lives far away from the downtown, maybe because they don't have to work in downtown.
+The \textit{underclass} distribute more dispersively all over the whole city.
+Compared to the rich, they prefer the outer space because of the lower living cost.
+Lots of \textit{antizen} live in Nanshan District, where there are many universities and high-tech industrial parks full of well educated people.
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/case1_2}
+ \caption{Home Distributions of the Four Groups}
  \label{case12}
@@
 
-\begin{figure}
-\centering
-\subfigure[Top aristocracy.]{
-\resizebox*{4.4cm}{!}{\includegraphics{pictures/case131.eps}}}\hspace{5pt}
-\subfigure[The underclass.]{
-\resizebox*{4.4cm}{!}{\includegraphics{pictures/case132.eps}}}\hspace{5pt}
-\subfigure[New rich.]{
-\resizebox*{4.4cm}{!}{\includegraphics{pictures/case133.eps}}}\hspace{5pt}
-\subfigure[Antizen.]{
-\resizebox*{4.4cm}{!}{\includegraphics{pictures/case134.eps}}}\hspace{5pt}
-\caption{Distribution of ``not essential" activity of different groups.}
+% To understand how citizens live in the city, there are two crucial aspects to be known: during the night where they sleep, and where do they do during the daytime.
+``Home location" could answer the first question.
+The second one is harder to summarise because of the complexity of daytime activities.
+In our method, we divide daytime mobility activities into
+
+To have a better knowledge of mobility patterns of the four groups, trips are categorized into three categories, ``home", ``work'' for regular trips with the purpose of going home, work (or school for students), ``other'' for irregular trips with the purpose of shopping, visiting friends.
+Figure~\ref{case13}(a) shows the 2.5D overview of the three kinds of traveling categories.
+Each TAZ is grown to the same height, i.e., the unit one, and the height proportion of each traveling categories encodes the percentage of certain purpose in the whole, pink for ``others'', blue for ``work'' and green for ``home''.
+Although inside TAZ prisms are blocked in the Figure~\ref{case13}, our attention is drawn to the lifestyle of \textit{New Rich}.
+It is founded that the \textit{New Rich} travel for ``other'' purpose a lot, compared to other groups.
+To explore further, the detail slicing (introduced in Section~\ref{subsec:25D}) is applied to the four groups.
+Figure~\ref{case13}(b) shows three slices.
+It can be seen that individuals with low income (\textit{underclass} and \textit{antizen}) spend relatively more time on work, especially the \textit{underclass}.
+Working percentage is very small in-group \textit{new rich}.
+They live a more diverse lifestyle because they do many other things (the pink ones) except working.
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/case1_3}
+ \caption{Mobility Patterns of ``work", ``home" and ``not essential" of the Four Groups: (a) the overview of the three pecentage; (b) three slices for detailed comparison.}
  \label{case13}
 \end{figure}
-The most important factors in \textit{Folding Beijing} are wealth and social status.
-In this case, we select ``income" and ``education" to express the two factors to explore citizens' mobility and city usage.
 
-We deem persons earning more than 300,000 yuan a year are in rich group, while less than 100,000 yuan are in poor group.
-Persons with undergraduate diploma belong to high education group.
-So, there are four groups formed.
-The first one is ``top aristocracy" with high income and education level.
-Opposite of them, ``the underclass" have lowest income and little education.
-Group ``new rich" collects people who are rich but have less education.
-``Antizen" is a new word to describe people have good education but earn little, which is the fourth group.
+% By comparing them, it can be seen that the poor spend more time on work, especially ``the underclass".
+Working percentage is really small in-group ``new rich".
+They have diverse lives because they do many other things except for working.
 
-Fig.
-\ref{case11} shows the top 13 persons' images in each group.
-Except for income and education, other social features describe every group in different ways.
-As shown, nearly all of ``top aristocracy" are locals owing house and car.
-On the contrary, ``the underclass" do not owe local residence, neither the house and car.
-``New rich" can afford house.
-Most of them are in service industry.
-
-To understand how citizens live in the city, there are two crucial aspects to be known: during the night where they sleep, and where do they go during the daytime.
-We divide daytime mobility activities into ``essential activity" and ``no essential activity" two categories to capture movement patterns.
-``Essential activity" is made up with ``go to work", ``go to school" and ``go back home".
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.95\linewidth]{pictures/case1_4}
+%   \caption{Examples of XXXXX.}
+%   \label{case14}
+% \end{figure}
+% two categories to capture mobility patterns.
+``routine activity" is made up with ``go to work", ``go to school" and ``go back home".
 Movements with other purposes are ``not essential".
-People do these movement activities due to their personal willingness and living patterns.
+People do these movement activities due to their personal willingness and living style.
 Therefore, ``home location", ``working location" and ``not essential" activity space outline one's living space.
@@
 
-Fig.
-\ref{case12} shows examples of living space of the four groups.
-Fig.
-\ref{case12}(a) and Fig.
-\ref{case12}(b) show the distributions of home and working space.
-These two distributions are similar in four groups.
-``Top aristocracy" and ``new rich" live concentrated in downtown area of Shenzhen, where the living cost is higher, especially the housing cost.
-``The underclass" distribute dispersively all over the whole city.
-Compared to the rich, the outer space are prefered because of the lower living cost.
-Lots of ``antizen" live in Nanshan District.
-There are many universities and high-tech industrial parks are located in Nanshan which attracts good educated persons.
-The distribution of ``not essential activity" is shown in Fig.
-\ref{case13}.
-From the dimension of space, ``new rich" prefer to live in the west of the city.
-They do not go south east in most times.
+% In Fig. \ref{case13}, the distributions of ``essential" activity including ``go to work" and ``go home", and ``not essential activity" are shown.
+
+% From the dimension of space, ``new rich" prefer to live in the west of the city.
+They do not go south-east in most times.
 Other three groups reach the whole city.
-The height of the bar stands for the percentage of ``not essential activity" in the whole activities.
-Higher height means that the group has more willingness and cost more time in ``not essential activity", while lower height means more time on work.
-Comparing four groups, it can be seen that the poor spend more time on work, especially ``the underclass".
-Working percentage is really small in group ``new rich".
+The height of the bar stands for the percentage of each kind of activity.
+Higher height means that the group has more willingness and cost more time in ``, not the essential activity", while lower height means more time on work.
+As we described in Section XXX, 遮挡问题, 我们使用切面解决。 Fig.
+\ref{case14} give three examples within each group to check the detailed information in the 2.5D graph.
+By comparing them, it can be seen that the poor spend more time on work, especially ``the underclass".
+Working percentage is really small in-group ``new rich".
 They have diverse lives because they do many other things except for working.
 
-\subsection{Case 2: Home-work Distance}
-\begin{figure}
-\centering
-\subfigure[Group of people whose income more than 500,000yuan per year.]{
-\resizebox*{4.4cm}{!}{\includegraphics{pictures/case21.eps}}}\hspace{5pt}
-\subfigure[Group of people whose income between 200,000 yuan to 300,000 yuan per year.]{
-\resizebox*{4.4cm}{!}{\includegraphics{pictures/case22.eps}}}\hspace{5pt}
-\subfigure[Group of people whose income less than 100,000yuan per year.]{
-\resizebox*{4.4cm}{!}{\includegraphics{pictures/case23.eps}}}\hspace{5pt}
-\subfigure[Group of people who owe house.]{
-\resizebox*{4.4cm}{!}{\includegraphics{pictures/case24.eps}}}\hspace{5pt}
-\subfigure[Group of people who rent house.]{
-\resizebox*{4.4cm}{!}{\includegraphics{pictures/case25.eps}}}\hspace{5pt}
-\caption{Home-work distances of different groups.}
+\subsection{Case 2: Home-work Distance VS Income/House}
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/case2}
+ \caption{Home-work distances of different groups: (a) with different salary levels; (b) with or without house.}
  \label{case2}
 \end{figure}
-Home-work space and commuting behavior is an important concept in economics, geography and sociology.
-It is influenced by many factors like transportation, housing, land using, etc.
-Understanding it helps know how city functions for a better planning.
-In this case, we use a graph of ``working space and commuting distance" to demonstrate our system's help in movement behavior understanding.
 
-We use ``income" and ``have house" to distinguish citizens and learn their home-work distance.
-Fig.
-\ref{case2} shows examples of five groups.
-Fig.
-\ref{case2}(a), Fig.
-\ref{case2}(b) and Fig.
-\ref{case2}(c) are formed according to ``income".
-They are ``more than 500,000 yuan", ``200,000 to 300,000 yuan" and ``less than 100,000 yuan" levels separately.
-Fig.
-\ref{case2}(d) and Fig.
-\ref{case2}(e) are for group of people ``owing house" and ``rent house".
+% \begin{figure}
+% \centering
+% \subfigure[Group of people whose income more than 500,000yuan per year.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case21.eps}}}\hspace{5pt}
+% \subfigure[Group of people whose income between 200,000 yuan to 300,000 yuan per year.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case22.eps}}}\hspace{5pt}
+% \subfigure[Group of people whose income less than 100,000yuan per year.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case23.eps}}}\hspace{5pt}
+% \subfigure[Group of people who owe house.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case24.eps}}}\hspace{5pt}
+% \subfigure[Group of people who rent house.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case25.eps}}}\hspace{5pt}
+% \caption{Home-work distances of different groups.}
+% \label{case2}
+% \end{figure}
 
-The height of the bar stands for working frequency of the TAZ.
-From the figure, it is seen that the working locations are mainly in three areas which are circled in white in Fig.
+Home-work distance is an essential metric in economics, geography, and sociology.
+It refers to the distance between house and workplace.
+It is influenced by many factors like transportation, housing, land use, etc.
+Understanding the home-work distance of a region helps to evaluate whether the region is well planned or not.
+In this case, we demonstrate our system's help in home-work distance understanding.
+
+Considering income potentially determines where people live, we use income as the characteristics to select three groups, the group over 500K, the group during 200-300K and the group less than 100K.
+In Figure~\ref{case2}, the height of the bar stands for visiting frequency of the TAZ and its color encodes the average home-work distance, red for close and yellow for far.
+As Figure~\ref{case2}(a) shows, for all the three groups in different income levels, most of the TAZs have dark red or red color which indicates the home-work distance is generally short, especially in downtown.
+Only those with less than 100K salary work outside the center, such as the space in the green circle.
+When comparing the three groups in the downtown area, it is seen that it takes more time to go to work in Futian District as the decrease of the income.
+
+We explore the home-work distance of groups with and without a house. 
+Figure~\ref{case2}(b) shows the close-up views.
+It is found that the Nanshan District has a shorter home-work distance for individuals without a house, while Futian District has shorter for those with a house.
+Nanshan is relatively newer to Futian so that there might be more easily-accessible houses to be rent.
+
+  % District belongs to all but Futian District belongs to the rich.
+The poor could rent house living in Nanshan and Luohu to enjoy short home-work distance.
+In Futian, only the rich working there have short home-work distance.
+There may be no much housing for rent.
+
+ % From the figure, it is seen that the working locations are mainly in three areas which are circled in white in Fig.
 \ref{case2}(c).
-Space in green circle is another hot working area which only are preferred by the poor.
-
-The color of the bar stands for home-work distance of people working in the TAZ.
-On the whole, home-work distance is short in Shenzhen for most of the TAZs with different groups have darker color, especially in downtown.
-When focusing on downtown area, it is seen that there are differences between Futian District with the other two.
+Space in green circle is another hot working area which only is preferred by the poor.
+% On the whole, home-work distance is short in Shenzhen for most of the TAZs with different groups have a darker color, especially in downtown.
+When focusing on the downtown area, it is seen that there are differences between Futian District with the other two.
 By comparing three groups distinguished by income, it takes more time to work in Futian District with the decrease of the income.
@@
 \ref{case2}(d) and Fig.
-\ref{case2}(e), we find that Nanshan District and Luohu District belongs to all but Futian District belongs to the rich.
-The poor could rent house living in Nanshan and Luohu to enjoy short home-work distance.
-In Futian, only the rich working there have short home-work distance.
-There may be no much housing for rent.
+\ref{case2}(e),
+
+\subsection{Case 3: Life-style VS Jobs}
+
+% \begin{figure}
+% \centering
+% \subfigure[Officer.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/311.eps}}}\hspace{5pt}
+% \subfigure[Workman.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/321.eps}}}\hspace{5pt}
+% \subfigure[Student.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/331.eps}}}\hspace{5pt}
+% \subfigure[Businessman.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/341.eps}}}\hspace{5pt}
+% \caption{Percentage of movement with purposes in group of different jobs.}
+% \label{case31}
+% \end{figure}
+
+In this case, we explore the correlation between mobility patterns with the job, to see whether the job has an impact on the movement.
+Officer, workman, student, and businessman are selected as examples and the population of trips for certain purposes is shown In Figure~\ref{case3}.
+The height of bars encodes the amount of visit to each TAZ, and color encodes the traveling purpose.
+There are 10 different kinds of traveling purposes.
+For quick linking between color and purposes, the regular trips such as go to work, school and home are dyed in cold color, and the irregular trips such as go shopping, hospital, etc, are dyed in the warm color.
+As Figure~\ref{case3} shows, for officers, the TAZs changes dramatically in height.
+Some TAZs have much more visiting than others because officers are more constrained to work in some buildings than individuals with other jobs.
+The relative percentage of irregular activity differs for the four groups.
+For Workman, about 80 percent of movements are the regular purpose, either go to work or go back home.
+For students, the percentage becomes to be about 50 percentage.
+Compared to them, officer and businessman have more flexible and diversified lifestyle.
+
+% Each social attribute has an impact on movement patterns.
+There are 9 kinds of jobs in the data which offers rich information.
+Therefore, in this case, we use ``job" as the target social attribute to explore its influence on citizens' movement patterns.
+
+% At first, with 2.5D spatial visual form, we learn what people move for and the percentage of movements with a given purpose.
+
+% The height of each bar stands for the number of movements to the TAZ.
+Purposes are encoded in color as the legends show.
+From the perspective of the height of bars, it is seen that the amount of visitors to each TAZ of officers is really different.
+Several TAZs have the dominant visiting.
+In Figure~\ref{case3}(a), the heights of yellow bars and rose red bars in different TAZs have great differed.
+This phenomenon is not that obvious in other three groups.
+In addition, the percentage of ``not essential" activity differs.
+For Workman, about 80 percent of movements are ``essential" ones.
+For students, the percentage becomes to be about 50 percentage.
+Compared to them, officer and businessman have more flexible and diversified lives.
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/case3}
+ \caption{Trip purposes distribution of four groups with different jobs}
+ \label{case3}
+\end{figure}
+
+Next, we concentrated on one purpose to see whether it is related to jobs.
+Here we use ``dinner or entertainment" as the example.
+As Fig \ref{case32} shows, the height of TAZ bars represents the visiting amount of trips for dinner or entertainment.
+Color stands for moving distance to reach this TAZ.
+As we can see, officers prefer to entertain in the downtown area, while workmen cover a larger area.
+Students tend to concentrate on Nanshan district, probably near schools.
+For the businessmen, they go lots of places for dinner or entertainment.
+The biggest difference with other groups is that they would travel a long distance to go somewhere far from downtown areas.
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/case3_2}
+ \caption{The ``dinner or entertain" purpose of four groups with different jobs}
+ \label{case32}
+\end{figure}
+
+% \begin{figure}
+% \centering
+% \subfigure[Officer.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/314.eps}}}\hspace{5pt}
+% \subfigure[Workman.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/324.eps}}}\hspace{5pt}
+% \subfigure[Student.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/334.eps}}}\hspace{5pt}
+% \subfigure[Businessman.]{
+% \resizebox*{4.4cm}{!}{\includegraphics{pictures/344.eps}}}\hspace{5pt}
+% \caption{}
+% \label{case32}
+% \end{figure}

### 2018-06-04 manuscript/data.tex
1st submit to ChinaVis 2018

@@
 
-The advent of mobile sensing techniques makes it possible to develop urban geography from social media source.
-Complementary to the conventional census, social media brings the benefit of larger sampling frequency and higher disaggregate in terms of space and time.
+The advent of mobile sensing techniques and social media applications makes it possible to collect spatial data from the social media source.
+Complementary to the conventional census, it brings the benefit of larger sampling frequency and a broader range in terms of space and time.
 It is possible to reach a wide range of individuals and collect the movement in human inactive time, such as the mid-night.
@@
 
-In this work, we perform the census survey in Shenzhen, which is one of the most modern metropolis in China.
+In this work, we perform the census survey in Shenzhen, which is one of the most modern metropolia in China.
 The experiment is deployed on Wechat, a widely used social media application.
@@
 
-\textbf{Individual Characteristics} Figure~\ref{fig:data_over} lists the \textit{eight domains}, including social, economic and deomgraphic aspects, to give a generalized description of the individual characteristics.
+\textbf{Individual Characteristics} Figure~\ref{fig:data_over} lists the \textit{eight domains}, including social, economic and demographic aspects, to give a generalized description of the individual characteristics.
 The profile will serve as the ingredients for the analysis of mobility patterns over diverse individuals.
@@
 Each trip requires the information of \textit{start/end location}, \textit{start/end time}, \textit{traveling purpose}.
-
 To encourage the trip uploading, a credit system retains the contribution of individuals on trips and rewards the volunteers with the top credits (Figure~\ref{fig:app}(c)).
@@
 
-Over the releasing time period from \m{2016-11 to 2018-01}, 21435 individules (48\% females and 52\% males) were reached and \m{229155} trips are collected.
-The majority of our 25481 volunteers contribute \m{11} trips averagly.
+Over the releasing time period from \m{2015-11 to 2016-01}, 21435 individuals (48\% females and 52\% males) were reached and \m{229155} trips are collected.
+Each volunteer contributes \m{11} trips average.
 
 Our case-study data is confined to a small proportion of Wechat users who opt to contribute their information and trips.
-Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of individuals in the city.
+Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of the population in the city.
 
 Figure~\ref{fig:data_age_edu} gives the distribution of age and education over the population.
-It shows that samples cover a wide range of all ages, dominately between 18 to 45.
+It shows that samples cover a wide range of ages, dominating between 18 to 45.
 There is also a few records pertaining to individuals below the age of 18 or above 70.
@@
 Figure~\ref{fig:data_age_edu} gives the distribution of education levels, ranging from low to high.
-The technical college and university dominates the education at the 61\% occupancy rate.
+The technical college and university dominate the samples at the 61\% occupancy rate.
 
@@
 
-Figure~\ref{fig:data_job_inc}(a) shows the job types of sampled individuals, who are servants, workers, officers, bussinessmen.
+Figure~\ref{fig:data_job_inc}(a) shows the job types of sampled individuals, who are servants, workers, officers, businessmen and so on.
 The covering of jobs is pretty wide.
@@
 The majority get paid below 200 000.
-Some individuals with higher salary are also reached in our census.
+Individuals with higher salary are also reached in our census.
 
@@
 Figure~\ref{fig:data_geometry} shows the basic statistics related to trips.
-In Figure~\ref{fig:data_geometry}(a), the active traveling time (here, we take the start time as the representative of active time) follows the common sense of urban life.
+In Figure~\ref{fig:data_geometry}(a), the active traveling time (here, we take the start time as the representative of active time) follows the common knowledge of urban life.
 There are obvious morning and late afternoon peaks.
 Figure~\ref{fig:data_geometry}(b) gives the counting of different traveling purposes.
-95\% trips are tagged with traveling purpose in the data.
+95\% trips are tagged with clear raveling purpose in the data.
 33\% are going home and 37\% are going to work.
-Besides this kind of routine traveling, there are also substantial trips such as going shopping, going hospital, etc.
-Figure~\ref{fig:data_geometry}(c) shows the spatial distribution of the origins and destinations spot.
-It is found that more trips uploaded by volunteers located in Futian and Nanshan districts, the city's heart part of than the surrounding outer areas.
+Besides this kind of routine traveling, there are also substantial trips such as going shopping, going the hospital, etc.
+Figure~\ref{fig:data_geometry}(c) shows the spatial distribution of the origins and destinations.
+It is found that more dots are located in Futian and Nanshan districts, the city's heart than the surrounding areas.
 This is consistent to Batty's exposition of the focus of city networks and interaction patterns~\cite{batty2013new}.
@@
 
-Because there is always unevitable bias inherent in fully representing the ground true of society awide, the prelimeary statistical analysis shows positive sign of a relatively even sampling of the population.
+Because there is always inevitable bias inherent in fully representing the ground truth of the population, the preliminary statistical analysis shows positive sign of a relatively even sampling of the population.
 % As a note, although it is a subset of all people with

### 2018-06-04 manuscript/relatedwork.tex
1st submit to ChinaVis 2018

@@
 
-This work concerns to the research topic of spatial data visual analytics.
+This work concerns the research topic of spatial data visual analytics.
 Spatio-temporal data has three components, i.e., spatial, temporal and thematic~\cite{andrienko2013visual}.
 Lots of related work focus on the spatio-temporal analysis in movement data, in the absence of thematic information.
-The presense of geo-tagged social media data flourishes the exploration of thematic information along with movement.
+The presence of geotagged social media data flourishes the exploration of thematic information along with movement.
 By analyzing the texts, those work explain what drive the moving activities or what is resulted from.
-This work continues the thematic research in movement data, but focus more on individual charecteristics.
-Landed by a census experiment, this work is able to analyze the profile information directly, to get rid of indirect data inferred from social media data as other related work do.
+This work continues the thematic research in movement data but focuses more on individual characteristics.
+Landed by a census experiment, this work is able to analyze the profile information directly, to get rid of indirect data inferred from social media data as other related works do.
 
@@
 
- With the development of location-acquistion techniques, massive spatial trajectories are collected, to keep track of the trajectories of various moving objects.
-Many techniques have been proposed to process, mining trajectory~\cite{Zheng2015_trajectory}.
-In the field of visualization and visual analytic, spatial visualizations are specifically designed for the time, locations, spatial-temporal information and other properties in the traffic data~\cite{chen2015survey}.
+ With the development of location-acquisition techniques, massive spatial trajectories are collected, to keep track of the trajectories of various moving objects.
+Many techniques have been proposed to process, mine trajectory~\cite{Zheng2015_trajectory}.
+In the field of visualization and visual analytics, spatial visualizations are specifically designed for the time, locations, spatial-temporal information and other properties in the traffic data~\cite{chen2015survey}.
 A large number of visual analytics tools and applications cover situation-aware exploration, pattern discovery and traffic situation monitoring.
 Wang et al~\cite{wang2013visual} extract the traffic jam propagation graph extraction to reveal underlying data patterns.
-Guo et al.~\cite{guo2011tripvista} and Zeng et al.~\cite{zeng2013visualizing} et al.
-construct geographical regions and visually aggregate the in-between movements as flows.
-To discover the route travel patterns, Lu et al.~\cite{lu2015trajrank} propose TrajRank to explore the route travel behaviour based on ranking.
-For multiple routes, Liu et al.~\cite{liu2011_routediversity} study the route diversity between locations and Lu et al.~\cite{Lu2017_multipleroute} explore the route choice behaviour among multiple routes.
+Guo et al.~\cite{guo2011tripvista} and Zeng et al.~\cite{zeng2013visualizing} construct geographical regions and visually aggregate the in-between movements as flows.
+To discover the route travel patterns, Lu et al.~\cite{lu2015trajrank} propose TrajRank to explore the route travel behavior based on ranking.
+For multiple routes, Liu et al.~\cite{liu2011_routediversity} study the route diversity between locations and Lu et al.~\cite{Lu2017_multipleroute} explore the route choice behavior among multiple routes.
 
@@
 
-As the prevence of social medial serivces, social media data with geo-tags are collected to track people's movements in daily lifes.
-As an analogue of remote sensing data in social science research, the geospatial big data has been proposed as social sensing ~\cite{liu2015social}.
+As the presence of social media services, social media data with geo-tags are collected to track people's movements in daily lives.
+As an analog of remote sensing data in social science research, the geospatial big data has been proposed as social sensing ~\cite{liu2015social}.
 Hence, analyzing movement information along with rich text has become a hot research area in recent years.
 Those works infer thematic information from the semantic texts.
-Cao et al.~\cite{cao2012whisper} propose \textit{Whisper} for tracing the pathways of tweets on a spatial hierarchical layouts, to investigate how information flow among multiple places.
+Cao et al.~\cite{cao2012whisper} propose \textit{Whisper} for tracing the pathways of tweets on a spatial hierarchical layout, to investigate how information flow among multiple places.
 Krueger et al.~\cite{krueger2014visual} used GPS and location-based service data to support the analysis of movement behaviors.
-Chen et al.~\cite{chen2016interactive} present a visual analytics system to support the exploraiton of sparcely sampled trajectory from social media.
-Some other researches tend to infer real information, such as names, gender, etc~\cite{peddinti2014internet}, to break down the demographic characteristics of social media users.
-Luo et al.~\cite{luo2016explore} derive race, gender and age as three demographics dimensions to analyze its impact on the urban human mobility patterns.
-Since real information is not enforced in social media, wrong infering is inevitable.
+Chen et al.~\cite{chen2016interactive} present a visual analytics system to support the exploration of sparsely sampled trajectory from social media.
+Some other researchers tend to infer real information, such as names, gender, etc, from social media data~\cite{peddinti2014internet}, to break down the demographic characteristics of social media users.
+Luo et al.~\cite{luo2016explore} derive race, gender, and age as three demographics dimensions to analyze its impact on the urban human mobility patterns.
+Since real information is not enforced in social media, the wrong inferring is inevitable.
 Longley et al.~\cite{Longley2015}~\cite{Paul2016_twitter} identifies and assess the biases inherent in social media usage in social research and evaluate the deployment of social media data in research applications.

### 2018-06-04 manuscript/visualdesign.tex
1st submit to ChinaVis 2018

@@
 
-The design of system is driven by tasks, to align the analysis of mobility patterns with individual characteristics characteristics.
-Before diving into the design of system, we introduce the couple of specifical tasks the system intended for.
+The design of the system is driven by tasks, to align the analysis of mobility patterns with individual characteristics.
+Before diving into the design of the system, we introduce the couple of specifical tasks the system intended for.
 
@@
 \item \textit{Task 1: Identify the group with specific individual characteristics}: to get groups of people with common or close attributes, to explore the correlation among individual characteristics.
-\item \textit{Task 2: Explore the mobility patterns of a group}: to explore where, how and why an interested group go in city. 
+\item \textit{Task 2: Explore the mobility patterns of a group}: to explore where, how and why an interested group go in the city. 
 \item \textit{Task 3: Compare mobility patterns among multiple groups}: to know the similarities and differences between different groups in their mobility patterns, to investigate the relationship between movement and individual characteristics.
@@
 The visual design needs to help end-users to pick desirable ones from the mass.
-\item \textit{Good overview of the multivarible individuals (C2)}: following the visual analytics manta by Shneiderman~\cite{RN459}, it is very important to provide a good overview of all the individuals then the users know where to explore.
-\item \textit{Effective multivarible cross-filter for individual characteristics (C3)}: there are eight domains to describe an individual.
-The system is supposed to provide a straright-forward way for easy filtering by the eight criteria.
+\item \textit{Good overview of the multivariate individuals (C2)}: following the visual analytics manta by Shneiderman~\cite{RN459}, it is very important to provide a good overview of all the individuals then the users know where to explore.
+\item \textit{Effective multivariable cross-filter for individual characteristics (C3)}: there are eight domains to describe an individual.
+The system is supposed to provide a straight-forward way for easy filtering by the eight criteria.
 \item \textit{Compact visualization of mobility patterns in the constraint of spatial space (C4)}: the analysis of mobility patterns not only includes the conventional spatial and temporal dimensions, but also other abstract dimensions, e.g., travel purpose, visiting frequency, etc.
 The system should handle a compact layout to support the easy correlation between spatial and abstract information.
-\item \textit{Flexible interactions to explore the mobility patterns either within one group or between groups (C5)}: to support the comparison among groups, \textit{Task 3}, the system should maintains flexbile interactions which allows the end-users to explore freely.
+\item \textit{Flexible interactions to explore the mobility patterns either within one group or between groups (C5)}: to support the comparison among groups, \textit{Task 3}, the system should maintain flexible interactions which allow the end-users to explore freely.
 \end{itemize}
@@
 It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}).
-In the individual panel, an interactive inforgraphics, t-SNE visualization and data-driven profiles support users to narrow the scope down to groups of individuals with interested characteristics.
-With the chosen group of individuals, its moving related information is visualized and explored in an 2.5D spatio-temporal view.
+In the individual panel, interactive infographics, t-SNE visualization, and data-driven profiles support users to narrow the scope down to groups of individuals with interested characteristics.
+With the chosen group of individuals, its moving related information is visualized and explored in a 2.5D spatio-temporal view.
 
@@
 
-Glyph-based visualization~\cite{borgo2013glyph} is the form of visual design to compose multivaribles into a collection of unified visual symbols, known as glyph.
-Glyph is intended for quick understanding and aligned comparison.
-Among glyph design, Chernoff Face~\cite{chernoff1973use} represents data variabules by the different features of a cartoon face.
+Glyph-based visualization~\cite{borgo2013glyph} is the form of visual design to compose multivariable into a collection of unified visual symbols, known as a glyph.
+A glyph is intended for quick understanding and aligned comparison.
+Among glyph design, Chernoff Face~\cite{chernoff1973use} represents data variables by the different features of a cartoon face.
 Following the idea of Chernoff Face, we design a type of glyph, a graphical representation of people with specific individual characteristics.
 The idea behind using faces is that humans easily recognize faces and notice small changes without difficulty (\textit{C1}).
-Those visual profiles are intended for intutive visual understanding, from abstract to concrete and semantic understanding, to support users to target the interested individual groups effectively.
+Those visual profiles are intended for intuitive visual understanding, from abstract to concrete and semantic understanding, to support users to target the interested individual groups effectively.
 
@@
 The eight domains are encoded by visual symbols and organically organized in a human figure.
-There are bascially three types of variables to drive the figure, i.e., the numeric, categorical and boolean ones.
+There are basically three types of variables to drive the figure, i.e., the numeric, categorical and boolean ones.
 For numeric attributes such as income and education levels, visual symbol keeps consistent design but with changing visual variation, such as size, thickness.
-For the categorical attributes such as job, visual symbols are designed seperately for better semantic meaning.
+For the categorical attributes such as job, visual symbols are designed separately for better semantic meaning.
 For the boolean attribute like car, house, a symbol is designed to indicate its existence.
-With this consideration, the domains are designed as following:
+With this consideration, the domains are designed as follows:
 
@@
 
-% By different composition, stimulus pattern which has the abstract deomgraphic measurement of individuals.
+% By different composition, stimulus pattern which has the abstract demographic measurement of individuals.
 
 \begin{itemize}
-\item \textbf{Gender} the gender is visually mapped to the hair style of the avatar. 
+\item \textbf{Gender} the gender is visually mapped to the hairstyle of the avatar. 
 \item \textbf{Age} age is implied by the decoration on the hair.
 For the elder above 70, the hair is dyed to gray.
-For the youth beneath 18, a hair decoration is adapted for the different hair styles of girls and boys.
-\item \textbf{Education} The thickness of eye glasses is used to indicate the different levels in education.
+For the youth beneath 18, a hair decoration is adapted for the different hairstyles of girls and boys.
+\item \textbf{Education} The thickness of eyeglasses is used to indicate the different levels of education.
 \item \textbf{Job} The clothes is designed to imply the job of the individual. There are 9 types of clothes.
@@
 The textual number beneath indicates the population.
-It is found that the majority of workmen earn low salary and most of them have no residential license.
-On the contrary, for the officers, all of them have residential license and most of them has house.
+It is found that the majority of workmen earn a low salary and most of them have no residential license.
+On the contrary, for the officers, all of them have the residential license and most of them have a house.
 Some of the retired people are in old age.
-Most of managers are at undergraduates, even graduates.
+Most of the managers are at undergraduates, even graduates.
 
@@
 where $\alpha_i$ is the variance of the Gaussian that is centered on $x_i$.
-Specifically in our context, the high-dimensional Euclidean distances $\left \| x_i - x_j \right \|$ between $x_i$ and $x_j$ needs to be apdated the numerical and categorical characteristics.
+Specifically in our context, the high-dimensional Euclidean distances $\left \| x_i - x_j \right \|$ between $x_i$ and $x_j$ needs to be adpated the numerical and categorical characteristics.
 Characteristics such as age, income, are numerical and comparable, so the difference exactly explains when they are different.
-But the other characteritics, i.e.
-job, real estate, car, residention, are ordinal.
+But the other characteristics, i.e.
+job, real estate, car, residential, are ordinal.
 There is not the numeric order.
@@
 As Figure~\ref{fig:tsne}shows, all 21435 volunteers are embedded in the 2D view, where the closer two dots are, the more similar they are in the eight characteristics.
-Figure~\ref{fig:tsne} examplifies four features groups of dots in neighbour.
+Figure~\ref{fig:tsne} exemplifies four features groups of dots in a neighbor.
 
-Multiple views of abstract view, t-SNE proection and semantic data driven profile visualization are coordinated in a Cross-filter machinesm~\cite{Weaver2010}.
+Multiple views of abstract view, t-SNE protection, and semantic data-driven profile visualization are coordinated in a Cross-filter machinesm~\cite{Weaver2010}.
 It allows end-users to interactive drill-down into individuals with interested characteristics from multiple perspectives(\textit{C3}).
-Starting from the abstract criterion constraints, the scope of interest is narrowed down to individuals with(out) certian characteristics.
-And then further cross-filtering with semantically visual profiles can be performed, to check the combination of 8 characteristical variables.
+Starting from the abstract criterion constraints, the scope of interest is narrowed down to individuals with(out) certain characteristics.
+And then further cross-filtering with semantically visual profiles can be performed to check the combination of 8 characteristical variables.
 
@@
 \subsection{2.5D Spatial Visualization}
+\label{subsec:25D}
 
 Embedding multiple variables in the spatial map is a challenging problem.
-Distorting 2D spatial for better space usage, such as the partial route embedding~\cite{sun2016embedding} is an effective where there are a few local focis.
+Distorting 2D spatial for better space usage, such as the partial route embedding~\cite{sun2016embedding} is an effective method when there are a few local foci.
 When it comes to the global visualization, there is always a trade-off between occlusion-free and the compact spatial perception.
-Following the idea of stacking 2.5D space design~\cite{Tominski2012_stacking}, the space in this work is embedded in 2.5D space, to relax the z-axis for addtional abstract information encoding.
+Following the idea of stacking 2.5D space design~\cite{Tominski2012_stacking}, the space in this work is embedded in 2.5D space, to relax the z-axis for additional abstract information encoding.
 
 Figure~\ref{fig:2.5D}(a) shows the 2.5D visualization.
-The spatial map is consisted of Traffic Analysis Zone (TAZ), which is the unit of geography holding a certain number of people.
+The spatial map consists of Traffic Analysis Zone (TAZ), which is the unit of geography holding a certain number of people.
 For the 2.5D, each TAZ is grown as a prism whose height and color are developed to encode abstract information, e.g., the occurrence of visiting.
-With difference encoding choices, it is capable to visualize the colleration between spatial and different attributes (\textit{C4}).
-For example, in Figure~\ref{fig:2.5D}(a), prisms' height and color both encode the ratio of none-routine trips (such as go entertainment, go hosptial, etc.) in the whole.
+With difference encoding choices, it is capable to visualize the correlation between spatial and different attributes (\textit{C4}).
+For example, in Figure~\ref{fig:2.5D}(a), prisms' height and color both encode the ratio of none-routine trips (such as go entertainment, go hospital, etc.) in the whole.
 For better 3D visual perception, lighting is turned on.
@@
 
-Several interaction are integrated in the spatial view to alleviate the occlusion problem (\textit{C5}).
-The manipuation of 2.5D view supports users with rotate, zoom, pan operations, which are so continously flexible that users probably find a suitable observing point.
+Several interactions are integrated into the spatial view to alleviating the occlusion problem (\textit{C5}).
+The manipulation of 2.5D view supports users with rotate, zoom, pan operations, which are so continuously flexible that users probably find a suitable observing point.
 In the cases where occlusion is inevitable, an interaction named as \textit{Detail Slicing} is developed, as Figure~\ref{fig:2.5D}(b) shows.
@@
 To contextualize the cross-section, TAZs are visually adapted according to the intersection by ray casting.
-The TAZ in foreground will be hidden, the intersected TAZs will be fully visualized and the ones in the background will be in semi-transparency.
-% Brunch of TAZ with similar visiting pattern and purpose are grouped by an heuristic DB-Scan Algorithm in the context of TAZ.
-From a center TAZ, walk to neighbour TAZ to check whether aggregation or not.
-The aggregated TAZ brunch indicates the region visiting by the group of people in same purpose, which is often the popular traveling places.
+The TAZ in the foreground will be hidden, the intersected TAZs will be fully visualized and the ones in the background will be in semi-transparency.
+% Brunch of TAZ with similar visiting pattern and purpose are grouped by a heuristic DB-Scan Algorithm in the context of TAZ.
+From a center TAZ, walk to neighbor TAZ to check whether aggregation or not.
+The aggregated TAZ brunch indicates the region visiting the group of people in the same purpose, which is often the popular traveling places.
 The TAZ brunch is visualized...
@@
  To compare the mobility patterns across different groups of people, a Small Multiple dock is used to reserve the ever explored interesting result (Figure~\ref{fig:teaser}(f)).
-To simply the comparion over spatial distribution, the snapshot is also rendered in the 2.5D space, which maintains the same interactions as the main 2.5D space does.
+To simply the comparison over spatial distribution, the snapshot is also rendered in the 2.5D space, which maintains the same interactions as the main 2.5D space does.
 
- % In this view, it supports end-users to direct manipulate the space, e.g., zooming, panning, etc. Also, detail information about the visiting can be checked by direct clicking on the TAZ.
+ % In this view, it supports end-users to directly manipulate the space, e.g., zooming, panning, etc. Also, detail information about the visiting can be checked by direct clicking on the TAZ.

### 2019-04-19 answer.tex
Add files via upload
template.tex: add comment as discussed yesterday.

%%%%%%%%%%%%%%%%%%%%%%% answer list.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% For answering the review comments of JOV.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%

\documentclass[UTF8]{article}
\usepackage{geometry}
\geometry{left=1.0cm}

\usepackage{epstopdf}
\usepackage{mathptmx}
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
\usepackage{verbatim}

\usepackage{color}
\newcommand{\m}{\textcolor{red}}

\usepackage{array}
\usepackage{multirow}
\usepackage{tabularx}

\usepackage{algpseudocode}
\usepackage{natbib}
\usepackage[misc]{ifsym}

\begin{document}

\begin{table}[h]
\centering
\caption{focus on}
    \begin{tabular}{|p{4cm}|p{9cm}|p{4cm}|}
    \hline
    Question & Details & Answer\\
    \hline
    Techniques & (R1)The techniques presented in this paper, the glyph visualization, the Tsne, and the 2.5D spatial view, are not novel. They are inappropriately combined without any design rationale or considerations.\newline & A:\color{red}{Modifying.}\\

    The glyph design & (R1)The cartoon-style glyph visualization is particularly inefficiently designed. I had hard time to use this view to differentiate profile attributes for a moderate number of people. Basically it was too distracted and difficult to recall and concentrate. I would strongly suggest using simpler glyph designs or even textual labels to represent and compare multi-attributes for groups of targets.\newline & A:\color{red}{Add a radar chart for groups.}\\

    The TSNE & (R1)The Tsne view is a routine for multidimensional exploration and seems useful, but the usefulness is never mentioned in the case studies.\newline & A:\color{red}{Modifying.}\\

    2.5D view & (R1)The 2.5D spatial view is neither effective. It does not make sense to directly reuse the 2.5D-design in this application domain. (R2)The 2.5D design for visualizing geo data is really ineffective.\newline & A:\color{red}{Modifying.}\\

    Case studies to demonstrate its usefulness & (R1)I hardly found any interesting points or unexpected findings from the studies. Many conclusions have been studied and discussed in previous visual analytics papers  (R2)I don't how the system will be used in practice. The authors make this clear and conduct interview studies with the users to further demonstrate the effectiveness of the visualization.\newline & A:\color{red}{Modifying.}\\

    Case studies & (R1)There even lacks a brief description about any ``individual" characteristics. How would you explore and compare the mobility- characteristics-correlation at the individual level (as claimed as a major contribution of this paper)?\newline & A:\color{red}{Modifying.}\\

    The relationships among tasks, considerations and designs. & (R2)It is unclear how these tasks were obtained. It is unclear who will be the end-users. These are missing links between the tasks and the design considerations. These tasks and design considerations are unlinked to the design of the system.\newline  & A:\color{red}{Adding experts discussion to rewrite these parts.}\\

    Case studies & (R1)There even lacks a brief description about any ``individual" characteristics. How would you explore and compare the mobility- characteristics-correlation at the individual level (as claimed as a major contribution of this paper)?\newline & A: \\
    \hline
    \end{tabular}
\end{table}

\begin{table}[h]
\centering
\caption{not so important}
    \begin{tabular}{|p{3cm}|p{9cm}|p{5cm}|}
    \hline
    Question & Details & Answer \\
    \hline
    Writing & (R1)The paper is not well written. Typos, awkward sentences, and grammatical errors are throughout the paper.\newline & A: \\

    Related work & (R1)The related work is insufficiently discussed and is not well organized.\newline & A: \\

    \hline
    \end{tabular}
\end{table}

\end{document}
% end of file template.tex

### 2019-04-19 template.tex
Add files via upload
template.tex: add comment as discussed yesterday.

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{subfigure}

\usepackage{mathptmx}

\usepackage{times}

\usepackage{algorithm}% http://ctan.org/pkg/algorithm
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx

\usepackage{url}
\usepackage{color}
\newcommand{\m}{\textcolor{black}}

\usepackage{xcolor}
\newcommand{\add}{\textcolor{blue}}

\usepackage{multirow}
\usepackage{tabularx}

\usepackage{algpseudocode}
\usepackage{natbib}
\usepackage[misc]{ifsym}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Unfolding the City: \textcolor{blue}{Exploring ...(city usage) with Social Characteristics} Exploring Mobility Patterns with Individual Characteristics}
%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}

%\subtitle{Do you have a subtitle?\\ If so, write it here}

%\titlerunning{Short form of title}        % if too long for running head

\author{Qi Wang \and Min Lu \and Yang Yue \and Qingquan Li}

%\authorrunning{Short form of author list} % if too long for running head

\institute{Q. Wang \and Q. Li(\Letter) \at
              the State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, Wuhan, China, and also ShenZhen Key Laboratory of Spatial Smart Sensing and Services, ShenZhen University, Shenzhen 518060, China \\
              Tel.: +86-13297983047\\
              \email{wangqi@whu.edu.cn}, {liqq@szu.edu.cn}           %  \\
           \and M. Lu \and Y. Yue \at
              School of Architecture and Urban Planning, and also ShenZhen Key Laboratory of Spatial Smart Sensing and Services, ShenZhen University, Shenzhen 518060, China \\
              \email{minlu@szu.edu.cn}, {yueyang@szu.edu.cn}           %  \\
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
A city is shaped not only by its assembled infrastructures but also the people living inside it. People in a wide range of individual characteristics visit places with different weights and preferences, sculpturing the city into a space of diverse mobility patterns. Different from the well study of anonymous travel behaviors, the mobility patterns of characterized individuals, is less studied because of the challenges in collection and analysis of data with privacy. In this work, we take a step forward and perform an online census to collect individual profiles and movements from large-scale volunteers. Then we develop a visual analytic system to investigate the mobility patterns of groups by specifying characteristics. To facilitate the identification of characterized groups, individuals are embedded in t-SNE projection for an abstract overview as well as drawn as vivid graphics by a data-driven profile method for detail examination. A 2.5D spatial visualization is proposed to maintain a compact multivariable analysis by relaxing the z-axis to encode information, such as visiting frequency, demands, traveling distance, etc. Together with the cross-filter and flexible 2.5D interactions, the effectiveness and usability of the system are well demonstrated by a study made in Shenzhen.

\keywords{Visual analytics \and mobility pattern \and individual characteristics \and city }
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\label{intro}
The science fiction \textit{Folding Beijing}~\citep{hao2016_foldingbeijing} depicts a world where three classes of people live in independent spatial-temporal patterns, though sharing the same earth surface. This is an artistical metaphor for one potential fact that people make different decisions in visiting places according to individual determinants, such as social, economic, educational factors, etc. This phenomenon has attracted the research interest for a long time in the sociological field. Back to 1970, Pahl~\citep{pahl1975whose} posed the question `whose city` and interest in understanding the territorial inequalities. Contemporary contestation also continually raise the banner `The City Belongs to All!'~\citep{Mayer2017_whosecity}. Having a good understanding of how the mobility patterns relate to characterized individuals sheds light on region utilization, diversity mix-up, and opportunities promotion.

In the past decades, the power of visual analytics in exploring spatial-temporal data has been recognized and well developed. Transportation problems are answered by various movement data, such as traffic jams in taxi GPS trajectoires~\citep{wang2013visual}, interchanging flows in public transportation~\citep{zeng2013visualizing}, etc. The presence of social media applications fuels the spatial analysis with rich semantic texts, so researchers get the chances to explore the thematic meaning of the moving behavior, such as events~\citep{chen2017map} or topics~\citep{bosch2013scatterblogs2}. Those works essentially contribute in deepening the contextual understanding of moving activity. But they rarely combine the mobility with individuals' characteristics because which cannot be 100\% inferred from social media profiles. There is still a research gap in exploring the relationship between mobility pattern and characteristics.

In this work, we contextualize the analysis of mobility pattern in the backcloth of individual characteristics. Our motivation is to fuse the movement data with individuals' profiles in an attempt to ascertain the dynamics pattern of groups with different characteristics. To this, we need to get the characterized information of movers. The sensitivity issue in privacy data is one of the main challenges. The conventional offline census takes lots of effort and too much time to be out of date. With the wide use of the mobile device, it is possible to count information online. In this work, with a census survey released via social media application, we ran an online demographical collection campaign. Then we developed a visual analytics system to explore the mobility patterns centered around people. The system incorporates visualizations of individuals' characteristics, including t-SNE for an overview and data-driven profile visualization for the detailed check, as well as 2.5D spatial visualization to explore the mobility patterns. Finally, applying our method in Shenzhen, several cases are derived to demonstrate the powers of our method. There are two contributions of this work:

(1) investigate mobility patterns with characteristics, which is a natural step into research of social understanding of the city.

(2) develop a visual analytic system, whose effectiveness and usability is well demonstrated by a study made in Shenzhen.

\section{Related work}

This work concerns the research topic of spatial data visual analytics. Spatio-temporal data has three components, i.e., spatial, temporal and thematic~\citep{andrienko2013visual}. Lots of related work focus on the spatio-temporal analysis in movement data, in the absence of thematic information. The presence of geotagged social media data flourishes the exploration of thematic information along with movement. By analyzing the texts, those work explain what drive the moving activities or what is resulted from. This work continues the thematic research in movement data but focuses more on individual characteristics. Landed by a census experiment, this work is able to analyze the profile information directly, to get rid of indirect data inferred from social media data as other related works do.

\subsection{Movement data analysis}
 With the development of location-acquisition techniques, massive spatial trajectories are collected, to keep track of the trajectories of various moving objects. Many techniques have been proposed to process, mine trajectory~\citep{Zheng2015_trajectory}. In the field of visualization and visual analytics, spatial visualizations are specifically designed for the time, locations, spatial-temporal information and other properties in the traffic data~\citep{chen2015survey}. A large number of visual analytics tools and applications cover situation-aware exploration, pattern discovery and traffic situation monitoring. Wang et al~\citep{wang2013visual} extract the traffic jam propagation graph extraction to reveal underlying data patterns. Guo et al.~\citep{guo2011tripvista} and Zeng et al.~\citep{zeng2013visualizing} construct geographical regions and visually aggregate the in-between movements as flows. To discover the route travel patterns, Lu et al.~\citep{lu2015trajrank} propose TrajRank to explore the route travel behavior based on ranking. For multiple routes, Liu et al.~\citep{liu2011_routediversity} study the route diversity between locations and Lu et al.~\citep{Lu2017_multipleroute} explore the route choice behavior among multiple routes.

\subsection{Geo-tagged Social Media Data Analysis}
As the presence of social media services, social media data with geo-tags are collected to track people's movements in daily lives. As an analog of remote sensing data in social science research, the geospatial big data has been proposed as social sensing ~\citep{liu2015social}. Hence, analyzing movement information along with rich text has become a hot research area in recent years. Those works infer thematic information from the semantic texts. Cao et al.~\citep{cao2012whisper} propose \textit{Whisper} for tracing the pathways of tweets on a spatial hierarchical layout, to investigate how information flow among multiple places. Krueger et al.~\citep{krueger2014visual} used GPS and location-based service data to support the analysis of movement behaviors. Chen et al.~\citep{chen2016interactive} present a visual analytics system to support the exploration of sparsely sampled trajectory from social media. Some other researchers tend to infer real information, such as names, gender, etc, from social media data~\citep{peddinti2014internet}, to break down the demographic characteristics of social media users. Luo et al.~\citep{luo2016explore} derive race, gender, and age as three demographics dimensions to analyze its impact on the urban human mobility patterns. Since real information is not enforced in social media, the wrong inferring is inevitable. Longley et al.~\citep{Longley2015}~\citep{Paul2016_twitter} identifies and assess the biases inherent in social media usage in social research and evaluate the deployment of social media data in research applications.

\section{Online Census}
The advent of mobile sensing techniques and social media applications makes it possible to collect spatial data from the social media source. Complementary to the conventional census, it brings the benefit of larger sampling frequency and a broader range in terms of space and time. It is possible to reach a wide range of individuals and collect the movement in human inactive time, such as the mid-night.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/survey_app}
 \caption{Census Interface: (a) personal characteristics collecting page; (b) trips collecting page; (c) credit system page}
 \label{fig:app}
\end{figure}

In this work, we perform the census survey in Shenzhen, which is one of the most modern metropolia in China. The experiment is deployed on Wechat, a widely used social media application. Figure~\ref{fig:app} shows the data collecting interfaces. Each individual hands in his or her personal characteristics. For privacy issue, all detailed personal information are desensitized to categorical levels (Figure~\ref{fig:app}(a)).

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data_over}
 \caption{Profile of Individual: eight individual characteristics enrich the analysis of mobility patterns}
 \label{fig:data_over}
\end{figure}

\textbf{Individual Characteristics} Figure~\ref{fig:data_over} lists the \textit{eight domains}, including social, economic and demographic aspects, to give a generalized description of the individual characteristics. The profile will serve as the ingredients for the analysis of mobility patterns over diverse individuals.

\textbf{Traveling Trips} Besides to those individual characteristics, each individual can upload dynamic traveling trips (Figure~\ref{fig:app}(b)). Each trip requires the information of \textit{start/end location}, \textit{start/end time}, \textit{traveling purpose}. To encourage the trip uploading, a credit system retains the contribution of individuals on trips and rewards the volunteers with the top credits (Figure~\ref{fig:app}(c)).

\subsection{Basic Statistics of Data}

Over the releasing time period from \m{2015-11 to 2016-01}, 21435 individuals (48\% females and 52\% males) were reached and \m{229155} trips are collected. Each volunteer contributes \m{11} trips average.

Our case-study data is confined to a small proportion of Wechat users who opt to contribute their information and trips.
Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\citep{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of the population in the city.

% In the report (looking for some report), the penetration of mobile device is \m{XXX}, almost every XX people got a Mobile Phone in the urban.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data1}
 \caption{Age and Education Distribution: (a) age; (b) education}
 \label{fig:data_age_edu}
\end{figure}

Figure~\ref{fig:data_age_edu} gives the distribution of age and education over the population. It shows that samples cover a wide range of ages, dominating between 18 to 45. There is also a few records pertaining to individuals below the age of 18 or above 70. The distribution follows the fact that Shenzhen is a city where the majority is young people. According to the 2015 Annual Census Statistics report\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5. Figure~\ref{fig:data_age_edu} gives the distribution of education levels, ranging from low to high. The technical college and university dominate the samples at the 61\% occupancy rate.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data2}
 \caption{Job and Income Distribution: (a) job; (b) income}
 \label{fig:data_job_inc}
\end{figure}

Figure~\ref{fig:data_job_inc}(a) shows the job types of sampled individuals, who are servants, workers, officers, businessmen and so on. The covering of jobs is pretty wide. Figure~\ref{fig:data_job_inc}(b) gives the radar diagram of the annual pay. The majority get paid below 200 000. Individuals with higher salary are also reached in our census.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data3}
 \caption{Statistics of Trips: (a) start time of trips; (b) purpose of trips; (c) distribution of origins/destinations }
 \label{fig:data_geometry}
\end{figure}

Figure~\ref{fig:data_geometry} shows the basic statistics related to trips. In Figure~\ref{fig:data_geometry}(a), the active traveling time (here, we take the start time as the representative of active time) follows the common knowledge of urban life. There are obvious morning and late afternoon peaks. Figure~\ref{fig:data_geometry}(b) gives the counting of different traveling purposes. 95\% trips are tagged with clear raveling purpose in the data. 33\% are going home and 37\% are going to work. Besides this kind of routine traveling, there are also substantial trips such as going shopping, going the hospital, etc. Figure~\ref{fig:data_geometry}(c) shows the spatial distribution of the origins and destinations. It is found that more dots are located in Futian and Nanshan districts, the city's heart than the surrounding areas. This is consistent to Batty's exposition of the focus of city networks and interaction patterns~\citep{batty2013new}.

% Trips are uploaded in a wide range of purpose in addition to home, work, but also includes XX entertainment, visiting, etc. The diverse purposes make it possible to characterize the flows across the city between different functional places.

Because there is always inevitable bias inherent in fully representing the ground truth of the population, the preliminary statistical analysis shows positive sign of a relatively even sampling of the population.

\section{Visual design}

\textcolor{blue}{Adding a background. Expert discussion. Summarize the tasks below.}

The design of the system is driven by tasks, to align the analysis of mobility patterns with individual characteristics. Before diving into the design of the system, we introduce the couple of specifical tasks the system intended for.

\begin{itemize}
\item \textit{Task 1: Identify the group with specific individual characteristics}: to get groups of people with common or close attributes, to explore the correlation among individual characteristics.
\item \textit{Task 2: Explore the mobility patterns of a group}: to explore where, how and why an interested group go in the city.
\item \textit{Task 3: Compare mobility patterns among multiple groups}: to know the similarities and differences between different groups in their mobility patterns, to investigate the relationship between movement and individual characteristics.
\end{itemize}

\subsection{Design Considerations}

With these three tasks, we derive following design considerations:

\begin{itemize}
\item \textit{Intuitive perception of an individual as an organic complex (C1)}: the system should make use of users' daily life experience in knowing people to provide intuitive visualization, instead of the lifeless representation by number. The visual design needs to help end-users to pick desirable ones from the mass.
\item \textit{Good overview of the multivariate individuals (C2)}: following the visual analytics manta by Shneiderman~\citep{RN459}, it is very important to provide a good overview of all the individuals then the users know where to explore.
\item \textit{Effective multivariable cross-filter for individual characteristics (C3)}: there are eight domains to describe an individual. The system is supposed to provide a straight-forward way for easy filtering by the eight criteria.
\item \textit{Compact visualization of mobility patterns in the constraint of spatial space (C4)}: the analysis of mobility patterns not only includes the conventional spatial and temporal dimensions, but also other abstract dimensions, e.g., travel purpose, visiting frequency, etc. The system should handle a compact layout to support the easy correlation between spatial and abstract information.
\item \textit{Flexible interactions to explore the mobility patterns either within one group or between groups (C5)}: to support the comparison among groups, \textit{Task 3}, the system should maintain flexible interactions which allow the end-users to explore freely.
\end{itemize}

% Classification method, flow clustering method, Semantic representation.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\linewidth]{pictures/teaser.eps}
 \caption{System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) a t-SNE visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) data-driven profiles support users with organic individual perception; (d) group of interested individuals can be saved; (e) movement of the chosen group is visualized and explored in 2.5D main view; (f) a dock is provided to restore and compare findings; (g) different choices of 2.5D encoding can be selected.}
 \label{fig:teaser}
\end{figure}

With those design considerations, we develop a visual analytics system as Figure~\ref{fig:teaser} shows. It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}). In the individual panel, interactive infographics, t-SNE visualization, and data-driven profiles support users to narrow the scope down to groups of individuals with interested characteristics. With the chosen group of individuals, its moving related information is visualized and explored in a 2.5D spatio-temporal view.

% overview of the data. Encode information but also allow users to set multiple criteria (\textit{C1}). Support users to slice the data by different domains.}
% Semantic understanding of social characteristics.

\subsection{Data-driven Profile Visualization}
\textcolor{blue}{Using two scales. Glyph-based visualization for finer scale, radar-based visualization for coarser scale.}

Glyph-based visualization~\citep{borgo2013glyph} is the form of visual design to compose multivariable into a collection of unified visual symbols, known as a glyph. A glyph is intended for quick understanding and aligned comparison. Among glyph design, Chernoff Face~\citep{chernoff1973use} represents data variables by the different features of a cartoon face. Following the idea of Chernoff Face, we design a type of glyph, a graphical representation of people with specific individual characteristics. The idea behind using faces is that humans easily recognize faces and notice small changes without difficulty (\textit{C1}). Those visual profiles are intended for intuitive visual understanding, from abstract to concrete and semantic understanding, to support users to target the interested individual groups effectively.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/design_profile}
 \caption{Design Profile: the eight characteritical domains are encoded and organized in an organic human figure.}
 \label{fig:design_profile}
\end{figure}

Figure~\ref{fig:design_profile} shows the legend for the user profile. The eight domains are encoded by visual symbols and organically organized in a human figure. There are basically three types of variables to drive the figure, i.e., the numeric, categorical and boolean ones. For numeric attributes such as income and education levels, visual symbol keeps consistent design but with changing visual variation, such as size, thickness. For the categorical attributes such as job, visual symbols are designed separately for better semantic meaning. For the boolean attribute like car, house, a symbol is designed to indicate its existence. With this consideration, the domains are designed as follows:

% For numeric attributes.

% By different composition, stimulus pattern which has the abstract demographic measurement of individuals.

\begin{itemize}
\item \textbf{Gender} the gender is visually mapped to the hairstyle of the avatar.
\item \textbf{Age} age is implied by the decoration on the hair. For the elder above 70, the hair is dyed to gray. For the youth beneath 18, a hair decoration is adapted for the different hairstyles of girls and boys.
\item \textbf{Education} The thickness of eyeglasses is used to indicate the different levels of education.
\item \textbf{Job} The clothes is designed to imply the job of the individual. There are 9 types of clothes.
\item \textbf{Belongings} for real estate, car, residential license are considered as the belongings to the individual, so we design each of them as an add-on decoration to imply whether the individual has it or not.
\item \textbf{Income} a money symbol is used to represent the income, whose size encodes the income level. The more money an individual earns, the larger the symbol is.
\end{itemize}

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=0.6\columnwidth]{pictures/design_example}
 \caption{Representative figures with the top 10 largest population in four jobs}
 \label{fig:div_example}
\end{figure}

With the visual mapping, the profile varies from individual to individual. By concretizing the attributes which otherwise is too abstract to percept, users can scan and search for interesting target effectively. Figure~\ref{fig:div_example} lists the figures with the top 10 largest population in some job. The textual number beneath indicates the population. It is found that the majority of workmen earn a low salary and most of them have no residential license. On the contrary, for the officers, all of them have the residential license and most of them have a house. Some of the retired people are in old age. Most of the managers are at undergraduates, even graduates.

\subsection{t-SNE Projection of Individuals}
\textcolor{blue}{Not tsne. A octagon radar graph to position all citizens. A clustering algorithm for commend similar persons into a new group.(maybe: interactions to set the weight of each characteristic)}

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/tsne}
 \caption{t-SNE project with four groups of the interest: (a) t-SNE project }
 \label{fig:tsne}
\end{figure}

In our case, each individual can be denoted as a vector $x_i$ with eight factors, and we get high dimensional data set $X={x_1, x_2, ..., x_n}$. The dimensionality reduction techniques are to preserve the local structure of high dimensional data in low dimensional space, which are efficient approaches to provide a good overview of the multivarible individuals (\textit{C2}). We adapt t-SNE project~\citep{maaten2008visualizing} to project $X$ as two-dimensional dots $Y={y_1, y_2, ..., y_n}$. One of steps in t-SNE is to compute the conditional probabilities to represent the similarity based on the distance between high dimenional datapoints. The conditional probability $p_{j\mid i}$ between $x_j$ and $x_i$ is given by:

\begin{equation}
p_{j\mid i} = \frac{exp({\left \| x_i - x_j \right \|}^2/2\alpha_i ^{2})}{\sum _{k\neq i}exp({\left \| x_i - x_k \right \|}^2/2\alpha_i ^{2})}
\end{equation}

where $\alpha_i$ is the variance of the Gaussian that is centered on $x_i$. Specifically in our context, the high-dimensional Euclidean distances $\left \| x_i - x_j \right \|$ between $x_i$ and $x_j$ needs to be adpated the numerical and categorical characteristics. Characteristics such as age, income, are numerical and comparable, so the difference exactly explains when they are different. But the other characteristics, i.e. job, real estate, car, residential, are ordinal. There is not the numeric order. For example, the job distance from a manager to a businessman and a workman is not comparable, which is considered the same distance, i.e., set to 1.

As Figure~\ref{fig:tsne}shows, all 21435 volunteers are embedded in the 2D view, where the closer two dots are, the more similar they are in the eight characteristics. Figure~\ref{fig:tsne} exemplifies four features groups of dots in a neighbor.

Multiple views of abstract view, t-SNE protection, and semantic data-driven profile visualization are coordinated in a Cross-filter machinesm~\citep{Weaver2010}. It allows end-users to interactive drill-down into individuals with interested characteristics from multiple perspectives(\textit{C3}). Starting from the abstract criterion constraints, the scope of interest is narrowed down to individuals with(out) certain characteristics. And then further cross-filtering with semantically visual profiles can be performed to check the combination of 8 characteristical variables.

\subsection{2.5D Spatial Visualization}
\textcolor{blue}{Just a map. Clustering or Grid. 2.5D for stack??}

\label{subsec:25D}

\begin{figure}[htb!]
\centering
\subfigure[]{
\resizebox*{9cm}{!}{\includegraphics{pictures/space1.eps}}}\hspace{5pt}
\subfigure[]{
\resizebox*{9cm}{!}{\includegraphics{pictures/space2.eps}}}\hspace{5pt}
\caption{2.5D Spatial Visualization: (a) 2.5D spatial visualization with z-axis to encode addition information; (b) detail slicing in 2.5D space.}
\label{fig:2.5D}
\end{figure}

Embedding multiple variables in the spatial map is a challenging problem. Distorting 2D spatial for better space usage, such as the partial route embedding~\citep{sun2016embedding} is an effective method when there are a few local foci. When it comes to the global visualization, there is always a trade-off between occlusion-free and the compact spatial perception. Following the idea of stacking 2.5D space design~\citep{Tominski2012_stacking}, the space in this work is embedded in 2.5D space, to relax the z-axis for additional abstract information encoding.

Figure~\ref{fig:2.5D}(a) shows the 2.5D visualization. The spatial map consists of Traffic Analysis Zone (TAZ), which is the unit of geography holding a certain number of people. For the 2.5D, each TAZ is grown as a prism whose height and color are developed to encode abstract information, e.g., the occurrence of visiting. With difference encoding choices, it is capable to visualize the correlation between spatial and different attributes (\textit{C4}). For example, in Figure~\ref{fig:2.5D}(a), prisms' height and color both encode the ratio of none-routine trips (such as go entertainment, go hospital, etc.) in the whole. For better 3D visual perception, lighting is turned on. Also, a lid is laid on the top of each prism to clearly bound its extent at the z-axis.

Several interactions are integrated into the spatial view to alleviating the occlusion problem (\textit{C5}). The manipulation of 2.5D view supports users with rotate, zoom, pan operations, which are so continuously flexible that users probably find a suitable observing point. In the cases where occlusion is inevitable, an interaction named as \textit{Detail Slicing} is developed, as Figure~\ref{fig:2.5D}(b) shows. Detail Slicing is the operation to put a cross-section in the 2.5D space to expose the TAZ inside. To contextualize the cross-section, TAZs are visually adapted according to the intersection by ray casting. The TAZ in the foreground will be hidden, the intersected TAZs will be fully visualized and the ones in the background will be in semi-transparency.

To compare the mobility patterns across different groups of people, a Small Multiple dock is used to reserve the ever explored interesting result (Figure~\ref{fig:teaser}(f)). To simply the comparison over spatial distribution, the snapshot is also rendered in the 2.5D space, which maintains the same interactions as the main 2.5D space does.

\section{Case study}

In this section, we apply the method described above to study the case of Shenzhen. We introduce the several cases to demonstrate the usage and effectiveness of the system.

\subsection{Case 1: Work-life Balance VS Income/Education}
\textcolor{blue}{theme: Using similar social characteristics to put citizens into target groups. change the name of the section. Using View1(selecting bar), View2(radar), View3(map, to see the distribution of home and work place)}

This work is inspired and motivated by the implication in science fiction~\textit{Folding Beijing}, which is that people are categorized into three classes and behave in the parallel spatial-temporal patterns. The first cast explores whether the folding city exists in reality or not.

\begin{figure}[htb!]
 \centering
 \includegraphics[width=\columnwidth]{pictures/case1_1}
 \caption{Four Groups Divided by Income and Education Characteristics}
 \label{case11}
\end{figure}

Although it is incomplete, income and education are two of the most essential characteristics to tag an individual with a good resource or not.
As Figure~\ref{case11} shows, taking income and education as the two dimensions, taking 300K yuan as the border between high and low income and an undergraduate bachelor degree as the border between high and low education level, four different groups are generated in the four quadrants. In the first quadrant, individuals are rich and well educated, who are in a group of so-called \textit{top aristocracy}. The second quadrant holds the group of \textit{new rich}, i.e., individuals with high income but low education income. In the third quadrant, they are the \textit{underclass} who has both low income and education level. The fourth quadrant is \textit{Antizen}, which is a new word to describe people have a good education but earn little.

Figure~\ref{case11} shows the top 12 profiles with the maximum population in each group. In each group, other characteristics surprisingly demonstrate the high correlation to income and education. For example, almost all of the \textit{top aristocracy} is with the residential license,  house, and car. On the contrary, \textit{underclass} do not have the residential license residence, neither the house nor the car. Most of \textit{New rich} has a house and work in the service industry.

Before diving into the complex mobility pattern analysis, we explore the home distribution of the four groups. As Figure~\ref{case12} shows, \textit{top aristocracy} and most of \textit{new rich} live concentrated in the downtown area of Shenzhen, where the living cost is higher, especially the housing cost. A small part of \textit{new rich} lives far away from the downtown, maybe because they don't have to work in downtown. The \textit{underclass} distribute more dispersively all over the whole city. Compared to the rich, they prefer the outer space because of the lower living cost. Lots of \textit{antizen} live in Nanshan District, where there are many universities and high-tech industrial parks full of well educated people.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case1_2}
 \caption{Home Distributions of the Four Groups}
 \label{case12}
\end{figure}

To have a better knowledge of mobility patterns of the four groups, trips are categorized into three categories, ``home", ``work'' for regular trips with the purpose of going home, work (or school for students), ``other'' for irregular trips with the purpose of shopping, visiting friends. Figure~\ref{case13}(a) shows the 2.5D overview of the three kinds of traveling categories. Each TAZ is grown to the same height, i.e., the unit one, and the height proportion of each traveling categories encodes the percentage of certain purpose in the whole, pink for ``others'', blue for ``work'' and green for ``home''. Although inside TAZ prisms are blocked in the Figure~\ref{case13}, our attention is drawn to the lifestyle of \textit{New Rich}. It is founded that the \textit{New Rich} travel for ``other'' purpose a lot, compared to other groups. To explore further, the detail slicing (introduced in Section~\ref{subsec:25D}) is applied to the four groups. Figure~\ref{case13}(b) shows three slices. It can be seen that individuals with low income (\textit{underclass} and \textit{antizen}) spend relatively more time on work, especially the \textit{underclass}. Working percentage is very small in-group \textit{new rich}. They live a more diverse lifestyle because they do many other things (the pink ones) except working.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case1_3}
 \caption{Mobility Patterns of ``work", ``home" and ``not essential" of the Four Groups: (a) the overview of the three pecentage; (b) three slices for detailed comparison.}
 \label{case13}
\end{figure}

\subsection{Case 2: Home-work Distance VS Income/House}
\textcolor{blue}{theme: the distribution of citizens' mobility when moving with a given purpose; or: attractiveness of region. Given a group, interaction with purpose, show distribution of each region. Using View3(map, each region with a radar graph to show distance distribution). VIEW4:??(od matrix?)(finer level?)}

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case2}
 \caption{Home-work distances of different groups: (a) with different salary levels; (b) with or without house.}
 \label{case2}
\end{figure}

Home-work distance is an essential metric in economics, geography, and sociology. It refers to the distance between house and workplace. It is influenced by many factors like transportation, housing, land use, etc. Understanding the home-work distance of a region helps to evaluate whether the region is well planned or not. In this case, we demonstrate our system's help in home-work distance understanding.

Considering income potentially determines where people live, we use income as the characteristics to select three groups, the group over 500K, the group during 200-300K and the group less than 100K. In Figure~\ref{case2}, the height of the bar stands for visiting frequency of the TAZ and its color encodes the average home-work distance, red for close and yellow for far. As Figure~\ref{case2}(a) shows, for all the three groups in different income levels, most of the TAZs have dark red or red color which indicates the home-work distance is generally short, especially in downtown. Only those with less than 100K salary work outside the center, such as the space in the green circle. When comparing the three groups in the downtown area, it is seen that it takes more time to go to work in Futian District as the decrease of the income.

We explore the home-work distance of groups with and without a house.
Figure~\ref{case2}(b) shows the close-up views. It is found that the Nanshan District has a shorter home-work distance for individuals without a house, while Futian District has shorter for those with a house. Nanshan is relatively newer to Futian so that there might be more easily-accessible houses to be rent.

\subsection{Case 3: Life-style VS Jobs}
\textcolor{blue}{theme: what persons do? trip purpose sequence? Given a group, interaction with purpose, show distribution of each region. Using View3(map, 2.5D), View4(a stacked bar to show quantity of each kinds of purpose.)}

In this case, we explore the correlation between mobility patterns with the job, to see whether the job has an impact on the movement. Officer, workman, student, and businessman are selected as examples and the population of trips for certain purposes is shown In Figure~\ref{case3}. The height of bars encodes the amount of visit to each TAZ, and color encodes the traveling purpose. There are 10 different kinds of traveling purposes. For quick linking between color and purposes, the regular trips such as go to work, school and home are dyed in cold color, and the irregular trips such as go shopping, hospital, etc, are dyed in the warm color. As Figure~\ref{case3} shows, for officers, the TAZs changes dramatically in height. Some TAZs have much more visiting than others because officers are more constrained to work in some buildings than individuals with other jobs. The relative percentage of irregular activity differs for the four groups. For Workman, about 80 percent of movements are the regular purpose, either go to work or go back home. For students, the percentage becomes to be about 50 percentage. Compared to them, officer and businessman have more flexible and diversified lifestyle.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case3}
 \caption{Trip purposes distribution of four groups with different jobs}
 \label{case3}
\end{figure}

Next, we concentrated on one purpose to see whether it is related to jobs. Here we use ``dinner or entertainment" as the example. As Fig \ref{case32} shows, the height of TAZ bars represents the visiting amount of trips for dinner or entertainment. Color stands for moving distance to reach this TAZ. As we can see, officers prefer to entertain in the downtown area, while workmen cover a larger area. Students tend to concentrate on Nanshan district, probably near schools. For the businessmen, they go lots of places for dinner or entertainment. The biggest difference with other groups is that they would travel a long distance to go somewhere far from downtown areas.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case3_2}
 \caption{The ``dinner or entertain" purpose of four groups with different jobs}
 \label{case32}
\end{figure}

\section{Conclusion}
\label{sec:conclusion}

This work demonstrates a throughout research flow from data collection, basic analysis to deep visual analysis of mobility patterns with individual characteristics. Considering the irresistible trend in mixing social data and spatial data to solve the urban problem, this work takes one step forward in exploring the relationship between movement and individuals' characteristics, which is rarely touched by previous geo-tagged social media visual analytics. The design of the visual analytic system is driven by three tasks about individuals and mobility patterns. Tapping into our daily experiences, the data-driven profile visualization provides an organic and intuitive representation of individuals. Its effectiveness in identifying similar or abnormal individuals from the mass has been demonstrated. The design of 2.5D spatial visualization continues the exploration of the typical research problem how to visualize spatial information and abstract information together. Although it is not a one-step solution, 2.5D visualization with the detail slicing is able to provide an occlusion-free analysis with spatial context preserved.

Our current research focuses on fundamental facets of the mobility patterns and doesn't draw a strong conclusion on the correlation between mobility pattern and individual characteristics. In next step, more delicate algorithms will be involved to extract high-level mobility patterns, such as the frequent visiting sequence of an individual group, etc. On the other hand, the data we used in this work shows its potential in representing the population. As the next step, research effort can be put into a more serious verification of how small sampled data can represent a large population.

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

% BibTeX users please use one of
\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
\bibliography{main}
%\bibliography{test}

\end{document}
% end of file template.tex

### 2019-04-20 answer.tex
revision begin

@@
     \hline
-    Techniques & (R1)The techniques presented in this paper, the glyph visualization, the Tsne, and the 2.5D spatial view, are not novel.
-They are inappropriately combined without any design rationale or considerations.\newline & A:\color{red}{Modifying.}\\
 
-    The glyph design & (R1)The cartoon-style glyph visualization is particularly inefficiently designed.
-I had hard time to use this view to differentiate profile attributes for a moderate number of people.
-Basically it was too distracted and difficult to recall and concentrate.
-I would strongly suggest using simpler glyph designs or even textual labels to represent and compare multi-attributes for groups of targets.\newline & A:\color{red}{Add a radar chart for groups.}\\
+    Design Rationale & (R1) The techniques presented in this paper, the glyph visualization, the Tsne, and the 2.5D spatial view, are not novel.
+They are inappropriately combined without any design rationale or considerations.\newline & A:\color{red}{We performed a in-depth interview with domain exports to understand their demands (added as a new Subsection XX), and refine the system design by several iterations.
+The visual design is reasoned according to the demands and derived rationales (updated in Section XX}\\
 
-    The TSNE & (R1)The Tsne view is a routine for multidimensional exploration and seems useful, but the usefulness is never mentioned in the case studies.\newline & A:\color{red}{Modifying.}\\
-
-    2.5D view & (R1)The 2.5D spatial view is neither effective.
-It does not make sense to directly reuse the 2.5D-design in this application domain.
-(R2)The 2.5D design for visualizing geo data is really ineffective.\newline & A:\color{red}{Modifying.}\\
-
-    Case studies to demonstrate its usefulness & (R1)I hardly found any interesting points or unexpected findings from the studies.
-Many conclusions have been studied and discussed in previous visual analytics papers  (R2)I don't how the system will be used in practice.
-The authors make this clear and conduct interview studies with the users to further demonstrate the effectiveness of the visualization.\newline & A:\color{red}{Modifying.}\\
-
-    Case studies & (R1)There even lacks a brief description about any ``individual" characteristics.
-How would you explore and compare the mobility- characteristics-correlation at the individual level (as claimed as a major contribution of this paper)?\newline & A:\color{red}{Modifying.}\\
-
-    The relationships among tasks, considerations and designs.
-& (R2)It is unclear how these tasks were obtained.
+    Design Rationale & (R2) It is unclear how these tasks were obtained.
 It is unclear who will be the end-users.
@@
 
-    Case studies & (R1)There even lacks a brief description about any ``individual" characteristics.
-How would you explore and compare the mobility- characteristics-correlation at the individual level (as claimed as a major contribution of this paper)?\newline & A: \\
+    The glyph design & (R1) The cartoon-style glyph visualization is particularly inefficiently designed.
+I had hard time to use this view to differentiate profile attributes for a moderate number of people.
+Basically it was too distracted and difficult to recall and concentrate.
+I would strongly suggest using simpler glyph designs or even textual labels to represent and compare multi-attributes for groups of targets.\newline & A:\color{red}{We took reviewer' comment into consideration, and added a star-like glyph designed (Section XX), to compensate the understanding of individuals' attributes from the abstract view.}\\
+
+    The TSNE & (R1) The Tsne view is a routine for multidimensional exploration and seems useful, but the usefulness is never mentioned in the case studies.\newline & A:\color{red}{We clarified the usage of T-sne projection in Case 1, where T-sne helps to find groups with interested high dimensional attributes.}\\
+
+    2.5D view & (R1) The 2.5D spatial view is neither effective.
+It does not make sense to directly reuse the 2.5D-design in this application domain.
+(R2)The 2.5D design for visualizing geo data is really ineffective.\newline & A:\color{red}{We took reivewer' advices of ineffective 2.5D and changed the spatial view to conventional 2D view.}\\
+
+    Case studies to demonstrate its usefulness & (R1)I hardly found any interesting points or unexpected findings from the studies.
+Many conclusions have been studied and discussed in previous visual analytics papers  \newline & A:\color{red}{We updated the case studies, including the observations in ..., ....}\\
+
+    Case studies & (R1) There even lacks a brief description about any ``individual" characteristics.
+How would you explore and compare the mobility- characteristics-correlation at the individual level (as claimed as a major contribution of this paper)?\newline & A:\color{red}{We enriched the exploration in ``individual" movement by...
+(Section XX).}\\
+
+    User Study & (R2) I don't how the system will be used in practice.
+The authors make this clear and conduct interview studies with the users to further demonstrate the effectiveness of the visualization.
+& A:\color{red}{We performed an interview with domain experts in usage, and reported their feedback in Section XXX.}\\
+
     \hline

### 2019-04-20 manuscript/overview.tex
revision begin

--- 2018-06-04 manuscript/visualdesign.tex
@@
-\section{Visual Design}
+\section{Overview}
+
+\lmc{Add a paragraph to introduce the motivation of this work, where we derive the tasks via the interview with domain exports.}
 
@@
 With the chosen group of individuals, its moving related information is visualized and explored in a 2.5D spatio-temporal view.
-
-% overview of the data. Encode information but also allow users to set multiple criteria (\textit{C1}). Support users to slice the data by different domains.}
-% Semantic understanding of social characteristics.
-
-\subsection{Data-driven Profile Visualization}
-
-Glyph-based visualization~\cite{borgo2013glyph} is the form of visual design to compose multivariable into a collection of unified visual symbols, known as a glyph.
-A glyph is intended for quick understanding and aligned comparison.
-Among glyph design, Chernoff Face~\cite{chernoff1973use} represents data variables by the different features of a cartoon face.
-Following the idea of Chernoff Face, we design a type of glyph, a graphical representation of people with specific individual characteristics.
-The idea behind using faces is that humans easily recognize faces and notice small changes without difficulty (\textit{C1}).
-Those visual profiles are intended for intuitive visual understanding, from abstract to concrete and semantic understanding, to support users to target the interested individual groups effectively.
-
-Figure~\ref{fig:design_profile} shows the legend for the user profile.
-The eight domains are encoded by visual symbols and organically organized in a human figure.
-There are basically three types of variables to drive the figure, i.e., the numeric, categorical and boolean ones.
-For numeric attributes such as income and education levels, visual symbol keeps consistent design but with changing visual variation, such as size, thickness.
-For the categorical attributes such as job, visual symbols are designed separately for better semantic meaning.
-For the boolean attribute like car, house, a symbol is designed to indicate its existence.
-With this consideration, the domains are designed as follows:
-
-% For numeric attributes.
-
-% By different composition, stimulus pattern which has the abstract demographic measurement of individuals.
-
-\begin{itemize}
-\item \textbf{Gender} the gender is visually mapped to the hairstyle of the avatar. 
-\item \textbf{Age} age is implied by the decoration on the hair.
-For the elder above 70, the hair is dyed to gray.
-For the youth beneath 18, a hair decoration is adapted for the different hairstyles of girls and boys.
-\item \textbf{Education} The thickness of eyeglasses is used to indicate the different levels of education.
-\item \textbf{Job} The clothes is designed to imply the job of the individual. There are 9 types of clothes.
-\item \textbf{Belongings} for real estate, car, residential license are considered as the belongings to the individual, so we design each of them as an add-on decoration to imply whether the individual has it or not.
-\item \textbf{Income} a money symbol is used to represent the income, whose size encodes the income level. The more money an individual earns, the larger the symbol is.
-\end{itemize}
-
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/design_profile}
- \caption{Design Profile: the eight characteritical domains are encoded and organized in an organic human figure.}
- \label{fig:design_profile}
-\end{figure}
-
-With the visual mapping, the profile varies from individual to individual.
-By concretizing the attributes which otherwise is too abstract to percept, users can scan and search for interesting target effectively.
-Figure~\ref{fig:div_example} lists the figures with the top 10 largest population in some job.
-The textual number beneath indicates the population.
-It is found that the majority of workmen earn a low salary and most of them have no residential license.
-On the contrary, for the officers, all of them have the residential license and most of them have a house.
-Some of the retired people are in old age.
-Most of the managers are at undergraduates, even graduates.
-
-% \begin{figure}[htb!]
-%  \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
-%  \includegraphics[width=\columnwidth]{pictures/design_div}
-%  \caption{Diverse Profile}
-%  \label{fig:div_profile}
-% \end{figure}
-
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/design_example}
- \caption{Representative figures with the top 10 largest population in four jobs}
- \label{fig:div_example}
-\end{figure}
-
-\subsection{t-SNE Projection of Individuals}
-
-% \begin{figure}[htb!]
-%  \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
-%  \includegraphics[width=0.7\columnwidth]{pictures/data_overview}
-%  \caption{Overview of Multiple Variables}
-%  \label{fig:figoverview}
-% \end{figure}
-
-In our case, each individual can be denoted as a vector $x_i$ with eight factors, and we get high dimensional data set $X={x_1, x_2, ..., x_n}$.
-The dimensionality reduction techniques are to preserve the local structure of high dimensional data in low dimensional space, which are efficient approaches to provide a good overview of the multivarible individuals (\textit{C2}).
-We adapt t-SNE project~\cite{maaten2008visualizing} to project $X$ as two-dimensional dots $Y={y_1, y_2, ..., y_n}$.
-One of steps in t-SNE is to compute the conditional probabilities to represent the similarity based on the distance between high dimenional datapoints.
-The conditional probability $p_{j\mid i}$ between $x_j$ and $x_i$ is given by:
-
-\begin{equation}
-p_{j\mid i} = \frac{exp({\left \| x_i - x_j \right \|}^2/2\alpha_i ^{2})}{\sum _{k\neq i}exp({\left \| x_i - x_k \right \|}^2/2\alpha_i ^{2})}
-\end{equation}
-
-where $\alpha_i$ is the variance of the Gaussian that is centered on $x_i$.
-Specifically in our context, the high-dimensional Euclidean distances $\left \| x_i - x_j \right \|$ between $x_i$ and $x_j$ needs to be adpated the numerical and categorical characteristics.
-Characteristics such as age, income, are numerical and comparable, so the difference exactly explains when they are different.
-But the other characteristics, i.e.
-job, real estate, car, residential, are ordinal.
-There is not the numeric order.
-For example, the job distance from a manager to a businessman and a workman is not comparable, which is considered the same distance, i.e., set to 1.
-
-% So $\left \| x_i - x_j \right \|$ is adapted as following:
-
-% \begin{equation}
-% \left \| x_i - x_j \right \| = 
-% \left\{\begin{matrix}
-% 0, f_{pi} \equiv f_{pj} \Lambda f_{p} \epsilon \{Gender, Residence, Estate, Car, Job\} \\ 
-% 1, f_{pi} \not\equiv f_{pj}  \Lambda f_{p} \epsilon \{Gender, Residence, Estate, Car, Job\} \\ 
-% \left \| f_{pi} - f_{pj} \right \|, f_p \epsilon\{Age, Education, Income, \}
-% \end{matrix}\right
-% \end{equation}
-
-As Figure~\ref{fig:tsne}shows, all 21435 volunteers are embedded in the 2D view, where the closer two dots are, the more similar they are in the eight characteristics.
-Figure~\ref{fig:tsne} exemplifies four features groups of dots in a neighbor.
-
-Multiple views of abstract view, t-SNE protection, and semantic data-driven profile visualization are coordinated in a Cross-filter machinesm~\cite{Weaver2010}.
-It allows end-users to interactive drill-down into individuals with interested characteristics from multiple perspectives(\textit{C3}).
-Starting from the abstract criterion constraints, the scope of interest is narrowed down to individuals with(out) certain characteristics.
-And then further cross-filtering with semantically visual profiles can be performed to check the combination of 8 characteristical variables.
-
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/tsne}
- \caption{t-SNE project with four groups of the interest: (a) t-SNE project }
- \label{fig:tsne}
-\end{figure}
-
-\subsection{2.5D Spatial Visualization}
-\label{subsec:25D}
-
-Embedding multiple variables in the spatial map is a challenging problem.
-Distorting 2D spatial for better space usage, such as the partial route embedding~\cite{sun2016embedding} is an effective method when there are a few local foci.
-When it comes to the global visualization, there is always a trade-off between occlusion-free and the compact spatial perception.
-Following the idea of stacking 2.5D space design~\cite{Tominski2012_stacking}, the space in this work is embedded in 2.5D space, to relax the z-axis for additional abstract information encoding.
-
-Figure~\ref{fig:2.5D}(a) shows the 2.5D visualization.
-The spatial map consists of Traffic Analysis Zone (TAZ), which is the unit of geography holding a certain number of people.
-For the 2.5D, each TAZ is grown as a prism whose height and color are developed to encode abstract information, e.g., the occurrence of visiting.
-With difference encoding choices, it is capable to visualize the correlation between spatial and different attributes (\textit{C4}).
-For example, in Figure~\ref{fig:2.5D}(a), prisms' height and color both encode the ratio of none-routine trips (such as go entertainment, go hospital, etc.) in the whole.
-For better 3D visual perception, lighting is turned on.
-Also, a lid is laid on the top of each prism to clearly bound its extent at the z-axis.
-
-\begin{figure}[htb!]
-\centering
-\subfigure[]{
-\resizebox*{9cm}{!}{\includegraphics{pictures/space1.eps}}}\hspace{5pt}
-\subfigure[]{
-\resizebox*{9cm}{!}{\includegraphics{pictures/space2.eps}}}\hspace{5pt}
-\caption{2.5D Spatial Visualization: (a) 2.5D spatial visualization with z-axis to encode addition information; (b) detail slicing in 2.5D space.}
-\label{fig:2.5D}
-\end{figure}
-
-Several interactions are integrated into the spatial view to alleviating the occlusion problem (\textit{C5}).
-The manipulation of 2.5D view supports users with rotate, zoom, pan operations, which are so continuously flexible that users probably find a suitable observing point.
-In the cases where occlusion is inevitable, an interaction named as \textit{Detail Slicing} is developed, as Figure~\ref{fig:2.5D}(b) shows.
-Detail Slicing is the operation to put a cross-section in the 2.5D space to expose the TAZ inside.
-To contextualize the cross-section, TAZs are visually adapted according to the intersection by ray casting.
-The TAZ in the foreground will be hidden, the intersected TAZs will be fully visualized and the ones in the background will be in semi-transparency.
-% Brunch of TAZ with similar visiting pattern and purpose are grouped by a heuristic DB-Scan Algorithm in the context of TAZ.
-From a center TAZ, walk to neighbor TAZ to check whether aggregation or not.
-The aggregated TAZ brunch indicates the region visiting the group of people in the same purpose, which is often the popular traveling places.
-The TAZ brunch is visualized...
-
- To compare the mobility patterns across different groups of people, a Small Multiple dock is used to reserve the ever explored interesting result (Figure~\ref{fig:teaser}(f)).
-To simply the comparison over spatial distribution, the snapshot is also rendered in the 2.5D space, which maintains the same interactions as the main 2.5D space does.
-
- % In this view, it supports end-users to directly manipulate the space, e.g., zooming, panning, etc. Also, detail information about the visiting can be checked by direct clicking on the TAZ.

### 2019-04-20 manuscript/visualdesign.tex
revision begin

@@
 
-The design of the system is driven by tasks, to align the analysis of mobility patterns with individual characteristics.
-Before diving into the design of the system, we introduce the couple of specifical tasks the system intended for.
-
-\begin{itemize}
-\item \textit{Task 1: Identify the group with specific individual characteristics}: to get groups of people with common or close attributes, to explore the correlation among individual characteristics.
-\item \textit{Task 2: Explore the mobility patterns of a group}: to explore where, how and why an interested group go in the city. 
-\item \textit{Task 3: Compare mobility patterns among multiple groups}: to know the similarities and differences between different groups in their mobility patterns, to investigate the relationship between movement and individual characteristics.
-\end{itemize}
-
-\subsection{Design Considerations}
-
-With these three tasks, we derive following design considerations:
-
-\begin{itemize}
-\item \textit{Intuitive perception of an individual as an organic complex (C1)}: the system should make use of users' daily life experience in knowing people to provide intuitive visualization, instead of the lifeless representation by number.
-The visual design needs to help end-users to pick desirable ones from the mass.
-\item \textit{Good overview of the multivariate individuals (C2)}: following the visual analytics manta by Shneiderman~\cite{RN459}, it is very important to provide a good overview of all the individuals then the users know where to explore.
-\item \textit{Effective multivariable cross-filter for individual characteristics (C3)}: there are eight domains to describe an individual.
-The system is supposed to provide a straight-forward way for easy filtering by the eight criteria.
-\item \textit{Compact visualization of mobility patterns in the constraint of spatial space (C4)}: the analysis of mobility patterns not only includes the conventional spatial and temporal dimensions, but also other abstract dimensions, e.g., travel purpose, visiting frequency, etc.
-The system should handle a compact layout to support the easy correlation between spatial and abstract information.
-\item \textit{Flexible interactions to explore the mobility patterns either within one group or between groups (C5)}: to support the comparison among groups, \textit{Task 3}, the system should maintain flexible interactions which allow the end-users to explore freely.
-\end{itemize}
-
-% Classification method, flow clustering method, Semantic representation.
-
-With those design considerations, we develop a visual analytics system as Figure~\ref{fig:teaser} shows.
-It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}).
-In the individual panel, interactive infographics, t-SNE visualization, and data-driven profiles support users to narrow the scope down to groups of individuals with interested characteristics.
-With the chosen group of individuals, its moving related information is visualized and explored in a 2.5D spatio-temporal view.
-
+\lm{With the design consideration (introduced in Section~\ref{}), we design a visual analytic system...} \lm{Show a overview figure, to introduce the relationship between multiple views}
 % overview of the data. Encode information but also allow users to set multiple criteria (\textit{C1}). Support users to slice the data by different domains.}
@@
 A glyph is intended for quick understanding and aligned comparison.
+\lm{Dual glyphs are designed, to illustrate the information of individual from two different perspectives, i.e., detailed inspection of individuals and efficient comparsion over multiple individuals.}
+
+\paragraph{Star-like Glyph} \lm{To compare over multiple individuals, a star-like glyph is designed to summary each individual, to ease the comparison by common cooridnating configurations....}
+
+\paragraph{Cartoon Glyph} ...
 Among glyph design, Chernoff Face~\cite{chernoff1973use} represents data variables by the different features of a cartoon face.

### 2019-04-21 manuscript/template.tex
new manuscript

--- 2019-04-19 template.tex
@@
 \usepackage{url}
-\usepackage{color}
+\usepackage{ulem}
+
+\usepackage{color, xcolor}
+\definecolor{darkg}{rgb}{0,0.6,0}
+\definecolor{lgreen}{rgb}{0,0.8,0}
+\definecolor{purple}{rgb}{0.93,0.48,0.03}
+\definecolor{orange}{rgb}{0.43,0.48,0.03}
+% \ifdraft
+%Our comments:
+\newcommand{\lmc}[1]{{\color{lgreen}[LM: #1]}}
+\newcommand{\wqc}[1]{{\color{orange}[WQ: #1]}}
+
+%Noticable new adds:
+\newcommand{\wq}[1]{{\color{blue}#1}}
+\newcommand{\lm}[1]{{\color{darkg}#1}}
+
 \newcommand{\m}{\textcolor{black}}
-
-\usepackage{xcolor}
-\newcommand{\add}{\textcolor{blue}}
 
@@
 
-\title{Unfolding the City: \textcolor{blue}{Exploring ...(city usage) with Social Characteristics} Exploring Mobility Patterns with Individual Characteristics}
+\title{Unfolding the City: \wq{Exploring Urban Spatial Attractiveness with Social Characteristics}}
 %\thanks{Grants or other notes
@@
 \label{intro}
+\wqc{change mobility pattern to spatial attractiveness}
 The science fiction \textit{Folding Beijing}~\citep{hao2016_foldingbeijing} depicts a world where three classes of people live in independent spatial-temporal patterns, though sharing the same earth surface.
@@
 
-\section{Visual design}
+\section{Overview}
+\wqc{Adding a background. Expert discussion. Summarize the tasks below.-0419}
+\lmc{Add a paragraph to introduce the motivation of this work, where we derive the tasks via the interview with domain exports.-0420}
 
-\textcolor{blue}{Adding a background. Expert discussion. Summarize the tasks below.}
+\wqc{Common human mobility indicators: travel distance, travel time, travel frequency, radius of gyration and movement entropy. }\\
+\wq{Spatial attractiveness is an important concept in GIS.
+Explain why.
+To derive the details, we interview the expert in GIS.
+Some questions like, how citizens live in the city, where they live, work and entertain?
+Which place is popular?
+For different citizens, whether a place has the same attraction?
+...
+With these questions, we summarize them into the tasks below, which need to be answered by our system.}
 
-The design of the system is driven by tasks, to align the analysis of mobility patterns with individual characteristics.
-Before diving into the design of the system, we introduce the couple of specifical tasks the system intended for.
+\sout{The design of the system is driven by tasks, to align the analysis of mobility patterns with individual characteristics.
+Before diving into the design of the system, introduce the couple of specifical tasks the system intended for.}
 
@@
 
+\iffalse
 \begin{figure}[htb!]
@@
 \end{figure}
+\fi
 
-With those design considerations, we develop a visual analytics system as Figure~\ref{fig:teaser} shows.
-It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}).
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\linewidth]{pictures/interfaceDraft.pdf}
+ \caption{\wq{System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) View1: a XXXX visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) View2: data-driven profiles support users with organic individual perception; (d) View3: map view for movement of the chosen group; (e) View4: for ranking or comparison; (g) View5: top N kinds of citizens with social characteristics.}}
+ \label{fig:interfaceDraft}
+\end{figure}
+
+\section{Visual Design}
+\lm{With the design consideration (introduced in Section~\ref{}), we design a visual analytic system...} \lm{Show a overview figure, to introduce the relationship between multiple views}
+
+With those design considerations, we develop a visual analytics system as \wq{Figure~\ref{fig:interfaceDraft} shows.} \wqc{instead of fig.
+teaser} It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}).
 In the individual panel, interactive infographics, t-SNE visualization, and data-driven profiles support users to narrow the scope down to groups of individuals with interested characteristics.
@@
 \subsection{Data-driven Profile Visualization}
-\textcolor{blue}{Using two scales. Glyph-based visualization for finer scale, radar-based visualization for coarser scale.}
 
-Glyph-based visualization~\citep{borgo2013glyph} is the form of visual design to compose multivariable into a collection of unified visual symbols, known as a glyph.
+Glyph-based visualization~\cite{borgo2013glyph} is the form of visual design to compose multivariable into a collection of unified visual symbols, known as a glyph.
 A glyph is intended for quick understanding and aligned comparison.
-Among glyph design, Chernoff Face~\citep{chernoff1973use} represents data variables by the different features of a cartoon face.
+\lm{Dual glyphs are designed, to illustrate the information of individual from two different perspectives, i.e., detailed inspection of individuals and efficient comparsion over multiple individuals.}
+
+\paragraph{Star-like Glyph} \lm{To compare over multiple individuals, a star-like glyph is designed to summary each individual, to ease the comparison by common cooridnating configurations....}
+
+\paragraph{Cartoon Glyph} ...
+Among glyph design, Chernoff Face~\cite{chernoff1973use} represents data variables by the different features of a cartoon face.
 Following the idea of Chernoff Face, we design a type of glyph, a graphical representation of people with specific individual characteristics.
@@
 Those visual profiles are intended for intuitive visual understanding, from abstract to concrete and semantic understanding, to support users to target the interested individual groups effectively.
-
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/design_profile}
- \caption{Design Profile: the eight characteritical domains are encoded and organized in an organic human figure.}
- \label{fig:design_profile}
-\end{figure}
 
@@
 
-\subsection{t-SNE Projection of Individuals}
-\textcolor{blue}{Not tsne.
-A octagon radar graph to position all citizens.
-A clustering algorithm for commend similar persons into a new group.(maybe: interactions to set the weight of each characteristic)}
+\wq{\subsection{XXXX Projection of Individuals}}
+\wqc{A octagon radar graph to position all citizens. A clustering algorithm for commend similar persons into a new group.(maybe: interactions to set the weight of each characteristic)}
 
@@
 \subsection{2.5D Spatial Visualization}
-\textcolor{blue}{Just a map. Clustering or Grid. 2.5D for stack??}
+\wqc{this part may be deleted.}
 
@@
 
+\wq{\subsection{A glyph design details (in view3)}
+We design a kind of glyph to express a high-dimensional travel indicators. It will be embeded in the map view\wqc{for case1}.}
+
+\wq{\subsection{Ranking or comparison method (in view4)}
+\wqc{for case3}We design ranking/comparison method with different weight of different purpose or different groups.}
+
+\section{Experts Feedback}
+
+\lmc{Add a section to introduce the domain experts' feedback}
+
+\lm{We interview XX domain experts from the GIS field. XX of them are with ... The procedure went as following. We first introduce them the system an...}
+
 \section{Case study}
@@
 \subsection{Case 1: Work-life Balance VS Income/Education}
-\textcolor{blue}{theme: Using similar social characteristics to put citizens into target groups.
-change the name of the section.
-Using View1(selecting bar), View2(radar), View3(map, to see the distribution of home and work place)}
+\wqc{Aim1: use view1 and view2 for groups. Aim2: show their basic activity spaces.}
 
@@
 
-Although it is incomplete, income and education are two of the most essential characteristics to tag an individual with a good resource or not.
+Although it is incomplete, income and education are two of the most essential characteristics to tag an individual with a good resource or not.\\
+\wq{EDIT paragraph below. not just give number, use view1 and view2 to filter the target groups.}\\
 As Figure~\ref{case11} shows, taking income and education as the two dimensions, taking 300K yuan as the border between high and low income and an undergraduate bachelor degree as the border between high and low education level, four different groups are generated in the four quadrants.
@@
 Lots of \textit{antizen} live in Nanshan District, where there are many universities and high-tech industrial parks full of well educated people.
+\wq{The glyphs on the map means the travel distance(even differentiate home-work distance(which is an important in mobility research), and extended travel distance), travel radius.} \wqc{the 3rd design in Section.design, a kind of glyph for high-dimensional mobility indicator}
 
@@
 
+\wqc{paragraph below may be deleted. It is about attractiveness entropy, which in case3}
 To have a better knowledge of mobility patterns of the four groups, trips are categorized into three categories, ``home", ``work'' for regular trips with the purpose of going home, work (or school for students), ``other'' for irregular trips with the purpose of shopping, visiting friends.
@@
 
-\subsection{Case 2: Home-work Distance VS Income/House}
-\textcolor{blue}{theme: the distribution of citizens' mobility when moving with a given purpose; or: attractiveness of region.
-Given a group, interaction with purpose, show distribution of each region.
-Using View3(map, each region with a radar graph to show distance distribution).
-VIEW4:??(od matrix?)(finer level?)}
+\subsection{Case 2: Spatial Attractiveness Based on One Purpose}
+\wqc{aim: select one purpose; View3 shows spatial attractiveness, including: quantity, distance, （direction）; View4 shows ranking of origins, (or others); (add a interaction in view5 for citizens in selected grid.)}
+
+\wq{Due to the various functions of the areas, for different space, the attractiveness for different aims differs.
+Therefore, in this case, we demonstrate the use of the system for exploring the spatial attractiveness for one purpose.}
 
@@
 
-\subsection{Case 3: Life-style VS Jobs}
-\textcolor{blue}{theme: what persons do?
-trip purpose sequence?
-Given a group, interaction with purpose, show distribution of each region.
-Using View3(map, 2.5D), View4(a stacked bar to show quantity of each kinds of purpose.)}
+\subsection{Case 3: Spatial Attractiveness Based on Mixed Purposes}
+\wqc{aim: with mixed purposes, show attractiveness quantity and entropy.
+View3 shows spatial attractiveness, including: quantity, distance, （direction）; View4 shows ranking of origins, (or others); (add a interaction in view5 for citizens in selected grid.)}
+
+\wq{Due to the various functions of the areas, for different space, the attractiveness for different aims differs.
+Therefore, in this case, we demonstrate the use of the system for exploring the spatial attractiveness for one purpose.}
 

### 2019-04-22 manuscript/template.tex
at first, read readme.txt in manuscript folder

@@
 \usepackage{url}
-\usepackage{ulem}
 
@@
 \newcommand{\wqc}[1]{{\color{orange}[WQ: #1]}}
-
-%Noticable new adds:
 \newcommand{\wq}[1]{{\color{blue}#1}}
@@
 \usepackage[misc]{ifsym}
-%
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-%
-% Insert the name of "your journal" with
-% \journalname{myjournal}
-%
+
 \begin{document}
 
-\title{Unfolding the City: \wq{Exploring Urban Spatial Attractiveness with Social Characteristics}}
+\title{Unfolding the City: \wq{Exploring Urban Spatial Attractiveness with Individual Characteristics}}
 %\thanks{Grants or other notes
@@
 \section{Introduction}
+\iffalse
+What is it that makes some places, regions or nations appear more attractive than others to live in, visit or invest in?
+Does it depend on the particular characteristics or situation of the persons considering the attractiveness, in what phase in life the persons find themselves, or are there some common features, perhaps place characteristics that are viewed positively by all, independently of context?
+
+\fi
+
 \label{intro}
-\wqc{change mobility pattern to spatial attractiveness}
+\wqc{change mobility pattern to spatial attractiveness}\\
 The science fiction \textit{Folding Beijing}~\citep{hao2016_foldingbeijing} depicts a world where three classes of people live in independent spatial-temporal patterns, though sharing the same earth surface.
@@
 
+A discussion with experts in GIS. We summarize the analytic tasks identified from the interviews of domain experts. Then the workflow of the proposed visual analytics system.
+
+\subsection{Goal}
 \wqc{Common human mobility indicators: travel distance, travel time, travel frequency, radius of gyration and movement entropy. }\\
-\wq{Spatial attractiveness is an important concept in GIS.
-Explain why.
-To derive the details, we interview the expert in GIS.
-Some questions like, how citizens live in the city, where they live, work and entertain?
-Which place is popular?
-For different citizens, whether a place has the same attraction?
-...
-With these questions, we summarize them into the tasks below, which need to be answered by our system.}
 
-\sout{The design of the system is driven by tasks, to align the analysis of mobility patterns with individual characteristics.
+Spatial attractiveness is an important concept to evaluate ...
+in commercial activity, tourism and urban research.
+We interview the expert in GIS.
+There are some core research concerns derived from domain exports.
+
+\begin{itemize}
+  \item \textit{Diversity of spatial attractiveness} Two types of diversity: diversity of the attracted persons, and diversity of attractiveness indicators.
+\wqc{cannot find this concept in papers, and, i am not sure about ``indicator"}
+  \item \textit{Magnitude of spatial attractiveness} How many persons could be attracted and how much the difficulty they overcome. \wqc{there is equation in related paper to support this.}
+\end{itemize}
+With these questions, we summarize them into the tasks below, which need to be answered by our system.
+
+\subsection{Tasks}
+\lm{The exploration of core concepts above are resolved further with following tasks...
+to align the analysis of mobility patterns with individual characteristics.
 Before diving into the design of the system, introduce the couple of specifical tasks the system intended for.}
 
+%The design of the system is driven by tasks, to align the analysis of mobility patterns with individual characteristics.
+Before diving into the design of the system, introduce the couple of specifical tasks the system intended for.
+
 \begin{itemize}
-\item \textit{Task 1: Identify the group with specific individual characteristics}: to get groups of people with common or close attributes, to explore the correlation among individual characteristics.
-\item \textit{Task 2: Explore the mobility patterns of a group}: to explore where, how and why an interested group go in the city.
-\item \textit{Task 3: Compare mobility patterns among multiple groups}: to know the similarities and differences between different groups in their mobility patterns, to investigate the relationship between movement and individual characteristics.
+\item \textit{Task 1: Identify the group with specific individual characteristics\wqc{What kind of citizens tend to be attracted?}}: to get groups of people with common or close attributes, to explore the correlation among individual characteristics.
+\item \textit{Task 2: Why the attracted citizens are attracted?}: to explore ...
+\item \textit{Task 3: How many citizens are extracted?}: to express ...
+\item \textit{Task 4: Where do the attracted citizens come from?}: City has different function areas.
+Some areas meet all the basic requirements of citizens' living activities, while some cannot.
+...
+to know the similarities and differences between different groups in their mobility patterns, to investigate the relationship between movement and individual characteristics.
 \end{itemize}
@@
 \section{Visual Design}
-\lm{With the design consideration (introduced in Section~\ref{}), we design a visual analytic system...} \lm{Show a overview figure, to introduce the relationship between multiple views}
 
-With those design considerations, we develop a visual analytics system as \wq{Figure~\ref{fig:interfaceDraft} shows.} \wqc{instead of fig.
-teaser} It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}).
+With those design considerations (introduced in Section~\ref{}), we develop a visual analytics system as Figure~\ref{fig:interfaceDraft} shows.
+It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}).
 In the individual panel, interactive infographics, t-SNE visualization, and data-driven profiles support users to narrow the scope down to groups of individuals with interested characteristics.
 With the chosen group of individuals, its moving related information is visualized and explored in a 2.5D spatio-temporal view.
+\lmc{Show a overview figure, to introduce the relationship between multiple views}
 
@@
 
-\paragraph{Star-like Glyph} \lm{To compare over multiple individuals, a star-like glyph is designed to summary each individual, to ease the comparison by common cooridnating configurations....}
+\paragraph{Star-like Glyph} \lm{To compare over multiple individuals, a star-like glyph is designed to summary each individual, to ease the comparison by common coordination configurations....}
 
@@
 With this consideration, the domains are designed as follows:
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/design_profile}
+ \caption{Design Profile: the eight characteritical domains are encoded and organized in an organic human figure.}
+ \label{fig:design_profile}
+\end{figure}
 
@@
 \wq{\subsection{XXXX Projection of Individuals}}
-\wqc{A octagon radar graph to position all citizens. A clustering algorithm for commend similar persons into a new group.(maybe: interactions to set the weight of each characteristic)}
+\wqc{A octagon radar graph to position all citizens.
+A clustering algorithm for commend similar persons into a new group.(maybe: interactions to set the weight of each characteristic)} \lmc{Yes, I think an interactive weight adjustment is good.}
 
@@
 
+\iffalse
 \subsection{2.5D Spatial Visualization}
-\wqc{this part may be deleted.}
-
 \label{subsec:25D}
@@
 To simply the comparison over spatial distribution, the snapshot is also rendered in the 2.5D space, which maintains the same interactions as the main 2.5D space does.
+\fi
 
-\wq{\subsection{A glyph design details (in view3)}
-We design a kind of glyph to express a high-dimensional travel indicators. It will be embeded in the map view\wqc{for case1}.}
+\wq{\subsection{A glyph design to show travel indicator (in view3, in case1)}
+We design a kind of glyph to express a high-dimensional travel indicators. It will be embeded in the map view\wqc{for case1}.
+The elements may be included in the glyph:
+\begin{itemize}
+  \item (home-work distance)
+  \item travel distance
+  \item travel radius
+  \item travel frequency
+\end{itemize}}
 
-\wq{\subsection{Ranking or comparison method (in view4)}
-\wqc{for case3}We design ranking/comparison method with different weight of different purpose or different groups.}
+\wq{\subsection{A glyph design to show attractiveness (in view3, in case2)}
+We design a kind of glyph to express spatial attractiveness.
+The elements may be included in the glyph:
+\begin{itemize}
+  \item quantity
+  \item distance
+\end{itemize}}
+
+\wq{\subsection{A glyph design to show attractiveness diversity(in view3, in case3)}
+We design a kind of glyph to express spatial attractiveness.
+The elements may be included in the glyph:
+\begin{itemize}
+  \item how many kinds of purpose?
+  \item the percentage of each purpose?
+\end{itemize}
+
+(if comparison between groups, the glyph up, show the diversity of multiple groups at the same time.)}
 
@@
 
-\subsection{Case 1: Work-life Balance VS Income/Education}
-\wqc{Aim1: use view1 and view2 for groups. Aim2: show their basic activity spaces.}
+\wq{\subsection{Case 1: find diversity of citizens based on social characteristics}}
+\wqc{Aim1: use view1 and view2 for groups. Aim2: show their basic activity spaces in view3 and view4. text no changes yet.}
 
@@
 Before diving into the complex mobility pattern analysis, we explore the home distribution of the four groups.
-As Figure~\ref{case12} shows, \textit{top aristocracy} and most of \textit{new rich} live concentrated in the downtown area of Shenzhen, where the living cost is higher, especially the housing cost.
+As Figure~\ref{case1draft} shows, \textit{top aristocracy} and most of \textit{new rich} live concentrated in the downtown area of Shenzhen, where the living cost is higher, especially the housing cost.
 A small part of \textit{new rich} lives far away from the downtown, maybe because they don't have to work in downtown.
@@
 Lots of \textit{antizen} live in Nanshan District, where there are many universities and high-tech industrial parks full of well educated people.
-\wq{The glyphs on the map means the travel distance(even differentiate home-work distance(which is an important in mobility research), and extended travel distance), travel radius.} \wqc{the 3rd design in Section.design, a kind of glyph for high-dimensional mobility indicator}
 
+\wq{The glyphs on the map means the travel distance, travel radius..., which is an important in mobility research. Describe the difference.}\\
+\wqc{the 3rd design in Section.design, a kind of glyph for high-dimensional mobility indicator.}
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/case1draft}
+ \caption{Home Distributions of the Four Groups}
+ \label{case1draft}
+\end{figure}
+
+\iffalse
 \begin{figure}[htb!]
@@
 
-\wqc{paragraph below may be deleted. It is about attractiveness entropy, which in case3}
 To have a better knowledge of mobility patterns of the four groups, trips are categorized into three categories, ``home", ``work'' for regular trips with the purpose of going home, work (or school for students), ``other'' for irregular trips with the purpose of shopping, visiting friends.
@@
 \end{figure}
+\fi
 
-\subsection{Case 2: Spatial Attractiveness Based on One Purpose}
-\wqc{aim: select one purpose; View3 shows spatial attractiveness, including: quantity, distance, （direction）; View4 shows ranking of origins, (or others); (add a interaction in view5 for citizens in selected grid.)}
-
-\wq{Due to the various functions of the areas, for different space, the attractiveness for different aims differs.
-Therefore, in this case, we demonstrate the use of the system for exploring the spatial attractiveness for one purpose.}
-
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/case2}
- \caption{Home-work distances of different groups: (a) with different salary levels; (b) with or without house.}
- \label{case2}
-\end{figure}
-
-Home-work distance is an essential metric in economics, geography, and sociology.
-It refers to the distance between house and workplace.
-It is influenced by many factors like transportation, housing, land use, etc.
-Understanding the home-work distance of a region helps to evaluate whether the region is well planned or not.
-In this case, we demonstrate our system's help in home-work distance understanding.
-
-Considering income potentially determines where people live, we use income as the characteristics to select three groups, the group over 500K, the group during 200-300K and the group less than 100K.
-In Figure~\ref{case2}, the height of the bar stands for visiting frequency of the TAZ and its color encodes the average home-work distance, red for close and yellow for far.
-As Figure~\ref{case2}(a) shows, for all the three groups in different income levels, most of the TAZs have dark red or red color which indicates the home-work distance is generally short, especially in downtown.
-Only those with less than 100K salary work outside the center, such as the space in the green circle.
-When comparing the three groups in the downtown area, it is seen that it takes more time to go to work in Futian District as the decrease of the income.
-
-We explore the home-work distance of groups with and without a house.
-Figure~\ref{case2}(b) shows the close-up views.
-It is found that the Nanshan District has a shorter home-work distance for individuals without a house, while Futian District has shorter for those with a house.
-Nanshan is relatively newer to Futian so that there might be more easily-accessible houses to be rent.
-
-\subsection{Case 3: Spatial Attractiveness Based on Mixed Purposes}
+\subsection{Case 2: Diversity of spatial attractiveness of indicators}
 \wqc{aim: with mixed purposes, show attractiveness quantity and entropy.
@@
 
-\wq{Due to the various functions of the areas, for different space, the attractiveness for different aims differs.
-Therefore, in this case, we demonstrate the use of the system for exploring the spatial attractiveness for one purpose.}
+\wq{Due to the various functions of the areas, for different space, the attractiveness indicators differs.
+Therefore, in this case, we demonstrate the use of the system for exploring diversity of spatial attractiveness indicators.
+}
+
+\wq{As Figure~\ref{case2draft} shows, in view3, glyph represents $\textbf{the quantity}$ and $\textbf{value of mixture of purposes}$.
+\wqc{(if we decide to give a computing equation to define it.)} in view4, ranking of each grid based on the quantity of each purpose.}
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/case2draft}
+ \caption{Trip purposes distribution of four groups with different jobs}
+ \label{case2draft}
+\end{figure}
 
@@
 \end{figure}
+\fi
+
+\subsection{Case 3: Magnitude of Spatial Attractiveness}
+\wqc{aim: select one purpose to show how many and where and how long. Use View3 and view4.}
+
+\wq{When zooming in to explore with only one purpose, we demonstrate the use of the system for exploring the magnitude of spatial attractiveness.}
+
+\wq{As Figure~\ref{case3draft} shows, in view3, glyph represents $\textbf{the quantity}$ and $\textbf{how many grids are linked(i.e.
+area)}$ and $\textbf{distribution of distances}$.
+in view4, show $\textbf{where are the linked grids}$ and $\textbf{the quantity of each linked grid}$ and $\textbf{distance}$.
+\wqc{not sure the form in view4, map or chart?
+if map, 1D or 2.5D?}}
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/case3draft}
+ \caption{Home-work distances of different groups: (a) with different salary levels; (b) with or without house.}
+ \label{case3draft}
+\end{figure}
+
+\iffalse
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/case2}
+ \caption{Home-work distances of different groups: (a) with different salary levels; (b) with or without house.}
+ \label{case2}
+\end{figure}
+
+Home-work distance is an essential metric in economics, geography, and sociology.
+It refers to the distance between house and workplace.
+It is influenced by many factors like transportation, housing, land use, etc.
+Understanding the home-work distance of a region helps to evaluate whether the region is well planned or not.
+In this case, we demonstrate our system's help in home-work distance understanding.
+
+Considering income potentially determines where people live, we use income as the characteristics to select three groups, the group over 500K, the group during 200-300K and the group less than 100K.
+In Figure~\ref{case2}, the height of the bar stands for visiting frequency of the TAZ and its color encodes the average home-work distance, red for close and yellow for far.
+As Figure~\ref{case2}(a) shows, for all the three groups in different income levels, most of the TAZs have dark red or red color which indicates the home-work distance is generally short, especially in downtown.
+Only those with less than 100K salary work outside the center, such as the space in the green circle.
+When comparing the three groups in the downtown area, it is seen that it takes more time to go to work in Futian District as the decrease of the income.
+
+We explore the home-work distance of groups with and without a house.
+Figure~\ref{case2}(b) shows the close-up views.
+It is found that the Nanshan District has a shorter home-work distance for individuals without a house, while Futian District has shorter for those with a house.
+Nanshan is relatively newer to Futian so that there might be more easily-accessible houses to be rent.
+\fi
 

### 2019-04-22 code/js/window1.js

@@ -1,87 +1,0 @@
-	function initEvent(item){
-		for(var i = 0; i < g_liAttrName.length; i ++){
-
-			var attrName = g_liAttrName[i];
-			var childItem = item.children[attrName];
-			var liOptionBar = childItem.getItems(
-				{'name': /^attr/});
-
-			for(var j = 0; j < liOptionBar.length; j ++){
-				var optionBar = liOptionBar[j]
-			    optionBar._AttrClick = true
-				optionBar.strokeWidth = 1;
-				optionBar.opacity = 1.
-				// optionBar.strokeColor = 'blue';
-				optionBar.onClick = function(){
-					this._AttrClick = !this._AttrClick;
-					if(this._AttrClick){
-						this.opacity = 1.;
-						// this.strokeColor = 'blue';
-						this.strokeWidth = 1;
-					}else{
-						this.opacity = 0.1;
-						this.strokeColor = null;
-						// this.strokeWidth = 2;
-					}
-                    get8dDataset(this._name, this._AttrClick);
-				}
-				optionBar.onMouseEnter = function(){
-					this.opacity = 1.;
-					this.strokeColor = 'gray';
-					this.strokeWidth = 0.5
-				}
-				optionBar.onMouseLeave = function(){
-
-					this.strokeColor = null;
-					// this.strokeWidth = 0.5
-					// if(this._AttrClick == false)
-						// this.strokeColor = null;
-				}
-			}
-		}
-	}
-
-
-	function get8dDataset(optionName, attrClicked){
-	       var zu = 0;
-	   	   if(optionName.indexOf('age')>0){
-	           zu = 0;
-	       }else if(optionName.indexOf('gen')>0){
-	           zu = 1;
-	       }else if(optionName.indexOf('edu')>0){
-	           zu = 2;
-	       }else if(optionName.indexOf('inc')>0){
-	           zu = 3;
-	       }else if(optionName.indexOf('job')>0){
-	           zu = 4;
-	       }else if(optionName.indexOf('res')>0){
-	           zu = 5;
-	       }else if(optionName.indexOf('car')>0){
-	           zu = 6;
-	       }else if(optionName.indexOf('hou')>0){
-	           zu = 7;
-	       }
-
-         var num = parseInt(optionName.substr(optionName.length-1,optionName.length-1));
-
-         if(attrClicked){
-             if(inp[zu].length==attributesLength[zu]){
-                 inp[zu] = [];
-                 inp[zu].push(num);
-             }else{
-                 inp[zu].push(num);
[…]

### 2019-04-22 code/js/window2.js

@@ -1,78 +1,0 @@
-function squareSelect(uids){
-         var clickTime = "";
-         var startLoc = [];
-         var endLoc = [];
-         var flag = "";
-	     var rect = svg.append("rect")
-	                   .attr("width", 0)
-	                   .attr("height", 0)
-	                   .style("fill", "rgba(22,22,22,0.3)")
-	                   .style("stroke", "#ccc")
-	                   .style("stroke-width", "2px")
-	                   .attr("id", "idSquareSelect");
-
-	          svg.on("mousedown", function(){
-	                 clickTime = (new Date()).getTime();
-	                 flag = true;
-	                 rect.attr("transform", "translate("+d3.event.layerX+","+d3.event.layerY+")");
-	                 startLoc = [d3.event.layerX, d3.event.layerY];
-	          });
-
-	          svg.on("mouseover", function(){
-                    if(d3.event.target.localName == 'svg' && flag==true ||d3.event.target.localName == "rect" && flag == true) {
-                             var width = d3.event.layerX - startLoc[0];
-                             var height = d3.event.layerY - startLoc[1];
-                             if (width < 0) {
-                                   rect.attr("transform", "translate(" + d3.event.layerX + "," + startLoc[1] + ")");
-                             }
-                             if (height < 0) {
-                                   rect.attr("transform", "translate(" + startLoc[0] + "," + d3.event.layerY + ")");
-                             }
-                             if (height < 0 && width < 0) {
-                                   rect.attr("transform", "translate(" + d3.event.layerX + "," + d3.event.layerY + ")");
-                             }
-                                   rect.attr("width", Math.abs(width)).attr("height", Math.abs(height));
-                    }
-	          });
-
-	          svg.on("mouseup", function(){
-                     if(flag == true){
-                             flag = false;
-                             endLoc = [d3.event.layerX, d3.event.layerY];
-                             var leftTop = [];
-                             var rightBottom = []
-                             if(endLoc[0]>=startLoc[0]){
-                                     leftTop[0] = startLoc[0];
-                                     rightBottom[0] = endLoc[0];
-                             }else{
-                                     leftTop[0] = endLoc[0];
-                                     rightBottom[0] = startLoc[0];
-                             }
-
-                             if(endLoc[1]>=startLoc[1]){
-                                     leftTop[1] = startLoc[1];
-                                     rightBottom[1] = endLoc[1];
-                             }else{
-                                     leftTop[1] = endLoc[1];
-                                     rightBottom[1] = startLoc[1];
[…]

### 2019-04-22 code/js/window3.js

@@ -1,366 +1,0 @@
-function clearCurrentFigures(m){
-			setSuserbaseVisible(false, m);
-			var temp = "temp"+m;
-			var libasePaths = g_16Root.getItems({'name': temp});
-			console.log(libasePaths.length);
-			for(var i = 0; i < libasePaths.length; i ++){
-				var path_temp = libasePaths[i];
-				path_temp.remove()
-			}
-			for(var i = 0; i < g_liText[m].length; i ++){
-				var path_temp = g_liText[m][i];
-				path_temp.remove()
-			}
-			g_liText[m] = []
-		}
-
-
-	function setSuserbaseVisible(visible, mode){
-	    var libasePaths;
-	    if(mode==5){
-	         libasePaths = g_16Root.getItems({'name': /^suser_base/});
-	    }else if(mode==0){
-	         libasePaths = g_16Root.getItems({'name': /^suser_base_0/});
-	    }else if(mode==1){
-	         libasePaths = g_16Root.getItems({'name': /^suser_base_1/});
-	    }else if(mode==2){
-	         libasePaths = g_16Root.getItems({'name': /^suser_base_2/});
-	    }else if(mode==3){
-	         libasePaths = g_16Root.getItems({'name': /^suser_base_3/});
-	    }
-		for(var i = 0; i < libasePaths.length; i ++){
-			var basePath = libasePaths[i];
-			basePath.visible = visible;
-		}
-	}
-
-  function initButtons(item){
-
-        for(var j=1;j<14;j++){
-            var a = "plus_"+String(j);
-            var plusBar = item.children[a];
-
-            plusBar.onClick = function(){
-                var n = parseInt(this._name.substr(5));
-                var g = document.getElementById("group");
-                g.style.left = String(n*3)+"%";
-                g.style.top = "96%";
-                g.style.visibility="visible";
-                g.ondblclick = function(){
-                     var v = g.options[g.selectedIndex].value;
-                     g.style.visibility = "hidden";
-                     addToGroups(n, v);
-                }
-            }
-            plusBar.onMouseEnter = function(){
-					this.strokeColor = 'blue';
-            }
-			plusBar.onMouseLeave = function(){
-					this.strokeColor = null;
-		    }
-        }
-
-         g_16Root.children['pre_page_button'].onClick = function(){
-                      console.log(' pre page click! ');
-                      if(page!=0){
-                           page--;
-                           if(current==1){
[…]

### 2019-04-22 code/js/window4v2.js

@@ -1,599 +1,0 @@
-function initPurpose(item){
-
-  for(var j=1;j<11;j++){
-            var a = "p"+String(j);
-            var pBar = item.children[a];
-
-
-            pBar._AttrClick = true
-			pBar.strokeWidth = 4;
-			pBar.strokeColor = 'black';
-		    pBar.onClick = function(){
-					this._AttrClick = !this._AttrClick;
-					if(this._AttrClick){
-						this.strokeColor = 'black';
-						this.strokeWidth = 4;
-					}else{
-						this.strokeColor = null;
-						this.strokeWidth = 1;
-					}
-			}
-			pBar.onMouseEnter = function(){
-					this.strokeColor = 'black';
-		    }
-			pBar.onMouseLeave = function(){
-					if(this._AttrClick == false)
-						this.strokeColor = null;
-			}
-        }
-}
-
-
- function d3threeD( exports ) {
-        var DEGS_TO_RADS = Math.PI / 180, UNIT_SIZE = 100;
-        var DIGIT_0 = 48, DIGIT_9 = 57, COMMA = 44, SPACE = 32, PERIOD = 46, MINUS = 45;
-        exports.transformSVGPath = function transformSVGPath( pathStr ) {
-            var path = new THREE.ShapePath();
-            var idx = 1, len = pathStr.length, activeCmd,
-                    x = 0, y = 0, nx = 0, ny = 0, firstX = null, firstY = null,
-                    x1 = 0, x2 = 0, y1 = 0, y2 = 0,
-                    rx = 0, ry = 0, xar = 0, laf = 0, sf = 0, cx, cy;
-            function eatNum() {
-                var sidx, c, isFloat = false, s;
-                // eat delims
-                while ( idx < len ) {
-                    c = pathStr.charCodeAt( idx );
-                    if ( c !== COMMA && c !== SPACE ) break;
-                    idx ++;
-                }
-                if ( c === MINUS ) {
-                    sidx = idx ++;
-                } else {
-                    sidx = idx;
-                }
-                // eat number
-                while ( idx < len ) {
-                    c = pathStr.charCodeAt( idx );
-                    if ( DIGIT_0 <= c && c <= DIGIT_9 ) {
-                        idx ++;
-                        continue;
-                    } else if ( c === PERIOD ) {
-                        idx ++;
-                        isFloat = true;
-                        continue;
-                    }
-                    s = pathStr.substring( sidx, idx );
[…]

### 2019-04-22 code/server/application.py

@@ -1,24 +1,0 @@
-#!/usr/bin/env python
-#coding:utf-8
-
-from url import url 
-
-import tornado.web
-import os
-
-# import pymongo
-# from pymongo import MongoClient
-
-setting = dict(
-  # template_path=os.path.join(os.path.dirname(__file__),"template"),
-  static_path=os.path.join(os.path.dirname(__file__),"../"), #.. 上级目录，.当前目录
-  template_path=os.path.join(os.path.dirname(__file__), "./")
-)
-
-application = tornado.web.Application(
-  handlers=url,
-  debug=True,
-  **setting
-)
-
-

### 2019-04-22 code/server/handler/hwhandler.py

@@ -1,142 +1,0 @@
-import tornado.web
-from tornado.options import options
-
-import pymongo
-from pymongo import MongoClient
-
-import setting
-
-from PIL import Image
-import io
-import os.path
-
-import json
-
-import subprocess
-
-
-class HWHandler(tornado.web.RequestHandler):
-    def post(self):
-        va = self.get_argument('value')
-        userId = va.split(',')
-
-        ods41 = {}
-        ods42 = {}
-        ods41, ods42 = self.getCount(userId)
-
-        max = 0;
-        for key in ods41.keys():
-            temp = ods41.get(key)
-            if(temp>max):
-                max = temp
-        for key2 in ods42.keys():
-            temp2 = ods42.get(key2)
-            if(temp2>max):
-                max = temp2
-
-        stringnumber41 = '['
-        flag = 1
-        for key3 in ods41.keys():
-            if flag==1:
-                stringnumber41 += "{\"id\":"+str(key3)+", \"n\":"+str(ods41.get(key3))+"}"
-                flag = 2
-            else:
-                stringnumber41 += ",{\"id\":" + str(key3) + ", \"n\":" + str(ods41.get(key3)) + "}"
-        stringnumber41 += "]"
-
-        stringnumber42 = '['
-        flag = 1
-        for key4 in ods42.keys():
-            if flag == 1:
-                stringnumber42 += "{\"id\":" + str(key4) + ", \"n\":" + str(ods42.get(key4)) + "}"
-                flag = 2
-            else:
-                stringnumber42 += ",{\"id\":" + str(key4) + ", \"n\":" + str(ods42.get(key4)) + "}"
-        stringnumber42 += "]"
-
-        result = {'r1': stringnumber41, 'r2': stringnumber42, 'max': max}
-        #print(result);
-        self.set_header('Access-Control-Allow-Origin', '*')
-        self.write(result)
-
-    def getCount(self, uidsinput):
-
-        mongo_url = "192.168.153.139:27017"
-        client = pymongo.MongoClient(mongo_url);
-        db = client['wechat']
-        collection = db["userbid"]
-
-        ods1 = {}
-        ods2 = {}
-        for j in range(len(uidsinput)):
-            cursor = collection.find({"uid": uidsinput[j]})
-
-            for item in cursor:
-                h = item['homebid']
-                if (h in ods1):
-                    temp = ods1.get(h)
-                    ods1[h] = temp + 1
-                else:
-                    ods1[h] = 1
-
-                w = item['companybid']
[…]

### 2019-04-22 code/server/handler/kdehandler.py

@@ -1,123 +1,0 @@
-
-import tornado.web
-from tornado.options import options
-
-import pymongo
-from pymongo import MongoClient
-
-import setting
-
-from PIL import Image
-import io
-import os.path
-
-import json
-
-import subprocess
-
-from scipy import stats
-import numpy as np
-from skimage import measure
-
-class KDEHandler(tornado.web.RequestHandler):
-	def post(self):
-		self.set_header('Access-Control-Allow-Origin', "*")
-		clusterNum = json.loads(self.get_argument('cluster'));
-		
-		print('clusterNum', clusterNum)
-
-		xmin=-6
-		xmax=6
-		ymin=-6
-		ymax=6
-		
-		m1,m2 = self.measure1(2000)
-		m3,m4 = self.measure(2000)
-
-		liDot1 = self.listZip(m1, m2)
-		liDot2 = self.listZip(m3, m4)
-
-		Z1 = self.kde(m1, m2)
-		Z2 = self.kde(m3, m4)
-
-		liDensity1 = list(Z1.ravel()) #self.kde(m1, m2)
-		liDensity2 = list(Z2.ravel()) #self.kde(m3, m4)
-		# list(np.rot90(Z).ravel());
-
-		mapContour1 = self.getContours(Z1)
-		mapContour2 = self.getContours(Z2)
-
-		liCluster = []
-		liCluster.append({
-			'dots': liDot1,
-			'densitys': liDensity1,
-			'mindensity': Z1.ravel().min(),
-			'maxdensity': Z1.ravel().max(),
-			'contours': mapContour1
-			})
-
-		liCluster.append({
-			'dots': liDot2,
-			'densitys': liDensity2,
-			'mindensity': Z2.ravel().min(),
-			'maxdensity': Z2.ravel().max(),
-			'contours': mapContour2
-			})
-
-		self.write({'clusters': liCluster, 'mm': [xmin, xmax, ymin, ymax]})
-
-	def listZip(self, m1, m2):
-		list1 = list(m1)
-		list2 = list(m2)
-		return list(zip(list1, list2))
-
-	def measure1(self, n):
-		m1 = np.random.normal(size=n)
-		m2 = np.random.normal(scale=0.5, size=n)
-		return 2 + m1-m2, -1 + (m1+m2)
-
-	def measure(self, n):
-	    m1 = np.random.normal(size=n)
-	    m2 = np.random.normal(scale=0.5, size=n)
[…]

### 2019-04-22 code/server/handler/odhandler.py

@@ -1,366 +1,0 @@
-import tornado.web
-from tornado.options import options
-
-import pymongo
-from pymongo import MongoClient
-
-import setting
-
-from PIL import Image
-import io
-import os.path
-
-import json
-
-import subprocess
-
-
-class ChartHandler(tornado.web.RequestHandler):
-    def post(self):
-        va = self.get_argument('value');
-        st = int(self.get_argument('st'));
-        et = int(self.get_argument('et'));
-        ebid = int(self.get_argument('ebid'));
-        userId = va.split(',')
-
-        ods = {}
-        sumtrips = 0
-        ods, sumtrips = self.getpurpose(userId, st, et, ebid)
-
-        stringnumber = '['
-        flag = 1
-        for key in ods.keys():
-            if flag==1:
-                stringnumber += "{\"x\":"+str(key)+", \"y\":"+str(ods.get(key)*100//sumtrips)+"}"
-                flag = 2
-            else:
-                stringnumber += ",{\"x\":" + str(key) + ", \"y\":" + str(ods.get(key)*100//sumtrips) + "}"
-        stringnumber += "]"
-
-        result = {'number': stringnumber}
-        #print(result);
-        self.set_header('Access-Control-Allow-Origin', '*');
-        self.write(result);
-
-    def getpurpose(self, uidsinput, time1, time2, ebid):
-
-        mongo_url = "192.168.153.139:27017"
-        client = pymongo.MongoClient(mongo_url);
-        db = client['wechat']
-
-        collection = db["od"]
-        ods = {}
-        for j in range(len(uidsinput)):
-            cursor = collection.find({"uid": uidsinput[j]})
-
-            for item in cursor:
-                t = item['endminute']
-                bid = item['ebid']
-                p = item['purpose']
-
-                if (t >= time1) and (t <= time2) and (bid == ebid):
-                    if (p in ods):
-                        temp = ods.get(p)
-                        ods[p] = temp + 1
-                    else:
-                        ods[p] = 1
-
-        sumod = 0
-        for value in ods.values():
-            sumod = sumod + value
-
-        return ods, round(sumod)
-
-
-
-class DataHandler(tornado.web.RequestHandler):
-    def post(self):
-        va = self.get_argument('value');
-        st = int(self.get_argument('st'));
-        et = int(self.get_argument('et'));
-        userId = va.split(',')
-
-        ods = {}
-        sumtrips = 0
[…]

### 2019-04-22 code/server/handler/pointhandler.py

@@ -1,26 +1,0 @@
-
-import tornado.web
-from tornado.options import options
-
-import pymongo
-from pymongo import MongoClient
-
-import setting
-
-from PIL import Image
-import io
-import os.path
-
-import json
-
-import subprocess
-
-class TestHandler(tornado.web.RequestHandler):
-    def get(self, word):
-        print('getsurvey handler', word);       
-        self.write('ok');
-
-
-class IndexHandler(tornado.web.RequestHandler):
-	def get(self):
-		self.render('index.html')

### 2019-04-22 code/server/setting.py

@@ -1,5 +1,0 @@
-from tornado.options import define,options
-
-define("port",default=30030,help="run on th given port",type=int)
-#define("db", default="trajlit", help="database", type=str)
-#define("title", default="Survey of trajectory visual analytics", help="the topic of literature, e.g. trajlit", type=str)

### 2019-04-22 code/server/url.py

@@ -1,32 +1,0 @@
-#!/usr/bin/env python
-#coding:utf-8
-
-import sys
-# from imp import reload
-# reload(sys)
-# sys.setdefaultencoding('utf-8')
-
-from handler.pointhandler import IndexHandler
-from handler.pointhandler import TestHandler
-from handler.odhandler import DataHandler
-from handler.odhandler import ChartHandler
-from handler.odhandler import PurposeHandler
-from handler.odhandler import PClusterHandler
-from handler.hwhandler import HWHandler
-from handler.hwhandler import ActHandler
-
-from handler.kdehandler import KDEHandler
-
-url=[
-	(r'/', IndexHandler),
-    (r'/test/(\w+)', TestHandler),
-    (r'/window5', DataHandler),
-    (r'/window4', HWHandler),
-    (r'/window43', ActHandler),
-    (r'/chart', ChartHandler),
-    (r'/purpose', PurposeHandler),
-    (r'/pCluster', PClusterHandler),
-
-
-    # (r'/clusterKDE', KDEHandler),
-]

### 2019-04-22 template.tex

@@
 
-\section{Visual design}
+\section{Overview}
+\wqc{Adding a background. Expert discussion. Summarize the tasks below.-0419}
+\lmc{Add a paragraph to introduce the motivation of this work, where we derive the tasks via the interview with domain exports.-0420}
 
-\textcolor{blue}{Adding a background. Expert discussion. Summarize the tasks below.}
+\subsection{Goal}
 
-The design of the system is driven by tasks, to align the analysis of mobility patterns with individual characteristics.
-Before diving into the design of the system, we introduce the couple of specifical tasks the system intended for.
+\wqc{Common human mobility indicators: travel distance, travel time, travel frequency, radius of gyration and movement entropy. }\\
+\wq{Spatial attractiveness is an important concept in GIS.
+Explain why.
+To derive the details, we interview the expert in GIS.
+Some questions like, how citizens live in the city, where they live, work and entertain?
+Which place is popular?
+For different citizens, whether a place has the same attraction?
+...
+With these questions, we summarize them into the tasks below, which need to be answered by our system.} \lm{Below are some core research concerns derived from domain exports.}
+
+\textbf{Spatial Attractiveness} \lmc{Can we find some reference about Spatial Attractiveness. If not, we can give an explaination by ourselves.}
+
+\textbf{Attractiveness Diversity} \lmc{Same...}
+
+\textbf{Attractiveness Differences} \lmc{Same...}
+
+\subsection{Tasks}
+
+\lm{The exploration of core concepts above are resolved further with following tasks...
+to align the analysis of mobility patterns with individual characteristics.
+Before diving into the design of the system, introduce the couple of specifical tasks the system intended for.}
 
@@
 \end{figure}
+\fi
 
-With those design considerations, we develop a visual analytics system as Figure~\ref{fig:teaser} shows.
-It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}).
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\linewidth]{pictures/interfaceDraft.eps}
+ \caption{\wq{System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) View1: a XXXX visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) View2: data-driven profiles support users with organic individual perception; (d) View3: map view for movement of the chosen group; (e) View4: for ranking or comparison; (g) View5: top N kinds of citizens with social characteristics.}}
+ \label{fig:interfaceDraft}
+\end{figure}
+
+\section{Visual Design}
+\lm{With the design consideration (introduced in Section~\ref{}), we design a visual analytic system...} \lm{Show a overview figure, to introduce the relationship between multiple views}
+
+With those design considerations, we develop a visual analytics system as \wq{Figure~\ref{fig:interfaceDraft} shows.} \wqc{instead of fig.
+teaser} It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}).
 In the individual panel, interactive infographics, t-SNE visualization, and data-driven profiles support users to narrow the scope down to groups of individuals with interested characteristics.
@@
 
-\subsection{t-SNE Projection of Individuals}
-\textcolor{blue}{Not tsne.
-A octagon radar graph to position all citizens.
-A clustering algorithm for commend similar persons into a new group.(maybe: interactions to set the weight of each characteristic)}
+\wq{\subsection{XXXX Projection of Individuals}}
+\wqc{A octagon radar graph to position all citizens.
+A clustering algorithm for commend similar persons into a new group.(maybe: interactions to set the weight of each characteristic)} \lmc{Yes, I think an interactive weight adjustment is good.}
 

### 2019-04-23 manuscript/template.tex
updated

@@
 We interview the expert in GIS.
-There are some core research concerns derived from domain exports.
+\lm{They identify \textit{Spatial Attractiveness}, and their correlation with individual social characteristics as the core research concern.
+Furthermore, they want to explore the space diversity according to its attractiveness to individuals.} \lmc{I think first we introduce spatial attractivenss, which is well defined by previous work.
+Then we explain the diversity of lands in attractivess (we need to find a better term), which we define.
+I think it is ok.}
 
 \begin{itemize}
+
+  \item \textit{Magnitude of spatial attractiveness} How many persons could be attracted and how much the difficulty they overcome.
+\wqc{there is equation in related paper to support this.} \lmc{can you expand the spatial attractivenss, such as citing existing paper, explaining the concept, maybe with the equation is better.}
+
   \item \textit{Diversity of spatial attractiveness} Two types of diversity: diversity of the attracted persons, and diversity of attractiveness indicators.
-\wqc{cannot find this concept in papers, and, i am not sure about ``indicator"}
-  \item \textit{Magnitude of spatial attractiveness} How many persons could be attracted and how much the difficulty they overcome. \wqc{there is equation in related paper to support this.}
+\wqc{cannot find this concept in papers, and, i am not sure about ``indicator"} \lmc{I defined this?}
+
 \end{itemize}
@@
 \item \textit{Task 1: Identify the group with specific individual characteristics\wqc{What kind of citizens tend to be attracted?}}: to get groups of people with common or close attributes, to explore the correlation among individual characteristics.
-\item \textit{Task 2: Why the attracted citizens are attracted?}: to explore ...
-\item \textit{Task 3: How many citizens are extracted?}: to express ...
-\item \textit{Task 4: Where do the attracted citizens come from?}: City has different function areas.
+\item \textit{Task 2: What is the correlation between space and citizens?
+(Spatial Attractiveness)} to understand...
+group of citizens are attracted to different places, e.g., to know the similarities and differences between different groups in their mobility patterns, to investigate the relationship between movement and individual characteristics.
+
+\item \textit{Task 3: What is the detailed properties of attractive differences?} ...
+How many citizens are extracted, the origins (Where do the attracted citizens come from?) What is the attractive differences over groups?
+
+% City has different function areas. Some areas meet all the basic requirements of citizens' living activities, while some cannot. ...
+
+% \item \textit{Task 2: Why the attracted citizens are attracted?}: to explore ... \lmc{I don't think we can explain why...}
+% \item \textit{Task 3: How many citizens are extracted?}: to express ... \lmc{I think it is just numbers, too weak to be a task}
+% \item \textit{Task 4: Where do the attracted citizens come from?}: \lmc{also here}.
+City has different function areas.
 Some areas meet all the basic requirements of citizens' living activities, while some cannot.
@@
  \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\linewidth]{pictures/interfaceDraft.pdf}
+ \includegraphics[width=\linewidth]{pictures/interfaceDraft.eps}
  \caption{\wq{System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) View1: a XXXX visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) View2: data-driven profiles support users with organic individual perception; (d) View3: map view for movement of the chosen group; (e) View4: for ranking or comparison; (g) View5: top N kinds of citizens with social characteristics.}}
@@
 \wq{\subsection{A glyph design to show travel indicator (in view3, in case1)}
-We design a kind of glyph to express a high-dimensional travel indicators. It will be embeded in the map view\wqc{for case1}.
+We design a kind of glyph to express a high-dimensional travel indicators. It will be embeded in the map view\wqc{for case1}. \lmc{This is great! more indicators, the better. }
 The elements may be included in the glyph:
@@
 We design a kind of glyph to express spatial attractiveness.
-The elements may be included in the glyph:
+The elements may be included in the glyph: \lmc{We can explain each of the indicator a bit. But do it later after the implementation.}
 \begin{itemize}
@@
 We design a kind of glyph to express spatial attractiveness.
-The elements may be included in the glyph:
+The elements may be included in the glyph: \lmc{we need to find terms similar to above}
 \begin{itemize}
-  \item how many kinds of purpose?
+  \item \lm{Purpose Number} how many kinds of purpose?
   \item  the percentage of each purpose?
@@
 \wq{As Figure~\ref{case2draft} shows, in view3, glyph represents $\textbf{the quantity}$ and $\textbf{value of mixture of purposes}$.
-\wqc{(if we decide to give a computing equation to define it.)} in view4, ranking of each grid based on the quantity of each purpose.}
+\wqc{(if we decide to give a computing equation to define it.)}\lmc{I think we can define a equation to compute it.} in view 4, ranking of each grid based on the quantity of each purpose.}
 \begin{figure}[htb!]
@@
 \wqc{aim: select one purpose to show how many and where and how long. Use View3 and view4.} 
+\lmc{So as far as I understand, in this case, we focus on exploring the attributes or properties of spatial attratctiveness, right? such as the number, distance, origins, etc.}
 

### 2019-05-03 manuscript/template.tex
new one 0503, with all figures in draft format

@@
 
-\title{Unfolding the City: \wq{Exploring Urban Spatial Attractiveness with Individual Characteristics}}
+\title{Unfolding the City: \wq{Exploring Urban Spatial Attractiveness with Individual Social Characteristics}}
 %\thanks{Grants or other notes
@@
 \section{Overview}
-\wqc{Adding a background. Expert discussion. Summarize the tasks below.-0419}
-\lmc{Add a paragraph to introduce the motivation of this work, where we derive the tasks via the interview with domain exports.-0420}
 
@@
 \begin{itemize}
-
-  \item \textit{Magnitude of spatial attractiveness} How many persons could be attracted and how much the difficulty they overcome.
+  \item \textit{Spatial attractiveness} How many persons could be attracted and how much the difficulty they overcome.
 \wqc{there is equation in related paper to support this.} \lmc{can you expand the spatial attractivenss, such as citing existing paper, explaining the concept, maybe with the equation is better.}
@@
 \wqc{cannot find this concept in papers, and, i am not sure about ``indicator"} \lmc{I defined this?}
-
 \end{itemize}
@@
  \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\linewidth]{pictures/interfaceDraft.eps}
+ \includegraphics[width=\linewidth]{pictures/interface53}
  \caption{\wq{System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) View1: a XXXX visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) View2: data-driven profiles support users with organic individual perception; (d) View3: map view for movement of the chosen group; (e) View4: for ranking or comparison; (g) View5: top N kinds of citizens with social characteristics.}}
@@
 A glyph is intended for quick understanding and aligned comparison.
-\lm{Dual glyphs are designed, to illustrate the information of individual from two different perspectives, i.e., detailed inspection of individuals and efficient comparsion over multiple individuals.}
+\lm{Dual glyphs are designed, to illustrate the information of individual from two different perspectives, i.e., detailed inspection of individuals and efficient comparison over multiple individuals.}
 
 \paragraph{Star-like Glyph} \lm{To compare over multiple individuals, a star-like glyph is designed to summary each individual, to ease the comparison by common coordination configurations....}
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\linewidth]{pictures/star53}
+ \caption{\wq{star-like glyph for a group of citizens.}}
+ \label{fig:interfaceDraft}
+\end{figure}
 
@@
 
-\wq{\subsection{XXXX Projection of Individuals}}
-\wqc{A octagon radar graph to position all citizens.
-A clustering algorithm for commend similar persons into a new group.(maybe: interactions to set the weight of each characteristic)} \lmc{Yes, I think an interactive weight adjustment is good.}
+\subsection{T-SNE Projection}
 
@@
 
-\iffalse
-\subsection{2.5D Spatial Visualization}
-\label{subsec:25D}
+\subsection{HAVE NO TILE FOR THIS}
+We design a kind of glyph to express a high-dimensional travel indicators. It will be embeded in the map view. \wqc{lack of a FIGURE}
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{
-\resizebox*{9cm}{!}{\includegraphics{pictures/space1.eps}}}\hspace{5pt}
-\subfigure[]{
-\resizebox*{9cm}{!}{\includegraphics{pictures/space2.eps}}}\hspace{5pt}
-\caption{2.5D Spatial Visualization: (a) 2.5D spatial visualization with z-axis to encode addition information; (b) detail slicing in 2.5D space.}
-\label{fig:2.5D}
-\end{figure}
-
-Embedding multiple variables in the spatial map is a challenging problem.
-Distorting 2D spatial for better space usage, such as the partial route embedding~\citep{sun2016embedding} is an effective method when there are a few local foci.
-When it comes to the global visualization, there is always a trade-off between occlusion-free and the compact spatial perception.
-Following the idea of stacking 2.5D space design~\citep{Tominski2012_stacking}, the space in this work is embedded in 2.5D space, to relax the z-axis for additional abstract information encoding.
-
-Figure~\ref{fig:2.5D}(a) shows the 2.5D visualization.
-The spatial map consists of Traffic Analysis Zone (TAZ), which is the unit of geography holding a certain number of people.
-For the 2.5D, each TAZ is grown as a prism whose height and color are developed to encode abstract information, e.g., the occurrence of visiting.
-With difference encoding choices, it is capable to visualize the correlation between spatial and different attributes (\textit{C4}).
-For example, in Figure~\ref{fig:2.5D}(a), prisms' height and color both encode the ratio of none-routine trips (such as go entertainment, go hospital, etc.) in the whole.
-For better 3D visual perception, lighting is turned on.
-Also, a lid is laid on the top of each prism to clearly bound its extent at the z-axis.
-
-Several interactions are integrated into the spatial view to alleviating the occlusion problem (\textit{C5}).
-The manipulation of 2.5D view supports users with rotate, zoom, pan operations, which are so continuously flexible that users probably find a suitable observing point.
-In the cases where occlusion is inevitable, an interaction named as \textit{Detail Slicing} is developed, as Figure~\ref{fig:2.5D}(b) shows.
-Detail Slicing is the operation to put a cross-section in the 2.5D space to expose the TAZ inside.
-To contextualize the cross-section, TAZs are visually adapted according to the intersection by ray casting.
-The TAZ in the foreground will be hidden, the intersected TAZs will be fully visualized and the ones in the background will be in semi-transparency.
-
-To compare the mobility patterns across different groups of people, a Small Multiple dock is used to reserve the ever explored interesting result (Figure~\ref{fig:teaser}(f)).
-To simply the comparison over spatial distribution, the snapshot is also rendered in the 2.5D space, which maintains the same interactions as the main 2.5D space does.
-\fi
-
-\wq{\subsection{A glyph design to show travel indicator (in view3, in case1)}
-We design a kind of glyph to express a high-dimensional travel indicators. It will be embeded in the map view\wqc{for case1}. \lmc{This is great! more indicators, the better. }
-The elements may be included in the glyph:
+The elements can be represented in the glyph:
 \begin{itemize}
-  \item (home-work distance)
-  \item travel distance
-  \item travel radius
-  \item travel frequency
-\end{itemize}}
-
-\wq{\subsection{A glyph design to show attractiveness (in view3, in case2)}
-We design a kind of glyph to express spatial attractiveness.
-The elements may be included in the glyph: \lmc{We can explain each of the indicator a bit. But do it later after the implementation.}
-\begin{itemize}
-  \item quantity
-  \item distance
-\end{itemize}}
-
-\wq{\subsection{A glyph design to show attractiveness diversity(in view3, in case3)}
-We design a kind of glyph to express spatial attractiveness.
-The elements may be included in the glyph: \lmc{we need to find terms similar to above}
-\begin{itemize}
-  \item \lm{Purpose Number} how many kinds of purpose?
-  \item  the percentage of each purpose?
+  \item value
+  \item distribution
+  \item proportion
 \end{itemize}
-
-(if comparison between groups, the glyph up, show the diversity of multiple groups at the same time.)}
 
@@
  \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/case1draft}
+ \includegraphics[width=\columnwidth]{pictures/c1-s3-53}
  \caption{Home Distributions of the Four Groups}
@@
 
-\subsection{Case 2: Diversity of spatial attractiveness of indicators}
+\subsection{Case 2: Spatial Attractiveness}
+\wqc{aim: select one purpose to show how many and where and how long.}
+\lmc{So as far as I understand, in this case, we focus on exploring the attributes or properties of spatial attratctiveness, right? such as the number, distance, origins, etc.}
+
+\wq{When zooming in to explore with only one purpose, we demonstrate the use of the system for exploring the magnitude of spatial attractiveness.}
+
+\wq{As Figure~\ref{case3draft} shows, in view3, glyph represents $\textbf{the quantity}$ and $\textbf{how many grids are linked(i.e. area)}$ and $\textbf{distribution of distances}$. }
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/c2-s2-53}
+ \caption{For purpose of shopping: (a) the rich; (b) the poor.}
+ \label{case3draft}
+\end{figure}
+
+\wq{After clicking a target grid, show $\textbf{where are the linked grids}$ and $\textbf{the quantity of each linked grid}$ and $\textbf{distance}$.
+Compare two grid which have similar quantity, the distributions differ.}
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/c2-click-s2-53}
+ \caption{For purpose of shopping: (a) spatial attractiveness of the poor; (b) Grid1; (c) Grid2.}
+ \label{case3draft}
+\end{figure}
+
+\iffalse
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/case2}
+ \caption{Home-work distances of different groups: (a) with different salary levels; (b) with or without house.}
+ \label{case2}
+\end{figure}
+
+Home-work distance is an essential metric in economics, geography, and sociology.
+It refers to the distance between house and workplace.
+It is influenced by many factors like transportation, housing, land use, etc.
+Understanding the home-work distance of a region helps to evaluate whether the region is well planned or not.
+In this case, we demonstrate our system's help in home-work distance understanding.
+
+Considering income potentially determines where people live, we use income as the characteristics to select three groups, the group over 500K, the group during 200-300K and the group less than 100K.
+In Figure~\ref{case2}, the height of the bar stands for visiting frequency of the TAZ and its color encodes the average home-work distance, red for close and yellow for far.
+As Figure~\ref{case2}(a) shows, for all the three groups in different income levels, most of the TAZs have dark red or red color which indicates the home-work distance is generally short, especially in downtown.
+Only those with less than 100K salary work outside the center, such as the space in the green circle.
+When comparing the three groups in the downtown area, it is seen that it takes more time to go to work in Futian District as the decrease of the income.
+
+We explore the home-work distance of groups with and without a house.
+Figure~\ref{case2}(b) shows the close-up views.
+It is found that the Nanshan District has a shorter home-work distance for individuals without a house, while Futian District has shorter for those with a house.
+Nanshan is relatively newer to Futian so that there might be more easily-accessible houses to be rent.
+\fi
+
+\subsection{Case 3: Diversity of spatial attractiveness of indicators}
 \wqc{aim: with mixed purposes, show attractiveness quantity and entropy.
@@
  \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/case2draft}
+ \includegraphics[width=\columnwidth]{pictures/c3-53}
  \caption{Trip purposes distribution of four groups with different jobs}
@@
 
-\subsection{Case 3: Magnitude of Spatial Attractiveness}
-\wqc{aim: select one purpose to show how many and where and how long. Use View3 and view4.} 
-\lmc{So as far as I understand, in this case, we focus on exploring the attributes or properties of spatial attratctiveness, right? such as the number, distance, origins, etc.}
-
-\wq{When zooming in to explore with only one purpose, we demonstrate the use of the system for exploring the magnitude of spatial attractiveness.}
-
-\wq{As Figure~\ref{case3draft} shows, in view3, glyph represents $\textbf{the quantity}$ and $\textbf{how many grids are linked(i.e.
-area)}$ and $\textbf{distribution of distances}$.
-in view4, show $\textbf{where are the linked grids}$ and $\textbf{the quantity of each linked grid}$ and $\textbf{distance}$.
-\wqc{not sure the form in view4, map or chart?
-if map, 1D or 2.5D?}}
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/case3draft}
- \caption{Home-work distances of different groups: (a) with different salary levels; (b) with or without house.}
- \label{case3draft}
-\end{figure}
-
-\iffalse
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/case2}
- \caption{Home-work distances of different groups: (a) with different salary levels; (b) with or without house.}
- \label{case2}
-\end{figure}
-
-Home-work distance is an essential metric in economics, geography, and sociology.
-It refers to the distance between house and workplace.
-It is influenced by many factors like transportation, housing, land use, etc.
-Understanding the home-work distance of a region helps to evaluate whether the region is well planned or not.
-In this case, we demonstrate our system's help in home-work distance understanding.
-
-Considering income potentially determines where people live, we use income as the characteristics to select three groups, the group over 500K, the group during 200-300K and the group less than 100K.
-In Figure~\ref{case2}, the height of the bar stands for visiting frequency of the TAZ and its color encodes the average home-work distance, red for close and yellow for far.
-As Figure~\ref{case2}(a) shows, for all the three groups in different income levels, most of the TAZs have dark red or red color which indicates the home-work distance is generally short, especially in downtown.
-Only those with less than 100K salary work outside the center, such as the space in the green circle.
-When comparing the three groups in the downtown area, it is seen that it takes more time to go to work in Futian District as the decrease of the income.
-
-We explore the home-work distance of groups with and without a house.
-Figure~\ref{case2}(b) shows the close-up views.
-It is found that the Nanshan District has a shorter home-work distance for individuals without a house, while Futian District has shorter for those with a house.
-Nanshan is relatively newer to Futian so that there might be more easily-accessible houses to be rent.
-\fi
-
 \section{Conclusion}

### 2019-05-05 structure/structure.tex
new folder Structure

--- 2019-05-03 manuscript/template.tex
@@
 
-\title{Unfolding the City: \wq{Exploring Urban Spatial Attractiveness with Individual Social Characteristics}}
+\title{Unfolding the City: Exploring Urban Spatial Attractiveness with Individual Social Characteristics}
 %\thanks{Grants or other notes
@@
 \begin{abstract}
-A city is shaped not only by its assembled infrastructures but also the people living inside it.
-People in a wide range of individual characteristics visit places with different weights and preferences, sculpturing the city into a space of diverse mobility patterns.
-Different from the well study of anonymous travel behaviors, the mobility patterns of characterized individuals, is less studied because of the challenges in collection and analysis of data with privacy.
-In this work, we take a step forward and perform an online census to collect individual profiles and movements from large-scale volunteers.
-Then we develop a visual analytic system to investigate the mobility patterns of groups by specifying characteristics.
-To facilitate the identification of characterized groups, individuals are embedded in t-SNE projection for an abstract overview as well as drawn as vivid graphics by a data-driven profile method for detail examination.
-A 2.5D spatial visualization is proposed to maintain a compact multivariable analysis by relaxing the z-axis to encode information, such as visiting frequency, demands, traveling distance, etc.
-Together with the cross-filter and flexible 2.5D interactions, the effectiveness and usability of the system are well demonstrated by a study made in Shenzhen.
 
-\keywords{Visual analytics \and mobility pattern \and individual characteristics \and city }
+\keywords{Visual analytics \and spatial attractiveness \and individual characteristics \and city }
 % \PACS{PACS code1 \and PACS code2 \and more}
@@
 Does it depend on the particular characteristics or situation of the persons considering the attractiveness, in what phase in life the persons find themselves, or are there some common features, perhaps place characteristics that are viewed positively by all, independently of context?
-
 \fi
 
-\label{intro}
-\wqc{change mobility pattern to spatial attractiveness}\\
-The science fiction \textit{Folding Beijing}~\citep{hao2016_foldingbeijing} depicts a world where three classes of people live in independent spatial-temporal patterns, though sharing the same earth surface.
-This is an artistical metaphor for one potential fact that people make different decisions in visiting places according to individual determinants, such as social, economic, educational factors, etc.
-This phenomenon has attracted the research interest for a long time in the sociological field.
-Back to 1970, Pahl~\citep{pahl1975whose} posed the question `whose city` and interest in understanding the territorial inequalities.
-Contemporary contestation also continually raise the banner `The City Belongs to All!'~\citep{Mayer2017_whosecity}.
-Having a good understanding of how the mobility patterns relate to characterized individuals sheds light on region utilization, diversity mix-up, and opportunities promotion.
+\paragraph{bgm}
 
-In the past decades, the power of visual analytics in exploring spatial-temporal data has been recognized and well developed.
-Transportation problems are answered by various movement data, such as traffic jams in taxi GPS trajectoires~\citep{wang2013visual}, interchanging flows in public transportation~\citep{zeng2013visualizing}, etc.
-The presence of social media applications fuels the spatial analysis with rich semantic texts, so researchers get the chances to explore the thematic meaning of the moving behavior, such as events~\citep{chen2017map} or topics~\citep{bosch2013scatterblogs2}.
-Those works essentially contribute in deepening the contextual understanding of moving activity.
-But they rarely combine the mobility with individuals' characteristics because which cannot be 100\% inferred from social media profiles.
-There is still a research gap in exploring the relationship between mobility pattern and characteristics.
+\paragraph{past, trajectory, not social characteristics}
 
-In this work, we contextualize the analysis of mobility pattern in the backcloth of individual characteristics.
-Our motivation is to fuse the movement data with individuals' profiles in an attempt to ascertain the dynamics pattern of groups with different characteristics.
-To this, we need to get the characterized information of movers.
-The sensitivity issue in privacy data is one of the main challenges.
-The conventional offline census takes lots of effort and too much time to be out of date.
-With the wide use of the mobile device, it is possible to count information online.
-In this work, with a census survey released via social media application, we ran an online demographical collection campaign.
-Then we developed a visual analytics system to explore the mobility patterns centered around people.
-The system incorporates visualizations of individuals' characteristics, including t-SNE for an overview and data-driven profile visualization for the detailed check, as well as 2.5D spatial visualization to explore the mobility patterns.
-Finally, applying our method in Shenzhen, several cases are derived to demonstrate the powers of our method.
-There are two contributions of this work:
+\paragraph{in this paper}
 
-(1) investigate mobility patterns with characteristics, which is a natural step into research of social understanding of the city.
-
-(2) develop a visual analytic system, whose effectiveness and usability is well demonstrated by a study made in Shenzhen.
+\paragraph{novelty}
 
 \section{Related work}
-
-This work concerns the research topic of spatial data visual analytics.
-Spatio-temporal data has three components, i.e., spatial, temporal and thematic~\citep{andrienko2013visual}.
-Lots of related work focus on the spatio-temporal analysis in movement data, in the absence of thematic information.
-The presence of geotagged social media data flourishes the exploration of thematic information along with movement.
-By analyzing the texts, those work explain what drive the moving activities or what is resulted from.
-This work continues the thematic research in movement data but focuses more on individual characteristics.
-Landed by a census experiment, this work is able to analyze the profile information directly, to get rid of indirect data inferred from social media data as other related works do.
-
-\subsection{Movement data analysis}
- With the development of location-acquisition techniques, massive spatial trajectories are collected, to keep track of the trajectories of various moving objects.
-Many techniques have been proposed to process, mine trajectory~\citep{Zheng2015_trajectory}.
-In the field of visualization and visual analytics, spatial visualizations are specifically designed for the time, locations, spatial-temporal information and other properties in the traffic data~\citep{chen2015survey}.
-A large number of visual analytics tools and applications cover situation-aware exploration, pattern discovery and traffic situation monitoring.
-Wang et al~\citep{wang2013visual} extract the traffic jam propagation graph extraction to reveal underlying data patterns.
-Guo et al.~\citep{guo2011tripvista} and Zeng et al.~\citep{zeng2013visualizing} construct geographical regions and visually aggregate the in-between movements as flows.
-To discover the route travel patterns, Lu et al.~\citep{lu2015trajrank} propose TrajRank to explore the route travel behavior based on ranking.
-For multiple routes, Liu et al.~\citep{liu2011_routediversity} study the route diversity between locations and Lu et al.~\citep{Lu2017_multipleroute} explore the route choice behavior among multiple routes.
-
-\subsection{Geo-tagged Social Media Data Analysis}
-As the presence of social media services, social media data with geo-tags are collected to track people's movements in daily lives.
-As an analog of remote sensing data in social science research, the geospatial big data has been proposed as social sensing ~\citep{liu2015social}.
-Hence, analyzing movement information along with rich text has become a hot research area in recent years.
-Those works infer thematic information from the semantic texts.
-Cao et al.~\citep{cao2012whisper} propose \textit{Whisper} for tracing the pathways of tweets on a spatial hierarchical layout, to investigate how information flow among multiple places.
-Krueger et al.~\citep{krueger2014visual} used GPS and location-based service data to support the analysis of movement behaviors.
-Chen et al.~\citep{chen2016interactive} present a visual analytics system to support the exploration of sparsely sampled trajectory from social media.
-Some other researchers tend to infer real information, such as names, gender, etc, from social media data~\citep{peddinti2014internet}, to break down the demographic characteristics of social media users.
-Luo et al.~\citep{luo2016explore} derive race, gender, and age as three demographics dimensions to analyze its impact on the urban human mobility patterns.
-Since real information is not enforced in social media, the wrong inferring is inevitable.
-Longley et al.~\citep{Longley2015}~\citep{Paul2016_twitter} identifies and assess the biases inherent in social media usage in social research and evaluate the deployment of social media data in research applications.
 
@@
 Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\citep{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of the population in the city.
-
-% In the report (looking for some report), the penetration of mobile device is \m{XXX}, almost every XX people got a Mobile Phone in the urban.
 
@@
 
-% Trips are uploaded in a wide range of purpose in addition to home, work, but also includes XX entertainment, visiting, etc.
-The diverse purposes make it possible to characterize the flows across the city between different functional places.
-
 Because there is always inevitable bias inherent in fully representing the ground truth of the population, the preliminary statistical analysis shows positive sign of a relatively even sampling of the population.
@@
 \section{Overview}
+By communicating with domain expert, we summarize the analytic tasks identified from the interviews of domain experts.
+Aimed at these tasks, we derive design considerations and introduce the workflow of the proposed visual analytics system.
 
-A discussion with experts in GIS. We summarize the analytic tasks identified from the interviews of domain experts. Then the workflow of the proposed visual analytics system.
+\subsection{Background}
 
-\subsection{Goal}
-\wqc{Common human mobility indicators: travel distance, travel time, travel frequency, radius of gyration and movement entropy. }\\
-
-Spatial attractiveness is an important concept to evaluate ...
-in commercial activity, tourism and urban research.
-We interview the expert in GIS.
-\lm{They identify \textit{Spatial Attractiveness}, and their correlation with individual social characteristics as the core research concern.
-Furthermore, they want to explore the space diversity according to its attractiveness to individuals.} \lmc{I think first we introduce spatial attractivenss, which is well defined by previous work.
-Then we explain the diversity of lands in attractivess (we need to find a better term), which we define.
-I think it is ok.}
+For understanding how to express spatial attractiveness, we have several interviewers with an expert in GIS who works on human mobility and urban informatics.
+The experts pointed out that the study of social-spatial interactions has become more important with big and open data evolved in.
+Instead of evaluated by static indicators, such as the characteristics of the spatial facilities, spatial attractiveness can be evaluated dynamically with human movement data.
+People have their own preferences when they go out for a specific purpose.
+It reflects the attractiveness of the place they selected.
+When the research scale is expanded into city-scale, whether spatial attractiveness is similar of the citizens with similar social characteristics.
+However, for GIS researchers, there is no efficient and effective methods which help to explore spatial attractiveness, citizens with multiple social characteristics, and their relationships.
+After several rounds of interviews with experts, we summarize the main analysis criteria below:
 
 \begin{itemize}
-  \item \textit{Spatial attractiveness} How many persons could be attracted and how much the difficulty they overcome.
-\wqc{there is equation in related paper to support this.} \lmc{can you expand the spatial attractivenss, such as citing existing paper, explaining the concept, maybe with the equation is better.}
+\item \textit{Multiple social characteristics}
 
-  \item \textit{Diversity of spatial attractiveness} Two types of diversity: diversity of the attracted persons, and diversity of attractiveness indicators.
-\wqc{cannot find this concept in papers, and, i am not sure about ``indicator"} \lmc{I defined this?}
+\item \textit{Spatial attractiveness} In urban planning and GIS, the definitions of spatial attractiveness is based on gravity model\wqc{add refer}.
+It means the more distant the less attractiveness.
+Hence, both the quantity of people attracted and movement distances are two crucial concepts to be explored.
+
+\item \textit{Attractiveness diversity} In urban planning, functional area is an important concept.
+When the area has more functions, for people here, their living requirements are more easily met, the attractiveness diversity of the area is higher.
+......
+
 \end{itemize}
-With these questions, we summarize them into the tasks below, which need to be answered by our system.
 
 \subsection{Tasks}
-\lm{The exploration of core concepts above are resolved further with following tasks...
+The exploration of core concepts above are resolved further with following tasks...
 to align the analysis of mobility patterns with individual characteristics.
-Before diving into the design of the system, introduce the couple of specifical tasks the system intended for.}
-
-%The design of the system is driven by tasks, to align the analysis of mobility patterns with individual characteristics.
 Before diving into the design of the system, introduce the couple of specifical tasks the system intended for.
@@
 group of citizens are attracted to different places, e.g., to know the similarities and differences between different groups in their mobility patterns, to investigate the relationship between movement and individual characteristics.
-
 \item \textit{Task 3: What is the detailed properties of attractive differences?} ...
 How many citizens are extracted, the origins (Where do the attracted citizens come from?) What is the attractive differences over groups?
-
-% City has different function areas. Some areas meet all the basic requirements of citizens' living activities, while some cannot. ...
-
-% \item \textit{Task 2: Why the attracted citizens are attracted?}: to explore ... \lmc{I don't think we can explain why...}
-% \item \textit{Task 3: How many citizens are extracted?}: to express ... \lmc{I think it is just numbers, too weak to be a task}
-% \item \textit{Task 4: Where do the attracted citizens come from?}: \lmc{also here}.
-City has different function areas.
-Some areas meet all the basic requirements of citizens' living activities, while some cannot.
-...
-to know the similarities and differences between different groups in their mobility patterns, to investigate the relationship between movement and individual characteristics.
 \end{itemize}
@@
 
-% Classification method, flow clustering method, Semantic representation.
-
-\iffalse
+\section{Visual Design}
 \begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\linewidth]{pictures/teaser.eps}
- \caption{System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) a t-SNE visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) data-driven profiles support users with organic individual perception; (d) group of interested individuals can be saved; (e) movement of the chosen group is visualized and explored in 2.5D main view; (f) a dock is provided to restore and compare findings; (g) different choices of 2.5D encoding can be selected.}
- \label{fig:teaser}
-\end{figure}
-\fi
-
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \centering 
  \includegraphics[width=\linewidth]{pictures/interface53}
- \caption{\wq{System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) View1: a XXXX visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) View2: data-driven profiles support users with organic individual perception; (d) View3: map view for movement of the chosen group; (e) View4: for ranking or comparison; (g) View5: top N kinds of citizens with social characteristics.}}
+ \caption{\wqc{to be edit.
+System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) View1: a XXXX visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) View2: data-driven profiles support users with organic individual perception; (d) View3: map view for movement of the chosen group; (e) View4: for ranking or comparison; (g) View5: top N kinds of citizens with social characteristics.}}
  \label{fig:interfaceDraft}
@@
 
-\section{Visual Design}
+With those design considerations described before, we develop a visual analytics system as Figure~\ref{fig:interfaceDraft} shows.
+It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}).
+In the individual panel, interactive infographics, t-SNE visualization, and data-driven social profiles support users to narrow the scope down to groups of individuals with interested characteristics.
+With the chosen group of individuals, spatial attractiveness is visualized and explored in a map view with the \wqc{no name} glyph we designed.
 
-With those design considerations (introduced in Section~\ref{}), we develop a visual analytics system as Figure~\ref{fig:interfaceDraft} shows.
-It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}).
-In the individual panel, interactive infographics, t-SNE visualization, and data-driven profiles support users to narrow the scope down to groups of individuals with interested characteristics.
-With the chosen group of individuals, its moving related information is visualized and explored in a 2.5D spatio-temporal view.
-\lmc{Show a overview figure, to introduce the relationship between multiple views}
+\subsection{Social Profile Visualization}
+To express the multiple dimensional social characteristics, we use three scales: bar glyph for all citizens, octagon glyph for a group of persons, and cartoon glyph for one person.
 
-% overview of the data. Encode information but also allow users to set multiple criteria (\textit{C1}). Support users to slice the data by different domains.}
-% Semantic understanding of social characteristics.
+\paragraph{Bar Glyph}
+As shown in Figure~{\ref{fig:interfaceDraft}}(a), bar glyphs are used to encode quantitative relationships.
+For each characteristic, we compute the quantity and the percentage of each type, and encode it in the length of the bar.
+Interaction is also bound.
+When clicking a bar, filtering will be done, and the filtering result will be used in grouping phrase.
 
-\subsection{Data-driven Profile Visualization}
-
+\paragraph{Octagon Glyph}
 Glyph-based visualization~\cite{borgo2013glyph} is the form of visual design to compose multivariable into a collection of unified visual symbols, known as a glyph.
 A glyph is intended for quick understanding and aligned comparison.
-\lm{Dual glyphs are designed, to illustrate the information of individual from two different perspectives, i.e., detailed inspection of individuals and efficient comparison over multiple individuals.}
 
-\paragraph{Star-like Glyph} \lm{To compare over multiple individuals, a star-like glyph is designed to summary each individual, to ease the comparison by common coordination configurations....}
+\paragraph{Cartoon Glyph}
+Among glyph design, Chernoff Face (Chernoff, 1973) represents data variables by the different features of a cartoon face.
+Following the idea of Chernoff Face, we design a type of glyph, a graphical representation of people with specific individual characteristics.
+The idea behind using faces is that humans easily recognize faces and notice small changes without difficulty (C1).
+Those visual profiles are intended for intuitive visual understanding, from abstract to concrete and semantic understanding, to support users to target the interested individual groups effectively.
 
 \begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\linewidth]{pictures/star53}
- \caption{\wq{star-like glyph for a group of citizens.}}
- \label{fig:interfaceDraft}
+ \centering 
+ \includegraphics[width=0.6\columnwidth]{pictures/cartoonglyph}
+ \caption{***********************}
+ \label{fig:cartoon}
 \end{figure}
 
-\paragraph{Cartoon Glyph} ...
-Among glyph design, Chernoff Face~\cite{chernoff1973use} represents data variables by the different features of a cartoon face.
-Following the idea of Chernoff Face, we design a type of glyph, a graphical representation of people with specific individual characteristics.
-The idea behind using faces is that humans easily recognize faces and notice small changes without difficulty (\textit{C1}).
-Those visual profiles are intended for intuitive visual understanding, from abstract to concrete and semantic understanding, to support users to target the interested individual groups effectively.
-
-Figure~\ref{fig:design_profile} shows the legend for the user profile.
-The eight domains are encoded by visual symbols and organically organized in a human figure.
+Figure~\ref{fig:cartoon} shows the legend for the user profile.
+The eight domains are encoded by vi- sual symbols and organically organized in a human figure.
 There are basically three types of variables to drive the figure, i.e., the numeric, categorical and boolean ones.
@@
 For the categorical attributes such as job, visual symbols are designed separately for better semantic meaning.
-For the boolean attribute like car, house, a symbol is designed to indicate its existence.
+For the boolean at- tribute like car, house, a symbol is designed to indicate its existence.
 With this consideration, the domains are designed as follows:
-
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/design_profile}
- \caption{Design Profile: the eight characteritical domains are encoded and organized in an organic human figure.}
- \label{fig:design_profile}
-\end{figure}
-
-% For numeric attributes.
-
-% By different composition, stimulus pattern which has the abstract demographic measurement of individuals.
 
@@
 
-\subsection{T-SNE Projection}
+\subsection{T-SNE Projection of Individuals}
 
@@
 
-\subsection{HAVE NO TILE FOR THIS}
-We design a kind of glyph to express a high-dimensional travel indicators. It will be embeded in the map view. \wqc{lack of a FIGURE}
+\subsection{Location-based multidimensional grid visualization}
+We design a kind of glyph to express a high-dimensional travel indicators. It will be embed in the map view.
 
@@
 \lmc{Add a section to introduce the domain experts' feedback}
-
 \lm{We interview XX domain experts from the GIS field. XX of them are with ... The procedure went as following. We first introduce them the system an...}
 
-\section{Case study}
+\section{Case studies}
 
@@
 
-\wq{\subsection{Case 1: find diversity of citizens based on social characteristics}}
-\wqc{Aim1: use view1 and view2 for groups. Aim2: show their basic activity spaces in view3 and view4. text no changes yet.}
-
-This work is inspired and motivated by the implication in science fiction~\textit{Folding Beijing}, which is that people are categorized into three classes and behave in the parallel spatial-temporal patterns.
-The first cast explores whether the folding city exists in reality or not.
-
-\begin{figure}[htb!]
- \centering
- \includegraphics[width=\columnwidth]{pictures/case1_1}
- \caption{Four Groups Divided by Income and Education Characteristics}
- \label{case11}
-\end{figure}
-
-Although it is incomplete, income and education are two of the most essential characteristics to tag an individual with a good resource or not.\\
-\wq{EDIT paragraph below. not just give number, use view1 and view2 to filter the target groups.}\\
-As Figure~\ref{case11} shows, taking income and education as the two dimensions, taking 300K yuan as the border between high and low income and an undergraduate bachelor degree as the border between high and low education level, four different groups are generated in the four quadrants.
-In the first quadrant, individuals are rich and well educated, who are in a group of so-called \textit{top aristocracy}.
-The second quadrant holds the group of \textit{new rich}, i.e., individuals with high income but low education income.
-In the third quadrant, they are the \textit{underclass} who has both low income and education level.
-The fourth quadrant is \textit{Antizen}, which is a new word to describe people have a good education but earn little.
-
-Figure~\ref{case11} shows the top 12 profiles with the maximum population in each group.
-In each group, other characteristics surprisingly demonstrate the high correlation to income and education.
-For example, almost all of the \textit{top aristocracy} is with the residential license,  house, and car.
-On the contrary, \textit{underclass} do not have the residential license residence, neither the house nor the car.
-Most of \textit{New rich} has a house and work in the service industry.
-
-Before diving into the complex mobility pattern analysis, we explore the home distribution of the four groups.
-As Figure~\ref{case1draft} shows, \textit{top aristocracy} and most of \textit{new rich} live concentrated in the downtown area of Shenzhen, where the living cost is higher, especially the housing cost.
-A small part of \textit{new rich} lives far away from the downtown, maybe because they don't have to work in downtown.
-The \textit{underclass} distribute more dispersively all over the whole city.
-Compared to the rich, they prefer the outer space because of the lower living cost.
-Lots of \textit{antizen} live in Nanshan District, where there are many universities and high-tech industrial parks full of well educated people.
-
-\wq{The glyphs on the map means the travel distance, travel radius..., which is an important in mobility research. Describe the difference.}\\
-\wqc{the 3rd design in Section.design, a kind of glyph for high-dimensional mobility indicator.}
-
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/c1-s3-53}
- \caption{Home Distributions of the Four Groups}
- \label{case1draft}
-\end{figure}
-
-\iffalse
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/case1_2}
- \caption{Home Distributions of the Four Groups}
- \label{case12}
-\end{figure}
-
-To have a better knowledge of mobility patterns of the four groups, trips are categorized into three categories, ``home", ``work'' for regular trips with the purpose of going home, work (or school for students), ``other'' for irregular trips with the purpose of shopping, visiting friends.
-Figure~\ref{case13}(a) shows the 2.5D overview of the three kinds of traveling categories.
-Each TAZ is grown to the same height, i.e., the unit one, and the height proportion of each traveling categories encodes the percentage of certain purpose in the whole, pink for ``others'', blue for ``work'' and green for ``home''.
-Although inside TAZ prisms are blocked in the Figure~\ref{case13}, our attention is drawn to the lifestyle of \textit{New Rich}.
-It is founded that the \textit{New Rich} travel for ``other'' purpose a lot, compared to other groups.
-To explore further, the detail slicing (introduced in Section~\ref{subsec:25D}) is applied to the four groups.
-Figure~\ref{case13}(b) shows three slices.
-It can be seen that individuals with low income (\textit{underclass} and \textit{antizen}) spend relatively more time on work, especially the \textit{underclass}.
-Working percentage is very small in-group \textit{new rich}.
-They live a more diverse lifestyle because they do many other things (the pink ones) except working.
-
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/case1_3}
- \caption{Mobility Patterns of ``work", ``home" and ``not essential" of the Four Groups: (a) the overview of the three pecentage; (b) three slices for detailed comparison.}
- \label{case13}
-\end{figure}
-\fi
+\subsection{Case 1: Group by similar social characteristics}
+\paragraph{Use bar and tsne to find four groups. figure to show groups.}
+\paragraph{Their home locations and basis travel features.}
 
 \subsection{Case 2: Spatial Attractiveness}
-\wqc{aim: select one purpose to show how many and where and how long.}
-\lmc{So as far as I understand, in this case, we focus on exploring the attributes or properties of spatial attratctiveness, right? such as the number, distance, origins, etc.}
+\paragraph{Select two groups, and target purpose. figure to compare spatial attractiveness.}
+\paragraph{click a grid, show OD. figure}
 
-\wq{When zooming in to explore with only one purpose, we demonstrate the use of the system for exploring the magnitude of spatial attractiveness.}
+\subsection{Case 3: Diversity of spatial attractiveness}
+\paragraph{Select group, figure to show diversity.}
+\paragraph{ranking, figure}
+\paragraph{two groups to compare, figure}
 
-\wq{As Figure~\ref{case3draft} shows, in view3, glyph represents $\textbf{the quantity}$ and $\textbf{how many grids are linked(i.e. area)}$ and $\textbf{distribution of distances}$. }
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/c2-s2-53}
- \caption{For purpose of shopping: (a) the rich; (b) the poor.}
- \label{case3draft}
-\end{figure}
-
-\wq{After clicking a target grid, show $\textbf{where are the linked grids}$ and $\textbf{the quantity of each linked grid}$ and $\textbf{distance}$.
-Compare two grid which have similar quantity, the distributions differ.}
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/c2-click-s2-53}
- \caption{For purpose of shopping: (a) spatial attractiveness of the poor; (b) Grid1; (c) Grid2.}
- \label{case3draft}
-\end{figure}
-
-\iffalse
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/case2}
- \caption{Home-work distances of different groups: (a) with different salary levels; (b) with or without house.}
- \label{case2}
-\end{figure}
-
-Home-work distance is an essential metric in economics, geography, and sociology.
-It refers to the distance between house and workplace.
-It is influenced by many factors like transportation, housing, land use, etc.
-Understanding the home-work distance of a region helps to evaluate whether the region is well planned or not.
-In this case, we demonstrate our system's help in home-work distance understanding.
-
-Considering income potentially determines where people live, we use income as the characteristics to select three groups, the group over 500K, the group during 200-300K and the group less than 100K.
-In Figure~\ref{case2}, the height of the bar stands for visiting frequency of the TAZ and its color encodes the average home-work distance, red for close and yellow for far.
-As Figure~\ref{case2}(a) shows, for all the three groups in different income levels, most of the TAZs have dark red or red color which indicates the home-work distance is generally short, especially in downtown.
-Only those with less than 100K salary work outside the center, such as the space in the green circle.
-When comparing the three groups in the downtown area, it is seen that it takes more time to go to work in Futian District as the decrease of the income.
-
-We explore the home-work distance of groups with and without a house.
-Figure~\ref{case2}(b) shows the close-up views.
-It is found that the Nanshan District has a shorter home-work distance for individuals without a house, while Futian District has shorter for those with a house.
-Nanshan is relatively newer to Futian so that there might be more easily-accessible houses to be rent.
-\fi
-
-\subsection{Case 3: Diversity of spatial attractiveness of indicators}
-\wqc{aim: with mixed purposes, show attractiveness quantity and entropy.
-View3 shows spatial attractiveness, including: quantity, distance, （direction）; View4 shows ranking of origins, (or others); (add a interaction in view5 for citizens in selected grid.)}
-
-\wq{Due to the various functions of the areas, for different space, the attractiveness indicators differs.
-Therefore, in this case, we demonstrate the use of the system for exploring diversity of spatial attractiveness indicators.
-}
-
-\wq{As Figure~\ref{case2draft} shows, in view3, glyph represents $\textbf{the quantity}$ and $\textbf{value of mixture of purposes}$.
-\wqc{(if we decide to give a computing equation to define it.)}\lmc{I think we can define a equation to compute it.} in view 4, ranking of each grid based on the quantity of each purpose.}
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/c3-53}
- \caption{Trip purposes distribution of four groups with different jobs}
- \label{case2draft}
-\end{figure}
-
-In this case, we explore the correlation between mobility patterns with the job, to see whether the job has an impact on the movement.
-Officer, workman, student, and businessman are selected as examples and the population of trips for certain purposes is shown In Figure~\ref{case3}.
-The height of bars encodes the amount of visit to each TAZ, and color encodes the traveling purpose.
-There are 10 different kinds of traveling purposes.
-For quick linking between color and purposes, the regular trips such as go to work, school and home are dyed in cold color, and the irregular trips such as go shopping, hospital, etc, are dyed in the warm color.
-As Figure~\ref{case3} shows, for officers, the TAZs changes dramatically in height.
-Some TAZs have much more visiting than others because officers are more constrained to work in some buildings than individuals with other jobs.
-The relative percentage of irregular activity differs for the four groups.
-For Workman, about 80 percent of movements are the regular purpose, either go to work or go back home.
-For students, the percentage becomes to be about 50 percentage.
-Compared to them, officer and businessman have more flexible and diversified lifestyle.
-
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/case3}
- \caption{Trip purposes distribution of four groups with different jobs}
- \label{case3}
-\end{figure}
-
-Next, we concentrated on one purpose to see whether it is related to jobs.
-Here we use ``dinner or entertainment" as the example.
-As Fig \ref{case32} shows, the height of TAZ bars represents the visiting amount of trips for dinner or entertainment.
-Color stands for moving distance to reach this TAZ.
-As we can see, officers prefer to entertain in the downtown area, while workmen cover a larger area.
-Students tend to concentrate on Nanshan district, probably near schools.
-For the businessmen, they go lots of places for dinner or entertainment.
-The biggest difference with other groups is that they would travel a long distance to go somewhere far from downtown areas.
-
-\iffalse
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/case3_2}
- \caption{The ``dinner or entertain" purpose of four groups with different jobs}
- \label{case32}
-\end{figure}
-\fi
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-This work demonstrates a throughout research flow from data collection, basic analysis to deep visual analysis of mobility patterns with individual characteristics.
-Considering the irresistible trend in mixing social data and spatial data to solve the urban problem, this work takes one step forward in exploring the relationship between movement and individuals' characteristics, which is rarely touched by previous geo-tagged social media visual analytics.
-The design of the visual analytic system is driven by three tasks about individuals and mobility patterns.
-Tapping into our daily experiences, the data-driven profile visualization provides an organic and intuitive representation of individuals.
-Its effectiveness in identifying similar or abnormal individuals from the mass has been demonstrated.
-The design of 2.5D spatial visualization continues the exploration of the typical research problem how to visualize spatial information and abstract information together.
-Although it is not a one-step solution, 2.5D visualization with the detail slicing is able to provide an occlusion-free analysis with spatial context preserved.
-
-Our current research focuses on fundamental facets of the mobility patterns and doesn't draw a strong conclusion on the correlation between mobility pattern and individual characteristics.
-In next step, more delicate algorithms will be involved to extract high-level mobility patterns, such as the frequent visiting sequence of an individual group, etc.
-On the other hand, the data we used in this work shows its potential in representing the population.
-As the next step, research effort can be put into a more serious verification of how small sampled data can represent a large population.
+\section{Discussion and Conclusion}
 

### 2019-12-31 ia/ia_vis_3d.tex
latex manu

--- 2019-04-19 template.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% This is a general template file for the LaTeX package SVJour3
-% for Springer journals.          Springer Heidelberg 2010/09/16
-%
-% Copy it to a new file with a new name and use it as the basis
-% for your article. Delete % signs as needed.
-%
-% This template includes a few options for different layouts and
-% content for various journals. Please consult a previous issue of
-% your journal as needed.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% First comes an example EPS file -- just ignore it and
-% proceed on the \documentclass line
-% your LaTeX will extract the file if required
-\begin{filecontents*}{example.eps}
-%!PS-Adobe-3.0 EPSF-3.0
-%%BoundingBox: 19 19 221 221
-%%CreationDate: Mon Sep 29 1997
-%%Creator: programmed by hand (JK)
-%%EndComments
-gsave
-newpath
-  20 20 moveto
-  20 220 lineto
-  220 220 lineto
-  220 20 lineto
-closepath
-2 setlinewidth
-gsave
-  .4 setgray fill
-grestore
-stroke
-grestore
-\end{filecontents*}
-%
-\RequirePackage{fix-cm}
-%
-\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-\smartqed  % flush right qed marks, e.g. at end of proof
-%
+\documentclass{ieeeaccess}
+\usepackage{cite}
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithm}
+\usepackage{algorithmicx}
+\usepackage{algpseudocode}
 \usepackage{graphicx}
+\usepackage{textcomp}
+
+\ifCLASSOPTIONcompsoc
+\usepackage[caption=false, font=normalsize, labelfont=sf, textfont=sf]{subfig}
+\else
+\usepackage[caption=false, font=footnotesize]{subfig}
+\fi
+
+\ifCLASSINFOpdf
+   \usepackage{graphicx}
+   \usepackage{lipsum}
+   \usepackage{booktabs}
+   \usepackage{threeparttable}
+   \usepackage{caption}
    \usepackage{epstopdf}
-\usepackage{subfigure}
-
-\usepackage{mathptmx}
-
-\usepackage{times}
-
-\usepackage{algorithm}% http://ctan.org/pkg/algorithm
-\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
-
-\usepackage{url}
-\usepackage{color}
-\newcommand{\m}{\textcolor{black}}
+   \usepackage{cite}
+\else
+\fi
 
 \usepackage{xcolor}
-\newcommand{\add}{\textcolor{blue}}
 
-\usepackage{multirow}
-\usepackage{tabularx}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\begin{document}
+\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
+\doi{10.1109/ACCESS.2017.DOI-}
 
-\usepackage{algpseudocode}
-\usepackage{natbib}
-\usepackage[misc]{ifsym}
-%
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-%
-% Insert the name of "your journal" with
-% \journalname{myjournal}
-%
-\begin{document}
+\title{Unfolding the City: Spatial Preference Based on Individual Characteristics}
 
-\title{Unfolding the City: \textcolor{blue}{Exploring ...(city usage) with Social Characteristics} Exploring Mobility Patterns with Individual Characteristics}
-%\thanks{Grants or other notes
-%about the article that should go on the front page should be
-%placed here. General acknowledgments should be placed at the end of the article.}
+\author{\uppercase{Qi wang}\authorrefmark{1,2}, \uppercase{min lu}\authorrefmark{2,3} and \uppercase{Qingquan Li}\authorrefmark{1,2}}
+\address[1]{State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, Wuhan 430072, China}
+\address[2]{Shenzhen Key Laboratory of Spatial Smart Sensing and Services, Shenzhen University, Shenzhen 518060, China}
+\address[3]{School of Architecture and Urban Planning, ShenZhen University, Shenzhen 518060, China}
 
-%\subtitle{Do you have a subtitle?\\ If so, write it here}
+\tfootnote{This work was jointly supported by the National Natural Science Foundation of China(No. 71961137003 and No. 41671387).}
 
-%\titlerunning{Short form of title}        % if too long for running head
+\markboth
+{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
+{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
 
-\author{Qi Wang \and Min Lu \and Yang Yue \and Qingquan Li}
-
-%\authorrunning{Short form of author list} % if too long for running head
-
-\institute{Q. Wang \and Q. Li(\Letter) \at
-              the State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, Wuhan, China, and also ShenZhen Key Laboratory of Spatial Smart Sensing and Services, ShenZhen University, Shenzhen 518060, China \\
-              Tel.: +86-13297983047\\
-              \email{wangqi@whu.edu.cn}, {liqq@szu.edu.cn}           %  \\
-           \and M. Lu \and Y. Yue \at
-              School of Architecture and Urban Planning, and also ShenZhen Key Laboratory of Spatial Smart Sensing and Services, ShenZhen University, Shenzhen 518060, China \\
-              \email{minlu@szu.edu.cn}, {yueyang@szu.edu.cn}           %  \\
-}
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-\maketitle
+\corresp{Corresponding author: Qingquan Li (e-mail: liqq@szu.edu.cn).}
 
@@
 A city is shaped not only by its assembled infrastructures but also the people living inside it.
-People in a wide range of individual characteristics visit places with different weights and preferences, sculpturing the city into a space of diverse mobility patterns.
-Different from the well study of anonymous travel behaviors, the mobility patterns of characterized individuals, is less studied because of the challenges in collection and analysis of data with privacy.
+People in a wide range of individual social characteristics visit places with different weights and preferences, sculpturing the city into a space of diverse mobility patterns.
+Different from the well study of anonymous travel behaviors, the daily movement of characterized individuals, is less studied because of the challenges in collection and analysis of data with privacy.
 In this work, we take a step forward and perform an online census to collect individual profiles and movements from large-scale volunteers.
@@
 A 2.5D spatial visualization is proposed to maintain a compact multivariable analysis by relaxing the z-axis to encode information, such as visiting frequency, demands, traveling distance, etc.
-Together with the cross-filter and flexible 2.5D interactions, the effectiveness and usability of the system are well demonstrated by a study made in Shenzhen.
+Together with the cross-filter and flexible 2.5D interactions, the effectiveness and usability of the system are well demonstrated by a study made in Shenzhen.\end{abstract}
 
-\keywords{Visual analytics \and mobility pattern \and individual characteristics \and city }
-% \PACS{PACS code1 \and PACS code2 \and more}
-% \subclass{MSC code1 \and MSC code2 \and more}
-\end{abstract}
+\begin{keywords}
+Visual analytics, spatial preference, individual characteristics, data collection
+\end{keywords}
+
+\titlepgskip=-15pt
+
+\maketitle
 
 \section{Introduction}
-\label{intro}
-The science fiction \textit{Folding Beijing}~\citep{hao2016_foldingbeijing} depicts a world where three classes of people live in independent spatial-temporal patterns, though sharing the same earth surface.
-This is an artistical metaphor for one potential fact that people make different decisions in visiting places according to individual determinants, such as social, economic, educational factors, etc.
+\label{sec:introduction}
+\PARstart{T}{he} science fiction \textbf{Folding Beijing}~\cite{hao2016_foldingbeijing} depicts a world where three social classes of people live in independent spatiotemporal patterns, though sharing the same earth surface.
+This is an artistical metaphor for one potential fact that people prefer to select different places according to individual characteristics, such as social, economic, educational features.
 This phenomenon has attracted the research interest for a long time in the sociological field.
-Back to 1970, Pahl~\citep{pahl1975whose} posed the question `whose city` and interest in understanding the territorial inequalities.
-Contemporary contestation also continually raise the banner `The City Belongs to All!'~\citep{Mayer2017_whosecity}.
-Having a good understanding of how the mobility patterns relate to characterized individuals sheds light on region utilization, diversity mix-up, and opportunities promotion.
+Back to 1970, Pahl~\cite{pahl1975whose} posed the question "whose city" and interest in understanding the territorial inequalities.
+Contemporary contestation also continually raises the banner "The City Belongs to All!"~\cite{Mayer2017_whosecity}.
+Having a good understanding of relationships between the spatial attractiveness and the characterized individuals sheds light on region utilization, diversity mix-up, and opportunities promotion.
 
-In the past decades, the power of visual analytics in exploring spatial-temporal data has been recognized and well developed.
-Transportation problems are answered by various movement data, such as traffic jams in taxi GPS trajectoires~\citep{wang2013visual}, interchanging flows in public transportation~\citep{zeng2013visualizing}, etc.
-The presence of social media applications fuels the spatial analysis with rich semantic texts, so researchers get the chances to explore the thematic meaning of the moving behavior, such as events~\citep{chen2017map} or topics~\citep{bosch2013scatterblogs2}.
+In the past decades, the power of visual analytics in exploring spatiotemporal data has been recognized and well developed.
+Various urban problems are answered, such as traffic jams~\cite{wang2013visual}, interchanging flows in public transportation~\cite{zeng2013visualizing}, etc.
+The presence of social media applications fuels the spatial analysis with rich semantic texts, so researchers get the chances to explore the thematic meaning of the moving behavior, such as events~\cite{chen2017map} or topics~\cite{bosch2013scatterblogs2}.
 Those works essentially contribute in deepening the contextual understanding of moving activity.
-But they rarely combine the mobility with individuals' characteristics because which cannot be 100\% inferred from social media profiles.
-There is still a research gap in exploring the relationship between mobility pattern and characteristics.
+However, they rarely combine the movement analysis with individuals' characteristics because which cannot be fully inferred from social media profiles.
+One of the main challenges is the sensitivity issue in privacy data.
+There is still a research gap in exploring the relationship between spatial pattern and social characteristics.
 
-In this work, we contextualize the analysis of mobility pattern in the backcloth of individual characteristics.
-Our motivation is to fuse the movement data with individuals' profiles in an attempt to ascertain the dynamics pattern of groups with different characteristics.
-To this, we need to get the characterized information of movers.
-The sensitivity issue in privacy data is one of the main challenges.
+In this work, we contextualize the analysis of citizens' spatial distribution in the backcloth of individual characteristics.
+With the motivation of fusing the movement data with individuals' profiles in an attempt to ascertain the spatial distribution for groups with different characteristics, we need to get the characterized information of movers.
 The conventional offline census takes lots of effort and too much time to be out of date.
@@
 In this work, with a census survey released via social media application, we ran an online demographical collection campaign.
-Then we developed a visual analytics system to explore the mobility patterns centered around people.
-The system incorporates visualizations of individuals' characteristics, including t-SNE for an overview and data-driven profile visualization for the detailed check, as well as 2.5D spatial visualization to explore the mobility patterns.
+Based on the data collected, we developed a visual analytics system to explore where do citizens prefer to go.
+The system incorporates visualizations of individuals' characteristics, including t-SNE for an overview and data-driven profile visualization for the detailed check, as well as 2.5D spatial visualization to explore the distribution of movements.
 Finally, applying our method in Shenzhen, several cases are derived to demonstrate the powers of our method.
@@
 
-\section{Related work}
-
+\section{Related Work}
 This work concerns the research topic of spatial data visual analytics.
-Spatio-temporal data has three components, i.e., spatial, temporal and thematic~\citep{andrienko2013visual}.
+Spatiotemporal data has three components, i.e., spatial, temporal and thematic~\cite{andrienko2013visual}.
 Lots of related work focus on the spatio-temporal analysis in movement data, in the absence of thematic information.
@@
 With the development of location-acquisition techniques, massive spatial trajectories are collected, to keep track of the trajectories of various moving objects.
-Many techniques have been proposed to process, mine trajectory~\citep{Zheng2015_trajectory}.
-In the field of visualization and visual analytics, spatial visualizations are specifically designed for the time, locations, spatial-temporal information and other properties in the traffic data~\citep{chen2015survey}.
+Many techniques have been proposed to process, mine trajectory~\cite{Zheng2015_trajectory}.
+In the field of visualization and visual analytics, spatial visualizations are specifically designed for the time, locations, spatial-temporal information and other properties in the traffic data~\cite{chen2015survey}.
 A large number of visual analytics tools and applications cover situation-aware exploration, pattern discovery and traffic situation monitoring.
-Wang et al~\citep{wang2013visual} extract the traffic jam propagation graph extraction to reveal underlying data patterns.
-Guo et al.~\citep{guo2011tripvista} and Zeng et al.~\citep{zeng2013visualizing} construct geographical regions and visually aggregate the in-between movements as flows.
-To discover the route travel patterns, Lu et al.~\citep{lu2015trajrank} propose TrajRank to explore the route travel behavior based on ranking.
-For multiple routes, Liu et al.~\citep{liu2011_routediversity} study the route diversity between locations and Lu et al.~\citep{Lu2017_multipleroute} explore the route choice behavior among multiple routes.
+Wang et al~\cite{wang2013visual} extract the traffic jam propagation graph extraction to reveal underlying data patterns.
+Guo et al.~\cite{guo2011tripvista} and Zeng et al.~\cite{zeng2013visualizing} construct geographical regions and visually aggregate the in-between movements as flows.
+To discover the route travel patterns, Lu et al.~\cite{lu2015trajrank} propose TrajRank to explore the route travel behavior based on ranking.
+For multiple routes, Liu et al.~\cite{liu2011_routediversity} study the route diversity between locations and Lu et al.~\cite{Lu2017_multipleroute} explore the route choice behavior among multiple routes.
 
@@
 As the presence of social media services, social media data with geo-tags are collected to track people's movements in daily lives.
-As an analog of remote sensing data in social science research, the geospatial big data has been proposed as social sensing ~\citep{liu2015social}.
+As an analog of remote sensing data in social science research, the geospatial big data has been proposed as social sensing ~\cite{liu2015social}.
 Hence, analyzing movement information along with rich text has become a hot research area in recent years.
 Those works infer thematic information from the semantic texts.
-Cao et al.~\citep{cao2012whisper} propose \textit{Whisper} for tracing the pathways of tweets on a spatial hierarchical layout, to investigate how information flow among multiple places.
-Krueger et al.~\citep{krueger2014visual} used GPS and location-based service data to support the analysis of movement behaviors.
-Chen et al.~\citep{chen2016interactive} present a visual analytics system to support the exploration of sparsely sampled trajectory from social media.
-Some other researchers tend to infer real information, such as names, gender, etc, from social media data~\citep{peddinti2014internet}, to break down the demographic characteristics of social media users.
-Luo et al.~\citep{luo2016explore} derive race, gender, and age as three demographics dimensions to analyze its impact on the urban human mobility patterns.
+Cao et al.~\cite{cao2012whisper} propose \textit{Whisper} for tracing the pathways of tweets on a spatial hierarchical layout, to investigate how information flow among multiple places.
+Krueger et al.~\cite{krueger2014visual} used GPS and location-based service data to support the analysis of movement behaviors.
+Chen et al.~\cite{chen2016interactive} present a visual analytics system to support the exploration of sparsely sampled trajectory from social media.
+Some other researchers tend to infer real information, such as names, gender, etc, from social media data~\cite{peddinti2014internet}, to break down the demographic characteristics of social media users.
+Luo et al.~\cite{luo2016explore} derive race, gender, and age as three demographics dimensions to analyze its impact on the urban human mobility patterns.
 Since real information is not enforced in social media, the wrong inferring is inevitable.
-Longley et al.~\citep{Longley2015}~\citep{Paul2016_twitter} identifies and assess the biases inherent in social media usage in social research and evaluate the deployment of social media data in research applications.
+Longley et al.~\cite{Longley2015}~\cite{Paul2016_twitter} identifies and assess the biases inherent in social media usage in social research and evaluate the deployment of social media data in research applications.
 
-\section{Online Census}
-The advent of mobile sensing techniques and social media applications makes it possible to collect spatial data from the social media source.
-Complementary to the conventional census, it brings the benefit of larger sampling frequency and a broader range in terms of space and time.
-It is possible to reach a wide range of individuals and collect the movement in human inactive time, such as the mid-night.
+\section{motivation}
 
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/survey_app}
- \caption{Census Interface: (a) personal characteristics collecting page; (b) trips collecting page; (c) credit system page}
+\label{sec:concept}
+This work was sparked from a meeting with two domain experts who work on human mobility and urban informatics in the geospatial field.
+The experts pointed out that as big and open data evolved in, the scope of urban research has been lifted from the spatial perspective up to social-spatial perspective.
+There is a rising research interest in understanding how groups of citizens with certain social characteristics select places during their daily lives.
+Whether people visit places with preference which are intrinsically affected by their social-economic characteristics?
+Is there a limitation or probabilities of interaction between different socio-economic groups in public spaces?
+With the advances of data acquisition and analysis techniques, they demanded to go beyond the conventional static sampled questionnaires, which usually survey visiting preferences.
+They sought for the possibility in revealing the spatial distribution in real-world visiting logs and urged to have a dynamic system which supports the interactive examination of spatial distribution in different contexts of social characteristics.
+
+Thereafter we booted up this project with several rounds of discussions, to frame the research problem with two core contents and the research procedure.
+The first concepts is \textbf{Social Characteristics}.
+Social characteristics of a person or group of citizens  are the descriptors which contribute to the specification of the populations.
+This work intends to cover the social characteristics from multi-facets, including descriptors such as gender, income, education, etc.
+The second content is \textbf{Spatial Distribution}.
+It is reflected by the popularity of a place to be visited.
+
+Motivated by their research interest in understanding the spatial attractiveness with individual social characteristics, this work goes through a procedure consists of two stages, i.e., data collection and basic reviewing, visual analytics design iteration with experts' feedback.
+
+\section{Data Description}
+\label{subsec:pipeline}
+Considering there is no existing public dataset could fit our topic well, this work is consolidated with a self-maintained data sourcing.
+We release an online data census to collect the social characteristics and movement logs of individuals for almost half a year.
+Then a series of statistical analysis is performed on the collected data for sampling bias checking.
+
+\subsection{Online Census}
+
+The advent of mobile sensing techniques and social media applications makes it possible to collect spatial data by apps within the phones.
+Complementary to the conventional census, it brings the benefit of convenient collections without much manpower and precise spatial locations by GPS instead of semantic description.
+Meanwhile, it is possible to collective the movement in human inactive time, such as the mid-night.
+
+In this work, we perform the census survey in Shenzhen, which is one of the most modern metropolis in China.
+The experiment is deployed on Wechat, the most widely used social media mobile application.
+Fig.
+\ref{fig:app} shows the data collecting interfaces.
+For privacy issue, all detailed personal information are desensitized to categorical levels.
+Considering the main aim on the relationship between spatial distribution of movements and individuals' characteristics, there are two crucial contents to be collected:
+
+\textbf{Individual Characteristics} Fig.
+\ref{fig:data_over} lists the eight domains, including social, economic and demographic aspects, to give a generalized description of the individual characteristics.
+The profile will serve as the ingredients for the analysis of mobility patterns over diverse individuals.
+
+\textbf{Traveling Trips} Besides to those individual characteristics, each individual can upload dynamic traveling trips (Fig.
+\ref{fig:app}(b)).
+Each trip requires the information of start/end location, start/end time, traveling purpose.
+To encourage the trip uploading, a credit system retains the contribution of individuals on trips and rewards the volunteers with the top credits (Fig.
+\ref{fig:app}(c)).
+
+\begin{figure}
+ \centering
+ \includegraphics[width=9cm]{pictures/survey_app}
+  \captionsetup{justification=centering}
+ \caption{Census Interface: (a) personal characteristics collecting page; (b) trips collecting page; (c) credit system page.}
  \label{fig:app}
@@
 
-In this work, we perform the census survey in Shenzhen, which is one of the most modern metropolia in China.
-The experiment is deployed on Wechat, a widely used social media application.
-Figure~\ref{fig:app} shows the data collecting interfaces.
-Each individual hands in his or her personal characteristics.
-For privacy issue, all detailed personal information are desensitized to categorical levels (Figure~\ref{fig:app}(a)).
-
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/data_over}
- \caption{Profile of Individual: eight individual characteristics enrich the analysis of mobility patterns}
+\begin{figure}
+ \centering
+ \includegraphics[width=9cm]{pictures/data_over}
+ \captionsetup{justification=centering}
+ \caption{Profile of Individual: eight individual characteristics enrich the analysis of mobility patterns.}
  \label{fig:data_over}
@@
 
-\textbf{Individual Characteristics} Figure~\ref{fig:data_over} lists the \textit{eight domains}, including social, economic and demographic aspects, to give a generalized description of the individual characteristics.
-The profile will serve as the ingredients for the analysis of mobility patterns over diverse individuals.
+\subsection{Statistics of Collected Data}
 
-\textbf{Traveling Trips} Besides to those individual characteristics, each individual can upload dynamic traveling trips (Figure~\ref{fig:app}(b)).
-Each trip requires the information of \textit{start/end location}, \textit{start/end time}, \textit{traveling purpose}.
-To encourage the trip uploading, a credit system retains the contribution of individuals on trips and rewards the volunteers with the top credits (Figure~\ref{fig:app}(c)).
-
-\subsection{Basic Statistics of Data}
-
-Over the releasing time period from \m{2015-11 to 2016-01}, 21435 individuals (48\% females and 52\% males) were reached and \m{229155} trips are collected.
-Each volunteer contributes \m{11} trips average.
-
-Our case-study data is confined to a small proportion of Wechat users who opt to contribute their information and trips.
-Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\citep{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of the population in the city.
-
-% In the report (looking for some report), the penetration of mobile device is \m{XXX}, almost every XX people got a Mobile Phone in the urban.
+Over the releasing time period from 2015-11 to 2016-01, 21,435 individuals (48\% females and 52\% males) participated in the census and 229,155 trips were collected.
+Each volunteer contributed 11 trips average.
 
@@
  \includegraphics[width=\columnwidth]{pictures/data1}
- \caption{Age and Education Distribution: (a) age; (b) education}
+ \caption{Age and Education Distribution: (a) age; (b) education.}
  \label{fig:data_age_edu}
@@
 
-Figure~\ref{fig:data_age_edu} gives the distribution of age and education over the population.
+Our case-study data is confined to a small proportion of Wechat users who opt to contribute their profile  and movements.
+Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of the population in the city.
+
+Fig.
+\ref{fig:data_age_edu} gives the distribution of age and education over the population.
 It shows that samples cover a wide range of ages, dominating between 18 to 45.
@@
 According to the 2015 Annual Census Statistics report\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5.
-Figure~\ref{fig:data_age_edu} gives the distribution of education levels, ranging from low to high.
+Fig, \ref{fig:data_age_edu}(b) gives the distribution of education levels, ranging from low to high.
 The technical college and university dominate the samples at the 61\% occupancy rate.
+
+Fig.
+\ref{fig:data_job_inc}(a) shows the job types of sampled individuals, who are servants, workers, officers, businessmen and so on.
+Fig.
+\ref{fig:data_job_inc}(b) gives the radar diagram of the annual pay.
+The majority get paid below 200,000.
+Individuals with higher salary are also reached in our census.
 
@@
 
-Figure~\ref{fig:data_job_inc}(a) shows the job types of sampled individuals, who are servants, workers, officers, businessmen and so on.
-The covering of jobs is pretty wide.
-Figure~\ref{fig:data_job_inc}(b) gives the radar diagram of the annual pay.
-The majority get paid below 200 000.
-Individuals with higher salary are also reached in our census.
+Fig.
+\ref{fig:data_geometry} shows the basic statistics related to movements.
+In Fig.
+~\ref{fig:data_geometry}(a), the active traveling time (here, we take the start time as the representative of active time) follows the common knowledge of urban life.
+There are obvious morning and late afternoon peaks.
+Fig.
+~\ref{fig:data_geometry}(b) gives the counting of different traveling purposes.
+95\% trips are tagged with clear raveling purpose in the data.
+33\% are going home and 37\% are going to work.
+Besides this kind of routine traveling, there are also substantial trips such as going shopping, going the hospital, etc.
+Fig.
+~\ref{fig:data_geometry}(c) shows the spatial distribution of the origins and destinations.
+It is found that more dots are located in Futian and Nanshan districts, the city's heart than the surrounding areas.
+This is consistent to Batty's exposition of the focus of city networks and interaction patterns~\cite{batty2013new}.
 
@@
 
-Figure~\ref{fig:data_geometry} shows the basic statistics related to trips.
-In Figure~\ref{fig:data_geometry}(a), the active traveling time (here, we take the start time as the representative of active time) follows the common knowledge of urban life.
-There are obvious morning and late afternoon peaks.
-Figure~\ref{fig:data_geometry}(b) gives the counting of different traveling purposes.
-95\% trips are tagged with clear raveling purpose in the data.
-33\% are going home and 37\% are going to work.
-Besides this kind of routine traveling, there are also substantial trips such as going shopping, going the hospital, etc.
-Figure~\ref{fig:data_geometry}(c) shows the spatial distribution of the origins and destinations.
-It is found that more dots are located in Futian and Nanshan districts, the city's heart than the surrounding areas.
-This is consistent to Batty's exposition of the focus of city networks and interaction patterns~\citep{batty2013new}.
-
-% Trips are uploaded in a wide range of purpose in addition to home, work, but also includes XX entertainment, visiting, etc.
-The diverse purposes make it possible to characterize the flows across the city between different functional places.
-
 Because there is always inevitable bias inherent in fully representing the ground truth of the population, the preliminary statistical analysis shows positive sign of a relatively even sampling of the population.
 
-\section{Visual design}
+\section{Visual Design}
 
-\textcolor{blue}{Adding a background. Expert discussion. Summarize the tasks below.}
+The design of visual analytics system is iterated via multi-pass discussions with the two domain experts.
+In this section, we first introduce specific tasks the system intended for and design rationales aligned to provide the user-friendly interface for domain experts.
+Then we introduce the visual design.
 
-The design of the system is driven by tasks, to align the analysis of mobility patterns with individual characteristics.
-Before diving into the design of the system, we introduce the couple of specifical tasks the system intended for.
+\subsection{Tasks}
+
+The exploration of core contents (introduced in Section~\ref{sec:concept}) is resolved further with the following tasks.
 
 \begin{itemize}
-\item \textit{Task 1: Identify the group with specific individual characteristics}: to get groups of people with common or close attributes, to explore the correlation among individual characteristics.
-\item \textit{Task 2: Explore the mobility patterns of a group}: to explore where, how and why an interested group go in the city.
-\item \textit{Task 3: Compare mobility patterns among multiple groups}: to know the similarities and differences between different groups in their mobility patterns, to investigate the relationship between movement and individual characteristics.
+\item \textbf{Task 1: Identify the group with specific individual characteristics}: to get groups of people with common or close attributes, to explore the correlation among individual characteristics.
+\item \textbf{Task 2: Explore the mobility distribution of a group}: to explore where, how and why an interested group go in the city.
+\item \textbf{Task 3: Compare mobility distribution among multiple groups}: to know the similarities and differences between different groups in their spatial preferences, to investigate the relationship between movement and individual characteristics.
 \end{itemize}
+
+\begin{figure*}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=18.1cm]{pictures/teaser.eps}
+ \caption{System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) a t-SNE visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) data-driven profiles support users with organic individual perception; (d) group of interested individuals can be saved; (e) movement of the chosen group is visualized and explored in 2.5D main view; (f) a dock is provided to restore and compare findings; (g) different choices of 2.5D encoding can be selected.}
+ \label{fig:teaser}
+\end{figure*}
 
@@
 \begin{itemize}
-\item \textit{Intuitive perception of an individual as an organic complex (C1)}: the system should make use of users' daily life experience in knowing people to provide intuitive visualization, instead of the lifeless representation by number.
+\item \textbf{Intuitive perception of an individual as an organic complex (C1)}: the system should make use of users' daily life experience in knowing people to provide intuitive visualization, instead of the lifeless representation by number.
 The visual design needs to help end-users to pick desirable ones from the mass.
-\item \textit{Good overview of the multivariate individuals (C2)}: following the visual analytics manta by Shneiderman~\citep{RN459}, it is very important to provide a good overview of all the individuals then the users know where to explore.
-\item \textit{Effective multivariable cross-filter for individual characteristics (C3)}: there are eight domains to describe an individual.
+\item \textbf{Good overview of the multivariate individuals (C2)}: following the visual analytics manta by Shneiderman~\cite{RN459}, it is very important to provide a good overview of all the individuals then the users know where to explore.
+\item \textbf{Effective multivariable cross-filter for individual characteristics (C3)}: there are eight domains to describe an individual.
 The system is supposed to provide a straight-forward way for easy filtering by the eight criteria.
-\item \textit{Compact visualization of mobility patterns in the constraint of spatial space (C4)}: the analysis of mobility patterns not only includes the conventional spatial and temporal dimensions, but also other abstract dimensions, e.g., travel purpose, visiting frequency, etc.
+\item \textbf{Compact visualization of mobility patterns in the constraint of spatial space (C4)}: the analysis of mobility patterns not only includes the conventional spatial and temporal dimensions, but also other abstract dimensions, e.g., travel purpose, visiting frequency, etc.
 The system should handle a compact layout to support the easy correlation between spatial and abstract information.
-\item \textit{Flexible interactions to explore the mobility patterns either within one group or between groups (C5)}: to support the comparison among groups, \textit{Task 3}, the system should maintain flexible interactions which allow the end-users to explore freely.
+\item \textbf{Flexible interactions to explore the mobility patterns either within one group or between groups (C5)}: to support the comparison among groups, \textbf{Task 3}, the system should maintain flexible interactions which allow the end-users to explore freely.
 \end{itemize}
 
-% Classification method, flow clustering method, Semantic representation.
+\subsection{Visualizations}
+\label{subsec:vis}
 
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\linewidth]{pictures/teaser.eps}
- \caption{System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) a t-SNE visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) data-driven profiles support users with organic individual perception; (d) group of interested individuals can be saved; (e) movement of the chosen group is visualized and explored in 2.5D main view; (f) a dock is provided to restore and compare findings; (g) different choices of 2.5D encoding can be selected.}
- \label{fig:teaser}
-\end{figure}
-
-With those design considerations, we develop a visual analytics system as Figure~\ref{fig:teaser} shows.
+With those design considerations, we develop a visual analytics system as Fig.
+\ref{fig:teaser} shows.
 It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}).
@@
 
-% overview of the data. Encode information but also allow users to set multiple criteria (\textit{C1}). Support users to slice the data by different domains.}
-% Semantic understanding of social characteristics.
+\subsubsection{Data-driven Profile Visualization}
 
-\subsection{Data-driven Profile Visualization}
-\textcolor{blue}{Using two scales. Glyph-based visualization for finer scale, radar-based visualization for coarser scale.}
-
-Glyph-based visualization~\citep{borgo2013glyph} is the form of visual design to compose multivariable into a collection of unified visual symbols, known as a glyph.
+Glyph-based visualization~\cite{borgo2013glyph} is the form of visual design to compose multivariable into a collection of unified visual symbols, known as a glyph.
 A glyph is intended for quick understanding and aligned comparison.
-Among glyph design, Chernoff Face~\citep{chernoff1973use} represents data variables by the different features of a cartoon face.
+Among glyph design, Chernoff Face~\cite{chernoff1973use} represents data variables by the different features of a cartoon face.
 Following the idea of Chernoff Face, we design a type of glyph, a graphical representation of people with specific individual characteristics.
@@
 Those visual profiles are intended for intuitive visual understanding, from abstract to concrete and semantic understanding, to support users to target the interested individual groups effectively.
+
+Fig.
+~\ref{fig:design_profile} shows the legend for the user profile.
+The eight domains are encoded by visual symbols and organically organized in a human figure.
+There are basically three types of variables to drive the figure, i.e., the numeric, categorical and boolean ones.
+For numeric attributes such as income and education levels, visual symbol keeps consistent design but with changing visual variation, such as size, thickness.
+For the categorical attributes such as job, visual symbols are designed separately for better semantic meaning.
+For the boolean attribute like car, house, a symbol is designed to indicate its existence.
+With this consideration, the domains are designed as follows:
+
+\begin{itemize}
+\item \textbf{Gender} It is visually mapped to the hairstyle of the avatar.
+\item \textbf{Age} Age is implied by the decoration on the hair.
+For the elder above 70, the hair is dyed to grey.
+For the youth beneath 18, a hair decoration is adapted for the different hairstyles of girls and boys.
+\item \textbf{Education} The thickness of eyeglasses is used to indicate the different levels of education.
+\item \textbf{Job} The clothes is designed to imply the job of the individual. There are 9 types of clothes.
+\item \textbf{Belongings} For real estate, car, residential license are considered as the belongings to the individual, so we design each of them as an add-on decoration to imply whether the individual has it or not.
+\item \textbf{Income} A money symbol is used to represent the income, whose size encodes the income level. The more money an individual earns, the larger the symbol is.
+\end{itemize}
 
@@
 
-Figure~\ref{fig:design_profile} shows the legend for the user profile.
-The eight domains are encoded by visual symbols and organically organized in a human figure.
-There are basically three types of variables to drive the figure, i.e., the numeric, categorical and boolean ones.
-For numeric attributes such as income and education levels, visual symbol keeps consistent design but with changing visual variation, such as size, thickness.
-For the categorical attributes such as job, visual symbols are designed separately for better semantic meaning.
-For the boolean attribute like car, house, a symbol is designed to indicate its existence.
-With this consideration, the domains are designed as follows:
-
-% For numeric attributes.
-
-% By different composition, stimulus pattern which has the abstract demographic measurement of individuals.
-
-\begin{itemize}
-\item \textbf{Gender} the gender is visually mapped to the hairstyle of the avatar.
-\item \textbf{Age} age is implied by the decoration on the hair.
-For the elder above 70, the hair is dyed to gray.
-For the youth beneath 18, a hair decoration is adapted for the different hairstyles of girls and boys.
-\item \textbf{Education} The thickness of eyeglasses is used to indicate the different levels of education.
-\item \textbf{Job} The clothes is designed to imply the job of the individual. There are 9 types of clothes.
-\item \textbf{Belongings} for real estate, car, residential license are considered as the belongings to the individual, so we design each of them as an add-on decoration to imply whether the individual has it or not.
-\item \textbf{Income} a money symbol is used to represent the income, whose size encodes the income level. The more money an individual earns, the larger the symbol is.
-\end{itemize}
-
-\begin{figure}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=0.6\columnwidth]{pictures/design_example}
- \caption{Representative figures with the top 10 largest population in four jobs}
- \label{fig:div_example}
-\end{figure}
-
 With the visual mapping, the profile varies from individual to individual.
 By concretizing the attributes which otherwise is too abstract to percept, users can scan and search for interesting target effectively.
-Figure~\ref{fig:div_example} lists the figures with the top 10 largest population in some job.
+Fig.
+\ref{fig:div_example} lists the figures with the top 10 largest population in some job.
 The textual number beneath indicates the population.
@@
 
-\subsection{t-SNE Projection of Individuals}
-\textcolor{blue}{Not tsne.
-A octagon radar graph to position all citizens.
-A clustering algorithm for commend similar persons into a new group.(maybe: interactions to set the weight of each characteristic)}
-
 \begin{figure}[htb!]
  \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/tsne}
- \caption{t-SNE project with four groups of the interest: (a) t-SNE project }
- \label{fig:tsne}
+ \includegraphics[width=\columnwidth]{pictures/design_example}
+ \caption{Representative figures with the top 10 largest population in four jobs}
+ \label{fig:div_example}
 \end{figure}
+
+\subsubsection{t-SNE Projection of Individuals}
 
@@
 The dimensionality reduction techniques are to preserve the local structure of high dimensional data in low dimensional space, which are efficient approaches to provide a good overview of the multivarible individuals (\textit{C2}).
-We adapt t-SNE project~\citep{maaten2008visualizing} to project $X$ as two-dimensional dots $Y={y_1, y_2, ..., y_n}$.
+We adapt t-SNE project~\cite{maaten2008visualizing} to project $X$ as two-dimensional dots $Y={y_1, y_2, ..., y_n}$.
 One of steps in t-SNE is to compute the conditional probabilities to represent the similarity based on the distance between high dimenional datapoints.
@@
 
-As Figure~\ref{fig:tsne}shows, all 21435 volunteers are embedded in the 2D view, where the closer two dots are, the more similar they are in the eight characteristics.
-Figure~\ref{fig:tsne} exemplifies four features groups of dots in a neighbor.
+As Fig.
+~\ref{fig:tsne} shows, all 21435 volunteers are embedded in the 2D view, where the closer two dots are, the more similar they are in the eight characteristics.
+Fig.
+~\ref{fig:tsne} exemplifies four features groups of dots in a neighbor.
 
-Multiple views of abstract view, t-SNE protection, and semantic data-driven profile visualization are coordinated in a Cross-filter machinesm~\citep{Weaver2010}.
+Multiple views of abstract view, t-SNE protection, and semantic data-driven profile visualization are coordinated in a Cross-filter mechanism~\cite{Weaver2010}.
 It allows end-users to interactive drill-down into individuals with interested characteristics from multiple perspectives(\textit{C3}).
@@
 
-\subsection{2.5D Spatial Visualization}
-\textcolor{blue}{Just a map. Clustering or Grid. 2.5D for stack??}
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/tsne}
+ \caption{t-SNE project with four groups of the interest: (a) t-SNE project }
+ \label{fig:tsne}
+\end{figure}
 
+\subsubsection{2.5D Spatial Visualization}
 \label{subsec:25D}
 
-\begin{figure}[htb!]
+Embedding multiple variables in the spatial map is a challenging problem.
+Distorting 2D spatial for better space usage, such as the partial route embedding~\cite{sun2016embedding} is an effective method when there are a few local foci.
+When it comes to the global visualization, there is always a trade-off between occlusion-free and the compact spatial perception.
+Following the idea of stacking 2.5D space design~\cite{Tominski2012_stacking}, the space in this work is embedded in 2.5D space, to relax the z-axis for additional abstract information encoding.
+
+Fig.
+~\ref{fig:2.5D}(a) shows the 2.5D visualization.
+The spatial map consists of Traffic Analysis Zone (TAZ), which is the unit of geography holding a certain number of people.
+For the 2.5D, each TAZ is grown as a prism whose height and color are developed to encode abstract information, e.g., the occurrence of visiting.
+With difference encoding choices, it is capable to visualize the correlation between spatial and different attributes (\textit{C4}).
+For example, in Fig.
+\ref{fig:2.5D}(a), prisms' height and color both encode the ratio of none-routine trips (such as go entertainment, go hospital, etc.) in the whole.
+For better 3D visual perception, lighting is turned on.
+Also, a lid is laid on the top of each prism to clearly bound its extent at the z-axis.
+
+\begin{figure}
     \centering
-\subfigure[]{
-\resizebox*{9cm}{!}{\includegraphics{pictures/space1.eps}}}\hspace{5pt}
-\subfigure[]{
-\resizebox*{9cm}{!}{\includegraphics{pictures/space2.eps}}}\hspace{5pt}
+	  \subfloat[]{
+       \includegraphics[width=86mm]{pictures/space1.eps}}
+    \label{1a}\hfill
+	  \subfloat[]{
+        \includegraphics[width=86mm]{pictures/space2.eps}}
+    \label{1b}\\
 \caption{2.5D Spatial Visualization: (a) 2.5D spatial visualization with z-axis to encode addition information; (b) detail slicing in 2.5D space.}
@@
 
-Embedding multiple variables in the spatial map is a challenging problem.
-Distorting 2D spatial for better space usage, such as the partial route embedding~\citep{sun2016embedding} is an effective method when there are a few local foci.
-When it comes to the global visualization, there is always a trade-off between occlusion-free and the compact spatial perception.
-Following the idea of stacking 2.5D space design~\citep{Tominski2012_stacking}, the space in this work is embedded in 2.5D space, to relax the z-axis for additional abstract information encoding.
-
-Figure~\ref{fig:2.5D}(a) shows the 2.5D visualization.
-The spatial map consists of Traffic Analysis Zone (TAZ), which is the unit of geography holding a certain number of people.
-For the 2.5D, each TAZ is grown as a prism whose height and color are developed to encode abstract information, e.g., the occurrence of visiting.
-With difference encoding choices, it is capable to visualize the correlation between spatial and different attributes (\textit{C4}).
-For example, in Figure~\ref{fig:2.5D}(a), prisms' height and color both encode the ratio of none-routine trips (such as go entertainment, go hospital, etc.) in the whole.
-For better 3D visual perception, lighting is turned on.
-Also, a lid is laid on the top of each prism to clearly bound its extent at the z-axis.
-
 Several interactions are integrated into the spatial view to alleviating the occlusion problem (\textit{C5}).
 The manipulation of 2.5D view supports users with rotate, zoom, pan operations, which are so continuously flexible that users probably find a suitable observing point.
-In the cases where occlusion is inevitable, an interaction named as \textit{Detail Slicing} is developed, as Figure~\ref{fig:2.5D}(b) shows.
+In the cases where occlusion is inevitable, an interaction named as \textbf{Detail Slicing} is developed, as Fig.
+~\ref{fig:2.5D}(b) shows.
 Detail Slicing is the operation to put a cross-section in the 2.5D space to expose the TAZ inside.
@@
 
-To compare the mobility patterns across different groups of people, a Small Multiple dock is used to reserve the ever explored interesting result (Figure~\ref{fig:teaser}(f)).
+ To compare the mobility patterns across different groups of people, a Small Multiple dock is used to reserve the ever explored interesting result (Fig.
+~\ref{fig:teaser}(f)).
 To simply the comparison over spatial distribution, the snapshot is also rendered in the 2.5D space, which maintains the same interactions as the main 2.5D space does.
 
-\section{Case study}
+\section{Case studies}
 
@@
 
-\subsection{Case 1: Work-life Balance VS Income/Education}
-\textcolor{blue}{theme: Using similar social characteristics to put citizens into target groups.
-change the name of the section.
-Using View1(selecting bar), View2(radar), View3(map, to see the distribution of home and work place)}
+\subsection{Case 1: Home-life distribution VS Income/education}
 
@@
 Although it is incomplete, income and education are two of the most essential characteristics to tag an individual with a good resource or not.
-As Figure~\ref{case11} shows, taking income and education as the two dimensions, taking 300K yuan as the border between high and low income and an undergraduate bachelor degree as the border between high and low education level, four different groups are generated in the four quadrants.
-In the first quadrant, individuals are rich and well educated, who are in a group of so-called \textit{top aristocracy}.
-The second quadrant holds the group of \textit{new rich}, i.e., individuals with high income but low education income.
-In the third quadrant, they are the \textit{underclass} who has both low income and education level.
-The fourth quadrant is \textit{Antizen}, which is a new word to describe people have a good education but earn little.
+As Fig.
+~\ref{case11} shows, taking income and education as the two dimensions, taking 300,000 yuan as the border between high and low income and an undergraduate bachelor degree as the border between high and low education level, four different groups are generated in the four quadrants.
+In the first quadrant, individuals are rich and well educated, who are in a group of so-called \textbf{top aristocracy}.
+The second quadrant holds the group of \textbf{new rich}, i.e., individuals with high income but low education income.
+In the third quadrant, they are the \textbf{underclass} who has both low income and education level.
+The fourth quadrant is \textbf{antizen}, which is a new word to describe people have a good education but earn little.
 
-Figure~\ref{case11} shows the top 12 profiles with the maximum population in each group.
+Fig.
+~\ref{case11} shows the top 12 profiles with the maximum population in each group.
 In each group, other characteristics surprisingly demonstrate the high correlation to income and education.
-For example, almost all of the \textit{top aristocracy} is with the residential license,  house, and car.
-On the contrary, \textit{underclass} do not have the residential license residence, neither the house nor the car.
-Most of \textit{New rich} has a house and work in the service industry.
+For example, almost all of the \textbf{top aristocracy} is with the residential license,  house, and car.
+On the contrary, \textbf{underclass} do not have the residential license residence, neither the house nor the car.
+Most of \textbf{new rich} has a house and work in the service industry.
 
 Before diving into the complex mobility pattern analysis, we explore the home distribution of the four groups.
-As Figure~\ref{case12} shows, \textit{top aristocracy} and most of \textit{new rich} live concentrated in the downtown area of Shenzhen, where the living cost is higher, especially the housing cost.
-A small part of \textit{new rich} lives far away from the downtown, maybe because they don't have to work in downtown.
-The \textit{underclass} distribute more dispersively all over the whole city.
+As Fig.
+~\ref{case12} shows, \textbf{top aristocracy} and most of \textbf{new rich} live concentrated in the downtown area of Shenzhen, where the living cost is higher, especially the housing cost.
+A small part of \textbf{new rich} lives far away from the downtown, maybe because they don't have to work in downtown.
+The \textbf{underclass} distribute more dispersively all over the whole city.
 Compared to the rich, they prefer the outer space because of the lower living cost.
-Lots of \textit{antizen} live in Nanshan District, where there are many universities and high-tech industrial parks full of well educated people.
+Lots of \textbf{antizens} live in Nanshan District, where there are many universities and high-tech industrial parks full of well educated people.
 
@@
 To have a better knowledge of mobility patterns of the four groups, trips are categorized into three categories, ``home", ``work'' for regular trips with the purpose of going home, work (or school for students), ``other'' for irregular trips with the purpose of shopping, visiting friends.
-Figure~\ref{case13}(a) shows the 2.5D overview of the three kinds of traveling categories.
+Fig.
+\ref{case13}(a) shows the 2.5D overview of the three kinds of traveling categories.
 Each TAZ is grown to the same height, i.e., the unit one, and the height proportion of each traveling categories encodes the percentage of certain purpose in the whole, pink for ``others'', blue for ``work'' and green for ``home''.
-Although inside TAZ prisms are blocked in the Figure~\ref{case13}, our attention is drawn to the lifestyle of \textit{New Rich}.
-It is founded that the \textit{New Rich} travel for ``other'' purpose a lot, compared to other groups.
+Although inside TAZ prisms are blocked in the Fig.
+~\ref{case13}, our attention is drawn to the lifestyle of \textbf{New Rich}.
+It is founded that the \textbf{New Rich} travel for ``other'' purpose a lot, compared to other groups.
 To explore further, the detail slicing (introduced in Section~\ref{subsec:25D}) is applied to the four groups.
-Figure~\ref{case13}(b) shows three slices.
-It can be seen that individuals with low income (\textit{underclass} and \textit{antizen}) spend relatively more time on work, especially the \textit{underclass}.
-Working percentage is very small in-group \textit{new rich}.
+Fig.
+~\ref{case13}(b) shows three slices.
+It can be seen that individuals with low income (\textbf{underclass} and \textbf{antizen}) spend relatively more time on work, especially the \textbf{underclass}.
+Working percentage is very small in-group \textbf{new rich}.
 They live a more diverse lifestyle because they do many other things (the pink ones) except working.
@@
 
-\subsection{Case 2: Home-work Distance VS Income/House}
-\textcolor{blue}{theme: the distribution of citizens' mobility when moving with a given purpose; or: attractiveness of region.
-Given a group, interaction with purpose, show distribution of each region.
-Using View3(map, each region with a radar graph to show distance distribution).
-VIEW4:??(od matrix?)(finer level?)}
+\subsection{Case 2: Spatial selection on work-home VS Income/House}
 
@@
 
-Home-work distance is an essential metric in economics, geography, and sociology.
-It refers to the distance between house and workplace.
-It is influenced by many factors like transportation, housing, land use, etc.
+Home and work places are two crucial places where people stays long during the daily lives.
+Within it, home-work distance is an essential metric in home/work places selection.
+Meanwhile, it is influenced by many factors like transportation, housing, land use, etc.
 Understanding the home-work distance of a region helps to evaluate whether the region is well planned or not.
@@
 Considering income potentially determines where people live, we use income as the characteristics to select three groups, the group over 500K, the group during 200-300K and the group less than 100K.
-In Figure~\ref{case2}, the height of the bar stands for visiting frequency of the TAZ and its color encodes the average home-work distance, red for close and yellow for far.
-As Figure~\ref{case2}(a) shows, for all the three groups in different income levels, most of the TAZs have dark red or red color which indicates the home-work distance is generally short, especially in downtown.
+In Fig.
+~\ref{case2}, the height of the bar stands for visiting frequency of the TAZ and its color encodes the average home-work distance, red for close and yellow for far.
+As Fig.
+~\ref{case2}(a) shows, for all the three groups in different income levels, most of the TAZs have dark red or red color which indicates the home-work distance is generally short, especially in downtown.
 Only those with less than 100K salary work outside the center, such as the space in the green circle.
@@
 We explore the home-work distance of groups with and without a house.
-Figure~\ref{case2}(b) shows the close-up views.
+Fig.
+~\ref{case2}(b) shows the close-up views.
 It is found that the Nanshan District has a shorter home-work distance for individuals without a house, while Futian District has shorter for those with a house.
@@
 
-\subsection{Case 3: Life-style VS Jobs}
-\textcolor{blue}{theme: what persons do?
-trip purpose sequence?
-Given a group, interaction with purpose, show distribution of each region.
-Using View3(map, 2.5D), View4(a stacked bar to show quantity of each kinds of purpose.)}
-
+\subsection{Case 3: space distribution of lifestyles VS Jobs}
 In this case, we explore the correlation between mobility patterns with the job, to see whether the job has an impact on the movement.
-Officer, workman, student, and businessman are selected as examples and the population of trips for certain purposes is shown In Figure~\ref{case3}.
+\textit{Officer, workman, student, and businessman} are selected as examples and the population of trips for certain purposes is shown In Fig.
+~\ref{case3}.
 The height of bars encodes the amount of visit to each TAZ, and color encodes the traveling purpose.
@@
 For quick linking between color and purposes, the regular trips such as go to work, school and home are dyed in cold color, and the irregular trips such as go shopping, hospital, etc, are dyed in the warm color.
-As Figure~\ref{case3} shows, for officers, the TAZs changes dramatically in height.
+As Fig.
+~\ref{case3} shows, for officers, the TAZs changes dramatically in height.
 Some TAZs have much more visiting than others because officers are more constrained to work in some buildings than individuals with other jobs.
@@
 
+\section{Expert Feedback}
+
+% \lmc{Add a section to introduce the domain experts' feedback}
+% \lm{We interview XX domain experts from the GIS field. XX of them are with ... The procedure went as following. We first introduce them the system an...}
+
+We ran an interview with the two domain experts, to ask about their feedback on the designed system.
+Overall, the two domain experts praised high for the full walk-through from data collection to analysis, towards the research problem of spatial preference with social individuals.
+They also appreciated the overall design of a visual analytic system and the finding cases.
+Specifically, they pointed out what they like and also to be improved.
+
+Expert A expressed her like in the data-driven profile visualization.
+She commented that ``it takes little effort to learn how to read it, which really taps into my daily experience.''.
+Expert B also commented the data-driven profile visualization provides an intuitive representation of individuals, though sometimes it is cumbersome to recognize each of them when there are too many.
+But he said the combination usage of profile and t-SNE is very efficient, which enables him to quickly identify individuals from the mass.
+Both two experts spoke highly about dynamic identifying groups of interest and on-the-fly analysis of the spatial preference.
+Expert A commented that ``the visual analytic system allows me to try any group of interest''.
+Expert B like the cross-filtering interactions across multiple views.
+For spatial visualization, both two experts thought our solution, 2.5D visualization is a grid-based spatial visualization is a fancy design choice.
+With detail slicing function, not only the overview of the spatial distribution, but also the inner details of each TAZ could be filtered out and check directly.
+
 \section{Conclusion}
 \label{sec:conclusion}
-
 This work demonstrates a throughout research flow from data collection, basic analysis to deep visual analysis of mobility patterns with individual characteristics.
-Considering the irresistible trend in mixing social data and spatial data to solve the urban problem, this work takes one step forward in exploring the relationship between movement and individuals' characteristics, which is rarely touched by previous geo-tagged social media visual analytics.
+Considering the irresistible trend in mixing social data and spatial data to solve the urban problem, this work takes one step forward in exploring the relationship between movement and individuals’ characteristics, which is rarely touched by previous geo-tagged social media visual analytics.
 The design of the visual analytic system is driven by three tasks about individuals and mobility patterns.
@@
 Although it is not a one-step solution, 2.5D visualization with the detail slicing is able to provide an occlusion-free analysis with spatial context preserved.
+Our current research focuses on fundamental facets of the spatial preference and doesn’t draw a strong conclusion on the correlation between movements and individual characteristics.
+In next step, more delicate algorithms will be involved to extract high-level mobility patterns, such as the frequent visiting sequence of an individual group, etc.
 
-Our current research focuses on fundamental facets of the mobility patterns and doesn't draw a strong conclusion on the correlation between mobility pattern and individual characteristics.
-In next step, more delicate algorithms will be involved to extract high-level mobility patterns, such as the frequent visiting sequence of an individual group, etc.
-On the other hand, the data we used in this work shows its potential in representing the population.
-As the next step, research effort can be put into a more serious verification of how small sampled data can represent a large population.
+\bibliographystyle{ieeetran}
+\bibliography{main}
 
-%\begin{acknowledgements}
-%If you'd like to thank anyone, place your comments here
-%and remove the percent signs.
-%\end{acknowledgements}
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bio/wq}}]{QI WANG} received the B.Eng.
+degree in information security from Wuhan University, China.
+She is currently working toward the Ph.D.
+degree in the State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University.
+Her research interests include transport geographic information system, spatiotemporal data analysis, mining and visualization.
+\end{IEEEbiography}
 
-% BibTeX users please use one of
-\bibliographystyle{spbasic}      % basic style, author-year citations
-%\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
-\bibliography{main}
-%\bibliography{test}
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bio/minlu}}]{Min lu} is an associate researcher at ShenZhen University.
+Her major research interest is data visualization and visual analytics, especially focusing on the urban data.
+She received Ph.D degree in Computer Science from Peking University in 2017 and BS degree in Computer Science from Beijing Normal University in 2011.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bio/lqq}}]{Qingquan Li} received the Ph.D.
+degree in geographic information system (GIS) and photogrammetry from Wuhan Technical University of Surveying and Mapping, Wuhan, China, in 1998.
+He is currently a Professor with Shenzhen University, Guangdong, China, and Wuhan University, Wuhan, China.
+His research areas include 3-D and dynamic data modeling in GIS, location-based service, surveying engineering, integration of GIS, Global Positioning System and remote sensing, intelligent transportation system, and urban informatics.
+\end{IEEEbiography}
+
+\EOD
 
 \end{document}
-% end of file template.tex

### 2020-01-09 ia/ia_vis_3d.tex
0109

@@
 
-\title{Unfolding the City: Spatial Preference Based on Individual Characteristics}
+\title{Unfolding the City: Spatial Preference Based on Individual Demographic Characteristics}
 
@@
 \address[2]{Shenzhen Key Laboratory of Spatial Smart Sensing and Services, Shenzhen University, Shenzhen 518060, China}
-\address[3]{School of Architecture and Urban Planning, ShenZhen University, Shenzhen 518060, China}
+\address[3]{School of Architecture and Urban Planning, Shenzhen University, Shenzhen 518060, China}
 
@@
 A city is shaped not only by its assembled infrastructures but also the people living inside it.
-People in a wide range of individual social characteristics visit places with different weights and preferences, sculpturing the city into a space of diverse mobility patterns.
-Different from the well study of anonymous travel behaviors, the daily movement of characterized individuals, is less studied because of the challenges in collection and analysis of data with privacy.
+People in a wide range of individual demographic characteristics visit places with different weights and preferences, sculpturing the city into a space of diverse spatial preferences.
+Different from the well study of anonymous travel behaviors, the daily movement of characterized individuals, is less studied due to the challenges in collection and analysis of data with privacy.
 In this work, we take a step forward and perform an online census to collect individual profiles and movements from large-scale volunteers.
-Then we develop a visual analytic system to investigate the mobility patterns of groups by specifying characteristics.
+Then we design a visual analytic system to investigate the spatial preference to groups by specifying demographic characteristics.
 To facilitate the identification of characterized groups, individuals are embedded in t-SNE projection for an abstract overview as well as drawn as vivid graphics by a data-driven profile method for detail examination.
@@
 \PARstart{T}{he} science fiction \textbf{Folding Beijing}~\cite{hao2016_foldingbeijing} depicts a world where three social classes of people live in independent spatiotemporal patterns, though sharing the same earth surface.
-This is an artistical metaphor for one potential fact that people prefer to select different places according to individual characteristics, such as social, economic, educational features.
+This is an artistic metaphor for one potential fact that people prefer to select different places to live according to individual characteristics, especially personal demographic characteristics.
 This phenomenon has attracted the research interest for a long time in the sociological field.
@@
 Contemporary contestation also continually raises the banner "The City Belongs to All!"~\cite{Mayer2017_whosecity}.
-Having a good understanding of relationships between the spatial attractiveness and the characterized individuals sheds light on region utilization, diversity mix-up, and opportunities promotion.
+Some approaches have been to discuss spatial distribution~\cite{RN909}, spatial interaction~\cite{RN1692} and place attractiveness~\cite{retailcity}.
+However, lacking of movers' characteristics, they almost only analyzed from the spatial perspective, and individual characteristic factors were not put into the context of the problems.
+It is required to explore the relationship between spatial preference and individual demographic characteristics for better region utilization, diversity mix-up, and opportunity promotion.
 
-In the past decades, the power of visual analytics in exploring spatiotemporal data has been recognized and well developed.
-Various urban problems are answered, such as traffic jams~\cite{wang2013visual}, interchanging flows in public transportation~\cite{zeng2013visualizing}, etc.
+Due to the multidimensional nature of demographic characteristics and spatial diversity of movements, it is challenging to explore, analysis and express the relationship between them.
+In the past decades, the power of visual analytics on urban problems has been recognized and well developed~\cite{wang2013visual, zeng2013visualizing}.
 The presence of social media applications fuels the spatial analysis with rich semantic texts, so researchers get the chances to explore the thematic meaning of the moving behavior, such as events~\cite{chen2017map} or topics~\cite{bosch2013scatterblogs2}.
-Those works essentially contribute in deepening the contextual understanding of moving activity.
-However, they rarely combine the movement analysis with individuals' characteristics because which cannot be fully inferred from social media profiles.
-One of the main challenges is the sensitivity issue in privacy data.
-There is still a research gap in exploring the relationship between spatial pattern and social characteristics.
+Those works essentially contribute on deepening the contextual understanding of moving activity.
+\colorbox{yellow}{However, they rarely combine the movement analysis with individuals' characteristics because which cannot be fully inferred from social media profiles.
+One of the main challenges is the sensitivity issue in privacy data.}
+The question of how to intuitively discover the relationship between spatial preference and multidimensional characteristics is worthy of further investigation.
 
-In this work, we contextualize the analysis of citizens' spatial distribution in the backcloth of individual characteristics.
-With the motivation of fusing the movement data with individuals' profiles in an attempt to ascertain the spatial distribution for groups with different characteristics, we need to get the characterized information of movers.
+In this work, we contextualize the analysis of citizens' spatial preference in the backcloth of individual demographic characteristics.
+With the motivation of it, we need to obtain the demographic characteristics of individuals and their daily movements.
 The conventional offline census takes lots of effort and too much time to be out of date.
-With the wide use of the mobile device, it is possible to count information online.
-In this work, with a census survey released via social media application, we ran an online demographical collection campaign.
-Based on the data collected, we developed a visual analytics system to explore where do citizens prefer to go.
-The system incorporates visualizations of individuals' characteristics, including t-SNE for an overview and data-driven profile visualization for the detailed check, as well as 2.5D spatial visualization to explore the distribution of movements.
-Finally, applying our method in Shenzhen, several cases are derived to demonstrate the powers of our method.
+With the wide use of the mobile device, it is possible to collect information online.
+In this work, we ran an online demographical collection campaign released via a social media application.
+Based on the data collected, we developed a visual analytics system to explore where do specified charactered citizens prefer to go.
+The system incorporates visualizations of individuals' characteristics, including t-SNE for an overview and data-driven profile visualization for the detailed check, as well as 2.5D spatial visualization to explore the spatial distribution of movements.
+Finally, applying our method in Shenzhen, several cases are derived to demonstrate the power of our method.
 There are two contributions of this work:
 
-(1) investigate mobility patterns with characteristics, which is a natural step into research of social understanding of the city.
+(1) investigate spatial preference with individual demographic characteristics, which is a natural step into research of social understanding of the city.
 
@@
 This work concerns the research topic of spatial data visual analytics.
-Spatiotemporal data has three components, i.e., spatial, temporal and thematic~\cite{andrienko2013visual}.
-Lots of related work focus on the spatio-temporal analysis in movement data, in the absence of thematic information.
+Lots of related work focus on the spatiotemporal analysis in movement data, in the absence of thematic information.
 The presence of geotagged social media data flourishes the exploration of thematic information along with movement.
 By analyzing the texts, those work explain what drive the moving activities or what is resulted from.
-This work continues the thematic research in movement data but focuses more on individual characteristics.
+This work continues the thematic research in movement data but focuses more on individual demographic characteristics.
 Landed by a census experiment, this work is able to analyze the profile information directly, to get rid of indirect data inferred from social media data as other related works do.
@@
 The experts pointed out that as big and open data evolved in, the scope of urban research has been lifted from the spatial perspective up to social-spatial perspective.
-There is a rising research interest in understanding how groups of citizens with certain social characteristics select places during their daily lives.
-Whether people visit places with preference which are intrinsically affected by their social-economic characteristics?
-Is there a limitation or probabilities of interaction between different socio-economic groups in public spaces?
+There is a rising research interest in understanding how categories of citizens with certain demographic characteristics visit places during their daily lives.
+Whether people select places with preference which are intrinsically affected by their social-economic characteristics?
+Is there a limitation or probabilities of interaction between different socio-economic groups in public space?
 With the advances of data acquisition and analysis techniques, they demanded to go beyond the conventional static sampled questionnaires, which usually survey visiting preferences.
-They sought for the possibility in revealing the spatial distribution in real-world visiting logs and urged to have a dynamic system which supports the interactive examination of spatial distribution in different contexts of social characteristics.
+They sought for the possibility in revealing the spatial distribution in real-world visiting logs and urged to have a dynamic system which supports the interactive exploration of spatial preference in different contexts of demographic characteristics.
 
 Thereafter we booted up this project with several rounds of discussions, to frame the research problem with two core contents and the research procedure.
-The first concepts is \textbf{Social Characteristics}.
-Social characteristics of a person or group of citizens  are the descriptors which contribute to the specification of the populations.
-This work intends to cover the social characteristics from multi-facets, including descriptors such as gender, income, education, etc.
-The second content is \textbf{Spatial Distribution}.
+The first content is \textbf{demographic characteristics}.
+Demographic characteristics of a person or a group of individuals are the descriptors which contribute to the specification of the populations.
+This work intends to cover the characteristics from multi-facets, including descriptors such as gender, income, education, etc.
+The second content is \textbf{spatial preference}.
 It is reflected by the popularity of a place to be visited.
 
-Motivated by their research interest in understanding the spatial attractiveness with individual social characteristics, this work goes through a procedure consists of two stages, i.e., data collection and basic reviewing, visual analytics design iteration with experts' feedback.
+Motivated by their research interest in understanding the spatial preference with individual demographic characteristics, this work goes through a procedure consists of two stages, i.e., data collection and basic reviewing, visual analytics design iteration with experts' feedback.
 
@@
 Considering there is no existing public dataset could fit our topic well, this work is consolidated with a self-maintained data sourcing.
-We release an online data census to collect the social characteristics and movement logs of individuals for almost half a year.
+We release an online information survey to collect the demographic characteristics and movement logs of individuals for almost half a year.
 Then a series of statistical analysis is performed on the collected data for sampling bias checking.
 
-\subsection{Online Census}
+\subsection{Online Survey}
 
 The advent of mobile sensing techniques and social media applications makes it possible to collect spatial data by apps within the phones.
-Complementary to the conventional census, it brings the benefit of convenient collections without much manpower and precise spatial locations by GPS instead of semantic description.
-Meanwhile, it is possible to collective the movement in human inactive time, such as the mid-night.
+Complementary to the conventional survey, it brings the benefit of convenience without much manpower and precise spatial locations by GPS instead of semantic description.
 
-In this work, we perform the census survey in Shenzhen, which is one of the most modern metropolis in China.
-The experiment is deployed on Wechat, the most widely used social media mobile application.
+In this work, we perform the survey in Shenzhen, which is one of the most modern metropolis in China.
+The experiment is deployed on Wechat, the most widely used social media mobile application in China.
 Fig.
-\ref{fig:app} shows the data collecting interfaces.
-For privacy issue, all detailed personal information are desensitized to categorical levels.
-Considering the main aim on the relationship between spatial distribution of movements and individuals' characteristics, there are two crucial contents to be collected:
+\ref{fig:app} shows \colorbox{yellow}{the interfaces of survey app.} For privacy issue, all detailed personal information are desensitized to categorical levels.
+Considering the main aim on the relationship between spatial preference and demographic characteristics, two crucial aspects need to be collected:
 
-\textbf{Individual Characteristics} Fig.
-\ref{fig:data_over} lists the eight domains, including social, economic and demographic aspects, to give a generalized description of the individual characteristics.
+\textbf{Demographic Characteristics} Fig.
+\ref{fig:data_over} lists the eight domains to give a generalized description of the individuals.
 The profile will serve as the ingredients for the analysis of mobility patterns over diverse individuals.
 
-\textbf{Traveling Trips} Besides to those individual characteristics, each individual can upload dynamic traveling trips (Fig.
+\textbf{Traveling Trips} Individuals can upload dynamic traveling trips (Fig.
 \ref{fig:app}(b)).
-Each trip requires the information of start/end location, start/end time, traveling purpose.
+Each trip requires the information of start/end location, start/end time, traveling purpose, and traveling mode.
+Locations are recorded by GPS modules in the phones.
 To encourage the trip uploading, a credit system retains the contribution of individuals on trips and rewards the volunteers with the top credits (Fig.
@@
 
-Over the releasing time period from 2015-11 to 2016-01, 21,435 individuals (48\% females and 52\% males) participated in the census and 229,155 trips were collected.
-Each volunteer contributed 11 trips average.
+Over the releasing time period from 2015-11 to 2016-01, 21,435 individuals participated in the census and 229,155 trips were collected. \colorbox{yellow}{Each volunteer contributed 11 trips average.}
 
@@
 
-Our case-study data is confined to a small proportion of Wechat users who opt to contribute their profile  and movements.
+Our case-study data is confined to a small proportion of Wechat users who opt to contribute their demographic profiles and movements.
 Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of the population in the city.
@@
 Fig.
-\ref{fig:data_age_edu} gives the distribution of age and education over the population.
-It shows that samples cover a wide range of ages, dominating between 18 to 45.
-There is also a few records pertaining to individuals below the age of 18 or above 70.
-The distribution follows the fact that Shenzhen is a city where the majority is young people.
+\ref{fig:data_age_edu} gives the distribution of gender, age and education over the population.
+For participated citizens, 48\% of them are female and 52\% are male.
+It is consistent with governmental statistics that 47\% of the whole citizens are female and 53\% are male\footnote{http://tjj.sz.gov.cn/zwgk/zfxxgkml/tjsj/tjgb/201804/t20180427\_11800902.htm}.
+The age collected covers a wide range, dominating between 18 and 45.
+There are also records pertaining to individuals below the age of 18 or above 70.
 According to the 2015 Annual Census Statistics report\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5.
+The age distribution in collected data follows the fact that Shenzhen is a city where the majority is young.
 Fig, \ref{fig:data_age_edu}(b) gives the distribution of education levels, ranging from low to high.
 The technical college and university dominate the samples at the 61\% occupancy rate.
-
 Fig.
 \ref{fig:data_job_inc}(a) shows the job types of sampled individuals, who are servants, workers, officers, businessmen and so on.
-Fig.
-\ref{fig:data_job_inc}(b) gives the radar diagram of the annual pay.
-The majority get paid below 200,000.
-Individuals with higher salary are also reached in our census.
+\colorbox{yellow}{Fig.
+\ref{fig:data_job_inc}(b) gives the radar diagram of the annual pay.} The majority get paid below 200,000.
+Citizens with higher salary are also reached in our census.
 
@@
 
+The basic statistics related to movements are shown in Fig.
+\ref{fig:data_geometry}.
+\colorbox{yellow}{Fig.
+~\ref{fig:data_geometry}(a) visualizes the distribution of trip quantity of each citizen.
+It has a heavy-tail trait, which follows the law of most human-related statistics}.
+In Fig.
+~\ref{fig:data_geometry}(b), the active traveling time (here, we take the start time as the representative of active time) follows the common knowledge about urban life.
+There are obvious morning and evening rush hours.
 Fig.
-\ref{fig:data_geometry} shows the basic statistics related to movements.
-In Fig.
-~\ref{fig:data_geometry}(a), the active traveling time (here, we take the start time as the representative of active time) follows the common knowledge of urban life.
-There are obvious morning and late afternoon peaks.
-Fig.
-~\ref{fig:data_geometry}(b) gives the counting of different traveling purposes.
+~\ref{fig:data_geometry}(c) gives the counting of different traveling purposes.
 95\% trips are tagged with clear raveling purpose in the data.
@@
 Fig.
-~\ref{fig:data_geometry}(c) shows the spatial distribution of the origins and destinations.
+~\ref{fig:data_geometry}(d) shows the spatial distribution of the origins and destinations.
 It is found that more dots are located in Futian and Nanshan districts, the city's heart than the surrounding areas.
@@
  \includegraphics[width=\columnwidth]{pictures/data3}
- \caption{Statistics of Trips: (a) start time of trips; (b) purpose of trips; (c) distribution of origins/destinations }
+ \caption{Statistics of Trips: (a) distribution of trip quantity of each citizen; (b) start time of trips; (c) purpose of trips; (d) distribution of origins/destinations. }
  \label{fig:data_geometry}
@@
 
-Because there is always inevitable bias inherent in fully representing the ground truth of the population, the preliminary statistical analysis shows positive sign of a relatively even sampling of the population.
+Due to lacking of governmental statistics, we cannot verify all characteristics and movements collected are consistent with all the citizens in Shenzhen.
+From the perspective of survey, there is always inevitable bias inherent in fully representing the ground truth of the population.
+However, the preliminary statistical analysis shows the rich scope of the data, which embodies positive sign of a relatively even sampling of the population.
 
@@
 \begin{itemize}
-\item \textbf{Task 1: Identify the group with specific individual characteristics}: to get groups of people with common or close attributes, to explore the correlation among individual characteristics.
-\item \textbf{Task 2: Explore the mobility distribution of a group}: to explore where, how and why an interested group go in the city.
-\item \textbf{Task 3: Compare mobility distribution among multiple groups}: to know the similarities and differences between different groups in their spatial preferences, to investigate the relationship between movement and individual characteristics.
+\item \textbf{Task 1: Identify the group with specific individual demographic characteristics}: to get groups of people with common or similar attributes, to explore the correlation among individual characteristics.
+\item \textbf{Task 2: Explore the spatial preference of a group}: to explore where, how and why an interested group go in the city.
+\item \textbf{Task 3: Compare spatial preference among multiple groups}: to express the similarities and differences between different groups in their spatial preferences, to investigate the relationship between movement and individual demographic characteristics.
 \end{itemize}
@@
 
-With these three tasks, we derive following design considerations:
+With three tasks above, we derive following design considerations:
 
 \begin{itemize}
-\item \textbf{Intuitive perception of an individual as an organic complex (C1)}: the system should make use of users' daily life experience in knowing people to provide intuitive visualization, instead of the lifeless representation by number.
+\item \textbf{Intuitive perception of an individual as an organic complex (C1)}: the system should make use of end-users' daily experience in sensing individuals' demographic characteristics to provide intuitive visualization, instead of the lifeless representation by number.
 The visual design needs to help end-users to pick desirable ones from the mass.
@@
 
-With those design considerations, we develop a visual analytics system as Fig.
+With all the design considerations, we develop a visual analytics system as Fig.
 \ref{fig:teaser} shows.
@@
 In the individual panel, interactive infographics, t-SNE visualization, and data-driven profiles support users to narrow the scope down to groups of individuals with interested characteristics.
-With the chosen group of individuals, its moving related information is visualized and explored in a 2.5D spatio-temporal view.
+With the specified group of individuals, its moving-related information is visualized and explored in a 2.5D spatiotemporal view.
 
@@
 Several interactions are integrated into the spatial view to alleviating the occlusion problem (\textit{C5}).
-The manipulation of 2.5D view supports users with rotate, zoom, pan operations, which are so continuously flexible that users probably find a suitable observing point.
-In the cases where occlusion is inevitable, an interaction named as \textbf{Detail Slicing} is developed, as Fig.
-~\ref{fig:2.5D}(b) shows.
+The manipulation of 2.5D view supports users with rotate, zoom, pan operations, which is continuously flexible that users can find a suitable observing point.
+In the cases where occlusion is inevitable, a 2D view for overview and an interaction, namely, Detail Slicing, are developed, \colorbox{yellow}{as Fig.
+~\ref{fig:2.5D}(b) and (c) shows.
+Overview view shows all TAZs in the form of 2D plane.} It is for quickly sensing the distribution of the whole city.
 Detail Slicing is the operation to put a cross-section in the 2.5D space to expose the TAZ inside.
@@
 
-% \lmc{Add a section to introduce the domain experts' feedback}
-% \lm{We interview XX domain experts from the GIS field. XX of them are with ... The procedure went as following. We first introduce them the system an...}
-
-We ran an interview with the two domain experts, to ask about their feedback on the designed system.
-Overall, the two domain experts praised high for the full walk-through from data collection to analysis, towards the research problem of spatial preference with social individuals.
+We ran an interview with the two domain experts, to ask about their feedbacks on the designed system.
+Overall, the two domain experts praised high for the full walk-through from data collection to analysis, towards the research problem of spatial preference with demographic characteristics.
 They also appreciated the overall design of a visual analytic system and the finding cases.
@@
 For spatial visualization, both two experts thought our solution, 2.5D visualization is a grid-based spatial visualization is a fancy design choice.
-With detail slicing function, not only the overview of the spatial distribution, but also the inner details of each TAZ could be filtered out and check directly.
+With detail slicing function, not only the overview of the spatial preference, but also the inner details of each TAZ could be filtered out and check directly.
 
@@
 \label{sec:conclusion}
-This work demonstrates a throughout research flow from data collection, basic analysis to deep visual analysis of mobility patterns with individual characteristics.
-Considering the irresistible trend in mixing social data and spatial data to solve the urban problem, this work takes one step forward in exploring the relationship between movement and individuals’ characteristics, which is rarely touched by previous geo-tagged social media visual analytics.
+This work demonstrates a throughout research flow from data collection, basic analysis to deep visual analysis of spatial preference with individual demographic characteristics.
+Considering the irresistible trend in mixing demographic data and spatial data to solve the urban problem, this work takes one step forward in exploring the relationship between movement and individuals’ characteristics, which is rarely touched by previous geo-tagged social media visual analytics.
 The design of the visual analytic system is driven by three tasks about individuals and mobility patterns.
@@
 Our current research focuses on fundamental facets of the spatial preference and doesn’t draw a strong conclusion on the correlation between movements and individual characteristics.
-In next step, more delicate algorithms will be involved to extract high-level mobility patterns, such as the frequent visiting sequence of an individual group, etc.
+In next step, more delicate algorithms will be involved to extract high-level spatial preference, such as the frequent visiting sequence of an individual group, etc.
 

### 2020-01-09 ia/ia_vis_3d.tex
new version

@@
 Fig.
-\ref{fig:app} shows \colorbox{yellow}{the interfaces of survey app.} For privacy issue, all detailed personal information are desensitized to categorical levels.
+\ref{fig:app} shows the interfaces of survey app.
+For privacy issue, all detailed personal information are desensitized to categorical levels.
 Considering the main aim on the relationship between spatial preference and demographic characteristics, two crucial aspects need to be collected:
@@
  \centering
- \includegraphics[width=9cm]{pictures/survey_app}
+ \includegraphics[width=9cm]{pictures/survey_app_eng}
   \captionsetup{justification=centering}
- \caption{Census Interface: (a) personal characteristics collecting page; (b) trips collecting page; (c) credit system page.}
+ \caption{Census app interface: (a) personal characteristics collecting page; (b) trips collecting page; (c) credit system page. (In real census survey, contents are shown in Chinese.)}
  \label{fig:app}
@@
 
-Over the releasing time period from 2015-11 to 2016-01, 21,435 individuals participated in the census and 229,155 trips were collected. \colorbox{yellow}{Each volunteer contributed 11 trips average.}
+Over the releasing time period from 2015-11 to 2016-01, 21,435 individuals participated in the census and 229,155 trips were collected.
+
+Our case-study data is confined to a small proportion of Wechat users who opt to contribute their demographic profiles and movements.
+Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, we performed a series of preliminary statistics.
+In Fig.\ref{fig:data_overview}, population distribution of each characteristic is shown.
+The length of the block is coded for population quantity.
 
@@
  \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/data1}
- \caption{Age and Education Distribution: (a) age; (b) education.}
- \label{fig:data_age_edu}
+ \includegraphics[width=\columnwidth]{pictures/data_overview}
+ \caption{Preliminary statistics of each characteristic in collected demographic data.}
+ \label{fig:data_overview}
 \end{figure}
 
-Our case-study data is confined to a small proportion of Wechat users who opt to contribute their demographic profiles and movements.
-Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of the population in the city.
+From the figure, 51.2\% of the participated citizens are male and 48.8\% are female.
+It is consistent with governmental statistics that 47\% of the whole citizens are female and 53\% are male\footnote{http://tjj.sz.gov.cn/zwgk/zfxxgkml/tjsj/tjgb/201804/t20180427\_11800902.htm}.
+The age collected covers a wide range, dominating between 18 and 45.
+There are also records pertaining to individuals below the age of 18 or above 70.
+According to the 2015 Annual Census Statistics report\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5.
+The age distribution in collected data follows the fact that Shenzhen is a city where the majority is young.
+From the distribution of education levels, ranging from low to high.
+The technical college and university dominate the samples at the 61\% occupancy rate.
+The majority get paid below 200,000.
+Citizens with higher salary are also reached in our census.
+Due to lacking of governmental statistics, we cannot verify all characteristics collected are consistent with all the citizens in Shenzhen.
+From the perspective of survey, there is always inevitable bias inherent in fully representing the ground truth of the population.
+However, the preliminary statistical analysis shows the rich scope of the data, which embodies positive sign of a relatively even sampling of the population in the city.
 
+\iffalse
 Fig.
@@
  \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \includegraphics[width=\columnwidth]{pictures/data1}
+ \caption{Age and Education Distribution: (a) age; (b) education.}
+ \label{fig:data_age_edu}
+\end{figure}
+
+\begin{figure}[htb!]
+ \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
  \includegraphics[width=\columnwidth]{pictures/data2}
@@
 \end{figure}
+\fi
 
@@
 \ref{fig:data_geometry}.
-\colorbox{yellow}{Fig.
+Fig.
 ~\ref{fig:data_geometry}(a) visualizes the distribution of trip quantity of each citizen.
-It has a heavy-tail trait, which follows the law of most human-related statistics}.
+It has a heavy-tail trait, which follows the law of most human-related statistics.
 In Fig.
@@
  \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
- \includegraphics[width=\columnwidth]{pictures/data3}
+ \includegraphics[width=\columnwidth]{pictures/data3_2}
  \caption{Statistics of Trips: (a) distribution of trip quantity of each citizen; (b) start time of trips; (c) purpose of trips; (d) distribution of origins/destinations. }
@@
 \end{figure}
-
-Due to lacking of governmental statistics, we cannot verify all characteristics and movements collected are consistent with all the citizens in Shenzhen.
-From the perspective of survey, there is always inevitable bias inherent in fully representing the ground truth of the population.
-However, the preliminary statistical analysis shows the rich scope of the data, which embodies positive sign of a relatively even sampling of the population.
 
@@
 \begin{figure*}[htb!]
- \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
+ \centering
  \includegraphics[width=18.1cm]{pictures/teaser.eps}

### 2020-01-18 ia/ia_vis_3d_final.tex
ia

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{textcomp}

\ifCLASSOPTIONcompsoc
\usepackage[caption=false, font=normalsize, labelfont=sf, textfont=sf]{subfig}
\else
\usepackage[caption=false, font=footnotesize]{subfig}
\fi

\ifCLASSINFOpdf
   \usepackage{graphicx}
   \usepackage{lipsum}
   \usepackage{booktabs}
   \usepackage{threeparttable}
   \usepackage{caption}
   \usepackage{epstopdf}
   \usepackage{cite}
\else
\fi

\usepackage{xcolor}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2017.DOI-}

\title{Unfolding the City: Spatial Preference Based on Individual Demographic Characteristics}

\author{\uppercase{Qi wang}\authorrefmark{1,2}, \uppercase{min lu}\authorrefmark{2,3} and \uppercase{Qingquan Li}\authorrefmark{1,2}}
\address[1]{State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, Wuhan 430072, China}
\address[2]{Shenzhen Key Laboratory of Spatial Smart Sensing and Services, Shenzhen University, Shenzhen 518060, China}
\address[3]{School of Architecture and Urban Planning, Shenzhen University, Shenzhen 518060, China}

\tfootnote{This work was jointly supported by the National Natural Science Foundation of China(No. 71961137003 and No. 41671387).}

\markboth
{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}

\corresp{Corresponding author: Qingquan Li (e-mail: liqq@szu.edu.cn).}

\begin{abstract}
A city is shaped not only by its assembled infrastructures but also by the people living inside it. People with a wide range of individual demographic characteristics visit places at different weights and with different preferences, sculpting a city into a space of diverse spatial preferences. Compared with the well-studied anonymous travel behaviors, the daily movement of characterized individuals has been less studied due to the challenges in the collection and analysis of data considering privacy. In this work, we take a step forward and perform an online census to collect individual profiles and movements from volunteers on a large-scale. Then, we design a visual analytic system to investigate the spatial preferences of groups by specifying demographic characteristics. To facilitate the identification of characterized groups, individuals are embedded in t-SNE projection for an abstract overview, and vivid graphics are drawn by a data-driven profile method for detailed examination. A 2.5D spatial visualization is proposed to maintain a compact multivariable analysis by relaxing the z-axis to encode information, such as visiting frequency, demands, and traveling distance. Together with a cross-filter and flexible 2.5D interactions, the effectiveness and usability of the system are demonstrated well by a study conducted in Shenzhen.\end{abstract}

\begin{keywords}
Visual analytics, spatial preference, individual characteristics, data collection
\end{keywords}

\titlepgskip=-15pt

\maketitle

\section{Introduction}
\label{sec:introduction}
\PARstart{T}{he} science fiction novella \textit{Folding Beijing}~\cite{hao2016_foldingbeijing} depicts a world where three social classes of people live in independent spatiotemporal patterns, though sharing the same earth surface. This work is an artistic metaphor for one possibility that people prefer to select different places to live according to their individual characteristics, especially their personal demographic characteristics. This phenomenon has attracted research interest for a long time in the sociological field. In 1970, Pahl~\cite{pahl1975whose} posed the question "whose city" and expressed interest in understanding territorial inequalities. Contemporary contestation also continually raises the banner "The City Belongs to All!"~\cite{Mayer2017_whosecity}. Some approaches include discussing spatial distribution~\cite{RN909}, spatial interaction~\cite{RN1692} and place attractiveness~\cite{retailcity}. However, because of the lack of movement characteristics, these aspects were analyzed from a spatial perspective, and individual characteristic factors were not placed into the context of the problems. It is necessary to explore the relationship between spatial preference and individual demographic characteristics for better region utilization, greater diversity, and opportunity promotion.

Due to the multidimensional nature of demographic characteristics and the spatial diversity of movements, it is challenging to explore, analyze and express the relationship between these parameters. In recent decades, the power of visual analytics in urban problems has been recognized and developed well~\cite{wang2013visual, zeng2013visualizing}. The presence of social media applications fuels spatial analysis with rich semantic texts, so researchers can explore the thematic meaning of the movement behaviors, such as events~\cite{chen2017map} and topics~\cite{bosch2013scatterblogs2}. These works essentially contribute to deepening the contextual understanding of movement activities.  Some works dive deep and infer individual characteristics from social media profiles~\cite{peddinti2014internet} to better describe the semantics of movement behavior. However, due to the limited exposure of personal information, there is still a research gap between understanding the movement behavior and underlying characteristics of movers.
%The question of how to intuitively discover the relationship between spatial preference and multidimensional characteristics is worthy of further investigation.

In this work, we aim to probe deeper in this direction and contextualize the analysis of citizens' spatial preferences against the backdrop of individual demographic characteristics. With this motivation, we ran a campaign to obtain the demographic characteristics of individuals and their daily movements. Conventional offline census requires too much effort and time. With the wide use of mobile devices, we collected information online; we released an online data sourcing program on a social media application that collected data for over half a year. The demographics and movement information of over 10K volunteers were collected during this period. Based on the data collected, we developed a visual analytics system to explore the association between spatial preference and individual demographic characteristics. The system incorporates visualizations of individuals' characteristics, including t-SNE for an overview and data-driven profile visualization for a detailed analysis, as well as 2.5D spatial visualization to explore the spatial distribution of movements. Finally, applying our method in Shenzhen, we derived several cases to demonstrate the power of our method. This work makes two contributions:

(1) We investigate spatial preference with individual demographic characteristics, which is a natural step in research on understanding the social behaviors of a city.

(2) We develop a visual analytic system, whose effectiveness and usability are demonstrated well by a study conducted in Shenzhen.

\section{Related Work}
This work concerns the research topic on visual analytics of movement data and the movers. Many related works focus on the spatiotemporal analysis of movement data in the absence of thematic information. The presence of geotagged social media data facilitates the exploration of thematic information along with movement information. Therefore, the related work is discussed from two aspects: movement data analysis, and geo-tagged social media data analysis.

\subsection{Movement data analysis}
With the development of location-acquisition techniques, massive spatial trajectories are collected to keep track of the trajectories of various moving objects. Techniques have been proposed to process and mine trajectories for spatial knowledge~\cite{Zheng2015_trajectory}. In the field of visualization and visual analytics, spatial visualizations are specifically designed for time, location, spatiotemporal information and other properties in movement data~\cite{chen2015survey}. Wang et al.~\cite{wang2013visual} extract traffic jam propagation graphs to reveal underlying data patterns. Guo et al.~\cite{guo2011tripvista} and Zeng et al.~\cite{zeng2013visualizing} construct geographic regions and visually aggregate the in-between movements as flows. To discover route travel patterns, Lu et al.~\cite{lu2015trajrank} propose TrajRank to explore route travel behavior based on ranking. For multiple routes, Liu et al.~\cite{liu2011_routediversity} study the route diversity between locations and Lu et al.~\cite{Lu2017_multipleroute} explore the route choice behavior among multiple routes. These large number of visual analytics tools and applications cover situation-aware exploration, pattern discovery and traffic situation monitoring. However, they prefer to discuss spatial feature of movements, neglecting the characteristics of the movers and the relationship between movement and movers. In this work, we focus on this to explore how to design visual analytics methods to relate demographic characteristics to spatial feature of movements.

\subsection{Geo-tagged Social Media Data Analysis}
In the presence of social media services, social media data with geo-tags are collected to track people's movements in their daily lives. As an analog of remote sensing data in social science research, geospatial big data has been proposed as social sensing ~\cite{liu2015social}. Hence, analyzing movement information along with rich text has become a popular research area in recent years. Krueger et al.~\cite{krueger2014visual} uses GPS and location-based service data to support the analysis of movement behaviors. Cao et al.~\cite{cao2012whisper} proposes \textit{Whisper} for tracing the pathways of tweets along a spatial hierarchical layout to investigate how information flows among multiple places. Some other researchers tend to infer real information, such as names, gender, and race, from social media data to form the image of social media users based on the demographic characteristics~\cite{peddinti2014internet} and analysis the impact of characteristics on urban human mobility patterns~\cite{luo2016explore}. These works infer thematic information from semantic texts. By analyzing the texts, these works explain what drives movement activities or what results from these activities. This work continues thematic research on movement data but focuses more on individual demographic characteristics. Since real information is not enforced in social media, incorrect inference is inevitable. The biases inherent in social media usage need to be assessed in social research and the deployment of social media data need to be evaluated in research applications~\cite{Longley2015, Paul2016_twitter} . Therefore, based on a census experiment, this work is able to analyze profile information directly to eliminate indirect data inferred from social media data as other related works do. Then an intuitive visualization is proposed to describe these characteristics of individuals.
\section{motivation}

\label{sec:concept}
This work was inspired in a meeting with two domain experts who work on human mobility and urban informatics in the geospatial field. The experts pointed out that as big and open data has evolved, the scope of urban research has been lifted from the spatial perspective up to the social-spatial perspective. There is increasing research interest in understanding how categories of citizens with certain demographic characteristics visit places during their daily lives. Do people select places according to preferences that are intrinsically affected by their socioeconomic characteristics? Is there a limitation to or probability of interaction between different socioeconomic groups in public spaces? With the advances in data acquisition and analysis techniques, these experts demanded to go beyond the conventional static sampled questionnaires, that usually survey visiting preferences. They sought to reveal the spatial distribution in real-world visiting logs and urged for the creation of a dynamic system that supports the interactive exploration of spatial preference in different contexts of demographic characteristics.

Thereafter, we began this project with several rounds of discussions to frame the research problem with two core contents and a research procedure. The first content is \textbf{demographic characteristics}. The demographic characteristics of a person or a group of individuals are the descriptors that contribute to the specifications of populations. This work intends to cover these characteristics from multiple facets, including descriptors such as gender, income, and education. The second content is \textbf{spatial preference}. This content is reflected by the popularity of a place for visiting.

Motivated by their research interest of the experts to understand the spatial preference with individual demographic characteristics, we go through a procedure consisting of two stages, i.e., data collection and basic reviewing and visual analytics design iteration with expert feedback.

\section{Data Description}
\label{subsec:pipeline}
Considering that no existing public dataset can fit our topic well, this work is consolidated with self-maintained data sourcing. We release an online information survey to collect the demographic characteristics and movement logs of individuals over almost half a year. Then a series of statistical analyses are performed on the collected data for sampling bias checking.

\subsection{Online Survey}

The advent of mobile sensing techniques and social media applications makes it possible to collect spatial data through apps within phones. Complementary to the conventional survey, this method is convenient, does not take much manpower and provides precise spatial locations by GPS instead of semantic descriptions.

In this work, we perform a survey in Shenzhen, which is one of the most modern metropolises in China. The experiment is deployed on WeChat, the most widely used social media mobile application in China. Fig. \ref{fig:app} shows the interfaces of the survey app. For privacy issues, all the detailed personal information is desensitized to categorical levels. Considering the main aim of the relationship between spatial preference and demographic characteristics, two crucial aspects need to be collected:

\textbf{Demographic Characteristics} Fig. \ref{fig:data_over} lists the eight domains needed to give a generalized description of an individual. The profile serves as the components for the analysis of mobility patterns of diverse individuals.

\textbf{Traveling Trips} Individuals can upload dynamic traveling trips (Fig. \ref{fig:app}(b)). Each trip requires information on the start/end location, start/end time, traveling purpose, and traveling mode. Locations are recorded by GPS modules in the phones. To encourage trip uploading, a credit system retains the contribution of individuals on trips and rewards the volunteers with the top credits (Fig. \ref{fig:app}(c)).

\begin{figure}
 \centering
 \includegraphics[width=9cm]{pictures/survey_app_eng}
  \captionsetup{justification=centering}
 \caption{Census app interface: (a) personal characteristics collection page; (b) trips collecting page; and (c) credit system page. (In the real census survey, the contents are shown in Chinese.)}
 \label{fig:app}
\end{figure}

\begin{figure}
 \centering
 \includegraphics[width=9cm]{pictures/data_over}
 \captionsetup{justification=centering}
 \caption{Profile of Individual: eight individual characteristics that enrich the analysis of spatial preference.}
 \label{fig:data_over}
\end{figure}

\subsection{Statistics of Collected Data}

Over the release time period from 2015-11 to 2016-01, 21,435 individuals participated in the census, and 229,155 trips were collected.

Our case-study data are confined to a small proportion of WeChat users who opt to contribute their demographic profiles and movements. Considering the caveat that self-selecting individuals are unlikely to represent any clearly defined population~\cite{Longley2015}, we calculate a series of preliminary statistics. In Fig. \ref{fig:data_overview}, the population distribution of each characteristic is shown. The length of the block is coded for population quantity.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data_overview}
 \caption{Preliminary statistics of each characteristic in collected demographic data.}
 \label{fig:data_overview}
\end{figure}

The figure shows that, 51.2\% of the participating citizens are male and 48.8\% are female. This result is consistent with governmental statistics stating that 47\% of all citizens are female and 53\% are male\footnote{http://tjj.sz.gov.cn/zwgk/zfxxgkml/tjsj/tjgb/201804/t20180427\_11800902.htm}. The age collected covers a wide range, with ages between 18 and 45 dominating. There are also records pertaining to individuals below the age of 18 or above 70. According to the 2015 Annual Census Statistics report\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aged 15-64 comprise 83.23\%, and the median age is 31.5. The age distribution in the collected data aligns with the fact that Shenzhen is a city where the majority of the population is young. From the distribution of education levels, ranging from low to high, technical colleges and universities dominate the samples at a 61\% occupancy rate. The majority get paid less than 200,000. Citizens with higher salaries are also reached in our census. Due to the lack of governmental statistics, we cannot verify that all the characteristics collected are consistent with all the citizens in Shenzhen. From the perspective of surveys, there is always inevitable bias inherent in fully representing the ground truth of the population. However, the preliminary statistical analysis shows the rich scope of the data, which is positive evidence of a relatively even sampling of the population of the city.

\iffalse
Fig. \ref{fig:data_age_edu} gives the distribution of gender, age and education over the population. For participated citizens, 48\% of them are female and 52\% are male. It is consistent with governmental statistics that 47\% of the whole citizens are female and 53\% are male\footnote{http://tjj.sz.gov.cn/zwgk/zfxxgkml/tjsj/tjgb/201804/t20180427\_11800902.htm}. The age collected covers a wide range, dominating between 18 and 45. There are also records pertaining to individuals below the age of 18 or above 70. According to the 2015 Annual Census Statistics report\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5. The age distribution in collected data follows the fact that Shenzhen is a city where the majority is young. Fig, \ref{fig:data_age_edu}(b) gives the distribution of education levels, ranging from low to high. The technical college and university dominate the samples at the 61\% occupancy rate. Fig. \ref{fig:data_job_inc}(a) shows the job types of sampled individuals, who are servants, workers, officers, businessmen and so on. \colorbox{yellow}{Fig. \ref{fig:data_job_inc}(b) gives the radar diagram of the annual pay.} The majority get paid below 200,000. Citizens with higher salary are also reached in our census.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data1}
 \caption{Age and Education Distribution: (a) age; (b) education.}
 \label{fig:data_age_edu}
\end{figure}

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data2}
 \caption{Job and Income Distribution: (a) job; (b) income}
 \label{fig:data_job_inc}
\end{figure}
\fi

The basic statistics related to movements are shown in Fig. \ref{fig:data_geometry}. Fig. ~\ref{fig:data_geometry}(a) visualizes the distribution of the trip quantity of each citizen. The distribution has a heavy-tail, which follows the trends of most human-related statistics. In Fig. ~\ref{fig:data_geometry}(b), the active traveling time (here, we take the start time as representative of the active time) follows the common knowledge about urban life. There are obvious morning and evening rush hours. Fig. ~\ref{fig:data_geometry}(c) shows the counts for different traveling purposes. Ninety-five percent of trips are tagged with a clear traveling purpose in the data. Thirty-three percent of trips are going home, and 37\% are going to work. In addition to this kind of routine travel, there are also substantial numbers of trips for other purposes such as going shopping and going the hospital. Fig. ~\ref{fig:data_geometry}(d) shows the spatial distribution of the origins and destinations. It is found that more dots are located in Futian and Nanshan Districts, the city's heart, than in the surrounding areas. This result is consistent with Batty's exposition of the focus of city networks and interaction patterns~\cite{batty2013new}.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data3_2}
 \caption{Statistics of trips: (a) distribution of trip quantities for each citizen; (b) start time of trips; (c) purpose of trips; and (d) distribution of origins/destinations. }
 \label{fig:data_geometry}
\end{figure}

\section{Visual Design}

The design of the visual analytics system is iterated via multipass discussions with the two domain experts. In this section, we first introduce specific tasks that the system is intended for and the design rationales aligned to provide a user-friendly interface for domain experts. Then, we introduce the visual design.

\subsection{Tasks}

The exploration of core contents (introduced in Section~\ref{sec:concept}) is resolved further with the following tasks.

\begin{itemize}
\item \textbf{Task 1: Identify groups with specific individual demographic characteristics}: to obtain groups of people with common or similar attributes and to explore the correlation among individual characteristics.
\item \textbf{Task 2: Explore the spatial preference of a group}: to explore where, how and why the group of interest moves in the city.
\item \textbf{Task 3: Compare spatial preference among multiple groups}: to express the similarities and differences between different groups in their spatial preferences and to investigate the relationship between movement and individual demographic characteristics.
\end{itemize}

\begin{figure*}[htb!]
 \centering
 \includegraphics[width=18.1cm]{pictures/teaser.eps}
 \caption{System Interface: (a) an interactive infographics provides the basic statistical facets of individuals; (b) a t-SNE visualization gives an overview of individuals, where the similarity in high-dimensional space is preserved in 2D space; (c) data-driven profiles support users with organic individual perception; (d) a group of individuals of interest can be saved; (e) the movement of the chosen group is visualized and explored in the 2.5D main view; (f) a dock is provided to restore and compare findings; and (g) different choices of 2.5D encoding can be selected.}
 \label{fig:teaser}
\end{figure*}

\subsection{Design Considerations}

With the three tasks above, we derive the following design considerations:

\begin{itemize}
\item \textbf{Intuitive perception of an individual as an organic complex (C1)}: the system should make use of end-user daily experience in sensing individual demographic characteristics to provide intuitive visualization instead of lifeless representation by numbers. The visual design needs to help end-users to pick desirable information from the whole.
\item \textbf{Good overview of multivariate individuals (C2)}: following the visual analytics mantra of Shneiderman~\cite{RN459}, it is very important to provide a good overview of all the individuals so the users know where to explore.
\item \textbf{Effective multivariable cross-filter for individual characteristics (C3)}: there are eight domains for describing an individual. The system is supposed to provide a straightforward method for easy filtering by the eight criteria.
\item \textbf{Compact visualization of spatial preference in the constraint of spatial space (C4)}: the analysis of spatial preference not only includes the conventional spatial and temporal dimensions but also other abstract dimensions, e.g., travel purpose and visiting frequency. The system should have a compact layout to support simple correlation between spatial and abstract information.
\item \textbf{Flexible interactions for exploring spatial preference either within one group or between groups (C5)}: to support comparisons among groups, \textbf{Task 3}, the system should maintain flexible interactions that allow the end-users to explore freely.
\end{itemize}

\subsection{Visualizations}
\label{subsec:vis}

With all the design considerations, we develop a visual analytics system, as shown in Fig. \ref{fig:teaser}. The system is composed of an individual panel (the left part) for individuals (\textit{Task 1}) and a spatial panel (the right part) for the mobility pattern (\textit{Tasks 2 and 3}). In the individual panel, interactive infographics, t-SNE visualization, and data-driven profiles allow users to narrow the scope down to groups of individuals with interesting characteristics. For a specified group of individuals, the moving-related information is visualized and explored in a 2.5D spatiotemporal view.

\subsubsection{Data-driven Profile Visualization}

Glyph-based visualization~\cite{borgo2013glyph} is a form of visual design for converting multiple variables into a collection of unified visual symbols, known as a glyph. A glyph is intended for quick understanding and aligned comparison. Among glyph designs, Chernoff Face~\cite{chernoff1973use} represents data variables by the different features of a cartoon face. Following the idea of Chernoff Face, we design a type of glyph that is a graphical representation of people with specific individual characteristics. The idea behind using faces is that humans easily recognize faces and notice small changes without difficulty (\textit{C1}). These visual profiles are intended for intuitive visual understanding, from abstract to concrete and semantic understanding, allowing users to effectively target the individual groups of interest.

Fig. ~\ref{fig:design_profile} shows the legend for the user profile. The eight domains are encoded by visual symbols and organically organized in a human figure. There are basically three types of variables to drive the figure, i.e., numeric, categorical and Boolean variables. For numeric attributes such as income and education levels, the visual symbols maintain a consistent design but with visual variations, such as size and thickness variations. For categorical attributes such as job, the visual symbols are designed separately for better semantic meaning. For  Boolean attributes like car and house ownership, symbols are designed to indicate positive values. With this consideration, the domains are designed as follows:

\begin{itemize}
\item \textbf{Gender} Gender is visually mapped by the hairstyle of the avatar.
\item \textbf{Age} Age is implied by the decoration on the hair. For people older than 70, the hair is dyed gray. For youth younger than 18, a hair decoration is added corresponding to the different hairstyles for girls and boys.
\item \textbf{Education} The thickness of the eyeglasses is used to indicate different levels of education.
\item \textbf{Job} The clothes are designed to imply the job of the individual. There are 9 types of clothes.
\item \textbf{Belongings} Real estate, cars and residential licenses are considered as possible belongings of an individual, so we design each of them as an add-on decoration to indicate whether the individual possesses each item or not.
\item \textbf{Income} A money symbol is used to represent income, and the size of the symbol encodes the income level. The more money an individual earns, the larger the symbol is.
\end{itemize}

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/design_profile}
 \caption{Design profile: the eight characteristic domains are encoded and organized in an organic human figure.}
 \label{fig:design_profile}
\end{figure}

With visual mapping, the profile varies from individual to individual. Because the attributes that are otherwise too abstract to perceive are concretized, users can scan and search for interesting targets effectively. Fig. \ref{fig:div_example} lists the figures with the top 10 largest population in some jobs. The textual number beneath indicates the population. The majority of workmen earn a low salary, and most of them have no residential license. In contrast, all of the officers have a residential license, and most of them have a house. Some of the retired people are old-aged. Most of the managers are undergraduates or even graduates.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/design_example}
 \caption{Representative figures of the top 10 largest populations for four jobs}
 \label{fig:div_example}
\end{figure}

\subsubsection{t-SNE Projection of Individuals}

In our case, each individual can be denoted as a vector $x_i$ with eight factors, and we obtain a high-dimensional data set $X={x_1, x_2, ..., x_n}$. Dimensionality reduction techniques preserve the local structure of high-dimensional data in low-dimensional space, and are efficient approaches for providing a good overview of multivariable individuals (\textit{C2}). We adapt t-SNE~\cite{maaten2008visualizing} to project $X$ as two-dimensional dots $Y={y_1, y_2, ..., y_n}$. One of the steps in t-SNE is to compute conditional probabilities to represent the similarity based on the distance between high-dimensional datapoints. The conditional probability $p_{j\mid i}$ between $x_j$ and $x_i$ is given by:

\begin{equation}
p_{j\mid i} = \frac{exp({\left \| x_i - x_j \right \|}^2/2\alpha_i ^{2})}{\sum _{k\neq i}exp({\left \| x_i - x_k \right \|}^2/2\alpha_i ^{2})}
\end{equation}

where $\alpha_i$ is the variance of the Gaussian that is centered on $x_i$. Specifically in our context, the high-dimensional Euclidean distances $\left \| x_i - x_j \right \|$ between $x_i$ and $x_j$ need to be adapted to the numerical and categorical characteristics. Characteristics such as age and income are numerical and comparable, so the difference precisely explains when these parameters are different. However, the other characteristics, i.e., job, real estate and car ownership, and residential status, are ordinal. There is no numeric order. For example, the job distances from a manager to a businessman and to a workman are not comparable and thus are considered to be the same distance, i.e., set to 1.

As Fig. ~\ref{fig:tsne} shows, all 21435 volunteers are embedded in the 2D view, where the closer two dots are, the more similar the groups are in the eight characteristics. Fig. ~\ref{fig:tsne} exemplifies four feature groups of dots in a neighborhood.

Multiple views including the abstract view, t-SNE projection, and semantic data-driven profile visualization are coordinated in a cross-filter mechanism~\cite{Weaver2010}. This allows end-users to interactively drill down to individuals with characteristics of interest from multiple perspectives(\textit{C3}). Starting from the abstract criterion constraints, the scope of interest is narrowed to individuals with(out) certain characteristics. Then, further cross-filtering with semantically visual profiles can be performed to check the combination of the 8 characteristic variables.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/tsne}
 \caption{t-SNE project with four groups of interest.}
 \label{fig:tsne}
\end{figure}

\subsubsection{2.5D Spatial Visualization}
\label{subsec:25D}

Embedding multiple variables in a spatial map is a challenging problem. Distorting 2D spatial features for better space usage, such as partial route embedding~\cite{sun2016embedding}, is an effective method when there are a few local foci. In regard to global visualization, there is always a trade-off between occlusion-free and the compact spatial perception. Following the idea of stacking 2.5D space design~\cite{Tominski2012_stacking}, the space in this work is embedded in 2.5D space, to relax the z-axis for additional abstract information encoding.

Fig. ~\ref{fig:2.5D}(a) shows the 2.5D visualization. The spatial map consists of the traffic analysis zone (TAZ), which is a unit of geography holding a certain number of people. For 2.5D, each TAZ is grown as a prism whose height and color are developed to encode abstract information, e.g., the occurrence of visits. With different encoding choices, the map is capable of visualizing the correlation between spatial and different attributes (\textit{C4}). For example, in Fig. \ref{fig:2.5D}(a), prism height and color both encode the ratio of nonroutine trips (such as going out for entertainment and going to hospital) in the whole. For better 3D visual perception, lighting is turned on. Additional, a lid is laid on the top of each prism to clearly bound its extent on the z-axis.

\begin{figure}
    \centering
	  \subfloat[]{
       \includegraphics[width=86mm]{pictures/space1.eps}}
    \label{1a}\hfill
	  \subfloat[]{
        \includegraphics[width=86mm]{pictures/space2.eps}}
    \label{1b}\hfill
      \subfloat[]{
        \includegraphics[width=86mm]{pictures/space3.eps}}
    \label{1c}\\
\caption{Spatial visualization in 2.5D: (a) 2.5D spatial visualization with additional information encoded in z-axis; (b) detail slicing in 2.5D space; and (c) overview view.}
\label{fig:2.5D}
\end{figure}

Several interactions are integrated into the spatial view to alleviate the occlusion problem (\textit{C5}). The manipulation of the 2.5D view supports users with rotate, zoom, and pan operations, which is continuously flexible so that users can find a suitable observation point. In the cases where occlusion is inevitable, an interaction, namely, detail slicing (Fig. ~\ref{fig:2.5D}(b)), and an overview view (Fig. ~\ref{fig:2.5D}(c)) are developed. Detail slicing is an operation that places a cross-section in the 2.5D space to expose the TAZ inside. To contextualize the cross-section, the TAZs are visually adapted according to the intersection by ray casting. The TAZs in the foreground are hidden, the intersected TAZs are fully visualized, and those in the background are semi-transparent. The overview view shows all the TAZs in the form of a 2D plane. All the TAZs are tiled horizontally. The vertical axis indicates the height of each prism in each TAZ. It is for quickly sensing the distribution of encoded content with prism within the whole city.

To compare the mobility patterns across different groups of people, a small multiple dock is used to reserve interesting results (Fig. ~\ref{fig:teaser}(f)). To simplify the comparison over the spatial distribution, a snapshot is also rendered in 2.5D space that maintains the same interactions as the main 2.5D space does.

\section{Case studies}

In this section, we apply the method described above to study the case of Shenzhen. We introduce several cases to demonstrate the usage and effectiveness of the visual analytics system.

\subsection{Case 1: Home-life distribution VS. Income/education}

Inspired by the implication in the science fiction novella ~\textit{Folding Beijing}, in which people are categorized into three classes and behave in parallel spatiotemporal patterns, we define our first case to explore whether the folding city exists in reality.

\begin{figure}[htb!]
 \centering
 \includegraphics[width=\columnwidth]{pictures/case1_1}
 \caption{Four groups divided by income and education.}
 \label{case11}
\end{figure}

Although not exhaustive, income and education are two of the most essential characteristics for identifying an individual who has good resources versus one who does not. As Fig. ~\ref{case11} shows, taking income and education as the two dimensions, with 300,000 yuan as the border between high and low income and an undergraduate bachelor's degree as the border between high and low education level, we generate four different groups in the four quadrants. In the first quadrant, individuals are rich and well-educated and are in the group of the so-called \textbf{top aristocracy}. The second quadrant holds the group of the \textbf{new rich}, i.e., individuals with high income but low education. In the third quadrant is the group of the \textbf{underclass}, who has both low income and education level. The fourth quadrant is group of the \textbf{antizens}, which is a new word to describe people who have a good education but earn little.

Fig. ~\ref{case11} shows the top 12 profiles with the maximum population in each group. In each group, other characteristics surprisingly demonstrate high correlations to income and education. For example, almost all of the members of the \textbf{top aristocracy} have the residential licenses,  houses, and cars. In contrast, members of the \textbf{underclass} do not have residential licenses, houses or cars. Most of the \textbf{new rich} have a house and work in the service industry.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case1_2}
 \caption{Home distributions of the four groups.}
 \label{case12}
\end{figure}

Before diving into the complex trip spatial preference analysis, we explore the home preferences of the four groups. As Fig. ~\ref{case12} shows, where the \textbf{top aristocracy} and most of the \textbf{new rich} live concentrated is in the downtown area of Shenzhen, where the cost of living is higher, especially housing costs. A small number of the \textbf{new rich} live far from downtown, perhaps because they do not have to work downtown. The \textbf{underclass} is distributed more dispersedly throughout the whole city. Compared to the rich, members of the \textbf{underclass} prefer the outer reaches of the city due to lower living costs. Many \textbf{antizens} live in Nanshan District, where there are many universities and high-tech industrial parks full of well-educated people.

\begin{figure}[htb!]
 \centering
 \includegraphics[width=\columnwidth]{pictures/case1_3_new-eps-converted-to.pdf}
 \caption{Spatial distributions of "work", "home" and "other" for the four groups: (a) the 2.5D view; (b) three slices for detailed comparison; (c) the overview view of all the TAZs in the city.}
 \label{case13}
\end{figure}

To gain better knowledge regarding the trip spatial preferences of the four groups, we categorized trips into three types based on "purpose". We defined "home" for going home and "work'' for going to work or going to school for students. These two types of trips are defined as "regular trips", implying daily necessary trips. The type "other'' is for irregular trips with the purpose of shopping, visiting friends, etc., that are not necessary every day. Fig. \ref{case13} shows the 2.5D visualization of the three types of trips for the four groups. For each TAZ, the prism is normalized to the same height, i.e., unit one, and the height proportion of each type is encoded by the percentage of all the trip quantities. The colors indicate types, pink for "other'', blue for "work'' and green for "home''. Fig. ~\ref{case13}(b) shows examples of the detail slicing, which supports interactions to let users find better perspectives in the inner city. Fig. ~\ref{case13}(c) offers an overview of the distributions of three types of trips in all the TAZs. In the figure, our attention is drawn to the lifestyle of the \textbf{New Rich}. The spatial preferences of the \textbf{New Rich} are distributed intensively in some TAZs. Compared to other groups, this group travels with the purpose of "other'' often. Individuals with low income (the \textbf{underclass} and \textbf{antizens}) spend relatively more time on work, especially the \textbf{underclass}. The working percentage is very small in the group \textbf{new rich}. The members of this group live a more diverse lifestyle because they do many things (pink "other") other than working.

\subsection{Case 2: Spatial preference for work-home VS Income/House}

\begin{figure}[htb!]
 \centering
 \includegraphics[width=\columnwidth]{pictures/case2}
 \caption{Home-work distances of different groups: (a) with different salary levels; (b) with or without a house.}
 \label{case2}
\end{figure}

Homes and work-places are two crucial types of places where people stay for long periods during their daily lives. The home-work distance is an essential metric in home/work place selection. This distance is influenced by many factors, such as transportation, housing, and land use. The home-work distribution and home-work distances of a region indicate the relationships between regions based on individuals' spatial preferences. In this case, we demonstrate our system's help in analyzing home-work spatial preferences.

Considering that income potentially determines where people live, we use income as the characteristic to form three groups: the group with income over 500K, the group with income between 200-300K and the group with income lower than 100K. In Fig. ~\ref{case2}, the height of the prism represents the visiting frequency of the TAZ, and its color encodes the average home-work distance, red for close and yellow for far. As Fig. ~\ref{case2}(a) shows, for all three groups at different income levels, most of the TAZs are dark red or red colored, which indicates that the home-work distance is generally short, especially in downtown areas. Only those with income lower than 100K work outside the center, such as the space in the green circle. When comparing the three groups in the downtown area, we see that it takes more time to go to work in Futian District as income decreases.

We explore the home-work distance of groups with and without a house. Fig. ~\ref{case2}(b) shows close-up views. It is found that Nanshan District has a shorter home-work distance for individuals without a house, while Futian District has a shorter home-work distance for those with a house. Nanshan is newer than Futian, so there might be more easily accessible houses for rent.

\subsection{Case 3: spatial preference of lifestyles VS Jobs}
In this case, we explore the association between spatial preference and the job to see whether job has an impact on spatial selection. Officers, workmen, students, and businessmen are selected as examples, and the population of trips for the specified purposes is shown in Fig. ~\ref{case3}. The height of the prisms encodes the number of visits to each TAZ, and the color encodes the traveling purpose. There are 10 different kinds of traveling purposes. For quick linking between color and purposes, regular trips such as going to work, school and home are shown in cold colors, and irregular trips such as going shopping and to the hospital are shown in warm colors. As Fig. ~\ref{case3} shows, for officers, the heights of the prisms change dramatically. Some TAZs have much more visits than others because officers are more constrained to work in some buildings than individuals with other jobs. The relative percentage of trips with irregular purposes(not "work", "school", or "home") differs for the four groups. For workmen, approximately 80\% of trips are for regular purposes ("work", "school" and "home"). For students, the percentage is approximately 50\%. Compared to these groups, officers and businessmen have more flexible and diverse lifestyles.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case3}
 \caption{Trip purpose distribution of four groups with different jobs}
 \label{case3}
\end{figure}

Next, we concentrated on one purpose to see whether the purpose is related to the "job". Here, we use "dinner or entertainment" as the example. As Fig. \ref{case32} shows, the height of prisms represents the number of visiting trips for dinner or entertainment. The color stands for the movement distance to reach this TAZ. As we can see, officers prefer to entertain in the downtown area, while workmen cover a larger area. Students tend to concentrate in Nanshan District, probably near schools. Businessmen go many places for dinner or entertainment. The largest difference from other groups is that businessmen tend to travel a long distance to go somewhere far from downtown areas.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case3_2}
 \caption{The ``dinner or entertain" purpose of four groups with different jobs}
 \label{case32}
\end{figure}

\section{Expert Feedback}

We ran an interview with the two domain experts, to ask for their feedback on the designed system. Overall, the two domain experts had high praise for the full walk-through from data collection to analysis towards the research problem of spatial preference with demographic characteristics. They also appreciated the overall design of the visual analytic system and the finding cases. Specifically, they pointed out what they liked and what could be improved.

Expert A expressed her appreciation of the data-driven profile visualization. She commented that "it takes little effort to learn how to read it, which really taps into my daily experience". Expert B commented that the data-driven profile visualization provides an intuitive representation of individuals, although sometimes it is cumbersome to recognize each of the group when there are too many. However, he said the combination of profile and t-SNE is very efficient and enables him to quickly identify individuals from the whole. Both experts spoke highly about the dynamic identification of groups of interest and the on-the-fly analysis of the spatial preferences. Expert A commented that "the visual analytic system allows me to try any group of interest''. Expert B liked the cross-filtering interactions across multiple views. For spatial visualization, both experts thought that our solution, 2.5D visualization in a grid-based spatial visualization, is a sophisticated design choice. With the detail slicing function and overview view, not only the overview of the spatial preference but also the inner details of each TAZ can be filtered out and checked directly.

\section{Conclusion}
\label{sec:conclusion}
This work demonstrates a thorough research flow from data collection and basic analysis to deep visual analysis of spatial preference with individual demographic characteristics. Considering the irresistible trend of mixing demographic data and spatial data to solve urban problems, this work takes one step forward in exploring the relationship between movement and individuals’ characteristics, which has rarely been addressed in previous geo-tagged social media visual analytics. The design of the visual analytic system is driven by three tasks regarding individuals and mobility patterns. Tapping into our daily experiences, the data-driven profile visualization provides an organic and intuitive representation of individuals. The effectiveness of the visualization in identifying similar or abnormal individuals from the whole is demonstrated. The design of 2.5D spatial visualization continues the exploration of the typical research problem of how to visualize spatial information and abstract information together. Although it is not a one-step solution, 2.5D visualization with detail slicing and overview view is able to provide occlusion-free analysis with the spatial context preserved.

Our current research focuses on fundamental facets of spatial preference and does not draw a strong conclusion on the correlation between movements and individual characteristics. In the next step, more delicate algorithms will be involved to extract high-level spatial preferences, such as the frequent visiting sequence of an individual group.

\bibliographystyle{ieeetran}
\bibliography{main}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bio/wq}}]{QI WANG} received the B.Eng. degree in information security from Wuhan University, China. She is currently working toward the Ph.D. degree in the State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University. Her research interests include transport geographic information system, spatiotemporal data analysis, mining and visualization.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bio/minlu}}]{Min lu} is an associate researcher at ShenZhen University. Her major research interest is data visualization and visual analytics, especially focusing on the urban data. She received Ph.D degree in Computer Science from Peking University in 2017 and BS degree in Computer Science from Beijing Normal University in 2011.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bio/lqq}}]{Qingquan Li} received the Ph.D. degree in geographic information system (GIS) and photogrammetry from Wuhan Technical University of Surveying and Mapping, Wuhan, China, in 1998. He is currently a Professor with Shenzhen University, Guangdong, China, and Wuhan University, Wuhan, China. His research areas include 3-D and dynamic data modeling in GIS, location-based service, surveying engineering, integration of GIS, Global Positioning System and remote sensing, intelligent transportation system, and urban informatics.
\end{IEEEbiography}

\EOD

\end{document}

### 2020-01-18 ia/ia_vis_3d_final-yellow.tex
with yellow

--- 2020-01-18 ia/ia_vis_3d_final.tex
@@
 \usepackage{textcomp}
+\usepackage{soul}
 
@@
 The presence of social media applications fuels spatial analysis with rich semantic texts, so researchers can explore the thematic meaning of the movement behaviors, such as events~\cite{chen2017map} and topics~\cite{bosch2013scatterblogs2}.
-These works essentially contribute to deepening the contextual understanding of movement activities.
-Some works dive deep and infer individual characteristics from social media profiles~\cite{peddinti2014internet} to better describe the semantics of movement behavior.
-However, due to the limited exposure of personal information, there is still a research gap between understanding the movement behavior and underlying characteristics of movers.
-%The question of how to intuitively discover the relationship between spatial preference and multidimensional characteristics is worthy of further investigation.
+\hl{These works essentially contribute to deepening the contextual understanding of movement activities.
+Some works dive deep and infer individual characteristics from social media profiles}~\cite{peddinti2014internet} \hl{to better describe the semantics of movement behavior.
+However, due to the limited exposure of personal information, there is still a research gap between understanding the movement behavior and underlying characteristics of movers.}
 
@@
 These large number of visual analytics tools and applications cover situation-aware exploration, pattern discovery and traffic situation monitoring.
-However, they prefer to discuss spatial feature of movements, neglecting the characteristics of the movers and the relationship between movement and movers.
-In this work, we focus on this to explore how to design visual analytics methods to relate demographic characteristics to spatial feature of movements.
+\hl{However, they prefer to discuss spatial feature of movements, neglecting the characteristics of the movers and the relationship between movement and movers.
+In this work, we focus on this to explore how to design visual analytics methods to relate demographic characteristics to spatial feature of movements.}
 
@@
 These works infer thematic information from semantic texts.
-By analyzing the texts, these works explain what drives movement activities or what results from these activities.
-This work continues thematic research on movement data but focuses more on individual demographic characteristics.
-Since real information is not enforced in social media, incorrect inference is inevitable.
-The biases inherent in social media usage need to be assessed in social research and the deployment of social media data need to be evaluated in research applications~\cite{Longley2015, Paul2016_twitter} .
-Therefore, based on a census experiment, this work is able to analyze profile information directly to eliminate indirect data inferred from social media data as other related works do.
-Then an intuitive visualization is proposed to describe these characteristics of individuals.
+\hl{By analyzing the texts, these works explain what drives movement activities or what results from these activities.
+This work continues thematic research on movement data but focuses more on individual demographic characteristics.} Since real information is not enforced in social media, incorrect inference is inevitable.
+The biases inherent in social media usage need to be assessed in social research and the deployment of social media data need to be evaluated in research applications~\cite{Longley2015, Paul2016_twitter}.
+\hl{Therefore, based on a census experiment, this work is able to analyze profile information directly to eliminate indirect data inferred from social media data as other related works do.
+Then an intuitive visualization is proposed to describe these characteristics of individuals.}
 \section{motivation}
@@
 Locations are recorded by GPS modules in the phones.
-To encourage trip uploading, a credit system retains the contribution of individuals on trips and rewards the volunteers with the top credits (Fig.
-\ref{fig:app}(c)).
+\hl{A credit system} (Fig.
+\ref{fig:app}(c)) \hl{is utilized to encourage participation.
+Individuals who have enough credits will obtain raffle tickets.
+There are three ways for credits: recommending friends to participate in the survey, filling personal information, and filling daily trips.}
 
@@
 Citizens with higher salaries are also reached in our census.
-Due to the lack of governmental statistics, we cannot verify that all the characteristics collected are consistent with all the citizens in Shenzhen.
+\hl{Due to the lack of governmental statistics, we cannot verify that all the characteristics collected are consistent with all the citizens in Shenzhen.
 From the perspective of surveys, there is always inevitable bias inherent in fully representing the ground truth of the population.
-However, the preliminary statistical analysis shows the rich scope of the data, which is positive evidence of a relatively even sampling of the population of the city.
+However, the preliminary statistical analysis shows the rich scope of the data, which is positive evidence of a relatively even sampling of the population of the city.}
 
@@
 The distribution has a heavy-tail, which follows the trends of most human-related statistics.
-In Fig.
+All trips are reported by the participants.
+\hl{To make sure the trips are available, we checked trips from temporal and spatial perspectives.} In Fig.
 ~\ref{fig:data_geometry}(b), the active traveling time (here, we take the start time as representative of the active time) follows the common knowledge about urban life.
@@
     \label{1c}\\
-\caption{Spatial visualization in 2.5D: (a) 2.5D spatial visualization with additional information encoded in z-axis; (b) detail slicing in 2.5D space; and (c) overview view.}
+\caption{Spatial visualization in 2.5D: (a) 2.5D spatial visualization with additional information encoded in z-axis; (b) detail slicing in 2.5D space; and \hl{(c) overview view.}}
 \label{fig:2.5D}
@@
 The TAZs in the foreground are hidden, the intersected TAZs are fully visualized, and those in the background are semi-transparent.
-The overview view shows all the TAZs in the form of a 2D plane.
+\hl{The overview view shows all the TAZs in the form of a 2D plane.
 All the TAZs are tiled horizontally.
 The vertical axis indicates the height of each prism in each TAZ.
-It is for quickly sensing the distribution of encoded content with prism within the whole city.
+It is for quickly sensing the distribution of encoded content with prism within the whole city.}
 
@@
  \includegraphics[width=\columnwidth]{pictures/case1_3_new-eps-converted-to.pdf}
- \caption{Spatial distributions of "work", "home" and "other" for the four groups: (a) the 2.5D view; (b) three slices for detailed comparison; (c) the overview view of all the TAZs in the city.}
+ \caption{Spatial distributions of "work", "home" and "other" for the four groups: (a) the 2.5D view; (b) three slices for detailed comparison; \hl{(c) the overview view of all the TAZs in the city.}}
  \label{case13}

### 2020-01-18 ia/ia_vis_3d_final.tex
with yellow

@@
 Locations are recorded by GPS modules in the phones.
-To encourage trip uploading, a credit system retains the contribution of individuals on trips and rewards the volunteers with the top credits (Fig.
-\ref{fig:app}(c)).
+A credit system (Fig.
+\ref{fig:app}(c)) is utilized to encourage participation.
+Individuals who have enough credits will obtain raffle tickets.
+There are three ways for credits: recommending friends to participate in the survey, filling personal information, and filling daily trips.
 
@@
 The distribution has a heavy-tail, which follows the trends of most human-related statistics.
+All trips are reported by the participants.
+To make sure the trips are available, we checked trips from temporal and spatial perspectives.
 In Fig.
